---
title: "Switchers-India"
output: 
  html_document: 
    keep_md: true
date: "2026-03-24"
---
This is the replication code for "Switchers." In this paper, we test hypotheses regarding the rise of far-right parties that were developed from the case of the West in India. We are particularly interested in how the combination of economic insecurity and demographic change affects moderates' voting behavior, and we test this using data on globalization (Foreign Direct Investment) and (internal) migration. The first X chunks in this code go step-by-step through the process of loading and cleaning the data that we use in our regressions, including creating relevant variables.

I kept your substantive choices intact: same FDI periods, same migration measures, same ideology thresholds, same model families. The main edits are structural: repeated state recodes become one lookup, repeated SC/ST cleaners become one function, file-binding loops become `map_dfr()`, diagnostics are split from data construction, and the model/table helpers are shortened. Source code reviewed from your uploaded Rmd text. 


```{r 1. Load libraries, message = FALSE}
# Load packages for data import, geospatial joins, modeling, and tables.
# Keep this list tight so missing dependencies are easy to diagnose.

library(tidyverse)
library(sf)
library(readxl)
library(haven)
library(janitor)
library(lubridate)
library(broom)
library(marginaleffects)
library(modelsummary)
library(fixest)
```


```{r 2. Shared helpers}
# Define reusable import, cleaning, recoding, and grouping helpers.
# These replace repeated state-code maps, file-binding loops, and ideology logic.

read_many <- function(path, pattern, reader = readr::read_csv, ..., ignore.case = TRUE) {
  list.files(path, pattern, recursive = TRUE, full.names = TRUE, ignore.case = ignore.case) %>%
    map_dfr(\(f) reader(f, ...))
}

read_many_sf <- function(path, pattern, ..., ignore.case = TRUE) {
  list.files(path, pattern, recursive = TRUE, full.names = TRUE, ignore.case = ignore.case) %>%
    map(read_sf, ...) %>%
    bind_rows()
}

clean_num <- function(x) {
  x %>%
    as.character() %>%
    str_squish() %>%
    na_if("") %>%
    na_if("-") %>%
    parse_number()
}

first_nonmissing <- function(x) {
  dplyr::first(x[!is.na(x)], default = NA)
}

safe_mean <- function(x) {
  out <- mean(x, na.rm = TRUE)
  if_else(is.nan(out), NA_real_, out)
}

safe_z <- function(x) {
  x <- as.numeric(x)
  s <- sd(x, na.rm = TRUE)
  if (is.na(s) || s == 0) rep(NA_real_, length(x)) else (x - mean(x, na.rm = TRUE)) / s
}

norm_name <- function(x) {
  x %>%
    as.character() %>%
    str_remove_all("\\*") %>%
    str_to_upper() %>%
    str_replace_all("&", "AND") %>%
    str_replace_all("[^A-Z0-9]+", " ") %>%
    str_squish()
}

norm_delhi_dist <- function(x) {
  norm_name(x) %>%
    str_remove("\\s+DISTRICT$") %>%
    str_remove("\\s+DELHI$") %>%
    str_remove("^DELHI\\s+")
}

state_codes <- c(
  "Andaman & Nicobar Islands" = 35,
  "Andhra Pradesh" = 28,
  "Arunachal Pradesh" = 12,
  "Assam" = 18,
  "Bihar" = 10,
  "Chandigarh" = 4,
  "Chhattisgarh" = 22,
  "Dadra & Nagar Haveli" = 26,
  "Daman & Diu" = 25,
  "Delhi" = 7,
  "Goa" = 30,
  "Gujarat" = 24,
  "Haryana" = 6,
  "Himachal Pradesh" = 2,
  "Jammu & Kashmir" = 1,
  "Jharkhand" = 20,
  "Karnataka" = 29,
  "Kerala" = 32,
  "Lakshadweep" = 31,
  "Madhya Pradesh" = 23,
  "Maharashtra" = 27,
  "Manipur" = 14,
  "Meghalaya" = 17,
  "Mizoram" = 15,
  "Nagaland" = 13,
  "Odisha" = 21,
  "Orissa" = 21,
  "Puducherry" = 34,
  "Punjab" = 3,
  "Rajasthan" = 8,
  "Sikkim" = 11,
  "Tamil Nadu" = 33,
  "Telangana" = 28,
  "Tripura" = 16,
  "Uttar Pradesh" = 9,
  "Uttarakhand" = 5,
  "West Bengal" = 19
)

state_name_to_no <- function(x) {
  x <- str_replace_all(as.character(x), "_", " ")
  as.numeric(unname(state_codes[x]))
}

ideology_group <- function(recognition, statism, cut = 0.25) {
  has_score <- !is.na(recognition) | !is.na(statism)
  inside <- function(x) is.na(x) | (x > -cut & x < cut)
  above  <- function(x) is.na(x) | x > cut
  below  <- function(x) is.na(x) | x < -cut
  
  case_when(
    has_score & inside(recognition) & inside(statism) ~ "C",
    has_score & above(recognition)  & above(statism)  ~ "R",
    has_score & below(recognition)  & below(statism)  ~ "L",
    TRUE ~ NA_character_
  )
}

make_code_key <- function(x) {
  if_else(is.na(x), NA_character_, paste0("CODE_", as.integer(x)))
}

district_name_key <- function(x) {
  paste0("NAME_", norm_name(x))
}
```


```{r 3. Load assembly constituency-level data, message = FALSE}
# Load AC election, map, crosswalk, FDI, and population inputs.
# Use vectorized file import instead of hand-written rbind loops.

pc_elections <- read_csv("data/election/lok_dhaba_ge.csv", show_col_types = FALSE)

ac_map <- read_many_sf(
  "data/election/2014_shp",
  pattern = "\\.assembly\\.shp$"
)

ac_name_key <- read_csv("data/shrug/ac08_name_key.csv", show_col_types = FALSE)

ac_xwalk <- read_sf("data/assembly-constituencies/India_AC.shp")
fdi <- read_csv("data/IN_FDI_2004_2014.csv", show_col_types = FALSE)
ac_pop <- read_csv("data/shrug/con08_pop_area_key.csv", show_col_types = FALSE)
```


```{r 4a. Load district demographic inputs, message = FALSE}
# Load district-level census, employment, population, and migration files.
# Cleaning functions below standardize messy Census tables before joining.

districts <- read_xlsx("data/dist_codes.xlsx")
econ_census <- read_csv("data/shrug/ec13_pc11dist.csv", show_col_types = FALSE)
pop <- read_csv("data/pop/pop.csv", show_col_types = FALSE)
```

```{r 4b. Clean district SC/ST files, message = FALSE}
# Clean census appendix files for district SC/ST population.
# One cleaner handles both tables because their layouts are identical.

clean_group_file <- function(path, code_col, keep_code, out_col) {
  read_excel(path, col_names = FALSE, col_types = "text") %>%
    select(2:10) %>%
    set_names(c(
      "state_code", "district_code", "area_name", code_col, "group_name",
      "area_type", "persons", "males", "females"
    )) %>%
    mutate(across(everything(), ~ str_squish(as.character(.x)))) %>%
    filter(area_type == "Total", district_code != "00", .data[[code_col]] == keep_code) %>%
    transmute(
  state_code,
  district_code,
  district_no_local = as.double(str_remove(district_code, "^0+")),
  district_name = area_name %>%
    str_remove("^District\\s*-\\s*") %>%
    str_remove("\\s+\\d{3}$") %>%
    str_squish(),
  dist_code_2011 = str_extract(area_name, "\\d{3}$"),
  "{out_col}" := clean_num(persons)
)
}

sc_pop <- read_many(
  "data/pop/sc_pop",
  "-PCA-A10-APPENDIX\\.xlsx$",
  \(f) clean_group_file(f, "sc_code", "000", "sc_persons")
)

st_pop <- read_many(
  "data/pop/st_pop",
  "-PCA-A11-APPENDIX\\.xlsx$",
  \(f) clean_group_file(f, "st_code", "500", "st_persons")
)
```


```{r 4c. Clean district population change, message = FALSE}
# Clean district population change tables and keep 2011 rows.
# The output gives district population and decadal population growth.

clean_pop_change_file <- function(path) {
  read_excel(path, col_names = FALSE, col_types = "text") %>%
    select(1:9) %>%
    set_names(c(
      "state_code", "district_code", "district_name", "census_year",
      "persons", "abs_change_from_last_census", "pct_change_from_last_census",
      "males", "females"
    )) %>%
    mutate(across(everything(), ~ str_squish(as.character(.x)))) %>%
    filter(str_detect(census_year, "^\\d{4}\\*?$")) %>%
    fill(state_code, district_code, district_name, .direction = "down") %>%
    filter(district_code != "000") %>%
    mutate(
      census_year = as.integer(str_remove(census_year, "\\*")),
      across(c(persons, abs_change_from_last_census, pct_change_from_last_census, males, females), clean_num)
    )
}

pop_change <- read_many("data/pop/pop_change", "\\.xlsx?$", clean_pop_change_file) %>%
  filter(census_year == 2011) %>%
  select(
    state_code,
    district_code,
    district_name,
    district_pop_2011 = persons,
    pct_change_from_last_census
  )
```


```{r 4d. Clean district migration stocks, message = FALSE}
# Clean 2011 district migration stock tables.
# Keep interstate migrants and the duration bands used downstream.

migration_cols <- c(
  "state_code", "district_code", "area_name", "last_residence",
  "last_residence_type", "place_of_enumeration",
  "2011_Total_Persons", "2011_Total_Males", "2011_Total_Females",
  "2011_Total_Persons_<1", "2011_Total_Males_<1", "2011_Total_Females_<1",
  "2011_Total_Persons_1-4", "2011_Total_Males_1-4", "2011_Total_Females_1-4",
  "2011_Total_Persons_5-9", "2011_Total_Males_5-9", "2011_Total_Females_5-9",
  "2011_Total_Persons_10-19", "2011_Total_Males_10-19", "2011_Total_Females_10-19",
  "2011_Total_Persons_>20", "2011_Total_Males_>20", "2011_Total_Females_>20",
  "2011_Total_Persons_NK", "2011_Total_Males_NK", "2011_Total_Females_NK"
)

clean_migration_file <- function(path) {
  read_excel(path, col_names = FALSE, col_types = "text") %>%
    select(2:28) %>%
    set_names(migration_cols) %>%
    mutate(across(everything(), ~ str_squish(as.character(.x)))) %>%
    filter(str_detect(state_code, "^\\d+$"), str_detect(district_code, "^\\d{3}$"), district_code != "000") %>%
    mutate(across(starts_with("2011_"), clean_num))
}

migration <- read_many("data/pop/migration", "\\.xlsx?$", clean_migration_file) %>%
  filter(
    last_residence == "States in India beyond the state of enumeration",
    last_residence_type == "Total",
    place_of_enumeration == "Total"
  ) %>%
  transmute(
    state_code,
    district_code,
    district_name = as.character(area_name),
    `2011_Total_Persons`,
    `2011_Total_Persons_<1`,
    `2011_Total_Persons_1-4`,
    `2011_Total_Persons_5-9`,
    `2011_Total_Persons_10-19`
  )
```


```{r 4e. Clean district migration change, message = FALSE}
# Load district migration change files and keep interstate total migration.
# Replaces the manual for-loop rbind with one map_dfr call.

mig_change <- read_many(
  "data/pop/migration_change",
  "_2001_2011_merged\\.csv$",
  read_csv,
  show_col_types = FALSE
) %>%
  filter(
    Last_Residence == "STATES IN INDIA BEYOND THE STATE OF ENUMERATION",
    Last_Residence_Type == "TOTAL",
    Enumeration_Site_Type == "TOTAL"
  ) %>%
  transmute(
    `2011_District` = as.character(`2011_District`),
    `2011_Area`,
    `delta_Total_Persons`,
    `delta_Total_Persons_<1`,
    `delta_Total_Persons_1-4`,
    `delta_Total_Persons_5-9`,
    `delta_Total_Persons_10-19`
  )
```


```{r 5. Load district-level GDP data, message = FALSE}
# Load district GDP levels and reshape district GDP growth files.
# Keep growth files long because column names are district names.

gdp <- read_csv("data/gdp/gdp.csv", show_col_types = FALSE)

clean_gdp_change_file <- function(path) {
  read_csv(path, show_col_types = FALSE) %>%
    rename(year = 1, description = 2) %>%
    rename_with(str_squish) %>%
    pivot_longer(-c(year, description), names_to = "district", values_to = "value") %>%
    transmute(
      year,
      description,
      district = str_squish(district),
      value = parse_number(as.character(value)),
      source_file = basename(path)
    ) %>%
    filter(!is.na(value))
}

gdp_change <- read_many("data/gdp/gdp_change", "\\.csv$", clean_gdp_change_file)
```


```{r 6. Load survey and additional data, message = FALSE}
# Load Lokniti survey files and assembly election returns.
# Polling-station returns are not loaded until they are used.

nes_2009 <- read_sav("data/lokniti/nes_2009.sav")
nes_2014 <- read_sav("data/lokniti/nes_2014.sav")

ac_elections <- read_csv("data/election/lok_dhaba_ae.csv", show_col_types = FALSE)
```


```{r 7. Clean ac_map}
# Add numeric state and PC identifiers to the AC map.
# Geometry repair stays here because this map anchors spatial joins.

ac_map_clean <- ac_map %>%
  mutate(
    state_no = state_name_to_no(state),
    pc = as.double(pc)
  ) %>%
  st_make_valid()
```


```{r 8a. Crosswalk constants}
# Define special cases for district joins and states with true zero SC/ST populations.
# These are substantive harmonization choices, so keep them explicit.

zero_st_states <- c(7, 3, 6, 34) # Delhi, Punjab, Haryana, Puducherry
zero_sc_states <- c(12, 13)      # Arunachal Pradesh, Nagaland

gdp_name_override <- tribble(
  ~state_no, ~census_dist_norm, ~gdp_dist_norm,
  24, "AHMADABAD",      "AHMEDABAD",
  24, "KACHCHH",        "KUTCH",
  24, "BANAS KANTHA",   "BANASKANTHA",
  24, "SABAR KANTHA",   "SABARKANTHA",
  24, "MAHESANA",       "MEHSANA",
  24, "DOHAD",          "DAHOD",
  19, "BARDHMAN",       "BURDWAN",
  19, "BARDHAMAN",      "BURDWAN",
  19, "BARDDHAMAN",     "BURDWAN",
  19, "HUGLI",          "HOOGHLY",
  19, "HAORA",          "HOWRAH",
  19, "DARJILING",      "DARJEELING",
  19, "KOCH BIHAR",     "COOCH BEHAR",
  33, "KANNIYAKUMARI",  "KANYAKUMARI",
  29, "BANGALORE",      "BANGALORE URBAN",
  29, "CHIKMAGALUR",    "CHICKMAGALUR",
  29, "CHAMARAJANAGAR", "CHAMARAJA NAGAR",
  27, "NASHIK",         "NASIK",
  27, "BID",            "BEED",
  27, "RAIGARH",        "RAIGAD",
  27, "AHMADNAGAR",     "AHMEDNAGAR",
  6,  "SONIPAT",        "SONEPAT",
  6,  "HISAR",          "HISSAR",
  32, "ERNAKULAM",      "ERANAKULAM"
)
```


```{r 8b. Build district GDP per capita}
# Calculate district per-capita GDP for 2009 and 2013.
# Names are normalized here so GDP can join to Census districts.

pc_gdp <- gdp %>%
  filter(Year %in% c("2009 (2004)", "2013 (2004)")) %>%
  transmute(
    state_no = state_name_to_no(`State Name`),
    gdp_state_name = `State Name`,
    gdp_dist_name = `Dist Name`,
    gdp_dist_norm = norm_name(`Dist Name`),
    `Dist Code`,
    gdp_year = str_extract(Year, "^\\d{4}"),
    gdp = `TOTAL CONSTANT PRICES (Millions in Rs)` * 1e6
  ) %>%
  left_join(pop, by = "Dist Code") %>%
  mutate(
    pc_gdp = gdp / (`TOTAL POPULATION (1000 Number)` * 1000),
    pc_gdp_col = paste0("pc_gdp_", gdp_year)
  ) %>%
  select(state_no, gdp_state_name, gdp_dist_name, gdp_dist_norm, pc_gdp_col, pc_gdp) %>%
  pivot_wider(names_from = pc_gdp_col, values_from = pc_gdp)
```


```{r 8c. Build district demographic crosswalk}
# Merge district-level economic, caste, migration, population, and GDP variables.
# The output is one district-level table ready for AC allocation.

dist_xwalk <- districts %>%
  filter(`District Code` != "000", `Sub District Code` == "00000") %>%
  distinct(`District Code`, .keep_all = TRUE) %>%
  transmute(
    `State Code`,
    `District Code`,
    `Town-Village Name`,
    state_no = as.double(`State Code`),
    census_dist_norm = norm_name(`Town-Village Name`)
  )

pop_change_name <- pop_change %>%
  transmute(
    state_no = as.double(state_code),
    census_dist_norm = norm_name(district_name),
    district_pop_2011_name = district_pop_2011,
    pct_change_from_last_census_name = pct_change_from_last_census
  )

demog_dist_xwalk <- dist_xwalk %>%
  left_join(
    econ_census,
    by = c(
      "State Code" = "pc11_state_id",
      "District Code" = "pc11_district_id"
    ),
    relationship = "one-to-one"
  ) %>%
  select(
    `State Code`, `District Code`, `Town-Village Name`,
    state_no, census_dist_norm,
    ec13_emp_all, ec13_emp_f, ec13_emp_m, ec13_emp_gov,
    ec13_emp_manuf, ec13_emp_services
  ) %>%
  left_join(
    sc_pop %>%
      select(
        dist_code_2011,
        sc_district_no = district_no_local,
        sc_persons
      ),
    by = c("District Code" = "dist_code_2011"),
    relationship = "one-to-one"
  ) %>%
  left_join(
    st_pop %>%
      select(
        dist_code_2011,
        st_district_no = district_no_local,
        st_persons
      ),
    by = c("District Code" = "dist_code_2011"),
    relationship = "one-to-one"
  ) %>%
  left_join(
    pop_change,
    by = c("District Code" = "district_code"),
    relationship = "one-to-one"
  ) %>%
  left_join(
    pop_change_name,
    by = c("state_no", "census_dist_norm"),
    relationship = "many-to-one"
  ) %>%
  mutate(
    district_pop_2011 = coalesce(district_pop_2011, district_pop_2011_name),
    pct_change_from_last_census = coalesce(
      pct_change_from_last_census,
      pct_change_from_last_census_name
    )
  ) %>%
  select(-district_pop_2011_name, -pct_change_from_last_census_name) %>%
  left_join(
    migration,
    by = c("District Code" = "district_code"),
    relationship = "one-to-one"
  ) %>%
  left_join(
    mig_change,
    by = c("District Code" = "2011_District"),
    relationship = "one-to-one"
  ) %>%
  left_join(gdp_name_override, by = c("state_no", "census_dist_norm")) %>%
  mutate(gdp_dist_join = coalesce(gdp_dist_norm, census_dist_norm)) %>%
  left_join(
    pc_gdp,
    by = c("state_no", "gdp_dist_join" = "gdp_dist_norm")
  ) %>%
  mutate(
    district_no = coalesce(sc_district_no, st_district_no),
    district_name_norm = norm_name(`Town-Village Name`),
    district_join_key_code = make_code_key(district_no),
    district_join_key_name = paste0("NAME_", district_name_norm),
    sc_persons = if_else(state_no %in% zero_sc_states & is.na(sc_persons), 0, sc_persons),
    st_persons = if_else(state_no %in% zero_st_states & is.na(st_persons), 0, st_persons)
  )

demog_dist_for_join <- demog_dist_xwalk %>%
  rename(district_no_demog = district_no) %>%
  mutate(
    district_join_key = district_join_key_code
  )
```


```{r 8d. Delhi district override}
# Assign Delhi ACs to districts using maximum spatial overlap.
# This replaces unreliable Delhi district codes in the AC crosswalk.

delhi_ac_manual <- tribble(
  ~state_no, ~ac, ~district_name_manual,
  7, 63, "North East",
  7, 64, "North East",
  7, 67, "North East",
  7, 68, "North East",
  7, 41, "South",
  7, 54, "South",
  7, 61, "East",
  7, 62, "East",
  7, 42, "South",
  7, 50, "South",
  7, 49, "South",
  7, 51, "South",
  7, 52, "South",
  7, 53, "South"
  ) %>%
  mutate(district_name_norm_manual = norm_delhi_dist(district_name_manual)) %>%
  left_join(
    demog_dist_xwalk %>%
      filter(state_no == 7) %>%
      transmute(
        state_no,
        district_name_norm_manual = norm_delhi_dist(`Town-Village Name`),
        district_no_manual = district_no
      ),
    by = c("state_no", "district_name_norm_manual")
  )

delhi_dist_geo <- read_sf("data/delhi_districts.geojson", quiet = TRUE) %>%
  clean_names() %>%
  st_make_valid()

delhi_dist_name_col <- names(delhi_dist_geo) %>%
  keep(~ str_detect(.x, regex("district|dist|name", ignore_case = TRUE))) %>%
  first()

stopifnot(!is.na(delhi_dist_name_col))

delhi_dist_codes <- demog_dist_xwalk %>%
  filter(state_no == 7) %>%
  transmute(
    delhi_district_name_norm = norm_delhi_dist(`Town-Village Name`),
    district_no_fixed = district_no,
    district_name_fixed = `Town-Village Name`
  )

delhi_dist_geo <- delhi_dist_geo %>%
  mutate(delhi_district_name_norm = norm_delhi_dist(.data[[delhi_dist_name_col]])) %>%
  left_join(delhi_dist_codes, by = "delhi_district_name_norm")

delhi_ac_district <- ac_map_clean %>%
  filter(state_no == 7) %>%
  select(state_no, ac, geometry) %>%
  st_transform(6933) %>%
  st_intersection(
    delhi_dist_geo %>%
      select(district_no_fixed, district_name_fixed, geometry) %>%
      st_transform(6933)
  ) %>%
  mutate(overlap_area = as.numeric(st_area(geometry))) %>%
  st_drop_geometry() %>%
  slice_max(overlap_area, by = c(state_no, ac), n = 1, with_ties = FALSE) %>%
  select(state_no, ac, district_no_fixed, district_name_fixed)

```


```{r 8e. Build AC demographic inputs}
# Parse AC IDs and build turnout-based allocation weights.
# Valid votes are a fallback for true elector weights.

ac_demog <- ac_pop %>%
  transmute(
    state_no = as.double(str_remove(str_match(ac08_id, "^\\d{4}-(\\d{2})-\\d{3}$")[, 2], "^0")),
    ac = as.double(str_remove(str_extract(ac08_id, "\\d{3}$"), "^0+")),
    con08_pop = con08_pc01_pca_tot_p,
    con08_land_area
  )

ac_weights <- pc_elections %>%
  filter(Year %in% c(2009, 2014)) %>%
  transmute(
    state_no = state_name_to_no(State_Name),
    ac = Constituency_No,
    year = Year,
    valid_votes = Valid_Votes
  ) %>%
  summarise(
    valid_votes = first_nonmissing(valid_votes),
    .by = c(state_no, ac, year)
  ) %>%
  pivot_wider(
    id_cols = c(state_no, ac),
    names_from = year,
    values_from = valid_votes,
    names_prefix = "valid_votes_"
  ) %>%
  mutate(
    valid_votes_avg = rowMeans(pick(valid_votes_2009, valid_votes_2014), na.rm = TRUE),
    valid_votes_avg = if_else(is.nan(valid_votes_avg), NA_real_, valid_votes_avg),
    elector_weight = coalesce(valid_votes_2009, valid_votes_avg, valid_votes_2014)
  ) %>%
  select(state_no, ac, elector_weight)

ac_name_key_clean <- ac_name_key %>%
  transmute(
    state_no = as.double(str_remove(
      str_match(ac08_id, "^\\d{4}-(\\d{2})-\\d{3}$")[, 2],
      "^0"
    )),
    ac = as.double(str_remove(str_extract(ac08_id, "\\d{3}$"), "^0+")),
    ac_name_key = ac08_name,
    district_no_key = as.double(pc01_district_id),
    district_name_key = pc01_district_name,
    district_join_key_name_key = district_name_key(pc01_district_name),
    district_join_key_code_key = make_code_key(as.double(pc01_district_id))
  )
```


```{r 8f. Build AC district crosswalk}
# Join ACs to district-level demographic variables.
# Primary key: state_no + normalized district name.
# District code is retained only as a diagnostic.
# PC is diagnostic only and is never used as a join key.

manual_ac_district <- tribble(
  ~state_no, ~ac, ~district_manual,

  # Madhya Pradesh: Indore urban ACs
  23, 205, "Indore",
  23, 206, "Indore",
  23, 207, "Indore",
  23, 208, "Indore",

  # Gujarat: Ahmedabad urban ACs
  24, 45, "Ahmadabad",
  24, 46, "Ahmadabad",
  24, 47, "Ahmadabad",
  24, 48, "Ahmadabad",
  24, 49, "Ahmadabad",
  24, 50, "Ahmadabad",
  24, 51, "Ahmadabad",
  24, 52, "Ahmadabad",
  24, 53, "Ahmadabad",
  24, 54, "Ahmadabad",
  24, 55, "Ahmadabad",
  24, 56, "Ahmadabad",

  # Gujarat: Surat urban ACs
  24, 161, "Surat",
  24, 162, "Surat",
  24, 163, "Surat",
  24, 164, "Surat",
  24, 165, "Surat",
  24, 166, "Surat",
  24, 167, "Surat",

  # Ambiguous ACs resolved manually
  18, 33, "Bongaigaon",
  18, 42, "Barpeta",
  20, 57, "Saraikela Kharsawan",
  20, 59, "Ranchi",
  20, 70, "Simdega"
) %>%
  mutate(
    district_join_key_name_manual = district_name_key(district_manual)
  )

manual_unmatched <- manual_ac_district %>%
  anti_join(
    demog_dist_for_join %>%
      distinct(state_no, district_join_key_name),
    by = c("state_no", "district_join_key_name_manual" = "district_join_key_name")
  )

if (nrow(manual_unmatched) > 0) {
  print(manual_unmatched, n = Inf)
  stop("Some manual district names do not match demog_dist_for_join.")
}

ac_dist_raw <- ac_xwalk %>%
  st_drop_geometry() %>%
  transmute(
    state_no = as.double(ST_CODE),
    xwalk_pc = as.double(PC_NO), # diagnostic only
    ac = as.double(AC_NO),
    district = DIST_NAME,
    district_no = as.double(DT_CODE),
    xwalk_dist_norm = norm_name(DIST_NAME),
    district_join_key_code = make_code_key(district_no), # diagnostic only
    district_join_key_name = district_name_key(DIST_NAME),
    manual_xwalk = FALSE
  ) %>%
  filter(ac > 0) %>%
  left_join(
    delhi_ac_district %>%
      select(state_no, ac, district_no_fixed, district_name_fixed),
    by = c("state_no", "ac")
  ) %>%
  left_join(
    delhi_ac_manual %>%
      select(state_no, ac, district_no_manual, district_name_manual),
    by = c("state_no", "ac")
  ) %>%
  left_join(
    manual_ac_district %>%
      select(state_no, ac, district_manual, district_join_key_name_manual),
    by = c("state_no", "ac")
  ) %>%
  mutate(
    district_no = case_when(
      state_no == 7 ~ coalesce(district_no_fixed, district_no_manual, district_no),
      TRUE ~ district_no
    ),
    district = case_when(
      !is.na(district_manual) ~ district_manual,
      state_no == 7 & !is.na(district_name_fixed) ~ district_name_fixed,
      state_no == 7 & !is.na(district_name_manual) ~ district_name_manual,
      TRUE ~ district
    ),
    xwalk_dist_norm = norm_name(district),
    district_join_key_code = case_when(
      state_no == 7 & !is.na(district_no) ~ make_code_key(district_no),
      TRUE ~ district_join_key_code
    ),
    district_join_key_name = case_when(
      !is.na(district_join_key_name_manual) ~ district_join_key_name_manual,
      state_no == 7 ~ district_name_key(district),
      TRUE ~ district_join_key_name
    )
  ) %>%
  select(
    -district_no_fixed,
    -district_name_fixed,
    -district_no_manual,
    -district_name_manual,
    -district_manual,
    -district_join_key_name_manual
  )

ambiguous_acs <- ac_dist_raw %>%
  summarise(
    n_districts = n_distinct(district_join_key_name),
    .by = c(state_no, ac)
  ) %>%
  filter(n_districts > 1) %>%
  select(state_no, ac)

ac_dist_resolved <- ac_dist_raw %>%
  left_join(
    ambiguous_acs %>% mutate(ambiguous_ac = TRUE),
    by = c("state_no", "ac")
  ) %>%
  left_join(
    ac_name_key_clean %>%
      select(
        state_no,
        ac,
        district_no_key,
        district_name_key,
        district_join_key_name_key,
        district_join_key_code_key
      ),
    by = c("state_no", "ac"),
    relationship = "many-to-one"
  ) %>%
  mutate(
    ambiguous_ac = replace_na(ambiguous_ac, FALSE),
    matches_ac_name_key = district_join_key_name == district_join_key_name_key
  ) %>%
  group_by(state_no, ac) %>%
  mutate(
    use_ac_name_key = ambiguous_ac & any(matches_ac_name_key, na.rm = TRUE)
  ) %>%
  filter(!use_ac_name_key | matches_ac_name_key) %>%
  ungroup() %>%
  mutate(
    district_no = if_else(use_ac_name_key, district_no_key, district_no),
    district = if_else(use_ac_name_key, district_name_key, district),
    xwalk_dist_norm = norm_name(district),
    district_join_key_code = if_else(
      use_ac_name_key,
      district_join_key_code_key,
      district_join_key_code
    ),
    district_join_key_name = if_else(
      use_ac_name_key,
      district_join_key_name_key,
      district_join_key_name
    )
  ) %>%
  select(
    -ambiguous_ac,
    -district_no_key,
    -district_name_key,
    -district_join_key_name_key,
    -district_join_key_code_key,
    -matches_ac_name_key,
    -use_ac_name_key
  ) %>%
  distinct(state_no, ac, district_join_key_name, .keep_all = TRUE)

multi_district_acs <- ac_dist_resolved %>%
  summarise(
    n_districts = n_distinct(district_join_key_name),
    districts = paste(sort(unique(district)), collapse = "; "),
    district_keys = paste(sort(unique(district_join_key_name)), collapse = "; "),
    .by = c(state_no, ac)
  ) %>%
  filter(n_districts > 1) %>%
  arrange(state_no, ac)

if (nrow(multi_district_acs) > 0) {
  print(multi_district_acs, n = Inf)
  stop("Some ACs still map to multiple districts.")
}

ac_dist_base <- ac_dist_resolved %>%
  distinct(state_no, ac, .keep_all = TRUE)

manual_xwalk_rows <- manual_ac_district %>%
  anti_join(ac_dist_base, by = c("state_no", "ac")) %>%
  transmute(
    state_no,
    xwalk_pc = NA_real_,
    ac = as.double(ac),
    district = district_manual,
    district_no = NA_real_,
    xwalk_dist_norm = norm_name(district_manual),
    district_join_key_code = NA_character_,
    district_join_key_name = district_join_key_name_manual,
    manual_xwalk = TRUE
  )

ac_dist_prejoin <- bind_rows(ac_dist_base, manual_xwalk_rows)

ac_dist_duplicates <- ac_dist_prejoin %>%
  count(state_no, ac) %>%
  filter(n > 1)

if (nrow(ac_dist_duplicates) > 0) {
  print(ac_dist_duplicates, n = Inf)
  stop("AC-district crosswalk is not unique after manual rows.")
}

ac_dist_xwalk <- ac_dist_prejoin %>%
  left_join(
    demog_dist_for_join %>%
      select(-any_of(c("district_join_key", "district_join_key_code"))),
    by = c("state_no", "district_join_key_name"),
    relationship = "many-to-one",
    na_matches = "never"
  )

demog_ac_map <- ac_map_clean %>%
  rename(map_pc = pc) %>%
  left_join(ac_demog, by = c("state_no", "ac")) %>%
  left_join(ac_weights, by = c("state_no", "ac")) %>%
  left_join(
    ac_dist_xwalk,
    by = c("state_no", "ac"),
    relationship = "many-to-one"
  )
```


```{r 8g. Crosswalk diagnostics}
# Diagnose district keys, district joins, and AC-district duplication.
# AC-district rows are required to be unique by state_no + ac

# District demographic keys should be unique.
demog_dist_for_join %>%
  count(state_no, district_join_key_code) %>%
  filter(n > 1) %>%
  print(n = Inf)

# Manual-name lookup keys should also be unique.
demog_dist_for_join %>%
  count(state_no, district_join_key_name) %>%
  filter(n > 1) %>%
  arrange(state_no, district_join_key_name) %>%
  print(n = Inf)

# Joining district demographics should not expand rows.
tibble(
  rows_before_demog_join = nrow(ac_dist_prejoin),
  rows_after_demog_join = nrow(ac_dist_xwalk)
) %>%
  print()

# Raw district controls should no longer be missing for normal states.
ac_dist_xwalk %>%
  summarise(
    n = n(),
    missing_emp_raw = sum(is.na(ec13_emp_all)),
    missing_sc_raw = sum(is.na(sc_persons)),
    missing_st_raw = sum(is.na(st_persons)),
    missing_migration_raw = sum(is.na(`2011_Total_Persons_<1`)),
    .by = state_no
  ) %>%
  arrange(desc(missing_emp_raw)) %>%
  print(n = Inf)

# Check whether numeric-key matches attach the expected district names.
# Some spelling variants are fine; large systematic mismatches are not.
ac_dist_xwalk %>%
  filter(!is.na(ec13_emp_all)) %>%
  mutate(
    xwalk_district_norm = norm_name(district),
    name_agrees = xwalk_district_norm == district_name_norm
  ) %>%
  filter(!name_agrees) %>%
  distinct(
    state_no,
    district,
    xwalk_district_norm,
    `Town-Village Name`,
    district_name_norm,
    district_join_key_name
  ) %>%
  arrange(state_no, district) %>%
  print(n = Inf)

# AC-district crosswalk must be unique.
ac_dist_xwalk %>%
  count(state_no, ac) %>%
  filter(n > 1) %>%
  print(n = Inf)

# Delhi and zero-SC/zero-ST special cases.
ac_dist_xwalk %>%
  filter(state_no %in% c(7, 12, 13)) %>%
  summarise(
    n = n(),
    missing_join_key = sum(is.na(district_join_key_code)),
    missing_emp = sum(is.na(ec13_emp_all)),
    missing_sc = sum(is.na(sc_persons)),
    missing_st = sum(is.na(st_persons)),
    missing_migration = sum(is.na(`2011_Total_Persons_<1`)),
    .by = state_no
  ) %>%
  print(n = Inf)

demog_dist_xwalk %>%
  filter(
    !is.na(sc_district_no),
    !is.na(st_district_no),
    sc_district_no != st_district_no
  ) %>%
  select(
    state_no,
    `District Code`,
    `Town-Village Name`,
    sc_district_no,
    st_district_no
  ) %>%
  print(n = Inf)
```


```{r 9a. Calculate proportional demographic data}
# Allocate district-level demographic counts to ACs using AC population or turnout weights.
# This preserves known AC population where plausible and allocates missing/remainder population.

alloc_cols <- c(
  "ec13_emp_all", "ec13_emp_f", "ec13_emp_m", "ec13_emp_gov",
  "ec13_emp_manuf", "ec13_emp_services",
  "sc_persons", "st_persons",
  "2011_Total_Persons", "2011_Total_Persons_<1", "2011_Total_Persons_1-4",
  "2011_Total_Persons_5-9", "2011_Total_Persons_10-19",
  "delta_Total_Persons", "delta_Total_Persons_<1", "delta_Total_Persons_1-4",
  "delta_Total_Persons_5-9", "delta_Total_Persons_10-19"
) %>%
  intersect(names(demog_ac_map))

demog_ac_alloc <- demog_ac_map %>%
  mutate(
    geom_land_area = as.numeric(st_area(st_transform(geometry, 6933))) / 1e6,
    con08_land_area = coalesce(con08_land_area, geom_land_area),
    con08_pop = clean_num(con08_pop),
    elector_weight = clean_num(elector_weight),
    district_pop_persons = clean_num(district_pop_2011),
    across(all_of(alloc_cols), clean_num)
  ) %>%
  group_by(state_no, district_join_key_name) %>%
  mutate(
    district_pop_persons = first_nonmissing(district_pop_persons),
    ac_has_pop = !is.na(con08_pop) & con08_pop > 0,
    ac_has_weight = !is.na(elector_weight) & elector_weight > 0,
    n_ac = n(),
    n_known = sum(ac_has_pop),
    n_missing = sum(!ac_has_pop),
    known_pop_sum = sum(con08_pop[ac_has_pop], na.rm = TRUE),
    remainder_pop = pmax(district_pop_persons - known_pop_sum, 0),
    missing_weight_sum = sum(elector_weight[!ac_has_pop & ac_has_weight], na.rm = TRUE),
    all_weight_sum = sum(elector_weight[ac_has_weight], na.rm = TRUE),
    use_full_elector_allocation = !is.na(district_pop_persons) & known_pop_sum > 1.05 * district_pop_persons,
    proxy_ac_pop = case_when(
      ac_has_pop & !use_full_elector_allocation ~ con08_pop,
      all_weight_sum > 0 & ac_has_weight & (use_full_elector_allocation | n_known == 0) ~
        district_pop_persons * elector_weight / all_weight_sum,
      all_weight_sum == 0 & !is.na(district_pop_persons) & (use_full_elector_allocation | n_known == 0) ~
        district_pop_persons / n_ac,
      !ac_has_pop & n_known > 0 & remainder_pop > 0 & missing_weight_sum > 0 & ac_has_weight ~
        remainder_pop * elector_weight / missing_weight_sum,
      !ac_has_pop & n_known > 0 & remainder_pop > 0 & missing_weight_sum == 0 ~
        remainder_pop / n_missing,
      !ac_has_pop & !is.na(district_pop_persons) & all_weight_sum > 0 & ac_has_weight ~ 
        district_pop_persons * elector_weight / all_weight_sum,
      !ac_has_pop & !is.na(district_pop_persons) & all_weight_sum == 0 ~ 
        district_pop_persons / n_ac,
      TRUE ~ NA_real_
    ),
    proxy_ac_pop_source = case_when(
      ac_has_pop & !use_full_elector_allocation ~ "con08_pop",
      use_full_elector_allocation & all_weight_sum > 0 ~ "full_district_turnout_alloc",
      use_full_elector_allocation & all_weight_sum == 0 ~ "full_district_equal_alloc",
      !ac_has_pop & n_known > 0 & missing_weight_sum > 0 ~ "remainder_turnout_alloc",
      !ac_has_pop & n_known > 0 & missing_weight_sum == 0 ~ "remainder_equal_alloc",
      n_known == 0 & all_weight_sum > 0 ~ "full_district_turnout_alloc",
      n_known == 0 & all_weight_sum == 0 ~ "full_district_equal_alloc",
      !ac_has_pop & !is.na(district_pop_persons) & all_weight_sum > 0 & ac_has_weight ~ 
        "fallback_turnout_alloc", 
      !ac_has_pop & !is.na(district_pop_persons) & all_weight_sum == 0 ~ 
        "fallback_equal_alloc",
      TRUE ~ "missing"
    ),
    share_denom = sum(proxy_ac_pop, na.rm = TRUE),
    ac_alloc_share = case_when(
      share_denom > 0 ~ proxy_ac_pop / share_denom,
      n_ac > 0 ~ 1 / n_ac,
      TRUE ~ NA_real_
      ),
    known_pop_exceeds_district_pop = !is.na(district_pop_persons) & known_pop_sum > district_pop_persons
  ) %>%
  ungroup() %>%
  mutate(
    across(all_of(alloc_cols), ~ .x * ac_alloc_share, .names = "{.col}_ac_alloc"),
    sc_persons_ac_alloc = if_else(state_no %in% zero_sc_states & is.na(sc_persons_ac_alloc), 0, sc_persons_ac_alloc),
    st_persons_ac_alloc = if_else(state_no %in% zero_st_states & is.na(st_persons_ac_alloc), 0, st_persons_ac_alloc)
  )

# Collapse to one AC row after allocation.
# Allocated counts are summed; AC-level fields are kept once.

sum_or_na <- function(x) {
  if (all(is.na(x))) NA_real_ else sum(x, na.rm = TRUE)
}

alloc_out_cols <- names(demog_ac_alloc) %>%
  str_subset("_ac_alloc$")

demog_ac_alloc_ac <- demog_ac_alloc %>%
  st_drop_geometry() %>%
  summarise(
    across(all_of(alloc_out_cols), sum_or_na),
    proxy_ac_pop = sum_or_na(proxy_ac_pop),
    con08_land_area = first_nonmissing(con08_land_area),
    elector_weight = first_nonmissing(elector_weight),
    pc_gdp_2009 = first_nonmissing(pc_gdp_2009),
    pc_gdp_2013 = first_nonmissing(pc_gdp_2013),
    used_turnout_alloc = any(str_detect(proxy_ac_pop_source, "turnout"), na.rm = TRUE),
    used_equal_alloc = any(str_detect(proxy_ac_pop_source, "equal"), na.rm = TRUE),
    all_proxy_sources = paste(sort(unique(na.omit(proxy_ac_pop_source))), collapse = "; "),
    .by = c(state_no, ac)
  )
```


```{r 9b. Demographic allocation diagnostics}
# Summarize allocation quality by state.
# This is diagnostic output only and should not mutate the analysis object.

demog_ac_alloc_ac %>%
  summarise(
    n = n(),
    missing_proxy_ac_pop = sum(is.na(proxy_ac_pop)),
    missing_emp = sum(is.na(ec13_emp_all_ac_alloc)),
    missing_sc = sum(is.na(sc_persons_ac_alloc)),
    missing_st = sum(is.na(st_persons_ac_alloc)),
    .by = state_no
  ) %>%
  filter(if_any(starts_with("missing_"), ~ .x > 0)) %>%
  arrange(desc(missing_proxy_ac_pop)) %>%
  print(n = Inf)
```


```{r 10. Calculate new migration variables}
# Convert migrant-duration bands into annualized AC-level exposure measures.
# Wide variables feed the time-series, cross-sectional, and logit models.

mig_periods <- tribble(
  ~period, ~mig_col,                    ~period_length, ~period_order,
  "10_19", "2011_Total_Persons_10-19", 10,             1,
  "5_9",   "2011_Total_Persons_5-9",   5,              2,
  "1_4",   "2011_Total_Persons_1-4",   4,              3,
  "lt1",   "2011_Total_Persons_<1",    1,              4
) %>%
  mutate(mig_col = paste0(mig_col, "_ac_alloc"))

id_cols <- c("state_no", "ac")

mig_vars_wide <- demog_ac_alloc_ac %>%
  select(
    all_of(id_cols),
    ac_pop = proxy_ac_pop,
    total_migrants = `2011_Total_Persons_ac_alloc`,
    all_of(mig_periods$mig_col)
  ) %>%
  pivot_longer(all_of(mig_periods$mig_col), names_to = "mig_col", values_to = "migration") %>%
  left_join(mig_periods, by = "mig_col") %>%
  mutate(across(c(ac_pop, total_migrants, migration), as.numeric)) %>%
  arrange(across(all_of(id_cols)), period_order) %>%
  group_by(across(all_of(id_cols))) %>%
  mutate(
    mig_annualized = migration / period_length,
    mig_annualized_lag = lag(mig_annualized),
    mig_share_total_migrants = if_else(total_migrants > 0, mig_annualized / total_migrants, NA_real_),
    mig_share_ac_pop = if_else(ac_pop > 0, mig_annualized / ac_pop, NA_real_),
    log_mig_ratio = if_else(
      mig_annualized > 0 & mig_annualized_lag > 0,
      log(mig_annualized / mig_annualized_lag),
      NA_real_
    ),
    log1p_mig_ratio = log1p(mig_annualized) - log1p(mig_annualized_lag)
  ) %>%
  ungroup() %>%
  select(
    all_of(id_cols),
    period,
    mig_share_total_migrants,
    mig_share_ac_pop,
    log_mig_ratio,
    log1p_mig_ratio
  ) %>%
  pivot_wider(
    id_cols = all_of(id_cols),
    names_from = period,
    values_from = c(
      mig_share_total_migrants,
      mig_share_ac_pop,
      log_mig_ratio,
      log1p_mig_ratio
    )
  )

demog_ac_alloc_ac <- demog_ac_alloc_ac %>%
  left_join(mig_vars_wide, by = id_cols) %>%
  mutate(
    emp_rate = if_else(
      proxy_ac_pop > 0,
      ec13_emp_all_ac_alloc / proxy_ac_pop,
      NA_real_
    ),
    m_emp_rate = if_else(
      proxy_ac_pop > 0,
      ec13_emp_m_ac_alloc / proxy_ac_pop,
      NA_real_
    ),
    sc_pop_share = case_when(
      state_no %in% zero_sc_states & !is.na(proxy_ac_pop) ~ 0,
      proxy_ac_pop > 0 ~ sc_persons_ac_alloc / proxy_ac_pop,
      TRUE ~ NA_real_
    ),
    st_pop_share = case_when(
      state_no %in% zero_st_states & !is.na(proxy_ac_pop) ~ 0,
      proxy_ac_pop > 0 ~ st_persons_ac_alloc / proxy_ac_pop,
      TRUE ~ NA_real_
    ),
    delta_pc_gdp = pc_gdp_2013 / pc_gdp_2009
  )
```


```{r 11. Merge in pc_elections}
# Collapse candidate-level GE returns to AC-year far-right vote share.
# Far-right parties are defined once here and reused for survey vote coding.

fr_parties <- c("BJP", "SHS", "MNS")
fr_codes <- c(2, 46, 91)

pc_elections_clean <- pc_elections %>%
  filter(Year %in% c(2009, 2014)) %>%
  transmute(
    state = State_Name,
    state_no = state_name_to_no(State_Name),
    ac = Constituency_No,
    year = Year,
    pc_name = PC_Name,
    pc = PC_No,
    ac_name = Constituency_Name,
    party = Party,
    votes = Votes,
    valid_votes = Valid_Votes
  ) %>%
  summarise(
    valid_votes = first_nonmissing(valid_votes),
    fr_party_votes = sum(if_else(party %in% fr_parties, votes, 0), na.rm = TRUE),
    fr_party_vote_share = if_else(valid_votes > 0, 100 * fr_party_votes / valid_votes, NA_real_),
    .by = c(state, state_no, pc_name, pc, ac_name, ac, year)
  )

pc_demog_ac_alloc <- pc_elections_clean %>%
  left_join(demog_ac_alloc_ac, by = c("state_no", "ac"))
```


```{r 12. Clean FDI}
# Parse FDI coordinates and convert valid projects to sf points.
# Invalid or missing coordinates are dropped before spatial joins.

services <- c(
  "Business Services",
  "Customer Contact Centre",
  "Research & Development",
  "Sales, Marketing & Support",
  "Shared Services Centre",
  "Technical Support Centre"
)

fdi_coords <- fdi %>%
  mutate(fdi_id = row_number()) %>%
  extract(
    Coordinates,
    into = c("lat", "lon"),
    regex = "^\\s*(-?\\d+(?:\\.\\d+)?)\\s*,\\s*(-?\\d+(?:\\.\\d+)?)\\s*$",
    remove = FALSE,
    convert = TRUE
  ) %>%
  filter(!is.na(lat), !is.na(lon)) %>%
  st_as_sf(coords = c("lon", "lat"), crs = 4326, remove = FALSE) %>%
  st_transform(st_crs(ac_map_clean))
```


```{r 13. Build adjacency table}
# Build an AC exposure map linking each AC to itself and adjacent ACs.
# This lets each FDI project count for the containing AC and neighboring ACs.

ac_index <- ac_map_clean %>%
  mutate(ac_uid = row_number()) %>%
  select(ac_uid, state_no, ac, geometry)

fdi_lookup_local <- fdi_coords %>%
  st_join(ac_index, join = st_within, left = TRUE) %>%
  st_drop_geometry() %>%
  transmute(fdi_id, local_ac_uid = ac_uid)

ac_neighbors <- tibble(
  local_ac_uid = ac_index$ac_uid,
  neighbor_row = st_touches(ac_index)
) %>%
  unnest_longer(neighbor_row, values_to = "neighbor_row") %>%
  transmute(
    local_ac_uid,
    neighbor_ac_uid = ac_index$ac_uid[neighbor_row],
    exposure_type = "adjacent"
  )

ac_self <- tibble(
  local_ac_uid = ac_index$ac_uid,
  neighbor_ac_uid = ac_index$ac_uid,
  exposure_type = "own"
)

ac_exposure_map <- bind_rows(ac_self, ac_neighbors) %>%
  left_join(
    ac_index %>%
      st_drop_geometry() %>%
      transmute(neighbor_ac_uid = ac_uid, state_no, ac),
    by = "neighbor_ac_uid"
  )
```


```{r 14a. Classify FDI projects}
# Assign each FDI project to exposed ACs and classify period/activity.
# Exposure includes own-AC and adjacent-AC projects.

fdi_ac <- fdi_coords %>%
  left_join(
    fdi_lookup_local %>%
      filter(!is.na(local_ac_uid)) %>%
      left_join(ac_exposure_map, by = "local_ac_uid", relationship = "many-to-many") %>%
      distinct(fdi_id, state_no, ac, exposure_type),
    by = "fdi_id",
    relationship = "one-to-many"
  ) %>%
  clean_names() %>%
  mutate(
    project_month = as.Date(parse_date_time(project_date, orders = c("b Y", "B Y"))),
    period = case_when(
      between(project_month, as.Date("2004-04-01"), as.Date("2009-04-01")) ~ "1",
      between(project_month, as.Date("2009-05-01"), as.Date("2014-05-01")) ~ "2",
      TRUE ~ NA_character_
    ),
    activity = str_squish(activity),
    activity_type = case_when(
      activity == "Manufacturing" ~ "manufacturing",
      activity %in% services ~ "services",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(state_no), !is.na(ac), !is.na(period)) %>%
  st_drop_geometry()
```


```{r 14b. Aggregate FDI exposure}
# Aggregate FDI exposure counts by AC, period, and activity type.
# Missing exposure cells are set to zero before creating ratios.

fdi_summary <- bind_rows(
  fdi_ac %>%
    count(state_no, ac, period, name = "n") %>%
    mutate(activity_type = "total"),
  
  fdi_ac %>%
    filter(!is.na(activity_type)) %>%
    count(state_no, ac, period, activity_type, name = "n")
) %>%
  pivot_wider(
    id_cols = c(state_no, ac),
    names_from = c(period, activity_type),
    values_from = n,
    names_glue = "fdi_{period}_{activity_type}_n",
    values_fill = 0
  ) %>%
  mutate(
    across(starts_with("fdi_"), ~ replace_na(.x, 0)),
    fdi_total_ever_n = fdi_1_total_n + fdi_2_total_n,
    fdi_mfg_ever_n = fdi_1_manufacturing_n + fdi_2_manufacturing_n,
    fdi_svc_ever_n = fdi_1_services_n + fdi_2_services_n,
    fdi_max_period_n = pmax(fdi_1_total_n, fdi_2_total_n, na.rm = TRUE),
    fdi_outlier_99 = fdi_total_ever_n > quantile(fdi_total_ever_n, 0.99, na.rm = TRUE),
    fdi_no_outlier_99 = !fdi_outlier_99
  )
```


```{r 14c. FDI exposure diagnostics}
# Plot raw and logged AC-level FDI exposure distributions.
# These plots diagnose skew and motivate logged exposure changes.

fdi_outlier_cutoff_99 <- quantile(fdi_summary$fdi_total_ever_n, 0.99, na.rm = TRUE)

ggplot(fdi_summary, aes(fdi_total_ever_n)) +
  geom_histogram(binwidth = 1, boundary = -0.5) +
  geom_vline(xintercept = fdi_outlier_cutoff_99, linetype = "dashed") +
  labs(
    x = "FDI sites in or adjacent to assembly constituency, 2004-2014",
    y = "Assembly constituencies",
    title = "Distribution of AC-level FDI exposure"
  )

ggplot(fdi_summary, aes(log1p(fdi_total_ever_n))) +
  geom_histogram(bins = 30) +
  labs(
    x = "log(1 + FDI sites in or adjacent to AC), 2004-2014",
    y = "Assembly constituencies",
    title = "Distribution of logged AC-level FDI exposure"
  )
```


```{r 14d. Merge FDI into AC panel}
# Merge FDI exposure into AC-year election-demographic data.
# Create logged FDI changes, GDP change, employment, caste, and migration controls.

fdi_pc_demog_ac <- pc_demog_ac_alloc %>%
  left_join(fdi_summary, by = c("state_no", "ac"), relationship = "many-to-one") %>%
  mutate(
    across(starts_with("fdi_"), ~ replace_na(.x, 0)),
    ratio_fdi_total_n = log1p(fdi_2_total_n) - log1p(fdi_1_total_n),
    ratio_fdi_mfg_n = log1p(fdi_2_manufacturing_n) - log1p(fdi_1_manufacturing_n),
    ratio_fdi_svc_n = log1p(fdi_2_services_n) - log1p(fdi_1_services_n),
    ann_2000s_mig = 0.55 * (`2011_Total_Persons_1-4_ac_alloc` + `2011_Total_Persons_5-9_ac_alloc`),
    ann_2000s_share_total_migrants = ann_2000s_mig / `2011_Total_Persons_ac_alloc`,
    ann_2000s_share_ac_pop = ann_2000s_mig / proxy_ac_pop
  )
```


```{r 15. Clean Lokniti data}
# Recode survey items into recognition/statism indices for 2009 and 2014.
# State codes are harmonized to Census/ECI state numbers.

nes_state_recode <- function(x) {
  recode(
    as.numeric(x),
    `1` = 28, `2` = 12, `3` = 18, `4` = 10, `5` = 30, `6` = 24,
    `7` = 6, `8` = 2, `9` = 1, `10` = 29, `11` = 32, `12` = 23,
    `13` = 27, `14` = 14, `15` = 17, `16` = 15, `17` = 13,
    `18` = 21, `19` = 3, `20` = 8, `21` = 11, `22` = 33,
    `23` = 16, `24` = 9, `25` = 19, `26` = 35, `27` = 4,
    `28` = 26, `29` = 25, `30` = 7, `31` = 31, `32` = 34,
    `33` = 20, `34` = 22, `35` = 5, `36` = 28,
    .default = NA_real_
  )
}

nes_2009_clean <- nes_2009 %>%
  mutate(
    state_no = nes_state_recode(st_id),
    q26a = case_match(q26a, 1 ~ 2, 2 ~ 1, 8 ~ 0, 3 ~ -1, 4 ~ -2),
    q27  = case_match(q27,  2 ~ 1, c(7, 8) ~ 0, 1 ~ -1),
    a4b  = case_match(a4b,  4 ~ 2, 3 ~ 1, 8 ~ 0, 2 ~ -1, 1 ~ -2),
    a4c  = case_match(a4c,  1 ~ 2, 2 ~ 1, 8 ~ 0, 3 ~ -1, 4 ~ -2),
    a4d  = case_match(a4d,  1 ~ 2, 2 ~ 1, 8 ~ 0, 3 ~ -1, 4 ~ -2),
    a4g  = case_match(a4g,  4 ~ 2, 3 ~ 1, 8 ~ 0, 2 ~ -1, 1 ~ -2),
    a5   = case_match(a5,   2 ~ 1, 8 ~ 0, 1 ~ -1),
    a6a  = case_match(a6a,  2 ~ 1, 8 ~ 0, 1 ~ -1),
    a6b  = case_match(a6b,  2 ~ 1, 8 ~ 0, 1 ~ -1),
    across(c(q26a, q27, a4b, a4c, a4d, a4g, a5, a6a, a6b), safe_z, .names = "z_{.col}"),
    recognition = rowMeans(replace(pick(z_a6a, z_a5, z_a4c, z_a4b), 
                                   pick(a6a, a5, a4c, a4b) == 0, NA), na.rm = TRUE),
    statism = rowMeans(replace(pick(z_a4d, z_a4g, z_q26a, z_a6b, z_q27),
                               pick(a4d, a4g, q26a, a6b, q27) == 0, NA), na.rm = TRUE),
    across(c(recognition, statism), ~ if_else(is.nan(.x), NA_real_, .x))
  )

nes_2014_clean <- nes_2014 %>%
  mutate(
    state_no = nes_state_recode(state_id),
    q10b = case_match(q10b, 1 ~ 2, 2 ~ 1, 8 ~ 0, 3 ~ -1, 4 ~ -2),
    q10e = case_match(q10e, 4 ~ 2, 3 ~ 1, 8 ~ 0, 2 ~ -1, 1 ~ -2),
    q23c = case_match(q23c, 4 ~ 2, 3 ~ 1, 8 ~ 0, 2 ~ -1, 1 ~ -2),
    across(c(q10b, q10e, q23c), safe_z, .names = "z_{.col}"),
    recognition = rowMeans(replace(pick(z_q10b, z_q10e), pick(q10b, q10e) == 0, NA), na.rm = TRUE),
    statism = rowMeans(replace(pick(z_q23c), pick(q23c) == 0, NA), na.rm = TRUE),
    recognition = if_else(is.nan(recognition), NA_real_, recognition)
  )
```


```{r 16. Create and merge grouped Lokniti file}
# Aggregate voter responses to AC-level ideology and far-right support measures.
# These AC-level survey aggregates define subgroup analyses.

vote_share <- function(vote, condition, codes = fr_codes) {
  x <- vote[replace_na(condition, FALSE)]
  if (!length(x)) NA_real_ else safe_mean(if_else(is.na(x), NA_real_, as.numeric(x %in% codes)))
}

is_center <- function(recognition, statism) ideology_group(recognition, statism) == "C"
is_right  <- function(recognition, statism) ideology_group(recognition, statism) == "R"
is_left   <- function(recognition, statism) ideology_group(recognition, statism) == "L"

nes_2009_grouped <- nes_2009_clean %>%
  summarise(
    loc_fr_vote_share_2009 = vote_share(q1a, TRUE),
    loc_fr_close_to_2009 = vote_share(q11a, TRUE),
    loc_fr_never_vote_2009 = vote_share(q12a, TRUE),
    recognition_2009 = safe_mean(recognition),
    statism_2009 = safe_mean(statism),
    mean_econ_trend_2009 = safe_mean(e2),
    mean_educ_2009 = safe_mean(z5),
    loc_up_caste_share_2009 = sum(z7a == 4 & z8 %in% c(1, 4, 6), na.rm = TRUE) / sum(!is.na(z7a) & !is.na(z8)),
    loc_h_obc_share_2009 = sum(z7a == 3 & z8 == 1, na.rm = TRUE) / sum(!is.na(z7a) & !is.na(z8)),
    mean_hhi_2009 = safe_mean(z18),
    loc_fr_mod_vote_share_2009 = vote_share(q1a, is_center(recognition, statism)),
    loc_fr_right_vote_share_2009 = vote_share(q1a, is_right(recognition, statism)),
    loc_fr_left_vote_share_2009 = vote_share(q1a, is_left(recognition, statism)),
    .by = c(state_no, pc_id, ac_id)
  ) %>%
  mutate(ac_id = as.integer(ac_id))

nes_2014_grouped <- nes_2014_clean %>%
  summarise(
    loc_fr_vote_share_2014 = vote_share(q1a, TRUE),
    loc_fr_close_to_2014 = vote_share(q11a, TRUE),
    recognition_2014 = safe_mean(recognition),
    statism_2014 = safe_mean(statism),
    mean_educ_2014 = safe_mean(z3),
    loc_up_caste_share_2014 = sum(z5a == 4 & z6 %in% c(1, 4, 6), na.rm = TRUE) / sum(!is.na(z5a) & !is.na(z6)),
    loc_h_obc_share_2014 = sum(z5a == 3 & z6 == 1, na.rm = TRUE) / sum(!is.na(z5a) & !is.na(z6)),
    mean_hhi_2014 = safe_mean(z13),
    loc_fr_mod_vote_share_2014 = vote_share(q1a, is_center(recognition, statism)),
    loc_fr_right_vote_share_2014 = vote_share(q1a, is_right(recognition, statism)),
    loc_fr_left_vote_share_2014 = vote_share(q1a, is_left(recognition, statism)),
    .by = c(state_no, pc_id, ac_id)
  ) %>%
  mutate(ac_id = as.integer(ac_id))

nes_fdi_pc_demog_ac <- fdi_pc_demog_ac %>%
  left_join(nes_2009_grouped, by = c("state_no", "pc" = "pc_id", "ac" = "ac_id")) %>%
  left_join(nes_2014_grouped, by = c("state_no", "pc" = "pc_id", "ac" = "ac_id")) %>%
  mutate(ac_ideology = ideology_group(recognition_2009, statism_2009))
```


```{r 17. Create voter-level Lokniti file}
# Stack 2009 and 2014 voter-level Lokniti data.
# Merge each respondent to AC-year FDI, migration, and demographic exposure.

plain_col <- function(x) {
  if (inherits(x, c("haven_labelled", "labelled", "labelled_spss"))) as.vector(x) else x
}

nes_clean <- bind_rows(
  nes_2009_clean %>%
    mutate(year = 2009) %>%
    mutate(across(everything(), plain_col)),
  
  nes_2014_clean %>%
    mutate(year = 2014) %>%
    rename(res = resno) %>%
    mutate(across(everything(), plain_col))
) %>%
  left_join(
    fdi_pc_demog_ac,
    by = c("state_no", "pc_id" = "pc", "ac_id" = "ac", "year")
  ) %>%
  mutate(voter_ideology = ideology_group(recognition, statism))
```

```{r 18. Create regression datasets}
# Build the three analysis datasets:
# 1. AC time-series
# 2. AC cross-section
# 3. Voter-level logit
#
# Cross-section and logit models use period-specific FDI/migration variables.
# Time-series models use change in far-right vote share from 2009 to 2014.

id_vars <- c("state", "state_no", "pc_name", "pc", "ac_name", "ac", "ac_ideology")

controls <- c(
  "emp_rate",
  "m_emp_rate",
  "sc_pop_share",
  "st_pop_share",
  "con08_land_area",
  "proxy_ac_pop"
)

per_100k <- function(x, pop) {
  if_else(
    !is.na(pop) & pop > 0,
    100000 * x / pop,
    NA_real_
  )
}

share_to_pp <- function(x) {
  100 * x
}

# Only define fr_codes here if it has not already been defined earlier.
if (!exists("fr_codes")) {
  fr_codes <- c(2, 46, 91)
}

ts_covariates <- c(
  "fdi_1_total_n",
  "fdi_1_manufacturing_n",
  "fdi_1_services_n",
  "fdi_2_total_n",
  "fdi_2_manufacturing_n",
  "fdi_2_services_n",

  "ratio_fdi_total_n",
  "ratio_fdi_mfg_n",
  "ratio_fdi_svc_n",

  "mig_share_total_migrants_lt1",
  "mig_share_ac_pop_lt1",
  "log1p_mig_ratio_lt1",

  "ann_2000s_share_total_migrants",
  "ann_2000s_share_ac_pop",

  controls,
  "fdi_total_ever_n",
  "fdi_no_outlier_99"
)

make_period_vars <- function(df) {
  df %>%
    mutate(
      fdi_total_n = case_when(
        year == 2009 ~ fdi_1_total_n,
        year == 2014 ~ fdi_2_total_n,
        TRUE ~ NA_real_
      ),
      fdi_mfg_n = case_when(
        year == 2009 ~ fdi_1_manufacturing_n,
        year == 2014 ~ fdi_2_manufacturing_n,
        TRUE ~ NA_real_
      ),
      fdi_svc_n = case_when(
        year == 2009 ~ fdi_1_services_n,
        year == 2014 ~ fdi_2_services_n,
        TRUE ~ NA_real_
      ),

      fdi_total_pc100k = per_100k(fdi_total_n, proxy_ac_pop),
      fdi_mfg_pc100k = per_100k(fdi_mfg_n, proxy_ac_pop),
      fdi_svc_pc100k = per_100k(fdi_svc_n, proxy_ac_pop),
      fdi_total_ever_pc100k = per_100k(fdi_total_ever_n, proxy_ac_pop),

      mig_share_total_migrants_period = case_when(
        year == 2009 ~ ann_2000s_share_total_migrants,
        year == 2014 ~ mig_share_total_migrants_lt1,
        TRUE ~ NA_real_
      ),
      mig_share_ac_pop_period = case_when(
        year == 2009 ~ ann_2000s_share_ac_pop,
        year == 2014 ~ mig_share_ac_pop_lt1,
        TRUE ~ NA_real_
      ),
      log1p_mig_ratio_period = case_when(
        year == 2009 ~ log1p_mig_ratio_5_9,
        year == 2014 ~ log1p_mig_ratio_lt1,
        TRUE ~ NA_real_
      ),

      mig_share_total_migrants_period_pp = share_to_pp(mig_share_total_migrants_period),
      mig_share_ac_pop_period_pp = share_to_pp(mig_share_ac_pop_period),

      year_fe = factor(year),
      state_fe = factor(state_no)
    )
}

ts_covars <- nes_fdi_pc_demog_ac %>%
  st_drop_geometry() %>%
  summarise(
    across(all_of(ts_covariates), first_nonmissing),
    ac_ideology = first_nonmissing(ac_ideology),
    .by = c(state_no, ac)
  )

ts_votes <- pc_elections_clean %>%
  filter(year %in% c(2009, 2014)) %>%
  summarise(
    fr_party_vote_share = first_nonmissing(fr_party_vote_share),
    .by = c(state_no, ac, year)
  ) %>%
  pivot_wider(
    id_cols = c(state_no, ac),
    names_from = year,
    values_from = fr_party_vote_share,
    names_prefix = "fr_party_vote_share_"
  )

ts_labels <- pc_elections_clean %>%
  filter(year == 2014) %>%
  summarise(
    state = first_nonmissing(state),
    pc = first_nonmissing(pc),
    pc_name = first_nonmissing(pc_name),
    ac_name = first_nonmissing(ac_name),
    .by = c(state_no, ac)
  )

ts_df <- ts_votes %>%
  left_join(ts_labels, by = c("state_no", "ac")) %>%
  left_join(ts_covars, by = c("state_no", "ac")) %>%
  mutate(
    delta_fr_party_vote_share = fr_party_vote_share_2014 - fr_party_vote_share_2009,

    # New FE: state FE replaces parliamentary constituency FE.
    state_fe = factor(state_no),

    # Keep pc_fe only for diagnostics/backward compatibility, but it is no longer used.
    pc_fe = interaction(state_no, pc, drop = TRUE),

    # Time-series FDI exposure: 2009–2014 FDI projects per 100,000 people.
    fdi_ts_total_pc100k = per_100k(fdi_2_total_n, proxy_ac_pop),
    fdi_ts_mfg_pc100k = per_100k(fdi_2_manufacturing_n, proxy_ac_pop),
    fdi_ts_svc_pc100k = per_100k(fdi_2_services_n, proxy_ac_pop),
    fdi_total_ever_pc100k = per_100k(fdi_total_ever_n, proxy_ac_pop),

    # Migration shares in percentage-point units.
    mig_share_total_migrants_lt1_pp = share_to_pp(mig_share_total_migrants_lt1),
    mig_share_ac_pop_lt1_pp = share_to_pp(mig_share_ac_pop_lt1)
  )

xs_df <- nes_fdi_pc_demog_ac %>%
  st_drop_geometry() %>%
  filter(!is.na(year)) %>%
  select(
    all_of(id_vars),
    year,
    fr_party_vote_share,
    fdi_1_total_n,
    fdi_1_manufacturing_n,
    fdi_1_services_n,
    fdi_2_total_n,
    fdi_2_manufacturing_n,
    fdi_2_services_n,
    fdi_total_ever_n,
    fdi_no_outlier_99,
    ann_2000s_share_total_migrants,
    ann_2000s_share_ac_pop,
    log1p_mig_ratio_5_9,
    mig_share_total_migrants_lt1,
    mig_share_ac_pop_lt1,
    log1p_mig_ratio_lt1,
    all_of(controls)
  ) %>%
  make_period_vars() %>%
  mutate(
  pc_fe = interaction(state_no, pc, drop = TRUE),
  state_fe = factor(state_no)
)

logit_df <- nes_clean %>%
  filter(!is.na(year)) %>%
  select(
    year,
    state_no,
    state,
    pc_id,
    pc_name,
    ac_id,
    ac_name,
    res,
    q1a,
    recognition,
    statism,
    voter_ideology,
    fdi_1_total_n,
    fdi_1_manufacturing_n,
    fdi_1_services_n,
    fdi_2_total_n,
    fdi_2_manufacturing_n,
    fdi_2_services_n,
    fdi_total_ever_n,
    fdi_no_outlier_99,
    ann_2000s_share_total_migrants,
    ann_2000s_share_ac_pop,
    log1p_mig_ratio_5_9,
    mig_share_total_migrants_lt1,
    mig_share_ac_pop_lt1,
    log1p_mig_ratio_lt1,
    all_of(controls)
  ) %>%
  rename(pc = pc_id, ac = ac_id) %>%
  make_period_vars() %>%
  mutate(
  fr_vote = case_when(
    is.na(q1a) ~ NA_real_,
    q1a %in% fr_codes ~ 1,
    TRUE ~ 0
  ),
  pc_fe = interaction(state_no, pc, drop = TRUE),
  state_fe = factor(state_no)
)

list(
  time_series = ts_df,
  assembly_xs = xs_df,
  voter_logit = logit_df
) %>%
  imap(\(d, nm) {
    message(nm, ": ", nrow(d), " rows")
  })
```


```{r 19. Model dictionaries and labels}
# Define interchangeable FDI, migration, subgroup, and label dictionaries.
# These dictionaries define the 135 base model families:
# 3 model families × 5 subsets × 3 FDI variables × 3 migration variables.

ts_fdi_vars <- c(
  total = "fdi_ts_total_pc100k",
  mfg = "fdi_ts_mfg_pc100k",
  svc = "fdi_ts_svc_pc100k"
)

ts_mig_vars <- c(
  log_ratio = "log1p_mig_ratio_lt1",
  share_mig = "mig_share_total_migrants_lt1_pp",
  share_acpop = "mig_share_ac_pop_lt1_pp"
)

xs_fdi_vars <- c(
  total = "fdi_total_pc100k",
  mfg = "fdi_mfg_pc100k",
  svc = "fdi_svc_pc100k"
)

xs_mig_vars <- c(
  log_ratio = "log1p_mig_ratio_period",
  share_mig = "mig_share_total_migrants_period_pp",
  share_acpop = "mig_share_ac_pop_period_pp"
)

fdi_ever_cutoff_99 <- quantile(
  ts_df$fdi_total_ever_pc100k,
  0.99,
  na.rm = TRUE
)

drop_fdi_ever_outliers <- function(d) {
  d %>%
    filter(
      is.na(fdi_total_ever_pc100k) |
        fdi_total_ever_pc100k <= fdi_ever_cutoff_99
    )
}

ac_subsets <- list(
  all = identity,
#  no_fdi_outliers = \(d) drop_fdi_ever_outliers(d),
  C_ac = \(d) filter(d, ac_ideology == "C"),
  L_ac = \(d) filter(d, ac_ideology == "L"),
  R_ac = \(d) filter(d, ac_ideology == "R")
)

voter_subsets <- list(
  all = identity,
#  no_fdi_outliers = \(d) drop_fdi_ever_outliers(d),
  C_voter = \(d) filter(d, voter_ideology == "C"),
  L_voter = \(d) filter(d, voter_ideology == "L"),
  R_voter = \(d) filter(d, voter_ideology == "R")
)

variable_labels <- c(
  delta_fr_party_vote_share = "Change in far-right vote share, 2009–2014",
  fr_party_vote_share = "Far-right vote share",
  fr_vote = "Far-right vote",

  fdi_ts_total_pc100k = "Total FDI projects per 100,000 people",
  fdi_ts_mfg_pc100k = "Manufacturing FDI projects per 100,000 people",
  fdi_ts_svc_pc100k = "Services FDI projects per 100,000 people",

  fdi_total_pc100k = "Period-specific total FDI projects per 100,000 people",
  fdi_mfg_pc100k = "Period-specific manufacturing FDI projects per 100,000 people",
  fdi_svc_pc100k = "Period-specific services FDI projects per 100,000 people",
  fdi_total_ever_pc100k = "Cumulative FDI projects per 100,000 people",

  log1p_mig_ratio_lt1 = "Log recent migration ratio",
  mig_share_total_migrants_lt1_pp = "Recent migrants as share of all migrants, percentage points",
  mig_share_ac_pop_lt1_pp = "Recent migrants as share of AC population, percentage points",

  log1p_mig_ratio_period = "Period-specific log migration ratio",
  mig_share_total_migrants_period_pp = "Period-specific migrant share of all migrants, percentage points",
  mig_share_ac_pop_period_pp = "Period-specific migrant share of AC population, percentage points",

  emp_rate = "Employment rate",
  m_emp_rate = "Male employment rate",
  sc_pop_share = "Scheduled Caste population share",
  st_pop_share = "Scheduled Tribe population share",
  con08_land_area = "Constituency land area",
  proxy_ac_pop = "Population",

  state_fe = "State fixed effects",
  year_fe = "Year fixed effects",
  pc_fe = "Parliamentary constituency fixed effects"
)

family_labels <- c(
  time_series = "AC time-series",
  assembly_xs = "AC cross-section",
  voter_logit = "Voter-level logit"
)

outcome_labels <- c(
  time_series = "Change in far-right vote share, 2009–2014",
  assembly_xs = "Far-right vote share",
  voter_logit = "Far-right vote"
)

subset_labels <- c(
  all = "All observations",
#  no_fdi_outliers = "Excluding top 1% cumulative FDI outliers",
  C_ac = "Centrist ACs",
  L_ac = "Left ACs",
  R_ac = "Right ACs",
  C_voter = "Centrist voters",
  L_voter = "Left voters",
  R_voter = "Right voters"
)

fdi_labels <- c(
  total = "Total FDI",
  mfg = "Manufacturing FDI",
  svc = "Services FDI"
)

mig_labels <- c(
  log_ratio = "Log migration ratio",
  share_mig = "Migrant share of all migrants",
  share_acpop = "Migrant share of AC population"
)

label_var <- function(x) {
  out <- unname(variable_labels[x])
  if_else(is.na(out), x, out)
}

label_subset <- function(x) {
  out <- unname(subset_labels[x])
  if_else(is.na(out), x, out)
}

label_family <- function(x) {
  out <- unname(family_labels[x])
  if_else(is.na(out), x, out)
}

label_fdi <- function(x) {
  out <- unname(fdi_labels[x])
  if_else(is.na(out), x, out)
}

label_mig <- function(x) {
  out <- unname(mig_labels[x])
  if_else(is.na(out), x, out)
}

coef_stars <- function(p) {
  case_when(
    is.na(p) ~ "",
    p < 0.001 ~ "***",
    p < 0.01 ~ "**",
    p < 0.05 ~ "*",
    TRUE ~ ""
  )
}

control_note <- paste(
  "Controls are employment rate, male employment rate, SC population share,",
  "ST population share, land area, and population."
)

stars_note <- "Standard errors in parentheses. * p<0.05, ** p<0.01, *** p<0.001."

subset_order <- c(
  "all",
#  "no_fdi_outliers",
  "C_ac",
  "L_ac",
  "R_ac",
  "C_voter",
  "L_voter",
  "R_voter"
)

fdi_order <- c("total", "mfg", "svc")
mig_order <- c("log_ratio", "share_mig", "share_acpop")
variant_order <- c("no_controls", "controls", "fe_controls")
```


```{r 20. Publication model runner}
# Fit exactly three specifications for each base model family:
# 1. No Controls
# 2. Controls
# 3. FE + Controls
#
# New FE choices:
# - time_series: state FE, absorbed using | state_fe
# - assembly_xs: year FE, included as RHS indicator year_fe
# - voter_logit: year FE, included as RHS indicator year_fe
#
# Standard errors:
# - No Controls and Controls: default, unclustered
# - FE + Controls:
#     * time_series: clustered by state_fe
#     * assembly_xs/logit: unclustered, because year FE has only two categories

required_report_pkgs <- c(
  "fixest",
  "broom",
  "marginaleffects",
  "insight",
  "gridExtra",
  "ggplot2"
)

missing_report_pkgs <- required_report_pkgs[
  !map_lgl(required_report_pkgs, requireNamespace, quietly = TRUE)
]

if (length(missing_report_pkgs) > 0) {
  stop(
    "Install required reporting packages: ",
    paste(missing_report_pkgs, collapse = ", ")
  )
}

make_publication_rhs <- function(fdi_var, mig_var,
                                 control_vars = character(0),
                                 rhs_fe_terms = character(0)) {
  rhs_terms <- c(
    str_c(fdi_var, " * ", mig_var),
    control_vars,
    rhs_fe_terms
  )

  rhs_terms <- rhs_terms[!is.na(rhs_terms) & rhs_terms != ""]

  str_c(rhs_terms, collapse = " + ")
}

make_publication_formula <- function(outcome, fdi_var, mig_var,
                                     control_vars = character(0),
                                     rhs_fe_terms = character(0),
                                     absorbed_fe_var = NULL) {
  rhs <- make_publication_rhs(
    fdi_var = fdi_var,
    mig_var = mig_var,
    control_vars = control_vars,
    rhs_fe_terms = rhs_fe_terms
  )

  if (is.null(absorbed_fe_var) || is.na(absorbed_fe_var) || absorbed_fe_var == "") {
    str_c(outcome, " ~ ", rhs)
  } else {
    str_c(outcome, " ~ ", rhs, " | ", absorbed_fe_var)
  }
}

fit_one_publication_model <- function(data, formula_string, estimator,
                                      vcov_var = NULL) {
  fml <- as.formula(formula_string)

  vcov_formula <- if (is.null(vcov_var) || is.na(vcov_var) || vcov_var == "") {
    NULL
  } else {
    as.formula(str_c("~", vcov_var))
  }

  if (estimator == "ols") {
    if (is.null(vcov_formula)) {
      return(fixest::feols(fml, data = data, warn = FALSE))
    } else {
      return(fixest::feols(fml, data = data, vcov = vcov_formula, warn = FALSE))
    }
  }

  if (estimator == "logit") {
    if (is.null(vcov_formula)) {
      return(fixest::feglm(
        fml,
        data = data,
        family = binomial("logit"),
        warn = FALSE
      ))
    } else {
      return(fixest::feglm(
        fml,
        data = data,
        family = binomial("logit"),
        vcov = vcov_formula,
        warn = FALSE
      ))
    }
  }

  stop("estimator must be 'ols' or 'logit'")
}

fit_publication_grid <- function(data, family_name, outcome, fdi_vars, mig_vars,
                                 subsets, estimator,
                                 absorbed_fe_var = NULL,
                                 rhs_fe_terms = character(0),
                                 vcov_var = NULL) {
  absorbed_fe_for_variant <- if (is.null(absorbed_fe_var)) NA_character_ else absorbed_fe_var
  vcov_for_variant <- if (is.null(vcov_var)) NA_character_ else vcov_var

  variants <- tibble(
    variant = c("no_controls", "controls", "fe_controls"),
    column_label = c("No Controls", "Controls", "FE + Controls"),
    control_vars = list(character(0), controls, controls),
    rhs_fe_terms = list(character(0), character(0), rhs_fe_terms),
    absorbed_fe_var = c(NA_character_, NA_character_, absorbed_fe_for_variant),
    vcov_var = c(NA_character_, NA_character_, vcov_for_variant),
    has_controls = c(FALSE, TRUE, TRUE),
    has_fe = c(FALSE, FALSE, TRUE)
  )

  expand_grid(
    subset_name = names(subsets),
    fdi_name = names(fdi_vars),
    mig_name = names(mig_vars),
    variant = variants$variant
  ) %>%
    left_join(variants, by = "variant") %>%
    mutate(
      family = family_name,
      model_type = estimator,
      fdi_var = unname(fdi_vars[fdi_name]),
      mig_var = unname(mig_vars[mig_name]),
      data_used = map(subset_name, \(x) subsets[[x]](data)),
      n_data = map_int(data_used, nrow),
      formula_string = pmap_chr(
        list(fdi_var, mig_var, control_vars, rhs_fe_terms, absorbed_fe_var),
        \(fdi_var, mig_var, control_vars, rhs_fe_terms, absorbed_fe_var) {
          make_publication_formula(
            outcome = outcome,
            fdi_var = fdi_var,
            mig_var = mig_var,
            control_vars = control_vars,
            rhs_fe_terms = rhs_fe_terms,
            absorbed_fe_var = absorbed_fe_var
          )
        }
      ),
      model = pmap(
        list(data_used, formula_string, vcov_var),
        \(data_used, formula_string, vcov_var) {
          tryCatch(
            fit_one_publication_model(
              data = data_used,
              formula_string = formula_string,
              estimator = estimator,
              vcov_var = vcov_var
            ),
            error = \(e) NULL
          )
        }
      ),
      base_spec_id = str_c(family, subset_name, fdi_name, mig_name, sep = "__"),
      model_id = str_c(family, subset_name, fdi_name, mig_name, variant, sep = "__")
    ) %>%
    select(
      family,
      base_spec_id,
      model_id,
      model_type,
      subset_name,
      fdi_name,
      mig_name,
      variant,
      column_label,
      has_controls,
      has_fe,
      control_vars,
      rhs_fe_terms,
      absorbed_fe_var,
      vcov_var,
      fdi_var,
      mig_var,
      n_data,
      formula_string,
      model
    )
}
```


```{r 21. Fit publication model grids}
# Fit 405 total regressions:
# 135 base model families × 3 columns per family.

ts_pub_models <- fit_publication_grid(
  data = ts_df,
  family_name = "time_series",
  outcome = "delta_fr_party_vote_share",
  fdi_vars = ts_fdi_vars,
  mig_vars = ts_mig_vars,
  subsets = ac_subsets,
  estimator = "ols",
  absorbed_fe_var = "state_fe",
  rhs_fe_terms = character(0),
  vcov_var = "state_fe"
)

xs_pub_models <- fit_publication_grid(
  data = xs_df,
  family_name = "assembly_xs",
  outcome = "fr_party_vote_share",
  fdi_vars = xs_fdi_vars,
  mig_vars = xs_mig_vars,
  subsets = ac_subsets,
  estimator = "ols",
  absorbed_fe_var = NULL,
  rhs_fe_terms = "year_fe",
  vcov_var = NULL
)

logit_pub_models <- fit_publication_grid(
  data = logit_df,
  family_name = "voter_logit",
  outcome = "fr_vote",
  fdi_vars = xs_fdi_vars,
  mig_vars = xs_mig_vars,
  subsets = voter_subsets,
  estimator = "logit",
  absorbed_fe_var = NULL,
  rhs_fe_terms = "year_fe",
  vcov_var = NULL
)

publication_models <- bind_rows(
  ts_pub_models,
  xs_pub_models,
  logit_pub_models
) %>%
  mutate(
    family_label = label_family(family),
    subset_label = label_subset(subset_name),
    fdi_label = label_fdi(fdi_name),
    migration_label = label_mig(mig_name),
    outcome_label = unname(outcome_labels[family])
  ) %>%
  arrange(
    match(family, c("time_series", "assembly_xs", "voter_logit")),
    match(subset_name, subset_order),
    match(fdi_name, fdi_order),
    match(mig_name, mig_order),
    match(variant, variant_order)
  )

publication_diagnostics <- publication_models %>%
  mutate(
    model_fit = !map_lgl(model, is.null),
    nobs = map_int(model, \(m) {
      if (is.null(m)) NA_integer_ else as.integer(stats::nobs(m))
    })
  ) %>%
  select(
    family,
    family_label,
    subset_name,
    subset_label,
    fdi_name,
    fdi_label,
    mig_name,
    migration_label,
    variant,
    column_label,
    n_data,
    nobs,
    model_fit,
    formula_string
  )

publication_diagnostics %>%
  summarise(
    n_models = n(),
    n_fit = sum(model_fit),
    min_nobs = min(nobs, na.rm = TRUE),
    median_nobs = median(nobs, na.rm = TRUE),
    max_nobs = max(nobs, na.rm = TRUE),
    .by = c(family_label, subset_label, column_label)
  ) %>%
  arrange(family_label, subset_label, column_label) %>%
  print(n = Inf)

publication_diagnostics %>%
  summarise(
    n_models = n(),
    n_fit = sum(model_fit),
    .by = family_label
  ) %>%
  print(n = Inf)
```


```{r 22. Publication table helpers}
# Convert fitted fixest models into journal-style four-column tables.

fmt_num <- function(x, digits = 3) {
  if (length(x) == 0 || is.na(x)) return("")
  formatC(x, digits = digits, format = "f")
}

fmt_obs <- function(x) {
  if (length(x) == 0 || is.na(x)) return("")
  format(x, big.mark = ",", scientific = FALSE, trim = TRUE)
}

get_tidy_safe <- function(model) {
  if (is.null(model)) return(tibble())
  tryCatch(
    broom::tidy(model),
    error = \(e) tibble()
  )
}

get_fitstat_numeric <- function(model, stat_types) {
  if (is.null(model)) return(NA_real_)

  for (stat_type in stat_types) {
    val <- tryCatch(
      fixest::fitstat(model, type = stat_type),
      error = \(e) NULL
    )

    if (!is.null(val)) {
      num <- suppressWarnings(as.numeric(unlist(val, use.names = FALSE)))
      num <- num[is.finite(num)]
      if (length(num) > 0) return(num[1])
    }
  }

  NA_real_
}

get_model_r2 <- function(model, model_type) {
  if (model_type == "logit") {
    get_fitstat_numeric(model, c("pr2", "r2"))
  } else {
    get_fitstat_numeric(model, c("r2"))
  }
}

get_coef_cell <- function(model, possible_terms) {
  tidied <- get_tidy_safe(model)

  if (nrow(tidied) == 0) return("")

  row <- tidied %>%
    filter(term %in% possible_terms) %>%
    slice_head(n = 1)

  if (nrow(row) == 0) return("")

  est <- fmt_num(row$estimate)
  se <- fmt_num(row$std.error)
  stars <- coef_stars(row$p.value)

  str_c(est, stars, "\n(", se, ")")
}

get_model_by_variant <- function(spec_models, variant_name) {
  out <- spec_models %>%
    filter(variant == variant_name) %>%
    pull(model)

  if (length(out) == 0) return(NULL)
  out[[1]]
}

get_nobs_by_variant <- function(spec_models, variant_name) {
  model <- get_model_by_variant(spec_models, variant_name)
  if (is.null(model)) return("")
  fmt_obs(as.integer(stats::nobs(model)))
}

get_r2_by_variant <- function(spec_models, variant_name) {
  model <- get_model_by_variant(spec_models, variant_name)
  model_type <- spec_models$model_type[1]
  fmt_num(get_model_r2(model, model_type))
}

make_publication_table_df <- function(spec_models) {
  fdi_var <- spec_models$fdi_var[1]
  mig_var <- spec_models$mig_var[1]

  no_controls_model <- get_model_by_variant(spec_models, "no_controls")
  controls_model <- get_model_by_variant(spec_models, "controls")
  fe_controls_model <- get_model_by_variant(spec_models, "fe_controls")

  model_list <- list(
    `No Controls` = no_controls_model,
    Controls = controls_model,
    `FE + Controls` = fe_controls_model
  )

  interaction_terms <- c(
    str_c(fdi_var, ":", mig_var),
    str_c(mig_var, ":", fdi_var)
  )

  table_rows <- tibble(
    Variables = c(
      "Intercept",
      label_var(mig_var),
      label_var(fdi_var),
      str_c(label_var(mig_var), " × ", label_var(fdi_var)),
      "Controls",
      "FE",
      "Obs",
      "R²"
    ),
    `No Controls` = c(
      get_coef_cell(no_controls_model, c("(Intercept)")),
      get_coef_cell(no_controls_model, mig_var),
      get_coef_cell(no_controls_model, fdi_var),
      get_coef_cell(no_controls_model, interaction_terms),
      "",
      "",
      get_nobs_by_variant(spec_models, "no_controls"),
      get_r2_by_variant(spec_models, "no_controls")
    ),
    Controls = c(
      get_coef_cell(controls_model, c("(Intercept)")),
      get_coef_cell(controls_model, mig_var),
      get_coef_cell(controls_model, fdi_var),
      get_coef_cell(controls_model, interaction_terms),
      "X",
      "",
      get_nobs_by_variant(spec_models, "controls"),
      get_r2_by_variant(spec_models, "controls")
    ),
    `FE + Controls` = c(
      get_coef_cell(fe_controls_model, c("(Intercept)")),
      get_coef_cell(fe_controls_model, mig_var),
      get_coef_cell(fe_controls_model, fdi_var),
      get_coef_cell(fe_controls_model, interaction_terms),
      "X",
      "X",
      get_nobs_by_variant(spec_models, "fe_controls"),
      get_r2_by_variant(spec_models, "fe_controls")
    )
  )

  table_rows
}
```


```{r 23. Discrete marginal effects}
# Compute discrete marginal effects of FDI at selected values of migration.
# These are used for the plot attached to each table page.
#
# For OLS models, marginal effects are on the outcome scale.
# For logit models, marginal effects are on the response/probability scale.

mfx_probs <- c(0.10, 0.25, 0.50, 0.75, 0.90)

mfx_prob_labels <- c(
  "p10",
  "p25",
  "p50",
  "p75",
  "p90"
)

get_model_data_safe <- function(model) {
  tryCatch(
    insight::get_data(model),
    error = \(e) NULL
  )
}

make_discrete_fdi_mfx_data <- function(model, model_type, fdi_var, mig_var,
                                       probs = mfx_probs,
                                       prob_labels = mfx_prob_labels) {
  if (is.null(model)) {
    return(tibble(error = "model is NULL"))
  }

  model_data <- get_model_data_safe(model)

  if (is.null(model_data) || !mig_var %in% names(model_data)) {
    return(tibble(error = "migration variable not found in model data"))
  }

  migration_values <- quantile(
    model_data[[mig_var]],
    probs = probs,
    na.rm = TRUE,
    names = FALSE
  )

  condition_grid <- tibble(
    prob = probs,
    point_label = prob_labels,
    condition_value = as.numeric(migration_values)
  ) %>%
    filter(!is.na(condition_value)) %>%
    distinct(condition_value, .keep_all = TRUE) %>%
    mutate(
      x_label = str_c(point_label, "\n", signif(condition_value, 4))
    )

  if (nrow(condition_grid) == 0) {
    return(tibble(error = "no valid migration values"))
  }

  newdata_args <- c(
    list(model = model),
    setNames(list(condition_grid$condition_value), mig_var)
  )

  newdata <- tryCatch(
    do.call(marginaleffects::datagrid, newdata_args),
    error = \(e) NULL
  )

  if (is.null(newdata)) {
    return(tibble(error = "could not create marginal-effects grid"))
  }

  mfx_args <- list(
    model = model,
    variables = fdi_var,
    newdata = newdata
  )

  if (model_type == "logit") {
    mfx_args$type <- "response"
  }

  mfx <- tryCatch(
    do.call(marginaleffects::slopes, mfx_args),
    error = \(e) e
  )

  if (inherits(mfx, "error")) {
    return(tibble(error = mfx$message))
  }

  mfx_tbl <- as_tibble(mfx)

  if (!"estimate" %in% names(mfx_tbl)) {
    return(tibble(error = "marginaleffects did not return estimates"))
  }

  if (!"conf.low" %in% names(mfx_tbl) && "std.error" %in% names(mfx_tbl)) {
    mfx_tbl <- mfx_tbl %>%
      mutate(
        conf.low = estimate - 1.96 * std.error,
        conf.high = estimate + 1.96 * std.error
      )
  }

  if (mig_var %in% names(mfx_tbl)) {
    mfx_tbl <- mfx_tbl %>%
      mutate(condition_value = .data[[mig_var]])
  } else {
    mfx_tbl <- mfx_tbl %>%
      mutate(condition_value = condition_grid$condition_value[seq_len(n())])
  }

  mfx_tbl %>%
    left_join(condition_grid, by = "condition_value") %>%
    mutate(error = NA_character_) %>%
    select(
      point_label,
      x_label,
      condition_value,
      estimate,
      std.error,
      conf.low,
      conf.high,
      p.value,
      error
    )
}

make_discrete_fdi_mfx_plot <- function(spec_models) {
  fe_model_row <- spec_models %>%
    filter(variant == "fe_controls") %>%
    slice_head(n = 1)

  if (nrow(fe_model_row) == 0 || is.null(fe_model_row$model[[1]])) {
    return(
      ggplot() +
        annotate("text", x = 0, y = 0, label = "FE + Controls model not available") +
        theme_void()
    )
  }

  mfx_data <- make_discrete_fdi_mfx_data(
    model = fe_model_row$model[[1]],
    model_type = fe_model_row$model_type,
    fdi_var = fe_model_row$fdi_var,
    mig_var = fe_model_row$mig_var
  )

  if ("error" %in% names(mfx_data) && all(!is.na(mfx_data$error))) {
    return(
      ggplot() +
        annotate("text", x = 0, y = 0, label = str_c("Marginal-effects error:\n", mfx_data$error[1])) +
        theme_void()
    )
  }

  mfx_data <- mfx_data %>%
    filter(is.na(error)) %>%
    mutate(
      x_label = factor(x_label, levels = x_label)
    )

  ggplot(mfx_data, aes(x = x_label, y = estimate)) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.15) +
    geom_point(size = 2) +
    labs(
      title = str_c(
        "Marginal effect of ",
        label_var(fe_model_row$fdi_var),
        " at selected migration values"
      ),
      subtitle = "Estimated from the FE + Controls specification",
      x = str_c(label_var(fe_model_row$mig_var), " held constant"),
      y = str_c("Marginal effect of ", label_var(fe_model_row$fdi_var))
    ) +
    theme_minimal(base_size = 10) +
    theme(
      plot.title = element_text(face = "bold"),
      axis.text.x = element_text(size = 8)
    )
}
```


```{r 24. PDF page helpers}
# Build one PDF page per base family:
# top = journal-style regression table
# bottom = discrete marginal-effects plot

make_table_grob <- function(table_df) {
  theme <- gridExtra::ttheme_minimal(
    base_size = 8,
    core = list(
      fg_params = list(
        fontsize = 7,
        lineheight = 0.9
      )
    ),
    colhead = list(
      fg_params = list(
        fontsize = 8,
        fontface = "bold"
      )
    )
  )

  table_grob <- gridExtra::tableGrob(
    table_df,
    rows = NULL,
    theme = theme
  )

  table_grob
}

make_page_title <- function(spec_models, table_number, total_tables) {
  row <- spec_models %>% slice_head(n = 1)

  str_c(
    row$family_label,
    " — Table ",
    table_number,
    " of ",
    total_tables,
    "\nSubset: ",
    row$subset_label,
    " | FDI: ",
    row$fdi_label,
    " | Migration: ",
    row$migration_label,
    "\nOutcome: ",
    row$outcome_label
  )
}

make_page_note <- function(family_name) {
  r2_note <- if (family_name == "voter_logit") {
    "For logit models, R² reports pseudo R². Logit table coefficients are log-odds; marginal-effects plots are on the probability scale."
  } else {
    "R² reports ordinary model R²."
  }

  fe_note <- case_when(
    family_name == "time_series" ~ "FE denotes state fixed effects.",
    family_name %in% c("assembly_xs", "voter_logit") ~ "FE denotes year fixed effects included as RHS indicators.",
    TRUE ~ "FE denotes fixed effects."
  )

  str_c(
    stars_note,
    " ",
    control_note,
    " ",
    fe_note,
    " ",
    r2_note
  )
}

draw_table_plot_page <- function(spec_models, table_number, total_tables) {
  table_df <- make_publication_table_df(spec_models)
  table_grob <- make_table_grob(table_df)
  plot_grob <- make_discrete_fdi_mfx_plot(spec_models)

  title_grob <- grid::textGrob(
    make_page_title(spec_models, table_number, total_tables),
    x = 0,
    hjust = 0,
    gp = grid::gpar(fontsize = 11, fontface = "bold")
  )

  note_grob <- grid::textGrob(
    make_page_note(spec_models$family[1]),
    x = 0,
    hjust = 0,
    gp = grid::gpar(fontsize = 7),
    just = "left"
  )

  page_grob <- gridExtra::arrangeGrob(
    title_grob,
    table_grob,
    plot_grob,
    note_grob,
    ncol = 1,
    heights = c(0.13, 0.42, 0.38, 0.07)
  )

  grid::grid.newpage()
  grid::grid.draw(page_grob)
}
```


```{r 25. Render publication PDFs}
# Render three boss-facing PDF reports:
# 1. 45 time-series tables
# 2. 45 cross-section tables
# 3. 45 logit tables

publication_report_dir <- "outputs/boss_publication_regression_tables"
dir.create(publication_report_dir, recursive = TRUE, showWarnings = FALSE)

render_family_pdf <- function(publication_models, family_name, output_file) {
  family_models <- publication_models %>%
    filter(family == family_name)

  page_index <- family_models %>%
    distinct(
      base_spec_id,
      family,
      family_label,
      subset_name,
      subset_label,
      fdi_name,
      fdi_label,
      mig_name,
      migration_label,
      outcome_label
    ) %>%
    arrange(
      match(subset_name, subset_order),
      match(fdi_name, fdi_order),
      match(mig_name, mig_order)
    )

  total_tables <- nrow(page_index)

  grDevices::pdf(
    file = output_file,
    width = 11,
    height = 8.5,
    onefile = TRUE
  )

  on.exit(grDevices::dev.off(), add = TRUE)

  walk(seq_len(total_tables), \(i) {
    spec_id <- page_index$base_spec_id[i]

    spec_models <- family_models %>%
      filter(base_spec_id == spec_id) %>%
      arrange(match(variant, variant_order))

    draw_table_plot_page(
      spec_models = spec_models,
      table_number = i,
      total_tables = total_tables
    )
  })

  invisible(output_file)
}

time_series_pdf <- file.path(
  publication_report_dir,
  "time_series_publication_tables.pdf"
)

cross_section_pdf <- file.path(
  publication_report_dir,
  "cross_section_publication_tables.pdf"
)

logit_pdf <- file.path(
  publication_report_dir,
  "logit_publication_tables.pdf"
)

render_family_pdf(
  publication_models = publication_models,
  family_name = "time_series",
  output_file = time_series_pdf
)

render_family_pdf(
  publication_models = publication_models,
  family_name = "assembly_xs",
  output_file = cross_section_pdf
)

render_family_pdf(
  publication_models = publication_models,
  family_name = "voter_logit",
  output_file = logit_pdf
)

message("Wrote time-series PDF to: ", time_series_pdf)
message("Wrote cross-section PDF to: ", cross_section_pdf)
message("Wrote logit PDF to: ", logit_pdf)
```


```{r 26. Save report diagnostics and index files}
# Save machine-readable indices alongside the PDFs.

publication_index <- publication_models %>%
  mutate(
    model_fit = !map_lgl(model, is.null),
    nobs = map_int(model, \(m) if (is.null(m)) NA_integer_ else as.integer(stats::nobs(m))),
    r2 = map2_dbl(model, model_type, get_model_r2)
  ) %>%
  select(
    family,
    family_label,
    base_spec_id,
    model_id,
    subset_name,
    subset_label,
    fdi_name,
    fdi_label,
    mig_name,
    migration_label,
    variant,
    column_label,
    has_controls,
    has_fe,
    n_data,
    nobs,
    r2,
    model_fit,
    formula_string
  )

readr::write_csv(
  publication_index,
  file.path(publication_report_dir, "publication_model_index.csv")
)

publication_summary <- publication_index %>%
  summarise(
    n_models = n(),
    n_fit = sum(model_fit),
    min_nobs = min(nobs, na.rm = TRUE),
    median_nobs = median(nobs, na.rm = TRUE),
    max_nobs = max(nobs, na.rm = TRUE),
    .by = c(family_label, subset_label, column_label)
  ) %>%
  arrange(family_label, subset_label, column_label)

readr::write_csv(
  publication_summary,
  file.path(publication_report_dir, "publication_model_summary.csv")
)

publication_summary %>%
  print(n = Inf)
```


```{r 27. Review generated report files}
# Compact final check.

list.files(publication_report_dir, full.names = TRUE)

publication_index %>%
  summarise(
    n_base_families = n_distinct(base_spec_id),
    n_regressions = n(),
    n_fit = sum(model_fit),
    .by = family_label
  ) %>%
  print(n = Inf)
```

```{r}
# Centrist policy-response profiles --------------------------------------

# Questions included in each election year
centrist_items <- list(
  `2009` = c(
    "q26a", "a4b", "a4c", "a4d", "a4g"
  ),
  `2014` = c(
    "q10b", "q10e", "q23c"
  )
)

# Display labels for the facets.
# Replace these abbreviated labels with the full question wording
# from the Lokniti questionnaire when preparing final figures.
item_labels <- c(
  q26a = "Q26a",
  a4b  = "A4b",
  a4c  = "A4c",
  a4d  = "A4d",
  a4g  = "A4g",
  q10b = "Q10b",
  q10e = "Q10e",
  q23c = "Q23c"
)

# Generic labels based on the direction of your recoding.
#
# Using "negative-coded" and "positive-coded" avoids incorrectly
# calling every response "left" or "right" before inserting the
# substantive wording for each question.
response_labels <- c(
  `-2` = "Strongly negative-coded",
  `-1` = "Negative-coded",
  `0`  = "Don't know / no opinion",
  `1`  = "Positive-coded",
  `2`  = "Strongly positive-coded"
)

make_centrist_profile_data <- function(
  data,
  year_value,
  items,
  weight_var = NULL
) {
  
  profile_data <- data %>%
    filter(
      year == year_value,
      voter_ideology == "C"
    ) %>%
    select(
      year,
      voter_ideology,
      all_of(items),
      any_of(weight_var)
    ) %>%
    pivot_longer(
      cols = all_of(items),
      names_to = "item",
      values_to = "response"
    ) %>%
    filter(!is.na(response)) %>%
    mutate(
      item = factor(
        item,
        levels = items,
        labels = unname(item_labels[items])
      ),
      response = as.integer(response)
    )
  
  # Calculate either unweighted or survey-weighted counts
  if (is.null(weight_var)) {
    
    profile_data <- profile_data %>%
      count(item, response, name = "weighted_n")
    
  } else {
    
    profile_data <- profile_data %>%
      mutate(
        analysis_weight = as.numeric(.data[[weight_var]])
      ) %>%
      filter(
        !is.na(analysis_weight),
        analysis_weight > 0
      ) %>%
      count(
        item,
        response,
        wt = analysis_weight,
        name = "weighted_n"
      )
  }
  
  profile_data %>%
    # Make absent response categories explicit.
    # This keeps colors and legends consistent across questions.
    complete(
      item,
      response = -2:2,
      fill = list(weighted_n = 0)
    ) %>%
    group_by(item) %>%
    mutate(
      share = weighted_n / sum(weighted_n),
      item_n = sum(weighted_n)
    ) %>%
    ungroup() %>%
    mutate(
      response = factor(
        response,
        levels = -2:2,
        labels = unname(response_labels)
      )
    )
}

plot_centrist_profile <- function(
  profile_data,
  year_value,
  weighted = FALSE
) {
  
  ggplot(
    profile_data,
    aes(
      x = share,
      y = item,
      fill = response
    )
  ) +
    geom_col(
      width = 0.72,
      position = "stack"
    ) +
    scale_x_continuous(
      labels = percent_format(accuracy = 1),
      expand = expansion(mult = c(0, 0.01))
    ) +
    scale_fill_brewer(
      palette = "RdBu",
      direction = -1,
      drop = FALSE
    ) +
    labs(
      title = paste0(
        "Policy-response profiles of centrist voters, ",
        year_value
      ),
      subtitle = paste0(
        if_else(
          weighted,
          "Survey-weighted",
          "Unweighted"
        ),
        " shares among respondents classified as centrist"
      ),
      x = "Share of centrist respondents",
      y = NULL,
      fill = "Response category",
      caption = paste0(
        "Centrist status is based on the Recognition and Statism indices. ",
        "The zero category represents don't know or no opinion, not necessarily ",
        "a substantively moderate policy position."
      )
    ) +
    theme_minimal(base_size = 12) +
    theme(
      panel.grid.major.y = element_blank(),
      panel.grid.minor = element_blank(),
      legend.position = "bottom",
      legend.box = "vertical",
      plot.title.position = "plot",
      plot.caption = element_text(hjust = 0)
    ) +
    guides(
      fill = guide_legend(
        nrow = 2,
        byrow = TRUE
      )
    )
}

centrist_profile_2009 <- make_centrist_profile_data(
  data = nes_clean,
  year_value = 2009,
  items = centrist_items[["2009"]]
)

centrist_profile_2014 <- make_centrist_profile_data(
  data = nes_clean,
  year_value = 2014,
  items = centrist_items[["2014"]]
)

fig_centrist_profile_2009 <- plot_centrist_profile(
  profile_data = centrist_profile_2009,
  year_value = 2009,
  weighted = FALSE
)

fig_centrist_profile_2014 <- plot_centrist_profile(
  profile_data = centrist_profile_2014,
  year_value = 2014,
  weighted = FALSE
)

fig_centrist_profile_2009
fig_centrist_profile_2014

ggsave(
  filename = "output/figures/centrist_policy_profiles_2009.png",
  plot = fig_centrist_profile_2009,
  width = 10,
  height = 6.5,
  dpi = 300
)

ggsave(
  filename = "output/figures/centrist_policy_profiles_2014.png",
  plot = fig_centrist_profile_2014,
  width = 10,
  height = 4.5,
  dpi = 300
)
```


