---
title: "Switchers India: Data Construction"
output:
  html_document:
    keep_md: true
date: "`r Sys.Date()`"
---

This script imports, cleans, harmonizes, and validates all raw data used in the
Switchers India analysis. It writes model-ready AC-year levels, first-difference,
voter-level, grouped ideology-cell, and ideology-item datasets to
`data/derived/switchers/`.

Centering constants are calculated once from unique AC-year rows and then reused
for every lower-level dataset. The script intentionally does not estimate
regressions or create publication reports. Those tasks are performed in
`Switchers-India-Analysis-Replacement.Rmd`.

```{r 1-load-libraries, message = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)



library(tidyverse)
library(sf)
library(readxl)
library(haven)
library(janitor)
library(lubridate)

DERIVED_DIR <- "data/derived/switchers"
DIAGNOSTIC_DIR <- file.path(DERIVED_DIR, "diagnostics")
dir.create(DERIVED_DIR, recursive = TRUE, showWarnings = FALSE)
dir.create(DIAGNOSTIC_DIR, recursive = TRUE, showWarnings = FALSE)
```


```{r 2-shared-helpers}
# Define reusable import, cleaning, recoding, and grouping helpers.
# These replace repeated state-code maps, file-binding loops, and ideology logic.

read_many <- function(path, pattern, reader = readr::read_csv, ..., ignore.case = TRUE) {
  list.files(path, pattern, recursive = TRUE, full.names = TRUE, ignore.case = ignore.case) %>%
    map_dfr(\(f) reader(f, ...))
}

read_many_sf <- function(path, pattern, ..., ignore.case = TRUE) {
  list.files(path, pattern, recursive = TRUE, full.names = TRUE, ignore.case = ignore.case) %>%
    map(read_sf, ...) %>%
    bind_rows()
}

clean_num <- function(x) {
  x %>%
    as.character() %>%
    str_squish() %>%
    na_if("") %>%
    na_if("-") %>%
    parse_number()
}

first_nonmissing <- function(x) {
  dplyr::first(x[!is.na(x)], default = NA)
}

safe_mean <- function(x) {
  out <- mean(x, na.rm = TRUE)
  if_else(is.nan(out), NA_real_, out)
}

safe_z <- function(x) {
  x <- as.numeric(x)
  s <- sd(x, na.rm = TRUE)
  if (is.na(s) || s == 0) rep(NA_real_, length(x)) else (x - mean(x, na.rm = TRUE)) / s
}

norm_name <- function(x) {
  x %>%
    as.character() %>%
    str_remove_all("\\*") %>%
    str_to_upper() %>%
    str_replace_all("&", "AND") %>%
    str_replace_all("[^A-Z0-9]+", " ") %>%
    str_squish()
}

norm_delhi_dist <- function(x) {
  norm_name(x) %>%
    str_remove("\\s+DISTRICT$") %>%
    str_remove("\\s+DELHI$") %>%
    str_remove("^DELHI\\s+")
}

state_codes <- c(
  "Andaman & Nicobar Islands" = 35,
  "Andhra Pradesh" = 28,
  "Arunachal Pradesh" = 12,
  "Assam" = 18,
  "Bihar" = 10,
  "Chandigarh" = 4,
  "Chhattisgarh" = 22,
  "Dadra & Nagar Haveli" = 26,
  "Daman & Diu" = 25,
  "Delhi" = 7,
  "Goa" = 30,
  "Gujarat" = 24,
  "Haryana" = 6,
  "Himachal Pradesh" = 2,
  "Jammu & Kashmir" = 1,
  "Jharkhand" = 20,
  "Karnataka" = 29,
  "Kerala" = 32,
  "Lakshadweep" = 31,
  "Madhya Pradesh" = 23,
  "Maharashtra" = 27,
  "Manipur" = 14,
  "Meghalaya" = 17,
  "Mizoram" = 15,
  "Nagaland" = 13,
  "Odisha" = 21,
  "Orissa" = 21,
  "Puducherry" = 34,
  "Punjab" = 3,
  "Rajasthan" = 8,
  "Sikkim" = 11,
  "Tamil Nadu" = 33,
  "Telangana" = 28,
  "Tripura" = 16,
  "Uttar Pradesh" = 9,
  "Uttarakhand" = 5,
  "West Bengal" = 19
)

state_name_to_no <- function(x) {
  x <- str_replace_all(as.character(x), "_", " ")
  as.numeric(unname(state_codes[x]))
}

ideology_group <- function(recognition, statism, cut = 0.25) {
  has_both_axes <- !is.na(recognition) & !is.na(statism)
  inside <- function(x) x > -cut & x < cut
  above  <- function(x) x > cut
  below  <- function(x) x < -cut

  case_when(
    has_both_axes & inside(recognition) & inside(statism) ~ "C",
    has_both_axes & above(recognition)  & above(statism)  ~ "R",
    has_both_axes & below(recognition)  & below(statism)  ~ "L",
    TRUE ~ NA_character_
  )
}

row_mean_valid <- function(data, min_valid = 1L) {
  data <- as.data.frame(data)
  n_valid <- rowSums(!is.na(data))
  out <- rowMeans(data, na.rm = TRUE)
  out[n_valid < min_valid | is.nan(out)] <- NA_real_
  out
}

variable_label <- function(x, fallback) {
  label <- attr(x, "label")
  if (is.null(label) || length(label) == 0 || is.na(label) || label == "") {
    fallback
  } else {
    as.character(label)
  }
}

make_code_key <- function(x) {
  if_else(is.na(x), NA_character_, paste0("CODE_", as.integer(x)))
}

district_name_key <- function(x) {
  paste0("NAME_", norm_name(x))
}
```


```{r 3-load-assembly-constituency-level-data, message = FALSE}
# Load AC election, map, crosswalk, FDI, and population inputs.
# Use vectorized file import instead of hand-written rbind loops.

pc_elections <- read_csv("data/election/lok_dhaba_ge.csv", show_col_types = FALSE)

ac_map <- read_many_sf(
  "data/election/2014_shp",
  pattern = "\\.assembly\\.shp$"
)

ac_name_key <- read_csv("data/shrug/ac08_name_key.csv", show_col_types = FALSE)

ac_xwalk <- read_sf("data/assembly-constituencies/India_AC.shp")
fdi <- read_csv("data/IN_FDI_2004_2014.csv", show_col_types = FALSE)
ac_pop <- read_csv("data/shrug/con08_pop_area_key.csv", show_col_types = FALSE)
```


```{r 4a-load-district-demographic-inputs, message = FALSE}
# Load district-level census, employment, population, and migration files.
# Cleaning functions below standardize messy Census tables before joining.

districts <- read_xlsx("data/dist_codes.xlsx")
econ_census <- read_csv("data/shrug/ec13_pc11dist.csv", show_col_types = FALSE)
pop <- read_csv("data/pop/pop.csv", show_col_types = FALSE)
```

```{r 4b-clean-district-sc-st-files, message = FALSE}
# Clean census appendix files for district SC/ST population.
# One cleaner handles both tables because their layouts are identical.

clean_group_file <- function(path, code_col, keep_code, out_col) {
  read_excel(path, col_names = FALSE, col_types = "text") %>%
    select(2:10) %>%
    set_names(c(
      "state_code", "district_code", "area_name", code_col, "group_name",
      "area_type", "persons", "males", "females"
    )) %>%
    mutate(across(everything(), ~ str_squish(as.character(.x)))) %>%
    filter(area_type == "Total", district_code != "00", .data[[code_col]] == keep_code) %>%
    transmute(
  state_code,
  district_code,
  district_no_local = as.double(str_remove(district_code, "^0+")),
  district_name = area_name %>%
    str_remove("^District\\s*-\\s*") %>%
    str_remove("\\s+\\d{3}$") %>%
    str_squish(),
  dist_code_2011 = str_extract(area_name, "\\d{3}$"),
  "{out_col}" := clean_num(persons)
)
}

sc_pop <- read_many(
  "data/pop/sc_pop",
  "-PCA-A10-APPENDIX\\.xlsx$",
  \(f) clean_group_file(f, "sc_code", "000", "sc_persons")
)

st_pop <- read_many(
  "data/pop/st_pop",
  "-PCA-A11-APPENDIX\\.xlsx$",
  \(f) clean_group_file(f, "st_code", "500", "st_persons")
)
```


```{r 4c-clean-district-population-change, message = FALSE}
# Clean district population change tables and keep 2011 rows.
# The output gives district population and decadal population growth.

clean_pop_change_file <- function(path) {
  read_excel(path, col_names = FALSE, col_types = "text") %>%
    select(1:9) %>%
    set_names(c(
      "state_code", "district_code", "district_name", "census_year",
      "persons", "abs_change_from_last_census", "pct_change_from_last_census",
      "males", "females"
    )) %>%
    mutate(across(everything(), ~ str_squish(as.character(.x)))) %>%
    filter(str_detect(census_year, "^\\d{4}\\*?$")) %>%
    fill(state_code, district_code, district_name, .direction = "down") %>%
    filter(district_code != "000") %>%
    mutate(
      census_year = as.integer(str_remove(census_year, "\\*")),
      across(c(persons, abs_change_from_last_census, pct_change_from_last_census, males, females), clean_num)
    )
}

pop_change <- read_many("data/pop/pop_change", "\\.xlsx?$", clean_pop_change_file) %>%
  filter(census_year == 2011) %>%
  select(
    state_code,
    district_code,
    district_name,
    district_pop_2011 = persons,
    pct_change_from_last_census
  )
```


```{r 4d-clean-district-migration-stocks, message = FALSE}
# Clean 2011 district migration stock tables.
# Keep interstate migrants and the duration bands used downstream.

migration_cols <- c(
  "state_code", "district_code", "area_name", "last_residence",
  "last_residence_type", "place_of_enumeration",
  "2011_Total_Persons", "2011_Total_Males", "2011_Total_Females",
  "2011_Total_Persons_<1", "2011_Total_Males_<1", "2011_Total_Females_<1",
  "2011_Total_Persons_1-4", "2011_Total_Males_1-4", "2011_Total_Females_1-4",
  "2011_Total_Persons_5-9", "2011_Total_Males_5-9", "2011_Total_Females_5-9",
  "2011_Total_Persons_10-19", "2011_Total_Males_10-19", "2011_Total_Females_10-19",
  "2011_Total_Persons_>20", "2011_Total_Males_>20", "2011_Total_Females_>20",
  "2011_Total_Persons_NK", "2011_Total_Males_NK", "2011_Total_Females_NK"
)

clean_migration_file <- function(path) {
  read_excel(path, col_names = FALSE, col_types = "text") %>%
    select(2:28) %>%
    set_names(migration_cols) %>%
    mutate(across(everything(), ~ str_squish(as.character(.x)))) %>%
    filter(str_detect(state_code, "^\\d+$"), str_detect(district_code, "^\\d{3}$"), district_code != "000") %>%
    mutate(across(starts_with("2011_"), clean_num))
}

migration <- read_many("data/pop/migration", "\\.xlsx?$", clean_migration_file) %>%
  filter(
    last_residence == "States in India beyond the state of enumeration",
    last_residence_type == "Total",
    place_of_enumeration == "Total"
  ) %>%
  transmute(
    state_code,
    district_code,
    district_name = as.character(area_name),
    `2011_Total_Persons`,
    `2011_Total_Persons_<1`,
    `2011_Total_Persons_1-4`,
    `2011_Total_Persons_5-9`,
    `2011_Total_Persons_10-19`,
    `2011_Total_Persons_>20`
  )
```


```{r 4e-clean-district-migration-change, message = FALSE}
# Load district migration change files and keep interstate total migration.
# Replaces the manual for-loop rbind with one map_dfr call.

mig_change <- read_many(
  "data/pop/migration_change",
  "_2001_2011_merged\\.csv$",
  read_csv,
  show_col_types = FALSE
) %>%
  filter(
    Last_Residence == "STATES IN INDIA BEYOND THE STATE OF ENUMERATION",
    Last_Residence_Type == "TOTAL",
    Enumeration_Site_Type == "TOTAL"
  ) %>%
  transmute(
    `2011_District` = as.character(`2011_District`),
    `2011_Area`,
    `delta_Total_Persons`,
    `delta_Total_Persons_<1`,
    `delta_Total_Persons_1-4`,
    `delta_Total_Persons_5-9`,
    `delta_Total_Persons_10-19`
  )
```


```{r 5-load-district-level-gdp-data, message = FALSE}
# Load district GDP levels and reshape district GDP growth files.
# Keep growth files long because column names are district names.

gdp <- read_csv("data/gdp/gdp.csv", show_col_types = FALSE)

clean_gdp_change_file <- function(path) {
  read_csv(path, show_col_types = FALSE) %>%
    rename(year = 1, description = 2) %>%
    rename_with(str_squish) %>%
    pivot_longer(-c(year, description), names_to = "district", values_to = "value") %>%
    transmute(
      year,
      description,
      district = str_squish(district),
      value = parse_number(as.character(value)),
      source_file = basename(path)
    ) %>%
    filter(!is.na(value))
}

gdp_change <- read_many("data/gdp/gdp_change", "\\.csv$", clean_gdp_change_file)
```


```{r 6-load-survey-and-additional-data, message = FALSE}
# Load Lokniti survey files and assembly election returns.
# Polling-station returns are not loaded until they are used.

nes_2009 <- read_sav("data/lokniti/nes_2009.sav")
nes_2014 <- read_sav("data/lokniti/nes_2014.sav")

ac_elections <- read_csv("data/election/lok_dhaba_ae.csv", show_col_types = FALSE)
```


```{r 7-clean-ac-map}
# Add numeric state and PC identifiers to the AC map.
# Geometry repair stays here because this map anchors spatial joins.

ac_map_clean <- ac_map %>%
  mutate(
    state_no = state_name_to_no(state),
    pc = as.double(pc)
  ) %>%
  st_make_valid()
```


```{r 8a-crosswalk-constants}
# Define special cases for district joins and states with true zero SC/ST populations.
# These are substantive harmonization choices, so keep them explicit.

zero_st_states <- c(7, 3, 6, 34) # Delhi, Punjab, Haryana, Puducherry
zero_sc_states <- c(12, 13)      # Arunachal Pradesh, Nagaland

gdp_name_override <- tribble(
  ~state_no, ~census_dist_norm, ~gdp_dist_norm,
  24, "AHMADABAD",      "AHMEDABAD",
  24, "KACHCHH",        "KUTCH",
  24, "BANAS KANTHA",   "BANASKANTHA",
  24, "SABAR KANTHA",   "SABARKANTHA",
  24, "MAHESANA",       "MEHSANA",
  24, "DOHAD",          "DAHOD",
  19, "BARDHMAN",       "BURDWAN",
  19, "BARDHAMAN",      "BURDWAN",
  19, "BARDDHAMAN",     "BURDWAN",
  19, "HUGLI",          "HOOGHLY",
  19, "HAORA",          "HOWRAH",
  19, "DARJILING",      "DARJEELING",
  19, "KOCH BIHAR",     "COOCH BEHAR",
  33, "KANNIYAKUMARI",  "KANYAKUMARI",
  29, "BANGALORE",      "BANGALORE URBAN",
  29, "CHIKMAGALUR",    "CHICKMAGALUR",
  29, "CHAMARAJANAGAR", "CHAMARAJA NAGAR",
  27, "NASHIK",         "NASIK",
  27, "BID",            "BEED",
  27, "RAIGARH",        "RAIGAD",
  27, "AHMADNAGAR",     "AHMEDNAGAR",
  6,  "SONIPAT",        "SONEPAT",
  6,  "HISAR",          "HISSAR",
  32, "ERNAKULAM",      "ERANAKULAM"
)
```


```{r 8b-build-district-gdp-per-capita}
# Calculate district per-capita GDP for 2009 and 2013.
# Names are normalized here so GDP can join to Census districts.

pc_gdp <- gdp %>%
  filter(Year %in% c("2009 (2004)", "2013 (2004)")) %>%
  transmute(
    state_no = state_name_to_no(`State Name`),
    gdp_state_name = `State Name`,
    gdp_dist_name = `Dist Name`,
    gdp_dist_norm = norm_name(`Dist Name`),
    `Dist Code`,
    gdp_year = str_extract(Year, "^\\d{4}"),
    gdp = `TOTAL CONSTANT PRICES (Millions in Rs)` * 1e6
  ) %>%
  left_join(pop, by = "Dist Code") %>%
  mutate(
    pc_gdp = gdp / (`TOTAL POPULATION (1000 Number)` * 1000),
    pc_gdp_col = paste0("pc_gdp_", gdp_year)
  ) %>%
  select(state_no, gdp_state_name, gdp_dist_name, gdp_dist_norm, pc_gdp_col, pc_gdp) %>%
  pivot_wider(names_from = pc_gdp_col, values_from = pc_gdp)
```


```{r 8c-build-district-demographic-crosswalk}
# Merge district-level economic, caste, migration, population, and GDP variables.
# The output is one district-level table ready for AC allocation.

dist_xwalk <- districts %>%
  filter(`District Code` != "000", `Sub District Code` == "00000") %>%
  distinct(`District Code`, .keep_all = TRUE) %>%
  transmute(
    `State Code`,
    `District Code`,
    `Town-Village Name`,
    state_no = as.double(`State Code`),
    census_dist_norm = norm_name(`Town-Village Name`)
  )

pop_change_name <- pop_change %>%
  transmute(
    state_no = as.double(state_code),
    census_dist_norm = norm_name(district_name),
    district_pop_2011_name = district_pop_2011,
    pct_change_from_last_census_name = pct_change_from_last_census
  )

demog_dist_xwalk <- dist_xwalk %>%
  left_join(
    econ_census,
    by = c(
      "State Code" = "pc11_state_id",
      "District Code" = "pc11_district_id"
    ),
    relationship = "one-to-one"
  ) %>%
  select(
    `State Code`, `District Code`, `Town-Village Name`,
    state_no, census_dist_norm,
    ec13_emp_all, ec13_emp_f, ec13_emp_m, ec13_emp_gov,
    ec13_emp_manuf, ec13_emp_services
  ) %>%
  left_join(
    sc_pop %>%
      select(
        dist_code_2011,
        sc_district_no = district_no_local,
        sc_persons
      ),
    by = c("District Code" = "dist_code_2011"),
    relationship = "one-to-one"
  ) %>%
  left_join(
    st_pop %>%
      select(
        dist_code_2011,
        st_district_no = district_no_local,
        st_persons
      ),
    by = c("District Code" = "dist_code_2011"),
    relationship = "one-to-one"
  ) %>%
  left_join(
    pop_change,
    by = c("District Code" = "district_code"),
    relationship = "one-to-one"
  ) %>%
  left_join(
    pop_change_name,
    by = c("state_no", "census_dist_norm"),
    relationship = "many-to-one"
  ) %>%
  mutate(
    district_pop_2011 = coalesce(district_pop_2011, district_pop_2011_name),
    pct_change_from_last_census = coalesce(
      pct_change_from_last_census,
      pct_change_from_last_census_name
    )
  ) %>%
  select(-district_pop_2011_name, -pct_change_from_last_census_name) %>%
  left_join(
    migration,
    by = c("District Code" = "district_code"),
    relationship = "one-to-one"
  ) %>%
  left_join(
    mig_change,
    by = c("District Code" = "2011_District"),
    relationship = "one-to-one"
  ) %>%
  left_join(gdp_name_override, by = c("state_no", "census_dist_norm")) %>%
  mutate(gdp_dist_join = coalesce(gdp_dist_norm, census_dist_norm)) %>%
  left_join(
    pc_gdp,
    by = c("state_no", "gdp_dist_join" = "gdp_dist_norm")
  ) %>%
  mutate(
    district_no = coalesce(sc_district_no, st_district_no),
    district_name_norm = norm_name(`Town-Village Name`),
    district_join_key_code = make_code_key(district_no),
    district_join_key_name = paste0("NAME_", district_name_norm),
    sc_persons = if_else(state_no %in% zero_sc_states & is.na(sc_persons), 0, sc_persons),
    st_persons = if_else(state_no %in% zero_st_states & is.na(st_persons), 0, st_persons)
  )

demog_dist_for_join <- demog_dist_xwalk %>%
  rename(district_no_demog = district_no) %>%
  mutate(
    district_join_key = district_join_key_code
  )
```


```{r 8d-delhi-district-override}
# Assign Delhi ACs to districts using maximum spatial overlap.
# This replaces unreliable Delhi district codes in the AC crosswalk.

delhi_ac_manual <- tribble(
  ~state_no, ~ac, ~district_name_manual,
  7, 63, "North East",
  7, 64, "North East",
  7, 67, "North East",
  7, 68, "North East",
  7, 41, "South",
  7, 54, "South",
  7, 61, "East",
  7, 62, "East",
  7, 42, "South",
  7, 50, "South",
  7, 49, "South",
  7, 51, "South",
  7, 52, "South",
  7, 53, "South"
  ) %>%
  mutate(district_name_norm_manual = norm_delhi_dist(district_name_manual)) %>%
  left_join(
    demog_dist_xwalk %>%
      filter(state_no == 7) %>%
      transmute(
        state_no,
        district_name_norm_manual = norm_delhi_dist(`Town-Village Name`),
        district_no_manual = district_no
      ),
    by = c("state_no", "district_name_norm_manual")
  )

delhi_dist_geo <- read_sf("data/delhi_districts.geojson", quiet = TRUE) %>%
  clean_names() %>%
  st_make_valid()

delhi_dist_name_col <- names(delhi_dist_geo) %>%
  keep(~ str_detect(.x, regex("district|dist|name", ignore_case = TRUE))) %>%
  first()

stopifnot(!is.na(delhi_dist_name_col))

delhi_dist_codes <- demog_dist_xwalk %>%
  filter(state_no == 7) %>%
  transmute(
    delhi_district_name_norm = norm_delhi_dist(`Town-Village Name`),
    district_no_fixed = district_no,
    district_name_fixed = `Town-Village Name`
  )

delhi_dist_geo <- delhi_dist_geo %>%
  mutate(delhi_district_name_norm = norm_delhi_dist(.data[[delhi_dist_name_col]])) %>%
  left_join(delhi_dist_codes, by = "delhi_district_name_norm")

delhi_ac_district <- ac_map_clean %>%
  filter(state_no == 7) %>%
  select(state_no, ac, geometry) %>%
  st_transform(6933) %>%
  st_intersection(
    delhi_dist_geo %>%
      select(district_no_fixed, district_name_fixed, geometry) %>%
      st_transform(6933)
  ) %>%
  mutate(overlap_area = as.numeric(st_area(geometry))) %>%
  st_drop_geometry() %>%
  slice_max(overlap_area, by = c(state_no, ac), n = 1, with_ties = FALSE) %>%
  select(state_no, ac, district_no_fixed, district_name_fixed)

```


```{r 8e-build-ac-demographic-inputs}
# Parse AC IDs and build turnout-based allocation weights.
# Valid votes are a fallback for true elector weights.

ac_demog <- ac_pop %>%
  transmute(
    state_no = as.double(str_remove(str_match(ac08_id, "^\\d{4}-(\\d{2})-\\d{3}$")[, 2], "^0")),
    ac = as.double(str_remove(str_extract(ac08_id, "\\d{3}$"), "^0+")),
    con08_pop = con08_pc01_pca_tot_p,
    con08_land_area
  )

ac_weights <- pc_elections %>%
  filter(Year %in% c(2009, 2014)) %>%
  transmute(
    state_no = state_name_to_no(State_Name),
    ac = Constituency_No,
    year = Year,
    valid_votes = Valid_Votes
  ) %>%
  summarise(
    valid_votes = first_nonmissing(valid_votes),
    .by = c(state_no, ac, year)
  ) %>%
  pivot_wider(
    id_cols = c(state_no, ac),
    names_from = year,
    values_from = valid_votes,
    names_prefix = "valid_votes_"
  ) %>%
  mutate(
    valid_votes_avg = rowMeans(pick(valid_votes_2009, valid_votes_2014), na.rm = TRUE),
    valid_votes_avg = if_else(is.nan(valid_votes_avg), NA_real_, valid_votes_avg),
    elector_weight = coalesce(valid_votes_2009, valid_votes_avg, valid_votes_2014)
  ) %>%
  select(state_no, ac, elector_weight)

ac_name_key_clean <- ac_name_key %>%
  transmute(
    state_no = as.double(str_remove(
      str_match(ac08_id, "^\\d{4}-(\\d{2})-\\d{3}$")[, 2],
      "^0"
    )),
    ac = as.double(str_remove(str_extract(ac08_id, "\\d{3}$"), "^0+")),
    ac_name_key = ac08_name,
    district_no_key = as.double(pc01_district_id),
    district_name_key = pc01_district_name,
    district_join_key_name_key = district_name_key(pc01_district_name),
    district_join_key_code_key = make_code_key(as.double(pc01_district_id))
  )
```


```{r 8f-build-ac-district-crosswalk}
# Join ACs to district-level demographic variables.
# Primary key: state_no + normalized district name.
# District code is retained only as a diagnostic.
# PC is diagnostic only and is never used as a join key.

manual_ac_district <- tribble(
  ~state_no, ~ac, ~district_manual,

  # Madhya Pradesh: Indore urban ACs
  23, 205, "Indore",
  23, 206, "Indore",
  23, 207, "Indore",
  23, 208, "Indore",

  # Gujarat: Ahmedabad urban ACs
  24, 45, "Ahmadabad",
  24, 46, "Ahmadabad",
  24, 47, "Ahmadabad",
  24, 48, "Ahmadabad",
  24, 49, "Ahmadabad",
  24, 50, "Ahmadabad",
  24, 51, "Ahmadabad",
  24, 52, "Ahmadabad",
  24, 53, "Ahmadabad",
  24, 54, "Ahmadabad",
  24, 55, "Ahmadabad",
  24, 56, "Ahmadabad",

  # Gujarat: Surat urban ACs
  24, 161, "Surat",
  24, 162, "Surat",
  24, 163, "Surat",
  24, 164, "Surat",
  24, 165, "Surat",
  24, 166, "Surat",
  24, 167, "Surat",

  # Ambiguous ACs resolved manually
  18, 33, "Bongaigaon",
  18, 42, "Barpeta",
  20, 57, "Saraikela Kharsawan",
  20, 59, "Ranchi",
  20, 70, "Simdega"
) %>%
  mutate(
    district_join_key_name_manual = district_name_key(district_manual)
  )

manual_unmatched <- manual_ac_district %>%
  anti_join(
    demog_dist_for_join %>%
      distinct(state_no, district_join_key_name),
    by = c("state_no", "district_join_key_name_manual" = "district_join_key_name")
  )

if (nrow(manual_unmatched) > 0) {
  print(manual_unmatched, n = Inf)
  stop("Some manual district names do not match demog_dist_for_join.")
}

ac_dist_raw <- ac_xwalk %>%
  st_drop_geometry() %>%
  transmute(
    state_no = as.double(ST_CODE),
    xwalk_pc = as.double(PC_NO), # diagnostic only
    ac = as.double(AC_NO),
    district = DIST_NAME,
    district_no = as.double(DT_CODE),
    xwalk_dist_norm = norm_name(DIST_NAME),
    district_join_key_code = make_code_key(district_no), # diagnostic only
    district_join_key_name = district_name_key(DIST_NAME),
    manual_xwalk = FALSE
  ) %>%
  filter(ac > 0) %>%
  left_join(
    delhi_ac_district %>%
      select(state_no, ac, district_no_fixed, district_name_fixed),
    by = c("state_no", "ac")
  ) %>%
  left_join(
    delhi_ac_manual %>%
      select(state_no, ac, district_no_manual, district_name_manual),
    by = c("state_no", "ac")
  ) %>%
  left_join(
    manual_ac_district %>%
      select(state_no, ac, district_manual, district_join_key_name_manual),
    by = c("state_no", "ac")
  ) %>%
  mutate(
    district_no = case_when(
      state_no == 7 ~ coalesce(district_no_fixed, district_no_manual, district_no),
      TRUE ~ district_no
    ),
    district = case_when(
      !is.na(district_manual) ~ district_manual,
      state_no == 7 & !is.na(district_name_fixed) ~ district_name_fixed,
      state_no == 7 & !is.na(district_name_manual) ~ district_name_manual,
      TRUE ~ district
    ),
    xwalk_dist_norm = norm_name(district),
    district_join_key_code = case_when(
      state_no == 7 & !is.na(district_no) ~ make_code_key(district_no),
      TRUE ~ district_join_key_code
    ),
    district_join_key_name = case_when(
      !is.na(district_join_key_name_manual) ~ district_join_key_name_manual,
      state_no == 7 ~ district_name_key(district),
      TRUE ~ district_join_key_name
    )
  ) %>%
  select(
    -district_no_fixed,
    -district_name_fixed,
    -district_no_manual,
    -district_name_manual,
    -district_manual,
    -district_join_key_name_manual
  )

ambiguous_acs <- ac_dist_raw %>%
  summarise(
    n_districts = n_distinct(district_join_key_name),
    .by = c(state_no, ac)
  ) %>%
  filter(n_districts > 1) %>%
  select(state_no, ac)

ac_dist_resolved <- ac_dist_raw %>%
  left_join(
    ambiguous_acs %>% mutate(ambiguous_ac = TRUE),
    by = c("state_no", "ac")
  ) %>%
  left_join(
    ac_name_key_clean %>%
      select(
        state_no,
        ac,
        district_no_key,
        district_name_key,
        district_join_key_name_key,
        district_join_key_code_key
      ),
    by = c("state_no", "ac"),
    relationship = "many-to-one"
  ) %>%
  mutate(
    ambiguous_ac = replace_na(ambiguous_ac, FALSE),
    matches_ac_name_key = district_join_key_name == district_join_key_name_key
  ) %>%
  group_by(state_no, ac) %>%
  mutate(
    use_ac_name_key = ambiguous_ac & any(matches_ac_name_key, na.rm = TRUE)
  ) %>%
  filter(!use_ac_name_key | matches_ac_name_key) %>%
  ungroup() %>%
  mutate(
    district_no = if_else(use_ac_name_key, district_no_key, district_no),
    district = if_else(use_ac_name_key, district_name_key, district),
    xwalk_dist_norm = norm_name(district),
    district_join_key_code = if_else(
      use_ac_name_key,
      district_join_key_code_key,
      district_join_key_code
    ),
    district_join_key_name = if_else(
      use_ac_name_key,
      district_join_key_name_key,
      district_join_key_name
    )
  ) %>%
  select(
    -ambiguous_ac,
    -district_no_key,
    -district_name_key,
    -district_join_key_name_key,
    -district_join_key_code_key,
    -matches_ac_name_key,
    -use_ac_name_key
  ) %>%
  distinct(state_no, ac, district_join_key_name, .keep_all = TRUE)

multi_district_acs <- ac_dist_resolved %>%
  summarise(
    n_districts = n_distinct(district_join_key_name),
    districts = paste(sort(unique(district)), collapse = "; "),
    district_keys = paste(sort(unique(district_join_key_name)), collapse = "; "),
    .by = c(state_no, ac)
  ) %>%
  filter(n_districts > 1) %>%
  arrange(state_no, ac)

if (nrow(multi_district_acs) > 0) {
  print(multi_district_acs, n = Inf)
  stop("Some ACs still map to multiple districts.")
}

ac_dist_base <- ac_dist_resolved %>%
  distinct(state_no, ac, .keep_all = TRUE)

manual_xwalk_rows <- manual_ac_district %>%
  anti_join(ac_dist_base, by = c("state_no", "ac")) %>%
  transmute(
    state_no,
    xwalk_pc = NA_real_,
    ac = as.double(ac),
    district = district_manual,
    district_no = NA_real_,
    xwalk_dist_norm = norm_name(district_manual),
    district_join_key_code = NA_character_,
    district_join_key_name = district_join_key_name_manual,
    manual_xwalk = TRUE
  )

ac_dist_prejoin <- bind_rows(ac_dist_base, manual_xwalk_rows)

ac_dist_duplicates <- ac_dist_prejoin %>%
  count(state_no, ac) %>%
  filter(n > 1)

if (nrow(ac_dist_duplicates) > 0) {
  print(ac_dist_duplicates, n = Inf)
  stop("AC-district crosswalk is not unique after manual rows.")
}

ac_dist_xwalk <- ac_dist_prejoin %>%
  left_join(
    demog_dist_for_join %>%
      select(-any_of(c("district_join_key", "district_join_key_code"))),
    by = c("state_no", "district_join_key_name"),
    relationship = "many-to-one",
    na_matches = "never"
  )

demog_ac_map <- ac_map_clean %>%
  rename(map_pc = pc) %>%
  left_join(ac_demog, by = c("state_no", "ac")) %>%
  left_join(ac_weights, by = c("state_no", "ac")) %>%
  left_join(
    ac_dist_xwalk,
    by = c("state_no", "ac"),
    relationship = "many-to-one"
  )
```


```{r 8g-crosswalk-diagnostics}
# Diagnose district keys, district joins, and AC-district duplication.
# AC-district rows are required to be unique by state_no + ac

# District demographic keys should be unique.
demog_dist_for_join %>%
  count(state_no, district_join_key_code) %>%
  filter(n > 1) %>%
  print(n = Inf)

# Manual-name lookup keys should also be unique.
demog_dist_for_join %>%
  count(state_no, district_join_key_name) %>%
  filter(n > 1) %>%
  arrange(state_no, district_join_key_name) %>%
  print(n = Inf)

# Joining district demographics should not expand rows.
tibble(
  rows_before_demog_join = nrow(ac_dist_prejoin),
  rows_after_demog_join = nrow(ac_dist_xwalk)
) %>%
  print()

# Raw district controls should no longer be missing for normal states.
ac_dist_xwalk %>%
  summarise(
    n = n(),
    missing_emp_raw = sum(is.na(ec13_emp_all)),
    missing_sc_raw = sum(is.na(sc_persons)),
    missing_st_raw = sum(is.na(st_persons)),
    missing_migration_raw = sum(is.na(`2011_Total_Persons_<1`)),
    .by = state_no
  ) %>%
  arrange(desc(missing_emp_raw)) %>%
  print(n = Inf)

# Check whether numeric-key matches attach the expected district names.
# Some spelling variants are fine; large systematic mismatches are not.
ac_dist_xwalk %>%
  filter(!is.na(ec13_emp_all)) %>%
  mutate(
    xwalk_district_norm = norm_name(district),
    name_agrees = xwalk_district_norm == district_name_norm
  ) %>%
  filter(!name_agrees) %>%
  distinct(
    state_no,
    district,
    xwalk_district_norm,
    `Town-Village Name`,
    district_name_norm,
    district_join_key_name
  ) %>%
  arrange(state_no, district) %>%
  print(n = Inf)

# AC-district crosswalk must be unique.
ac_dist_xwalk %>%
  count(state_no, ac) %>%
  filter(n > 1) %>%
  print(n = Inf)

# Delhi and zero-SC/zero-ST special cases.
ac_dist_xwalk %>%
  filter(state_no %in% c(7, 12, 13)) %>%
  summarise(
    n = n(),
    missing_join_key = sum(is.na(district_join_key_code)),
    missing_emp = sum(is.na(ec13_emp_all)),
    missing_sc = sum(is.na(sc_persons)),
    missing_st = sum(is.na(st_persons)),
    missing_migration = sum(is.na(`2011_Total_Persons_<1`)),
    .by = state_no
  ) %>%
  print(n = Inf)

demog_dist_xwalk %>%
  filter(
    !is.na(sc_district_no),
    !is.na(st_district_no),
    sc_district_no != st_district_no
  ) %>%
  select(
    state_no,
    `District Code`,
    `Town-Village Name`,
    sc_district_no,
    st_district_no
  ) %>%
  print(n = Inf)
```


```{r 9a-calculate-proportional-demographic-data}
# Allocate district-level demographic counts to ACs using AC population or turnout weights.
# This preserves known AC population where plausible and allocates missing/remainder population.

alloc_cols <- c(
  "ec13_emp_all", "ec13_emp_f", "ec13_emp_m", "ec13_emp_gov",
  "ec13_emp_manuf", "ec13_emp_services",
  "sc_persons", "st_persons",
  "2011_Total_Persons", "2011_Total_Persons_<1", "2011_Total_Persons_1-4",
  "2011_Total_Persons_5-9", "2011_Total_Persons_10-19",
  "2011_Total_Persons_>20",
  "delta_Total_Persons", "delta_Total_Persons_<1", "delta_Total_Persons_1-4",
  "delta_Total_Persons_5-9", "delta_Total_Persons_10-19"
) %>%
  intersect(names(demog_ac_map))

demog_ac_alloc <- demog_ac_map %>%
  mutate(
    geom_land_area = as.numeric(st_area(st_transform(geometry, 6933))) / 1e6,
    con08_land_area = coalesce(con08_land_area, geom_land_area),
    con08_pop = clean_num(con08_pop),
    elector_weight = clean_num(elector_weight),
    district_pop_persons = clean_num(district_pop_2011),
    across(all_of(alloc_cols), clean_num)
  ) %>%
  group_by(state_no, district_join_key_name) %>%
  mutate(
    district_pop_persons = first_nonmissing(district_pop_persons),
    ac_has_pop = !is.na(con08_pop) & con08_pop > 0,
    ac_has_weight = !is.na(elector_weight) & elector_weight > 0,
    n_ac = n(),
    n_known = sum(ac_has_pop),
    n_missing = sum(!ac_has_pop),
    known_pop_sum = sum(con08_pop[ac_has_pop], na.rm = TRUE),
    remainder_pop = pmax(district_pop_persons - known_pop_sum, 0),
    missing_weight_sum = sum(elector_weight[!ac_has_pop & ac_has_weight], na.rm = TRUE),
    all_weight_sum = sum(elector_weight[ac_has_weight], na.rm = TRUE),
    use_full_elector_allocation = !is.na(district_pop_persons) & known_pop_sum > 1.05 * district_pop_persons,
    proxy_ac_pop = case_when(
      ac_has_pop & !use_full_elector_allocation ~ con08_pop,
      all_weight_sum > 0 & ac_has_weight & (use_full_elector_allocation | n_known == 0) ~
        district_pop_persons * elector_weight / all_weight_sum,
      all_weight_sum == 0 & !is.na(district_pop_persons) & (use_full_elector_allocation | n_known == 0) ~
        district_pop_persons / n_ac,
      !ac_has_pop & n_known > 0 & remainder_pop > 0 & missing_weight_sum > 0 & ac_has_weight ~
        remainder_pop * elector_weight / missing_weight_sum,
      !ac_has_pop & n_known > 0 & remainder_pop > 0 & missing_weight_sum == 0 ~
        remainder_pop / n_missing,
      !ac_has_pop & !is.na(district_pop_persons) & all_weight_sum > 0 & ac_has_weight ~ 
        district_pop_persons * elector_weight / all_weight_sum,
      !ac_has_pop & !is.na(district_pop_persons) & all_weight_sum == 0 ~ 
        district_pop_persons / n_ac,
      TRUE ~ NA_real_
    ),
    proxy_ac_pop_source = case_when(
      ac_has_pop & !use_full_elector_allocation ~ "con08_pop",
      use_full_elector_allocation & all_weight_sum > 0 ~ "full_district_turnout_alloc",
      use_full_elector_allocation & all_weight_sum == 0 ~ "full_district_equal_alloc",
      !ac_has_pop & n_known > 0 & missing_weight_sum > 0 ~ "remainder_turnout_alloc",
      !ac_has_pop & n_known > 0 & missing_weight_sum == 0 ~ "remainder_equal_alloc",
      n_known == 0 & all_weight_sum > 0 ~ "full_district_turnout_alloc",
      n_known == 0 & all_weight_sum == 0 ~ "full_district_equal_alloc",
      !ac_has_pop & !is.na(district_pop_persons) & all_weight_sum > 0 & ac_has_weight ~ 
        "fallback_turnout_alloc", 
      !ac_has_pop & !is.na(district_pop_persons) & all_weight_sum == 0 ~ 
        "fallback_equal_alloc",
      TRUE ~ "missing"
    ),
    share_denom = sum(proxy_ac_pop, na.rm = TRUE),
    ac_alloc_share = case_when(
      share_denom > 0 ~ proxy_ac_pop / share_denom,
      n_ac > 0 ~ 1 / n_ac,
      TRUE ~ NA_real_
      ),
    known_pop_exceeds_district_pop = !is.na(district_pop_persons) & known_pop_sum > district_pop_persons
  ) %>%
  ungroup() %>%
  mutate(
    across(all_of(alloc_cols), ~ .x * ac_alloc_share, .names = "{.col}_ac_alloc"),
    sc_persons_ac_alloc = if_else(state_no %in% zero_sc_states & is.na(sc_persons_ac_alloc), 0, sc_persons_ac_alloc),
    st_persons_ac_alloc = if_else(state_no %in% zero_st_states & is.na(st_persons_ac_alloc), 0, st_persons_ac_alloc)
  )

# Collapse to one AC row after allocation.
# Allocated counts are summed; AC-level fields are kept once.

sum_or_na <- function(x) {
  if (all(is.na(x))) NA_real_ else sum(x, na.rm = TRUE)
}

alloc_out_cols <- names(demog_ac_alloc) %>%
  str_subset("_ac_alloc$")

demog_ac_alloc_ac <- demog_ac_alloc %>%
  st_drop_geometry() %>%
  summarise(
    across(all_of(alloc_out_cols), sum_or_na),
    proxy_ac_pop = sum_or_na(proxy_ac_pop),
    con08_land_area = first_nonmissing(con08_land_area),
    elector_weight = first_nonmissing(elector_weight),
    pc_gdp_2009 = first_nonmissing(pc_gdp_2009),
    pc_gdp_2013 = first_nonmissing(pc_gdp_2013),
    used_turnout_alloc = any(str_detect(proxy_ac_pop_source, "turnout"), na.rm = TRUE),
    used_equal_alloc = any(str_detect(proxy_ac_pop_source, "equal"), na.rm = TRUE),
    all_proxy_sources = paste(sort(unique(na.omit(proxy_ac_pop_source))), collapse = "; "),
    .by = c(state_no, ac)
  )
```


```{r 9b-demographic-allocation-diagnostics}
# Summarize allocation quality by state.
# This is diagnostic output only and should not mutate the analysis object.

demog_ac_alloc_ac %>%
  summarise(
    n = n(),
    missing_proxy_ac_pop = sum(is.na(proxy_ac_pop)),
    missing_emp = sum(is.na(ec13_emp_all_ac_alloc)),
    missing_sc = sum(is.na(sc_persons_ac_alloc)),
    missing_st = sum(is.na(st_persons_ac_alloc)),
    .by = state_no
  ) %>%
  filter(if_any(starts_with("missing_"), ~ .x > 0)) %>%
  arrange(desc(missing_proxy_ac_pop)) %>%
  print(n = Inf)
```

```{r 10-construct-five-year-migration-exposure}
# Reconstruct annual migration inflows from the Census duration bins.
#
# The duration categories are treated as interval totals:
#   5-9 years  -> five annual observations, 2002-2006
#   1-4 years  -> four annual observations, 2007-2010
#   <1 year    -> one annual observation, 2011
#
# For each election, create the five pre-election calendar years. Available
# annual rates are averaged, that average is assigned to any missing years,
# and the five annual values are summed. This generalizes the Bhavnani-Lacina
# interval-annualization procedure and makes the post-2011 imputation explicit.

migration_bin_spec <- tribble(
  ~bin,  ~source_col,                                ~first_year, ~last_year, ~bin_years,
  "5_9", "2011_Total_Persons_5-9_ac_alloc",       2002L,       2006L,      5,
  "1_4", "2011_Total_Persons_1-4_ac_alloc",       2007L,       2010L,      4,
  "lt1", "2011_Total_Persons_<1_ac_alloc",        2011L,       2011L,      1
)

migration_annual_ac <- demog_ac_alloc_ac %>%
  st_drop_geometry() %>%
  select(
    state_no,
    ac,
    proxy_ac_pop,
    all_of(migration_bin_spec$source_col)
  ) %>%
  pivot_longer(
    cols = all_of(migration_bin_spec$source_col),
    names_to = "source_col",
    values_to = "bin_total"
  ) %>%
  left_join(migration_bin_spec, by = "source_col") %>%
  mutate(
    bin_total = as.numeric(bin_total),
    annual_migrants = bin_total / bin_years,
    migration_year = map2(first_year, last_year, seq)
  ) %>%
  unnest(migration_year) %>%
  select(state_no, ac, proxy_ac_pop, migration_year, bin, annual_migrants)

election_windows <- tribble(
  ~year, ~window_start, ~window_end,
  2009L, 2004L,         2008L,
  2014L, 2009L,         2013L
)

migration_five_year <- demog_ac_alloc_ac %>%
  st_drop_geometry() %>%
  distinct(state_no, ac, proxy_ac_pop) %>%
  crossing(election_windows) %>%
  mutate(migration_year = map2(window_start, window_end, seq)) %>%
  unnest(migration_year) %>%
  left_join(
    migration_annual_ac %>%
      select(state_no, ac, migration_year, annual_migrants),
    by = c("state_no", "ac", "migration_year")
  ) %>%
  group_by(state_no, ac, proxy_ac_pop, year, window_start, window_end) %>%
  mutate(
    mig_observed_annual_mean = if_else(
      any(!is.na(annual_migrants)),
      mean(annual_migrants, na.rm = TRUE),
      NA_real_
    ),
    annual_migrants_filled = coalesce(
      annual_migrants,
      mig_observed_annual_mean
    ),
    migration_year_imputed = is.na(annual_migrants) &
      !is.na(mig_observed_annual_mean)
  ) %>%
  summarise(
    mig_5yr_total = if_else(
      all(is.na(annual_migrants_filled)),
      NA_real_,
      sum(annual_migrants_filled, na.rm = TRUE)
    ),
    mig_5yr_observed_total = if_else(
      all(is.na(annual_migrants)),
      NA_real_,
      sum(annual_migrants, na.rm = TRUE)
    ),
    mig_5yr_observed_years = sum(!is.na(annual_migrants)),
    mig_5yr_imputed_years = sum(migration_year_imputed),
    mig_5yr_imputed_amount = if_else(
      all(is.na(annual_migrants_filled)),
      NA_real_,
      sum(
        if_else(migration_year_imputed, annual_migrants_filled, 0),
        na.rm = TRUE
      )
    ),
    .groups = "drop"
  ) %>%
  mutate(
    log1p_mig_5yr_total = log1p(mig_5yr_total),
    mig_5yr_share_ac_pop = if_else(
      proxy_ac_pop > 0,
      mig_5yr_total / proxy_ac_pop,
      NA_real_
    ),
    mig_5yr_share_ac_pop_pp = 100 * mig_5yr_share_ac_pop
  )

# Add the election-invariant controls retained by the revised models. GDP and
# male employment are intentionally excluded from the regression pipeline.
demog_ac_alloc_ac <- demog_ac_alloc_ac %>%
  mutate(
    emp_rate = if_else(
      proxy_ac_pop > 0,
      ec13_emp_all_ac_alloc / proxy_ac_pop,
      NA_real_
    ),
    sc_pop_share = case_when(
      state_no %in% zero_sc_states & !is.na(proxy_ac_pop) ~ 0,
      proxy_ac_pop > 0 ~ sc_persons_ac_alloc / proxy_ac_pop,
      TRUE ~ NA_real_
    ),
    st_pop_share = case_when(
      state_no %in% zero_st_states & !is.na(proxy_ac_pop) ~ 0,
      proxy_ac_pop > 0 ~ st_persons_ac_alloc / proxy_ac_pop,
      TRUE ~ NA_real_
    ),
    mig_pre2004_total = if_else(
      !is.na(`2011_Total_Persons_>20_ac_alloc`) &
        !is.na(`2011_Total_Persons_10-19_ac_alloc`) &
        !is.na(`2011_Total_Persons_5-9_ac_alloc`),
      `2011_Total_Persons_>20_ac_alloc` +
        `2011_Total_Persons_10-19_ac_alloc` +
        (2 / 5) * `2011_Total_Persons_5-9_ac_alloc`,
      NA_real_
    ),
    mig_pre2004_share_ac_pop = if_else(
      proxy_ac_pop > 0,
      mig_pre2004_total / proxy_ac_pop,
      NA_real_
    ),
    mig_pre2004_share_ac_pop_pp = 100 * mig_pre2004_share_ac_pop
  )
```

```{r 11-clean-election-returns}
# Collapse candidate-level general-election returns to one AC-election row.
# Far-right parties and survey party codes are defined once and reused below.
# Clean election returns --------------------------------------------------

fr_parties <- c("BJP", "SHS", "MNS")
fr_codes <- c(2, 46, 91)

preferred_election_label <- function(x, party) {
  preferred <- x[
    !is.na(x) &
      !is.na(party) &
      party != "NOTA"
  ]

  if (length(preferred) > 0) {
    return(dplyr::first(preferred))
  }

  first_nonmissing(x)
}

pc_elections_candidate_level <- pc_elections %>%
  filter(Year %in% c(2009, 2014)) %>%
  transmute(
    state = as.character(State_Name),
    state_no = state_name_to_no(State_Name),
    ac = as.integer(Constituency_No),
    year = as.integer(Year),
    pc_name = as.character(PC_Name),
    pc = as.integer(PC_No),
    ac_name = as.character(Constituency_Name),
    party = as.character(Party),
    votes = as.numeric(Votes),
    valid_votes = as.numeric(Valid_Votes)
  )

# Numeric identifiers and valid-vote totals must be consistent within AC-year.
election_identifier_diagnostics <- pc_elections_candidate_level %>%
  summarise(
    n_pc_numbers = n_distinct(pc, na.rm = TRUE),
    n_valid_vote_totals = n_distinct(valid_votes, na.rm = TRUE),
    n_pc_names = n_distinct(pc_name, na.rm = TRUE),
    n_ac_names = n_distinct(ac_name, na.rm = TRUE),
    .by = c(state_no, ac, year)
  )

true_election_conflicts <- election_identifier_diagnostics %>%
  filter(
    n_pc_numbers > 1 |
      n_valid_vote_totals > 1
  )

if (nrow(true_election_conflicts) > 0) {
  print(true_election_conflicts, n = Inf)

  stop(
    "Some AC-election observations have conflicting PC numbers ",
    "or valid-vote totals."
  )
}

# Collapse by stable numeric identifiers only.
pc_elections_clean <- pc_elections_candidate_level %>%
  summarise(
    state = first_nonmissing(state),
    pc = first_nonmissing(pc),

    pc_name = preferred_election_label(
      pc_name,
      party
    ),

    ac_name = preferred_election_label(
      ac_name,
      party
    ),

    valid_votes = first_nonmissing(valid_votes),

    fr_party_votes = sum(
      if_else(
        party %in% fr_parties,
        votes,
        0
      ),
      na.rm = TRUE
    ),

    .by = c(
      state_no,
      ac,
      year
    )
  ) %>%
  mutate(
    fr_party_vote_share = if_else(
      !is.na(valid_votes) & valid_votes > 0,
      100 * fr_party_votes / valid_votes,
      NA_real_
    )
  ) %>%
  select(
    state,
    state_no,
    pc_name,
    pc,
    ac_name,
    ac,
    year,
    valid_votes,
    fr_party_votes,
    fr_party_vote_share
  ) %>%
  arrange(
    state_no,
    ac,
    year
  )

pc_election_duplicates <- pc_elections_clean %>%
  count(
    state_no,
    ac,
    year,
    name = "n"
  ) %>%
  filter(n > 1)

if (nrow(pc_election_duplicates) > 0) {
  print(pc_election_duplicates, n = Inf)

  stop(
    "pc_elections_clean is not unique by state_no, ac, and year."
  )
}

message(
  "Maximum rows per AC-year in pc_elections_clean: ",
  pc_elections_clean %>%
    count(state_no, ac, year) %>%
    summarise(maximum = max(n)) %>%
    pull(maximum)
)
```

```{r 12-parse-and-spatially-assign-fdi-projects}
# Parse project coordinates, identify each containing AC, and extend exposure
# to immediately adjacent ACs.

services <- c(
  "Business Services",
  "Customer Contact Centre",
  "Research & Development",
  "Sales, Marketing & Support",
  "Shared Services Centre",
  "Technical Support Centre"
)

fdi_coords <- fdi %>%
  mutate(fdi_id = row_number()) %>%
  extract(
    Coordinates,
    into = c("lat", "lon"),
    regex = "^\\s*(-?\\d+(?:\\.\\d+)?)\\s*,\\s*(-?\\d+(?:\\.\\d+)?)\\s*$",
    remove = FALSE,
    convert = TRUE
  ) %>%
  filter(!is.na(lat), !is.na(lon)) %>%
  st_as_sf(coords = c("lon", "lat"), crs = 4326, remove = FALSE) %>%
  st_transform(st_crs(ac_map_clean))

ac_index <- ac_map_clean %>%
  mutate(ac_uid_spatial = row_number()) %>%
  select(ac_uid_spatial, state_no, ac, geometry)

fdi_lookup_local <- fdi_coords %>%
  st_join(ac_index, join = st_within, left = TRUE) %>%
  st_drop_geometry() %>%
  transmute(fdi_id, local_ac_uid = ac_uid_spatial)

ac_neighbors <- tibble(
  local_ac_uid = ac_index$ac_uid_spatial,
  neighbor_row = st_touches(ac_index)
) %>%
  unnest_longer(neighbor_row, values_to = "neighbor_row") %>%
  transmute(
    local_ac_uid,
    neighbor_ac_uid = ac_index$ac_uid_spatial[neighbor_row],
    exposure_type = "adjacent"
  )

ac_self <- tibble(
  local_ac_uid = ac_index$ac_uid_spatial,
  neighbor_ac_uid = ac_index$ac_uid_spatial,
  exposure_type = "own"
)

ac_exposure_map <- bind_rows(ac_self, ac_neighbors) %>%
  left_join(
    ac_index %>%
      st_drop_geometry() %>%
      transmute(
        neighbor_ac_uid = ac_uid_spatial,
        state_no,
        ac
      ),
    by = "neighbor_ac_uid"
  )

fdi_ac <- fdi_coords %>%
  left_join(
    fdi_lookup_local %>%
      filter(!is.na(local_ac_uid)) %>%
      left_join(
        ac_exposure_map,
        by = "local_ac_uid",
        relationship = "many-to-many"
      ) %>%
      distinct(fdi_id, state_no, ac, exposure_type),
    by = "fdi_id",
    relationship = "one-to-many"
  ) %>%
  clean_names() %>%
  mutate(
    project_month = as.Date(
      parse_date_time(project_date, orders = c("b Y", "B Y"))
    ),
    year = case_when(
      between(
        project_month,
        as.Date("2004-04-01"),
        as.Date("2009-04-01")
      ) ~ 2009L,
      between(
        project_month,
        as.Date("2009-05-01"),
        as.Date("2014-05-01")
      ) ~ 2014L,
      TRUE ~ NA_integer_
    ),
    activity = str_squish(activity),
    activity_type = case_when(
      activity == "Manufacturing" ~ "manufacturing",
      activity %in% services ~ "services",
      TRUE ~ "other"
    )
  ) %>%
  filter(!is.na(state_no), !is.na(ac), !is.na(year)) %>%
  st_drop_geometry() %>%
  distinct(fdi_id, state_no, ac, year, activity_type, .keep_all = TRUE)
```

```{r 13-aggregate-election-specific-fdi-exposure}
# Total FDI includes every qualifying project. Manufacturing and services are
# separate subsets of the total.

fdi_summary_ac_year <- fdi_ac %>%
  summarise(
    fdi_5yr_total_n = n_distinct(fdi_id),
    fdi_5yr_mfg_n = n_distinct(fdi_id[activity_type == "manufacturing"]),
    fdi_5yr_svc_n = n_distinct(fdi_id[activity_type == "services"]),
    .by = c(state_no, ac, year)
  )

fdi_summary_ever <- fdi_summary_ac_year %>%
  summarise(
    fdi_total_ever_n = sum(fdi_5yr_total_n, na.rm = TRUE),
    fdi_mfg_ever_n = sum(fdi_5yr_mfg_n, na.rm = TRUE),
    fdi_svc_ever_n = sum(fdi_5yr_svc_n, na.rm = TRUE),
    .by = c(state_no, ac)
  ) %>%
  mutate(
    fdi_outlier_99 = fdi_total_ever_n > quantile(
      fdi_total_ever_n,
      0.99,
      na.rm = TRUE
    )
  )

fdi_outlier_cutoff_99 <- quantile(
  fdi_summary_ever$fdi_total_ever_n,
  0.99,
  na.rm = TRUE
)

p_fdi_raw <- ggplot(fdi_summary_ever, aes(fdi_total_ever_n)) +
  geom_histogram(binwidth = 1, boundary = -0.5) +
  geom_vline(xintercept = fdi_outlier_cutoff_99, linetype = "dashed") +
  labs(
    x = "FDI sites in or adjacent to AC, 2004-2014",
    y = "Assembly constituencies",
    title = "Distribution of AC-level FDI exposure"
  ) +
  theme_minimal()

p_fdi_logged <- ggplot(fdi_summary_ever, aes(log1p(fdi_total_ever_n))) +
  geom_histogram(bins = 30) +
  labs(
    x = "log(1 + FDI sites in or adjacent to AC), 2004-2014",
    y = "Assembly constituencies",
    title = "Distribution of logged AC-level FDI exposure"
  ) +
  theme_minimal()

p_fdi_raw
p_fdi_logged
```

```{r 14-build-uncentered-ac-year-levels-data}
# Join official election outcomes to one-row-per-AC contextual inputs. Every
# source table is checked before the join so a many-to-many join cannot silently
# multiply AC-year observations. GDP and male employment are deliberately not
# carried into the regression datasets.

assert_unique_rows <- function(data, keys, label) {
  duplicates <- data %>%
    group_by(across(all_of(keys))) %>%
    summarise(n = n(), .groups = "drop") %>%
    filter(n > 1)

  if (nrow(duplicates) > 0) {
    print(duplicates, n = Inf)
    stop(label, " is not unique by ", paste(keys, collapse = ", "), ".")
  }

  invisible(data)
}

per_100k <- function(x, population) {
  if_else(
    !is.na(population) & population > 0,
    100000 * x / population,
    NA_real_
  )
}

assert_unique_rows(pc_elections_clean, c("state_no", "ac", "year"), "Election returns")
assert_unique_rows(
  demog_ac_alloc_ac %>% st_drop_geometry(),
  c("state_no", "ac"),
  "AC demographic allocation"
)
assert_unique_rows(fdi_summary_ac_year, c("state_no", "ac", "year"), "FDI AC-year summary")
assert_unique_rows(fdi_summary_ever, c("state_no", "ac"), "FDI all-period summary")
assert_unique_rows(migration_five_year, c("state_no", "ac", "year"), "Migration AC-year summary")

ac_demographic_controls <- demog_ac_alloc_ac %>%
  st_drop_geometry() %>%
  select(
    state_no,
    ac,
    emp_rate,
    sc_pop_share,
    st_pop_share,
    con08_land_area,
    proxy_ac_pop,
    mig_pre2004_total,
    mig_pre2004_share_ac_pop,
    mig_pre2004_share_ac_pop_pp
  )

ac_year_levels_raw <- pc_elections_clean %>%
  left_join(
    ac_demographic_controls,
    by = c("state_no", "ac"),
    relationship = "many-to-one"
  ) %>%
  left_join(
    fdi_summary_ac_year,
    by = c("state_no", "ac", "year"),
    relationship = "many-to-one"
  ) %>%
  left_join(
    fdi_summary_ever,
    by = c("state_no", "ac"),
    relationship = "many-to-one"
  ) %>%
  left_join(
    migration_five_year %>% select(-proxy_ac_pop),
    by = c("state_no", "ac", "year"),
    relationship = "many-to-one"
  ) %>%
  mutate(
    across(
      c(
        fdi_5yr_total_n,
        fdi_5yr_mfg_n,
        fdi_5yr_svc_n,
        fdi_total_ever_n,
        fdi_mfg_ever_n,
        fdi_svc_ever_n
      ),
      ~ replace_na(.x, 0)
    ),
    fdi_outlier_99 = replace_na(fdi_outlier_99, FALSE),
    fdi_5yr_total_pc100k = per_100k(fdi_5yr_total_n, proxy_ac_pop),
    fdi_5yr_mfg_pc100k = per_100k(fdi_5yr_mfg_n, proxy_ac_pop),
    fdi_5yr_svc_pc100k = per_100k(fdi_5yr_svc_n, proxy_ac_pop),
    log_ac_population = if_else(
      !is.na(proxy_ac_pop) & proxy_ac_pop > 0,
      log(proxy_ac_pop),
      NA_real_
    ),
    log_land_area = if_else(
      !is.na(con08_land_area) & con08_land_area >= 0,
      log1p(con08_land_area),
      NA_real_
    ),
    ac_uid = paste(state_no, ac, sep = "_"),
    pc_cluster_id = paste(state_no, pc, sep = "_"),
    year_factor = factor(year, levels = c(2009, 2014)),
    state_fe = factor(state_no)
  ) %>%
  arrange(state_no, ac, year)

assert_unique_rows(
  ac_year_levels_raw,
  c("state_no", "ac", "year"),
  "Uncentered AC-year levels data"
)

forbidden_regression_variables <- c(
  "m_emp_rate",
  "pc_gdp_election",
  "pc_gdp_2009",
  "pc_gdp_2013",
  "delta_pc_gdp"
)

if (any(forbidden_regression_variables %in% names(ac_year_levels_raw))) {
  stop(
    "Obsolete variables leaked into the AC-year regression data: ",
    paste(
      intersect(forbidden_regression_variables, names(ac_year_levels_raw)),
      collapse = ", "
    )
  )
}
```

```{r 15-recode-nes-ideology-items-without-don-t-know-responses}
# Preserve every original response before recoding. Don't know, no opinion,
# refusals, and unmapped codes become NA before standardization, so they affect
# neither the item z-scores nor the respondent-level axis averages.

nes_state_recode <- function(x) {
  recode(
    as.numeric(x),
    `1` = 28, `2` = 12, `3` = 18, `4` = 10, `5` = 30, `6` = 24,
    `7` = 6, `8` = 2, `9` = 1, `10` = 29, `11` = 32, `12` = 23,
    `13` = 27, `14` = 14, `15` = 17, `16` = 15, `17` = 13,
    `18` = 21, `19` = 3, `20` = 8, `21` = 11, `22` = 33,
    `23` = 16, `24` = 9, `25` = 19, `26` = 35, `27` = 4,
    `28` = 26, `29` = 25, `30` = 7, `31` = 31, `32` = 34,
    `33` = 20, `34` = 22, `35` = 5, `36` = 28,
    .default = NA_real_
  )
}

item_spec_2009 <- tribble(
  ~item,  ~axis,          ~dk_codes,
  "a6a",  "Recognition", list(8),
  "a5",   "Recognition", list(8),
  "a4c",  "Recognition", list(8),
  "a4b",  "Recognition", list(8),
  "a4d",  "Statism",     list(8),
  "a4g",  "Statism",     list(8),
  "q26a", "Statism",     list(8),
  "a6b",  "Statism",     list(8),
  "q27",  "Statism",     list(c(7, 8))
)

item_spec_2014 <- tribble(
  ~item,   ~axis,          ~dk_codes,
  "q10b", "Recognition", list(8),
  "q10e", "Recognition", list(8),
  "q23c", "Statism",     list(8)
)

nes_2009_clean <- nes_2009 %>%
  mutate(
    state_no = nes_state_recode(st_id),
    across(
      all_of(item_spec_2009$item),
      identity,
      .names = "{.col}_raw"
    ),
    q26a = case_match(as.numeric(q26a_raw), 1 ~ 2, 2 ~ 1, 3 ~ -1, 4 ~ -2),
    q27  = case_match(as.numeric(q27_raw),  2 ~ 1, 1 ~ -1),
    a4b  = case_match(as.numeric(a4b_raw),  4 ~ 2, 3 ~ 1, 2 ~ -1, 1 ~ -2),
    a4c  = case_match(as.numeric(a4c_raw),  1 ~ 2, 2 ~ 1, 3 ~ -1, 4 ~ -2),
    a4d  = case_match(as.numeric(a4d_raw),  1 ~ 2, 2 ~ 1, 3 ~ -1, 4 ~ -2),
    a4g  = case_match(as.numeric(a4g_raw),  4 ~ 2, 3 ~ 1, 2 ~ -1, 1 ~ -2),
    a5   = case_match(as.numeric(a5_raw),   2 ~ 1, 1 ~ -1),
    a6a  = case_match(as.numeric(a6a_raw),  2 ~ 1, 1 ~ -1),
    a6b  = case_match(as.numeric(a6b_raw),  2 ~ 1, 1 ~ -1),
    across(
      all_of(item_spec_2009$item),
      safe_z,
      .names = "z_{.col}"
    ),
    recognition_n_valid = rowSums(
      !is.na(pick(z_a6a, z_a5, z_a4c, z_a4b))
    ),
    statism_n_valid = rowSums(
      !is.na(pick(z_a4d, z_a4g, z_q26a, z_a6b, z_q27))
    ),
    recognition = row_mean_valid(
      pick(z_a6a, z_a5, z_a4c, z_a4b),
      min_valid = 1L
    ),
    statism = row_mean_valid(
      pick(z_a4d, z_a4g, z_q26a, z_a6b, z_q27),
      min_valid = 1L
    ),
    voter_ideology = ideology_group(recognition, statism)
  )

nes_2014_clean <- nes_2014 %>%
  mutate(
    state_no = nes_state_recode(state_id),
    across(
      all_of(item_spec_2014$item),
      identity,
      .names = "{.col}_raw"
    ),
    q10b = case_match(as.numeric(q10b_raw), 1 ~ 2, 2 ~ 1, 3 ~ -1, 4 ~ -2),
    q10e = case_match(as.numeric(q10e_raw), 4 ~ 2, 3 ~ 1, 2 ~ -1, 1 ~ -2),
    q23c = case_match(as.numeric(q23c_raw), 4 ~ 2, 3 ~ 1, 2 ~ -1, 1 ~ -2),
    across(
      all_of(item_spec_2014$item),
      safe_z,
      .names = "z_{.col}"
    ),
    recognition_n_valid = rowSums(!is.na(pick(z_q10b, z_q10e))),
    statism_n_valid = rowSums(!is.na(pick(z_q23c))),
    recognition = row_mean_valid(
      pick(z_q10b, z_q10e),
      min_valid = 1L
    ),
    statism = row_mean_valid(
      pick(z_q23c),
      min_valid = 1L
    ),
    voter_ideology = ideology_group(recognition, statism)
  )
```

```{r 16-build-long-ideology-item-response-data}
# This long file supports the moderate-response distribution figure. Original
# SPSS response labels are preserved where available. Don't-know responses
# remain visible descriptively even though they were excluded from scoring.
#
# Set these to validated NES weight-variable names when documentation supports
# their use. NULL produces unit weights and marks weighted AC estimates as
# unavailable rather than presenting unit weights as survey-weighted results.

nes_weight_var_2009 <- NULL
nes_weight_var_2014 <- NULL

get_survey_weight <- function(data, weight_var = NULL) {
  if (is.null(weight_var)) {
    return(rep(1, nrow(data)))
  }

  if (!weight_var %in% names(data)) {
    stop("Survey-weight variable not found: ", weight_var)
  }

  weight <- as.numeric(data[[weight_var]])
  if_else(is.finite(weight) & weight > 0, weight, NA_real_)
}

build_item_response_long <- function(data, year_value, item_spec, weight_var = NULL) {
  respondent_id <- seq_len(nrow(data))
  survey_weight <- get_survey_weight(data, weight_var)
  survey_weight_validated <- !is.null(weight_var)

  map_dfr(seq_len(nrow(item_spec)), \(i) {
    item_name <- item_spec$item[i]
    raw_name <- paste0(item_name, "_raw")
    raw_value <- data[[raw_name]]
    score_value <- as.numeric(data[[item_name]])
    dk_codes <- unlist(item_spec$dk_codes[[i]])
    raw_numeric <- as.numeric(raw_value)

    tibble(
      year = year_value,
      respondent_id = respondent_id,
      state_no = as.numeric(data$state_no),
      pc_id = as.numeric(data$pc_id),
      ac_id = as.numeric(data$ac_id),
      voter_ideology = data$voter_ideology,
      recognition = data$recognition,
      statism = data$statism,
      item = item_name,
      axis = item_spec$axis[i],
      item_label = variable_label(raw_value, item_name),
      raw_response = raw_numeric,
      original_response_label = as.character(
        haven::as_factor(raw_value, levels = "labels")
      ),
      score = score_value,
      dont_know = raw_numeric %in% dk_codes,
      survey_weight = survey_weight,
      survey_weight_validated = survey_weight_validated
    ) %>%
      mutate(
        response_category = case_when(
          dont_know ~ "Don't know / no opinion",
          score == -2 ~ "Strongly negative-coded",
          score == -1 ~ "Negative-coded",
          score == 1 ~ "Positive-coded",
          score == 2 ~ "Strongly positive-coded",
          !is.na(raw_response) ~ "Other non-substantive",
          TRUE ~ NA_character_
        )
      )
  })
}

ideology_item_responses_long <- bind_rows(
  build_item_response_long(
    nes_2009_clean,
    2009L,
    item_spec_2009,
    nes_weight_var_2009
  ),
  build_item_response_long(
    nes_2014_clean,
    2014L,
    item_spec_2014,
    nes_weight_var_2014
  )
)
```

```{r 17-build-centered-levels-voter-binomial-and-first-difference-data}
# Build the respondent stack first. Context is joined by state, AC, and election
# year, which uniquely identifies the official AC-year record. The survey PC code
# is audited after the join rather than being used as an additional match key.

plain_col <- function(x) {
  if (inherits(x, c("haven_labelled", "labelled", "labelled_spss"))) {
    as.vector(x)
  } else {
    x
  }
}

nes_2009_for_stack <- nes_2009_clean %>%
  mutate(
    year = 2009L,
    respondent_uid = paste0("2009_", row_number()),
    survey_weight = get_survey_weight(nes_2009_clean, nes_weight_var_2009),
    survey_weight_validated = !is.null(nes_weight_var_2009)
  ) %>%
  mutate(across(everything(), plain_col))

nes_2014_for_stack <- nes_2014_clean %>%
  mutate(
    year = 2014L,
    respondent_uid = paste0("2014_", row_number()),
    survey_weight = get_survey_weight(nes_2014_clean, nes_weight_var_2014),
    survey_weight_validated = !is.null(nes_weight_var_2014)
  ) %>%
  rename(res = any_of("resno")) %>%
  mutate(across(everything(), plain_col))

voter_stack <- bind_rows(
  nes_2009_for_stack,
  nes_2014_for_stack
) %>%
  mutate(
    state_no = as.integer(state_no),
    pc_id = as.integer(pc_id),
    ac_id = as.integer(ac_id),
    fr_vote = case_when(
      is.na(q1a) ~ NA_real_,
      as.numeric(q1a) %in% fr_codes ~ 1,
      TRUE ~ 0
    ),
    voter_ideology = factor(
      as.character(voter_ideology),
      levels = c("C", "L", "R")
    )
  )

voter_context_for_composition <- voter_stack %>%
  left_join(
    ac_year_levels_raw,
    by = c(
      "state_no",
      "ac_id" = "ac",
      "year"
    ),
    relationship = "many-to-one",
    suffix = c("_survey", "")
  ) %>%
  mutate(
    survey_pc_matches_election_pc = case_when(
      is.na(pc_id) | is.na(pc) ~ NA,
      TRUE ~ pc_id == pc
    )
  )

ac_year_moderate_summary <- voter_context_for_composition %>%
  filter(!is.na(ac_uid)) %>%
  mutate(
    ideology_classified = voter_ideology %in% c("L", "C", "R"),
    moderate_indicator = case_when(
      voter_ideology == "C" ~ 1,
      voter_ideology %in% c("L", "R") ~ 0,
      TRUE ~ NA_real_
    )
  ) %>%
  summarise(
    n_survey_respondents = n(),
    n_classified_ideology = sum(ideology_classified),
    n_unclassified_ideology = sum(!ideology_classified),
    ideology_classification_rate = if_else(
      n_survey_respondents > 0,
      n_classified_ideology / n_survey_respondents,
      NA_real_
    ),
    recognition_mean = safe_mean(recognition),
    statism_mean = safe_mean(statism),
    left_share_unweighted = if_else(
      n_classified_ideology > 0,
      sum(voter_ideology == "L", na.rm = TRUE) / n_classified_ideology,
      NA_real_
    ),
    moderate_share_unweighted = if_else(
      n_classified_ideology > 0,
      sum(voter_ideology == "C", na.rm = TRUE) / n_classified_ideology,
      NA_real_
    ),
    right_share_unweighted = if_else(
      n_classified_ideology > 0,
      sum(voter_ideology == "R", na.rm = TRUE) / n_classified_ideology,
      NA_real_
    ),
    survey_weight_validated = any(survey_weight_validated),
    classified_weight = sum(
      survey_weight[
        ideology_classified &
          survey_weight_validated &
          !is.na(survey_weight) &
          survey_weight > 0
      ],
      na.rm = TRUE
    ),
    moderate_weight = sum(
      survey_weight[
        voter_ideology == "C" &
          survey_weight_validated &
          !is.na(survey_weight) &
          survey_weight > 0
      ],
      na.rm = TRUE
    ),
    moderate_share_weighted = if_else(
      survey_weight_validated & classified_weight > 0,
      moderate_weight / classified_weight,
      NA_real_
    ),
    .by = c(state_no, ac_id, year)
  ) %>%
  rename(ac = ac_id) %>%
  mutate(
    moderate_share_unweighted_pp = 100 * moderate_share_unweighted,
    moderate_share_weighted_pp = 100 * moderate_share_weighted
  )

assert_unique_rows(
  ac_year_moderate_summary,
  c("state_no", "ac", "year"),
  "AC-year ideology-composition summary"
)

ac_year_levels_uncentered <- ac_year_levels_raw %>%
  left_join(
    ac_year_moderate_summary,
    by = c("state_no", "ac", "year"),
    relationship = "one-to-one"
  )

# Common centering constants are calculated from unique AC-year rows only.
# Scale is 10 only for the moderate-share variable, so one unit equals a
# ten-percentage-point change. No centering is performed within years, samples,
# or ideological groups.
centering_plan <- tribble(
  ~variable,                          ~centered_variable,       ~scale,
  "fdi_5yr_total_pc100k",            "fdi_total_c",               1,
  "fdi_5yr_mfg_pc100k",              "fdi_mfg_c",                 1,
  "fdi_5yr_svc_pc100k",              "fdi_svc_c",                 1,
  "log1p_mig_5yr_total",             "log_migration_c",           1,
  "mig_5yr_share_ac_pop_pp",         "migration_share_c",         1,
  "emp_rate",                        "emp_rate_c",                1,
  "sc_pop_share",                    "sc_share_c",                1,
  "st_pop_share",                    "st_share_c",                1,
  "log_ac_population",               "log_population_c",         1,
  "log_land_area",                   "log_land_area_c",           1,
  "mig_pre2004_share_ac_pop_pp",     "prior_migrant_share_c",     1,
  "moderate_share_unweighted_pp",    "moderate_share_10pp_c",    10
)

centering_reference <- ac_year_levels_uncentered %>%
  distinct(state_no, ac, year, .keep_all = TRUE)

centering_constants <- centering_plan %>%
  mutate(
    center = map_dbl(
      variable,
      \(v) {
        values <- as.numeric(centering_reference[[v]])
        result <- mean(values[is.finite(values)], na.rm = TRUE)
        if (!is.finite(result)) {
          stop("Cannot calculate a finite centering constant for ", v, ".")
        }
        result
      }
    ),
    n_nonmissing = map_int(
      variable,
      \(v) sum(is.finite(as.numeric(centering_reference[[v]])))
    )
  )

apply_common_centering <- function(data, constants) {
  out <- data

  for (i in seq_len(nrow(constants))) {
    source_name <- constants$variable[i]
    target_name <- constants$centered_variable[i]
    center_value <- constants$center[i]
    scale_value <- constants$scale[i]

    out[[target_name]] <- (
      as.numeric(out[[source_name]]) - center_value
    ) / scale_value
  }

  out
}

ac_year_levels <- apply_common_centering(
  ac_year_levels_uncentered,
  centering_constants
) %>%
  mutate(
    year_factor = factor(year, levels = c(2009, 2014)),
    state_fe = factor(state_no)
  )

centering_diagnostics <- centering_constants %>%
  transmute(
    variable,
    centered_variable,
    center,
    scale,
    n_nonmissing,
    centered_mean = map_dbl(
      centered_variable,
      \(v) mean(ac_year_levels[[v]], na.rm = TRUE)
    )
  )

if (any(abs(centering_diagnostics$centered_mean) > 1e-10, na.rm = TRUE)) {
  print(centering_diagnostics, n = Inf)
  stop("One or more centered variables do not have mean zero in the reference AC-year data.")
}

assert_unique_rows(
  ac_year_levels,
  c("state_no", "ac", "year"),
  "Centered AC-year levels data"
)

# Rejoin the final centered contextual record to respondents. This ensures every
# voter, ideology cell, and contextual model uses exactly the same constants.
voter_year_pooled <- voter_stack %>%
  left_join(
    ac_year_levels,
    by = c(
      "state_no",
      "ac_id" = "ac",
      "year"
    ),
    relationship = "many-to-one",
    suffix = c("_survey", "")
  ) %>%
  mutate(
    survey_pc_matches_election_pc = case_when(
      is.na(pc_id) | is.na(pc) ~ NA,
      TRUE ~ pc_id == pc
    ),
    voter_ideology = factor(
      as.character(voter_ideology),
      levels = c("C", "L", "R")
    )
  )

# Grouped binomial cells retain the literal success and failure counts. The
# analysis script estimates the equivalent grouped-binomial likelihood using
# the observed far-right proportion with n_valid_vote as the trial weight.
ac_year_ideology_counts <- voter_year_pooled %>%
  filter(
    !is.na(ac_uid),
    voter_ideology %in% c("C", "L", "R")
  ) %>%
  summarise(
    n_respondents_in_cell = n(),
    n_valid_vote = sum(!is.na(fr_vote)),
    fr_vote_count = sum(fr_vote == 1, na.rm = TRUE),
    non_fr_vote_count = sum(fr_vote == 0, na.rm = TRUE),
    .by = c(state_no, ac_id, year, voter_ideology)
  ) %>%
  filter(n_valid_vote > 0) %>%
  mutate(
    fr_vote_count = as.integer(fr_vote_count),
    non_fr_vote_count = as.integer(non_fr_vote_count),
    n_valid_vote = as.integer(n_valid_vote),
    fr_vote_prop = fr_vote_count / n_valid_vote
  ) %>%
  rename(ac = ac_id) %>%
  left_join(
    ac_year_levels,
    by = c("state_no", "ac", "year"),
    relationship = "many-to-one"
  ) %>%
  mutate(
    voter_ideology = factor(
      as.character(voter_ideology),
      levels = c("C", "L", "R")
    )
  )

assert_unique_rows(
  ac_year_ideology_counts,
  c("state_no", "ac", "year", "voter_ideology"),
  "AC-year ideology counts"
)

if (any(
  ac_year_ideology_counts$fr_vote_count +
    ac_year_ideology_counts$non_fr_vote_count !=
    ac_year_ideology_counts$n_valid_vote
)) {
  stop("Ideology-cell success and failure counts do not sum to n_valid_vote.")
}

# Build a paired 2009-2014 first-difference dataset. Interaction changes are the
# difference in the centered product, not the product of the two changes.
fd_source <- ac_year_levels %>%
  filter(year %in% c(2009L, 2014L)) %>%
  mutate(
    product_total_log = fdi_total_c * log_migration_c,
    product_mfg_log = fdi_mfg_c * log_migration_c,
    product_svc_log = fdi_svc_c * log_migration_c,
    product_total_share = fdi_total_c * migration_share_c,
    product_mfg_share = fdi_mfg_c * migration_share_c,
    product_svc_share = fdi_svc_c * migration_share_c
  )

paired_ac_keys <- fd_source %>%
  summarise(
    n_years = n_distinct(year),
    .by = c(state_no, ac)
  ) %>%
  filter(n_years == 2)

fd_paired_source <- fd_source %>%
  semi_join(paired_ac_keys, by = c("state_no", "ac"))

assert_unique_rows(
  fd_paired_source,
  c("state_no", "ac", "year"),
  "First-difference source"
)

# Verify that controls described as time invariant truly repeat across waves.
time_invariant_variables <- c(
  "emp_rate",
  "sc_pop_share",
  "st_pop_share",
  "proxy_ac_pop",
  "con08_land_area",
  "log_ac_population",
  "log_land_area",
  "mig_pre2004_share_ac_pop_pp"
)

time_invariant_check <- fd_paired_source %>%
  select(state_no, ac, year, all_of(time_invariant_variables)) %>%
  pivot_wider(
    names_from = year,
    values_from = all_of(time_invariant_variables),
    names_glue = "{.value}_{year}"
  )

time_invariant_diagnostics <- map_dfr(
  time_invariant_variables,
  \(v) {
    old <- time_invariant_check[[paste0(v, "_2009")]]
    new <- time_invariant_check[[paste0(v, "_2014")]]
    mismatch <- xor(is.na(old), is.na(new)) |
      (!is.na(old) & !is.na(new) & abs(old - new) > 1e-12)

    tibble(
      variable = v,
      paired_acs = length(old),
      changed_or_missing_mismatch = sum(mismatch),
      max_absolute_change = if_else(
        any(!is.na(old) & !is.na(new)),
        max(abs(old - new), na.rm = TRUE),
        NA_real_
      )
    )
  }
)

if (any(time_invariant_diagnostics$changed_or_missing_mismatch > 0)) {
  print(time_invariant_diagnostics, n = Inf)
  stop(
    "Variables expected to cancel in first differences are not identical ",
    "between 2009 and 2014. Resolve this before estimating the panel models."
  )
}

ac_first_difference <- fd_paired_source %>%
  select(
    state_no,
    ac,
    year,
    state,
    pc,
    pc_name,
    ac_name,
    fr_party_vote_share,
    fdi_total_c,
    fdi_mfg_c,
    fdi_svc_c,
    log_migration_c,
    migration_share_c,
    product_total_log,
    product_mfg_log,
    product_svc_log,
    product_total_share,
    product_mfg_share,
    product_svc_share
  ) %>%
  pivot_wider(
    names_from = year,
    values_from = c(
      state,
      pc,
      pc_name,
      ac_name,
      fr_party_vote_share,
      fdi_total_c,
      fdi_mfg_c,
      fdi_svc_c,
      log_migration_c,
      migration_share_c,
      product_total_log,
      product_mfg_log,
      product_svc_log,
      product_total_share,
      product_mfg_share,
      product_svc_share
    ),
    names_glue = "{.value}_{year}"
  ) %>%
  mutate(
    delta_fr_vote_share =
      fr_party_vote_share_2014 - fr_party_vote_share_2009,
    delta_fdi_total = fdi_total_c_2014 - fdi_total_c_2009,
    delta_fdi_mfg = fdi_mfg_c_2014 - fdi_mfg_c_2009,
    delta_fdi_svc = fdi_svc_c_2014 - fdi_svc_c_2009,
    delta_log_migration = log_migration_c_2014 - log_migration_c_2009,
    delta_migration_share = migration_share_c_2014 - migration_share_c_2009,
    delta_product_total_log = product_total_log_2014 - product_total_log_2009,
    delta_product_mfg_log = product_mfg_log_2014 - product_mfg_log_2009,
    delta_product_svc_log = product_svc_log_2014 - product_svc_log_2009,
    delta_product_total_share =
      product_total_share_2014 - product_total_share_2009,
    delta_product_mfg_share =
      product_mfg_share_2014 - product_mfg_share_2009,
    delta_product_svc_share =
      product_svc_share_2014 - product_svc_share_2009,
    pc_changed_between_waves = case_when(
      is.na(pc_2009) | is.na(pc_2014) ~ NA,
      TRUE ~ pc_2009 != pc_2014
    ),
    pc_for_clustering = coalesce(pc_2014, pc_2009),
    pc_cluster_id = paste(state_no, pc_for_clustering, sep = "_"),
    ac_uid = paste(state_no, ac, sep = "_"),
    state_fe = factor(state_no)
  ) %>%
  select(
    state_no,
    ac,
    ac_uid,
    state_fe,
    pc_2009,
    pc_2014,
    pc_for_clustering,
    pc_cluster_id,
    pc_changed_between_waves,
    delta_fr_vote_share,
    starts_with("delta_fdi_"),
    delta_log_migration,
    delta_migration_share,
    starts_with("delta_product_")
  ) %>%
  arrange(state_no, ac)

assert_unique_rows(
  ac_first_difference,
  c("state_no", "ac"),
  "First-difference AC data"
)

# Explicitly verify that obsolete variables do not enter any saved regression
# dataset. They may remain in upstream raw objects used for auditing.
regression_datasets <- list(
  ac_year_levels = ac_year_levels,
  ac_first_difference = ac_first_difference,
  voter_year_pooled = voter_year_pooled,
  ac_year_ideology_counts = ac_year_ideology_counts
)

forbidden_saved_variables <- c(
  "m_emp_rate",
  "pc_gdp_election",
  "pc_gdp_2009",
  "pc_gdp_2013",
  "delta_pc_gdp"
)

for (dataset_name in names(regression_datasets)) {
  leaked <- intersect(
    forbidden_saved_variables,
    names(regression_datasets[[dataset_name]])
  )

  if (length(leaked) > 0) {
    stop(
      "Forbidden variables in ", dataset_name, ": ",
      paste(leaked, collapse = ", ")
    )
  }
}

# Retain the earlier human-readable name for composition diagnostics.
ac_ideology_summary <- ac_year_moderate_summary
```

```{r 18-validate-and-save-replacement-model-ready-data}
# Save stable analysis inputs and diagnostics. The analysis script loads these
# files rather than rerunning the raw-data and spatial-cleaning pipeline.

levels_diagnostics <- ac_year_levels %>%
  summarise(
    n_rows = n(),
    n_acs = n_distinct(ac_uid),
    n_pcs = n_distinct(pc_cluster_id),
    missing_vote_share = sum(is.na(fr_party_vote_share)),
    missing_log_migration = sum(is.na(log_migration_c)),
    missing_migration_share = sum(is.na(migration_share_c)),
    missing_prior_migrant_share = sum(is.na(prior_migrant_share_c)),
    missing_total_fdi = sum(is.na(fdi_total_c)),
    missing_moderate_share = sum(is.na(moderate_share_10pp_c)),
    .by = year
  )

first_difference_pairing_diagnostics <- tibble(
  ac_year_rows = nrow(ac_year_levels),
  unique_acs_in_levels = n_distinct(ac_year_levels$ac_uid),
  paired_acs = nrow(ac_first_difference),
  pc_changed_between_waves = sum(
    ac_first_difference$pc_changed_between_waves,
    na.rm = TRUE
  )
)

migration_diagnostics <- migration_five_year %>%
  summarise(
    n_ac_years = n(),
    mean_observed_years = mean(mig_5yr_observed_years, na.rm = TRUE),
    mean_imputed_years = mean(mig_5yr_imputed_years, na.rm = TRUE),
    share_any_imputation = mean(mig_5yr_imputed_years > 0, na.rm = TRUE),
    share_missing_total = mean(is.na(mig_5yr_total)),
    .by = year
  )

ideology_diagnostics <- bind_rows(
  nes_2009_clean %>%
    transmute(
      year = 2009L,
      recognition_n_valid,
      statism_n_valid,
      voter_ideology
    ),
  nes_2014_clean %>%
    transmute(
      year = 2014L,
      recognition_n_valid,
      statism_n_valid,
      voter_ideology
    )
) %>%
  summarise(
    n_respondents = n(),
    n_classified = sum(!is.na(voter_ideology)),
    classified_share = mean(!is.na(voter_ideology)),
    left_share_all = mean(voter_ideology == "L", na.rm = TRUE),
    center_share_all = mean(voter_ideology == "C", na.rm = TRUE),
    right_share_all = mean(voter_ideology == "R", na.rm = TRUE),
    mean_recognition_items = mean(recognition_n_valid, na.rm = TRUE),
    mean_statism_items = mean(statism_n_valid, na.rm = TRUE),
    .by = year
  )

voter_merge_diagnostics <- voter_year_pooled %>%
  summarise(
    n_voters = n(),
    matched_ac_year = sum(!is.na(ac_uid)),
    matched_share = mean(!is.na(ac_uid)),
    survey_pc_comparable = sum(!is.na(survey_pc_matches_election_pc)),
    survey_pc_match_share = mean(
      survey_pc_matches_election_pc,
      na.rm = TRUE
    ),
    n_far_right_vote_observed = sum(!is.na(fr_vote)),
    n_ideology_classified = sum(!is.na(voter_ideology)),
    validated_weight_available = any(survey_weight_validated),
    .by = year
  )

moderate_share_diagnostics <- ac_year_moderate_summary %>%
  summarise(
    n_ac_years = n(),
    median_respondents = median(n_survey_respondents, na.rm = TRUE),
    median_classified = median(n_classified_ideology, na.rm = TRUE),
    median_classification_rate = median(
      ideology_classification_rate,
      na.rm = TRUE
    ),
    missing_moderate_share = sum(is.na(moderate_share_unweighted_pp)),
    validated_weight_available = any(survey_weight_validated),
    .by = year
  )

ideology_cell_size_diagnostics <- ac_year_ideology_counts %>%
  summarise(
    n_cells = n(),
    median_valid_vote_n = median(n_valid_vote, na.rm = TRUE),
    cells_with_fewer_than_5_valid_votes = sum(n_valid_vote < 5),
    cells_with_fewer_than_10_valid_votes = sum(n_valid_vote < 10),
    .by = c(year, voter_ideology)
  )

analysis_variable_missingness <- bind_rows(
  ac_year_levels %>%
    summarise(
      across(
        c(
          fr_party_vote_share,
          fdi_total_c,
          fdi_mfg_c,
          fdi_svc_c,
          log_migration_c,
          migration_share_c,
          emp_rate_c,
          sc_share_c,
          st_share_c,
          log_population_c,
          log_land_area_c,
          prior_migrant_share_c,
          moderate_share_10pp_c
        ),
        ~ sum(is.na(.x))
      )
    ) %>%
    pivot_longer(everything(), names_to = "variable", values_to = "missing") %>%
    mutate(dataset = "ac_year_levels", .before = 1),
  ac_first_difference %>%
    summarise(
      across(
        c(
          delta_fr_vote_share,
          delta_fdi_total,
          delta_fdi_mfg,
          delta_fdi_svc,
          delta_log_migration,
          delta_migration_share,
          starts_with("delta_product_")
        ),
        ~ sum(is.na(.x))
      )
    ) %>%
    pivot_longer(everything(), names_to = "variable", values_to = "missing") %>%
    mutate(dataset = "ac_first_difference", .before = 1)
)

model_ready_dataset_summary <- tribble(
  ~dataset, ~rows, ~unit,
  "ac_year_levels", nrow(ac_year_levels), "AC-election year",
  "ac_first_difference", nrow(ac_first_difference), "AC paired 2009-2014",
  "voter_year_pooled", nrow(voter_year_pooled), "NES respondent",
  "ac_year_ideology_counts", nrow(ac_year_ideology_counts), "AC-election year × ideology",
  "ideology_item_responses_long", nrow(ideology_item_responses_long), "respondent-item"
)

write_csv(levels_diagnostics, file.path(DIAGNOSTIC_DIR, "levels_diagnostics.csv"))
write_csv(
  first_difference_pairing_diagnostics,
  file.path(DIAGNOSTIC_DIR, "first_difference_pairing_diagnostics.csv")
)
write_csv(
  time_invariant_diagnostics,
  file.path(DIAGNOSTIC_DIR, "first_difference_time_invariant_checks.csv")
)
write_csv(migration_diagnostics, file.path(DIAGNOSTIC_DIR, "migration_diagnostics.csv"))
write_csv(ideology_diagnostics, file.path(DIAGNOSTIC_DIR, "ideology_diagnostics.csv"))
write_csv(voter_merge_diagnostics, file.path(DIAGNOSTIC_DIR, "voter_merge_diagnostics.csv"))
write_csv(
  moderate_share_diagnostics,
  file.path(DIAGNOSTIC_DIR, "moderate_share_diagnostics.csv")
)
write_csv(
  ideology_cell_size_diagnostics,
  file.path(DIAGNOSTIC_DIR, "ideology_cell_size_diagnostics.csv")
)
write_csv(
  analysis_variable_missingness,
  file.path(DIAGNOSTIC_DIR, "analysis_variable_missingness.csv")
)
write_csv(
  centering_diagnostics,
  file.path(DIAGNOSTIC_DIR, "centering_diagnostics.csv")
)
write_csv(
  centering_constants,
  file.path(DERIVED_DIR, "centering_constants.csv")
)
write_csv(
  model_ready_dataset_summary,
  file.path(DERIVED_DIR, "model_ready_dataset_summary.csv")
)
write_csv(ac_ideology_summary, file.path(DERIVED_DIR, "ac_ideology_summary.csv"))

saveRDS(ac_year_levels, file.path(DERIVED_DIR, "ac_year_levels.rds"))
saveRDS(ac_first_difference, file.path(DERIVED_DIR, "ac_first_difference.rds"))
saveRDS(voter_year_pooled, file.path(DERIVED_DIR, "voter_year_pooled.rds"))
saveRDS(
  ac_year_ideology_counts,
  file.path(DERIVED_DIR, "ac_year_ideology_counts.rds")
)
saveRDS(
  ideology_item_responses_long,
  file.path(DERIVED_DIR, "ideology_item_responses_long.rds")
)
saveRDS(
  ac_year_moderate_summary,
  file.path(DERIVED_DIR, "ac_year_moderate_summary.rds")
)
saveRDS(migration_annual_ac, file.path(DERIVED_DIR, "migration_annual_ac.rds"))
saveRDS(migration_five_year, file.path(DERIVED_DIR, "migration_five_year.rds"))

manifest <- tribble(
  ~file, ~unit, ~description,
  "ac_year_levels.rds", "AC-election year", "Centered levels data for pooled contextual models",
  "ac_first_difference.rds", "AC paired 2009-2014", "First differences and changes in centered FDI-migration products",
  "voter_year_pooled.rds", "NES respondent", "Classified voter ideology and common centered AC-year exposures",
  "ac_year_ideology_counts.rds", "AC-election year × ideology", "Integer far-right and non-far-right counts for grouped binomial models",
  "ideology_item_responses_long.rds", "Respondent-item", "Original and scored ideology-question responses",
  "ac_year_moderate_summary.rds", "AC-election year", "Unweighted and optional weighted ideology composition",
  "centering_constants.csv", "Variable", "Common AC-year centering constants and scaling factors",
  "migration_annual_ac.rds", "AC-calendar year", "Annualized migration duration-bin estimates",
  "migration_five_year.rds", "AC-election year", "Five-year migration totals, shares, and imputation diagnostics"
)

write_csv(manifest, file.path(DERIVED_DIR, "data_manifest.csv"))

manifest
model_ready_dataset_summary
levels_diagnostics
first_difference_pairing_diagnostics
centering_diagnostics
voter_merge_diagnostics
ideology_cell_size_diagnostics
```

