---
title: "Switchers-India"
output: 
  html_document: 
    keep_md: true
date: "2026-03-24"
---
This code has been prepared to merge assembly constituency (AC) level election data from 2009 and 2014 with census indicators, SHRUG data, migration data, political party data, and Lokniti data from 2009 to 2014.

```{r Load libraries, message = FALSE}
library(tidyverse)
library(foreign)
library(xtable)
library(haven)
library(sf)
library(janitor)
library(broom)
```

```{r Create helper functions for loading data, message = FALSE}
# Build a helper function for cleaning PC names for use as labels
clean_constituency_name <- function(x) {
  x %>%
    as.character() %>%
    str_replace_all("\u00A0", " ") %>%          # replace non-breaking spaces
    str_to_upper() %>%                          # standardize case
    str_remove_all("\\s*\\((SC|ST)\\)\\s*") %>% # remove (SC) or (ST)
    str_replace_all("[^A-Z0-9]+", " ") %>%      # standardize punctuation/spaces
    str_squish()                                # collapse repeated spaces
}

# Build a helper function to avoid carrying over missing constituency names
first_nonmissing <- function(x) {
  x <- x[!is.na(x) & x != ""]
  if (length(x) == 0) NA_character_ else x[1]
}
```

```{r Load and clean 2009 AC voting data, message = FALSE}
# Load Jensenius et al.'s voting data for 2009
fileshere <- list.files("data/jensenius_et_al/PSdata_2009",
                        pattern = ".csv",
                        recursive = TRUE,
                        full.names = TRUE
                        )

# Merge state voting data into a single file 
for (h in 1:length(fileshere)) {
  onefile <- read.csv(fileshere[h])
  
  if (h == 1) {
    PSdata_2009 <- onefile
  } else {
    PSdata_2009 <- rbind(PSdata_2009, onefile)
  }
}

# Group voting data to the AC level
ACdata_2009 <- PSdata_2009 %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    PC_no = as.integer(PC_no),
    AC_no = as.integer(AC_no),
    PC_name = clean_constituency_name(PC_name),
    AC_name = clean_constituency_name(AC_name)
  ) %>% 
  group_by(State_no2011, AC_no) %>% 
  summarise(
    PC_no_09 = first_nonmissing(PC_no),
    PC_name_09 = first_nonmissing(PC_name),
    AC_name_09 = first_nonmissing(AC_name),
    across(starts_with("Votes_"), ~ sum(.x, na.rm = TRUE)),
    .groups = "drop"
  ) %>% 
  rename_with(
    ~ paste0(.x, "_09"),
    starts_with("Votes_")
  )
```

```{r Load and clean 2009 AC merge data, message = FALSE}
# Load 2009 merge files
fileshere <- list.files("data/jensenius_et_al/Mergefiles_2009", 
                        pattern = ".csv", 
                        recursive = TRUE, 
                        full.names = TRUE)

# Merge 2009 merge files into a single file
for (h in 1:length(fileshere)) {
  onefile <- read.csv(fileshere[h])
  
  if (h == 1) {
    merge_2009 <- onefile
    } else {
      merge_2009 <- rbind(merge_2009, onefile)	
    }
}

# Group voting data to the AC level and calculate the number of voters
ACmerge_2009 <- merge_2009 %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    AC_no = as.integer(AC_no),
    District_name2011 = clean_constituency_name(District_name2011),
    AC_name = clean_constituency_name(AC_name)
  ) %>% 
  group_by(State_no2011, AC_no) %>% 
  summarise(
    Electors_09 = sum(Electors, na.rm = TRUE),
    District_no2011_09 = first_nonmissing(District_no2011),
    District_name2011_09 = first_nonmissing(District_name2011),
    AC_name_09 = first_nonmissing(AC_name),
    .groups = "drop"
  )
```

```{r Merge 2009 voting and merge files}
elec_09 <- ACdata_2009 %>% 
  left_join(
    ACmerge_2009,
    by = c("State_no2011", "AC_no"),
    relationship = "one-to-one"
  )
```

```{r Load and clean 2014 AC voting data, message = FALSE}
# Load Jensenius et al.'s voting data for 2014
fileshere <- list.files("data/jensenius_et_al/PSdata_2014",
                        pattern = ".csv",
                        recursive = TRUE,
                        full.names = TRUE
                        )

# Merge state voting data into a single file 
for (h in 1:length(fileshere)) {
  onefile <- read.csv(fileshere[h])
  
  if (h == 1) {
    PSdata_2014 <- onefile
  } else {
    PSdata_2014 <- rbind(PSdata_2014, onefile)
  }
}

# Group voting data to the AC level
ACdata_2014 <- PSdata_2014 %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    PC_no = as.integer(PC_no),
    AC_no = as.integer(AC_no),
    PC_name = clean_constituency_name(PC_name),
    AC_name = clean_constituency_name(AC_name)
  ) %>% 
  group_by(State_no2011, AC_no) %>% 
  summarise(
    PC_no_14 = first_nonmissing(PC_no),
    PC_name_14 = first_nonmissing(PC_name),
    AC_name_14 = first_nonmissing(AC_name),
    across(starts_with("Votes_"), ~ sum(.x, na.rm = TRUE)),
    .groups = "drop"
  ) %>% 
  rename_with(
    ~ paste0(.x, "_14"),
    starts_with("Votes_")
  )
```

```{r Load and clean 2014 AC merge data, message = FALSE}
# Load 2014 merge files
fileshere <- list.files("data/jensenius_et_al/Mergefiles_2014", 
                        pattern = ".csv", 
                        recursive = TRUE, 
                        full.names = TRUE)

# Merge 2014 merge files into a single file
for (h in 1:length(fileshere)) {
  onefile <- read.csv(fileshere[h])
  
  if (h == 1) {
    merge_2014 <- onefile
    } else {
      merge_2014 <- rbind(merge_2014, onefile)	
    }
}

# Group voting data to the AC level and calculate the number of voters
ACmerge_2014 <- merge_2014 %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    AC_no = as.integer(AC_no),
    District_name2011 = clean_constituency_name(District_name2011),
    AC_name = clean_constituency_name(AC_name)
  ) %>% 
  group_by(State_no2011, AC_no) %>% 
  summarise(
    Electors_14 = sum(Electors, na.rm = TRUE),
    District_no2011_14 = first_nonmissing(District_no2011),
    District_name2011_14 = first_nonmissing(District_name2011),
    AC_name_14 = first_nonmissing(AC_name),
    .groups = "drop"
  )
```

```{r Merge 2014 voting and merge files}
elec_14 <- ACdata_2014 %>% 
  left_join(
    ACmerge_2014,
    by = c("State_no2011", "AC_no"),
    relationship = "one-to-one"
  )
```

```{r Merge 2009 and 2014 election files}
elec <- elec_09 %>% 
  left_join(elec_14, by = c("State_no2011", "AC_no"))
```

```{r Load candidate data and clean state IDs, message = FALSE}
# Load candidate information files
cand_noUP_09 <- read_csv("data/jensenius_et_al/Candidates_2009/candidate_order2009_noUP.csv")
cand_UP_09   <- read_csv("data/jensenius_et_al/Candidates_2009/candidate_order2009_UP.csv")
cand_14      <- read_csv("data/jensenius_et_al/Candidates_2014/candidate_order2014.csv")

# Assign state codes to states in the data
state_codes <- function(df) {
  df %>%
    mutate(
      State_no2011 = case_when(
        State_name == "Andhra Pradesh" ~ 28,
        State_name == "Bihar" ~ 10,
        State_name == "Gujarat" ~ 24,
        State_name == "Himachal Pradesh" ~ 2,
        State_name == "Jharkhand" ~ 20,
        State_name == "Madhya Pradesh" ~ 23,
        State_name == "Punjab" ~ 3,
        State_name == "Rajasthan" ~ 8,
        State_name == "Uttar Pradesh" ~ 9,
        State_name == "Uttarakhand" ~ 5,
        State_name == "West Bengal" ~ 19,
        TRUE ~ NA_integer_
      )
    )
}
```

```{r Create a far-right candidate lookup}
fr_parties <- c("BJP", "SHS")

fr_lookup <- function(cand_df, year, party_col = "Cand_party") {
  cand_df %>% 
    state_codes() %>% 
    mutate(
      Cand_no = as.integer(Cand_no)
    ) %>% 
    filter(.data[[party_col]] %in% fr_parties) %>% 
    group_by(State_no2011, PC_id) %>% 
    summarise(
      fr_cand = as.integer(n() > 0),
      fr_cand_nos = list(sort(unique(Cand_no[!is.na(Cand_no)]))),
      .groups = "drop"
    ) %>% 
    rename(
      !!paste0("fr_cand_", year) := fr_cand,
      !!paste0("fr_cand_nos_", year) := fr_cand_nos
    )
}
```

```{r Extract far-right candidate IDs}
fr_cands_09 <- bind_rows(cand_noUP_09, cand_UP_09) %>% 
  fr_lookup(year = "09", party_col = "Cand_party")

fr_cands_14 <- cand_14 %>% 
  fr_lookup(year = "14", party_col = "Cand_party")
```

```{r Define vote summation}
sum_candidate_votes <- function(df, cand_list_col, vote_suffix) {
  
  cand_lists <- df[[cand_list_col]]
  out <- rep(NA_real_, nrow(df))
  
  for (i in seq_len(nrow(df))) {
    
    cand_nos <- cand_lists[[i]]
    
    if (is.null(cand_nos) || length(cand_nos) == 0 || all(is.na(cand_nos))) {
      out[i] <- 0
      next
    }
    
    vote_cols <- paste0("Votes_cand", cand_nos, vote_suffix)
    vote_cols <- vote_cols[vote_cols %in% names(df)]
    
    if (length(vote_cols) == 0) {
      out[i] <- NA_real_
      next
    }
    
    vals <- unlist(df[i, vote_cols], use.names = FALSE)
    out[i] <- sum(vals, na.rm = TRUE)
  }
  
  out
}
```

```{r Join candidate files with election data}
elec_cand <- elec %>%
  left_join(
    fr_cands_09,
    by = c("State_no2011", "PC_no_09" = "PC_id"),
    relationship = "many-to-one"
  ) %>%
  left_join(
    fr_cands_14,
    by = c("State_no2011", "PC_no_14" = "PC_id"),
    relationship = "many-to-one"
  ) %>%
  mutate(
    fr_cands_09 = coalesce(fr_cand_09, 0L),
    fr_cands_14 = coalesce(fr_cand_14, 0L)
  )

elec_cand$fr_votes_09 <- sum_candidate_votes(
  elec_cand,
  cand_list_col = "fr_cand_nos_09",
  vote_suffix = "_09"
)

elec_cand$fr_votes_14 <- sum_candidate_votes(
  elec_cand,
  cand_list_col = "fr_cand_nos_14",
  vote_suffix = "_14"
)

elec_cand <- elec_cand %>%
  mutate(
    fr_vote_share_09 = if_else(
      !is.na(Votes_total_09) & Votes_total_09 > 0,
      fr_votes_09 / Votes_total_09,
      NA_real_
    ),
    
    fr_vote_share_14 = if_else(
      !is.na(Votes_total_14) & Votes_total_14 > 0,
      fr_votes_14 / Votes_total_14,
      NA_real_
    ),
    
    fr_vote_share_change = if_else(
      is.finite(fr_vote_share_09) & is.finite(fr_vote_share_14),
      fr_vote_share_14 - fr_vote_share_09,
      NA_real_
    )
  )
```

```{r Establish Lokniti state recoding}
nes_state_recode <- function(x) {
  case_when(
    x == 1 ~ 28,   # AP
    x == 4 ~ 10,   # BH
    x == 6 ~ 24,   # GJ
    x == 8 ~ 2,    # HP
    x == 33 ~ 20,  # JH
    x == 12 ~ 23,  # MP
    x == 19 ~ 3,   # PJ
    x == 20 ~ 8,   # RJ
    x == 24 ~ 9,   # UP
    x == 25 ~ 19,  # WB
    x == 35 ~ 5,   # UK
    TRUE ~ NA_integer_
  )
}
```

```{r Add a helper for safe Lokniti z-score computation}
safe_z <- function(x) {
  x <- as.numeric(x)
  m <- mean(x, na.rm = TRUE)
  s <- sd(x, na.rm = TRUE)
  
  if (is.na(s) || s == 0) {
    return(rep(NA_real_, length(x)))
  }
  
  (x - m) / s
}
```

```{r Clean 2009 Lokniti data, message = FALSE}
nes_2009 <- read_sav("data/lokniti/nes_2009.sav") %>% 
  mutate(State_no2011 = nes_state_recode(as.numeric(st_id))) %>% 
  filter(!is.na(State_no2011)) %>% 
  mutate(
    q26a = case_match(q26a, 1 ~ 2, 2 ~ 1, 8 ~ 0, 3 ~ -1, 4 ~ -2),
    q27 = case_match(q27, 2 ~ 1, c(7, 8) ~ 0, 1 ~ -1),
    a4b = case_match(a4b, 4 ~ 2, 3 ~ 1, 8 ~ 0, 2 ~ -1, 1 ~ -2),
    a4c = case_match(a4c, 1 ~ 2, 2 ~ 1, 8 ~ 0, 3 ~ -1, 4 ~ -2),
    a4d = case_match(a4d, 1 ~ 2, 2 ~ 1, 8 ~ 0, 3 ~ -1, 4 ~ -2),
    a4g = case_match(a4g, 4 ~ 2, 3 ~ 1, 8 ~ 0, 2 ~ -1, 1 ~ -2),
    a5 = case_match(a5, 2 ~ 1, 8 ~ 0, 1 ~ -1),
    a6a = case_match(a6a, 2 ~ 1, 8 ~ 0, 1 ~ -1),
    a6b = case_match(a6b, 2 ~ 1, 8 ~ 0, 1 ~ -1),
    
    z_q26a = safe_z(q26a),
    z_q27  = safe_z(q27),
    z_a4b  = safe_z(a4b),
    z_a4c  = safe_z(a4c),
    z_a4d  = safe_z(a4d),
    z_a4g  = safe_z(a4g),
    z_a5   = safe_z(a5),
    z_a6a  = safe_z(a6a),
    z_a6b  = safe_z(a6b)
  )

bjp_codes <- c(2, 46, 91)

vote_share <- function(vote, condition, codes = bjp_codes) {
  x <- vote[condition & !is.na(condition)]
  
  if (length(x) == 0) {
    return(NA_real_)
  }
  
  mean(if_else(is.na(x), NA, x %in% codes), na.rm = TRUE)
}

nes_2009_scored <- nes_2009 %>%
  mutate(
    recognition_score = rowMeans(
      pick(z_a6a, z_a5, z_a4c, z_a4b),
      na.rm = TRUE
    ),
    statism_score = rowMeans(
      pick(z_a4d, z_a4g, z_q26a, z_a6b, z_q27),
      na.rm = TRUE
    ),
    recognition_score = if_else(is.nan(recognition_score), NA_real_, recognition_score),
    statism_score = if_else(is.nan(statism_score), NA_real_, statism_score)
  )

group_nes_2009 <- nes_2009_scored %>% 
  group_by(State_no2011, ac_id) %>% 
  summarise(
    loc_bjp_vote_share_2009 = vote_share(q1a, TRUE),
    loc_bjp_close_to_2009 = vote_share(q11a, TRUE),
    loc_bjp_never_vote_2009 = vote_share(q12a, TRUE),
    
    recognition_score_2009 = mean(recognition_score, na.rm = TRUE),
    statism_score_2009 = mean(statism_score, na.rm = TRUE),
    
    mean_econ_trend_2009 = mean(e2, na.rm = TRUE),
    mean_educ_2009 = mean(z5, na.rm = TRUE),
    
    loc_up_caste_share_2009 = sum(z7a == 4 & z8 %in% c(1, 4, 6), na.rm = TRUE) / 
      sum(!is.na(z7a) & !is.na(z8)),
    
    loc_h_obc_share_2009 = sum(z7a == 3 & z8 == 1, na.rm = TRUE) / 
      sum(!is.na(z7a) & !is.na(z8)),
    
    mean_hhi_2009 = mean(z18, na.rm = TRUE),
    
    loc_bjp_mod_vote_share_2009 = vote_share(
      q1a,
      recognition_score > -0.25 & recognition_score < 0.25 &
        statism_score > -0.25 & statism_score < 0.25
    ),
    
    loc_bjp_right_vote_share_2009 = vote_share(
      q1a,
      recognition_score > 0.25 &
        statism_score > 0.25
    ),
    
    loc_bjp_left_vote_share_2009 = vote_share(
      q1a,
      recognition_score < -0.25 &
        statism_score < -0.25
    ),
    
    .groups = "drop"
  ) %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    ac_id = as.integer(ac_id)
  )
```

```{r Clean 2014 Lokniti data, message = FALSE}
nes_2014 <- read_sav("data/lokniti/nes_2014.sav") %>% 
  mutate(State_no2011 = nes_state_recode(as.numeric(state_id))) %>% 
  filter(!is.na(State_no2011)) %>% 
  mutate(
    q10b = case_match(q10b, 1 ~ 2, 2 ~ 1, 8 ~ 0, 3 ~ -1, 4 ~ -2),
    z_q10b = (q10b - mean(q10b)) / sd(q10b),
    
    q10e = case_match(q10e, 4 ~ 2, 3 ~ 1, 8 ~ 0, 2 ~ -1, 1 ~ -2),
    z_q10e = (q10e - mean(q10e)) / sd(q10e),
    
    q23c = case_match(q23c, 4 ~ 2, 3 ~ 1, 8 ~ 0, 2 ~ -1, 1 ~ -2), # this should have been 23d...
    z_q23c = (q23c - mean(q23c)) / sd(q23c)
  )

nes_2014_scored <- nes_2014 %>%
  mutate(
    recognition_score = rowMeans(
      pick(z_q10b, z_q10e),
      na.rm = TRUE
    ),
    statism_score = q23c,
    
    recognition_score = if_else(is.nan(recognition_score), NA_real_, recognition_score),
    statism_score = if_else(is.nan(statism_score), NA_real_, statism_score)
  )

group_nes_2014 <- nes_2014_scored %>% 
  group_by(State_no2011, ac_id) %>% 
  summarise(
    loc_bjp_vote_share_2014 = vote_share(q1a, TRUE),
    loc_bjp_close_to_2014 = vote_share(q11a, TRUE),
    
    recognition_score_2014 = mean(recognition_score, na.rm = TRUE),
    statism_score_2014 = mean(statism_score, na.rm = TRUE),
    
    mean_educ_2014 = mean(z3, na.rm = TRUE),
    
    loc_up_caste_share_2014 = sum(z5a == 4 & z6 %in% c(1, 4, 6), na.rm = TRUE) / 
      sum(!is.na(z5a) & !is.na(z6)),
    
    loc_h_obc_share_2014 = sum(z5a == 3 & z6 == 1, na.rm = TRUE) / 
      sum(!is.na(z5a) & !is.na(z6)),
    
    mean_hhi_2014 = mean(z13, na.rm = TRUE),
    
    loc_bjp_mod_vote_share_2014 = vote_share(
      q1a,
      recognition_score > -0.25 & recognition_score < 0.25 &
        statism_score > -0.25 & statism_score < 0.25
    ),
    
    loc_bjp_right_vote_share_2014 = vote_share(
      q1a,
      recognition_score > 0.25 &
        statism_score > 0.25
    ),
    
    loc_bjp_left_vote_share_2014 = vote_share(
      q1a,
      recognition_score < -0.25 &
        statism_score < -0.25
    ),
    
    .groups = "drop"
  ) %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    ac_id = as.integer(ac_id)
  )
```

```{r Join 2009 and 2014 Lokniti data to main data file}
elec_cand_nes <- elec_cand %>% 
  left_join(group_nes_2009, by = c("State_no2011", "AC_no" = "ac_id")) %>% 
  left_join(group_nes_2014, by = c("State_no2011", "AC_no" = "ac_id"))

# Remove unnecessary columns
elec_cand_nes <- elec_cand_nes %>% 
  select(c(State_no2011, AC_no, PC_no_09, PC_name_09, AC_name_09.x, Votes_total_09,
         Electors_09, District_no2011_09, District_name2011_09, PC_no_14,
         PC_name_14, AC_name_14.x, Votes_total_14, Electors_14, District_no2011_14,
         District_name2011_14, fr_cands_09, fr_cands_14, fr_votes_09, fr_votes_14,
         fr_vote_share_09, fr_vote_share_14, fr_vote_share_change, 118:135)) %>% 
  mutate(
    District_no2011_09 = as.integer(District_no2011_09),
    District_no2011_14 = as.integer(District_no2011_14),
    District_no2011 = coalesce(District_no2011_14, District_no2011_09)
    ) %>% 
  select(-c(District_no2011_09, District_no2011_14, District_name2011_09))
```

```{r Merge in EC 2013 and PC 2011 data}
# Create an object to save 
ec13_cols <- c(
  "ec13_emp_all", "ec13_emp_f", "ec13_emp_m", "ec13_emp_gov",
  "ec13_emp_priv", "ec13_emp_own_m", "ec13_emp_own_f",
  "ec13_emp_st", "ec13_emp_sc", "ec13_emp_obc"
)

# Create within-district weights based on each AC's share of the district's total electors
district_elector_weights <- elec_cand_nes %>%
  mutate(
    State_no2011 = as.integer(State_no2011),
    District_no2011 = as.integer(District_no2011),
    AC_no = as.integer(AC_no),
    Electors_14 = as.numeric(Electors_14)
  ) %>%
  distinct(State_no2011, District_no2011, AC_no, Electors_14) %>%
  filter(
    !is.na(State_no2011),
    !is.na(District_no2011),
    !is.na(AC_no)
  ) %>%
  group_by(State_no2011, District_no2011) %>%
  mutate(
    district_electors_14 = sum(Electors_14, na.rm = TRUE),
    elector_weight_14 = if_else(
      !is.na(Electors_14) & district_electors_14 > 0,
      Electors_14 / district_electors_14,
      NA_real_
    )
  ) %>%
  ungroup() %>%
  select(
    State_no2011,
    District_no2011,
    AC_no,
    Electors_14,
    district_electors_14,
    elector_weight_14
  )

shrug_ec13 <- read_csv(
  "data/shrug/ec13_pc11dist.csv",
  show_col_types = FALSE
) %>% 
  mutate(
    pc11_state_id = str_remove(pc11_state_id, "^0+") %>% as.integer(),
    pc11_district_id = str_remove(pc11_district_id, "^0+") %>% as.integer()
  ) %>% 
  select(
    pc11_state_id,
    pc11_district_id,
    all_of(ec13_cols)
  )

elec_cand_nes_ec <- elec_cand_nes %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    District_no2011 = as.integer(District_no2011),
    AC_no = as.integer(AC_no),
    Electors_14 = as.numeric(Electors_14)
  ) %>%
  left_join(
    shrug_ec13,
    by = c(
      "State_no2011" = "pc11_state_id",
      "District_no2011" = "pc11_district_id"
    ),
    relationship = "many-to-one"
  ) %>%
  group_by(State_no2011, District_no2011) %>%
  mutate(
    n_acs_in_district = n_distinct(AC_no),
    district_electors_14 = sum(Electors_14, na.rm = TRUE),
    
    elector_weight_14 = case_when(
      !is.na(Electors_14) & district_electors_14 > 0 ~
        Electors_14 / district_electors_14,
      
      district_electors_14 == 0 & n_acs_in_district > 0 ~
        1 / n_acs_in_district,
      
      TRUE ~ NA_real_
    )
  ) %>%
  ungroup() %>%
  mutate(
    across(
      all_of(ec13_cols),
      ~ .x * elector_weight_14,
      .names = "{.col}_ac_alloc"
    )
  )
```

```{r Merge in migration data and impute missing values}
migra <- list.files(
  path = "data/migration",
  pattern = "_2001_2011_merged\\.csv$",
  full.names = TRUE
)

migra_cols <- c(
  "2011_Total_Persons_<1",
  "2011_Total_Persons_1-4",
  "2011_Total_Persons_5-9"
)

dist_migra <- migra %>% 
  set_names() %>% 
  map_dfr(\(f) {
    read_csv(f, show_col_types = FALSE) %>%
      select(
        State,
        `2011_District`,
        Last_Residence,
        all_of(migra_cols)
      ) %>%
      mutate(
        State = as.integer(State),
        `2011_District` = as.integer(`2011_District`)
      ) %>%
      filter(
        Last_Residence == "STATES IN INDIA BEYOND THE STATE OF ENUMERATION",
        !is.na(`2011_District`),
        `2011_District` != 0
      ) %>%
      group_by(State, `2011_District`) %>%
      summarise(
        across(all_of(migra_cols), ~ sum(.x, na.rm = TRUE)),
        .groups = "drop"
      )
  }) %>%
  group_by(State, `2011_District`) %>%  
  summarise(
    across(all_of(migra_cols), ~ sum(.x, na.rm = TRUE)),
    .groups = "drop"
  )

elec_cand_nes_ec_m <- elec_cand_nes_ec %>%
  mutate(
    State_no2011 = as.integer(State_no2011),
    District_no2011 = as.integer(District_no2011),
    AC_no = as.integer(AC_no),
    Electors_09 = as.numeric(Electors_09)
  ) %>%
  left_join(
    dist_migra,
    by = c(
      "State_no2011" = "State",
      "District_no2011" = "2011_District"
    ),
    relationship = "many-to-one"
  ) %>%
  replace_na(as.list(setNames(rep(0, length(migra_cols)), migra_cols))) %>%
  group_by(State_no2011, District_no2011) %>%
  mutate(
    n_acs_in_district = n_distinct(AC_no),
    district_electors_09 = sum(Electors_09, na.rm = TRUE),
    
    elector_weight_09 = case_when(
      !is.na(Electors_09) & district_electors_09 > 0 ~
        Electors_09 / district_electors_09,
      
      district_electors_09 == 0 & n_acs_in_district > 0 ~
        1 / n_acs_in_district,
      
      TRUE ~ NA_real_
    )
  ) %>%
  ungroup() %>%
  mutate(
    across(
      all_of(migra_cols),
      ~ .x * elector_weight_09,
      .names = "alloc_{.col}"
    ),
    
    across(
      starts_with("alloc_2011_Total_Persons"),
      ~ log1p(.x),
      .names = "log_{.col}"
    )
  )

# Calculate the change in average change in migration between 2009 and 2014
elec_cand_nes_ec_m <- elec_cand_nes_ec_m %>%
  mutate(
    agr_2009 = if_else(
      `alloc_2011_Total_Persons_5-9` > 0,
      (`alloc_2011_Total_Persons_1-4` / 4) /
        (`alloc_2011_Total_Persons_5-9` / 5),
      NA_real_
    ),
    
    agr_2014 = if_else(
      `alloc_2011_Total_Persons_1-4` > 0,
      `alloc_2011_Total_Persons_<1` /
        (`alloc_2011_Total_Persons_1-4` / 4),
      NA_real_
    ),
    
    log_agr_2009 = if_else(agr_2009 > 0, log(agr_2009), NA_real_),
    log_agr_2014 = if_else(agr_2014 > 0, log(agr_2014), NA_real_)
  )
```

```{r Read in assembly shape files and assign them to ACs}

# Data come from Susewind 2014
fileshere <- list.files("data/mapping-indias-elections",
                        pattern = ".assembly.shp",
                        recursive = TRUE,
                        full.names = TRUE
                        )

for (h in 1:length(fileshere)) {
  onefile <- read_sf(fileshere[h])
  
  if (h == 1) {
    ac_map <- onefile
  } else {
    ac_map <- rbind(ac_map, onefile)
  }
}

ac_map <- ac_map %>% 
  mutate(
      State_no2011 = case_when(
        state == "Andhra Pradesh" ~ 28,
        state == "Bihar" ~ 10,
        state == "Gujarat" ~ 24,
        state == "Himachal Pradesh" ~ 2,
        state == "Jharkhand" ~ 20,
        state == "Madhya Pradesh" ~ 23,
        state == "Punjab" ~ 3,
        state == "Rajasthan" ~ 8,
        state == "Uttar Pradesh" ~ 9,
        state == "Uttarakhand" ~ 5,
        state == "West Bengal" ~ 19,
        TRUE ~ NA_integer_
      )
  ) %>% 
  select(State_no2011, ac, ac_name, geometry)
```

```{r Read in FDI data and match sites to ACs}
fdi_raw <- read_csv("data/IN_FDI_2004_2014.csv")

fdi_coords <- fdi_raw %>%
  extract(
    col = Coordinates,
    into = c("lat", "lon"),
    regex = "^\\s*(-?\\d+(?:\\.\\d+)?)\\s*,\\s*(-?\\d+(?:\\.\\d+)?)\\s*$",
    remove = FALSE,
    convert = TRUE
  ) %>%
  mutate(
    has_coord = !is.na(lat) & !is.na(lon)
  )

fdi_points <- fdi_coords %>%
  filter(has_coord) %>%
  st_as_sf(
    coords = c("lon", "lat"),
    crs = 4326,
    remove = FALSE
  )

ac_clean <- ac_map %>%
  st_make_valid() %>%
  select(State_no2011, ac, geometry)

fdi_points <- st_transform(fdi_points, st_crs(ac_clean))

fdi_points_joined <- fdi_points %>%
  st_join(ac_clean, join = st_within, left = TRUE)

fdi_ac_lookup <- fdi_points_joined %>%
  st_drop_geometry() %>%
  select(`#`, State_no2011, ac)

fdi_final <- fdi_coords %>%
  left_join(fdi_ac_lookup, by = "#")
```

```{r Assign periods to FDI}
fdi_final <- fdi_final %>% 
  mutate(
    project_month = as.Date(parse_date_time(
      `Project date`,
      orders = c("b Y", "B Y")
    )),
    period = case_when(
      project_month >= as.Date("2004-04-01") &
        project_month <= as.Date("2009-04-01") ~ "1",
      
      project_month >= as.Date("2009-05-01") &
        project_month <= as.Date("2014-05-01") ~ "2",
      
      TRUE ~ NA_character_
    )
  )
```

```{r Pivot a dataframe with investment qualities included}
fdi_ac <- fdi_final %>%
  filter(!is.na(State_no2011), !is.na(ac)) %>%
  clean_names() %>%
  mutate(
    period_clean = make_clean_names(as.character(period), allow_dupes = TRUE),
    activity_clean = make_clean_names(activity, allow_dupes = TRUE)
  )

fdi_ac_totals <- fdi_ac %>%
  filter(!is.na(period_clean)) %>%
  group_by(state_no2011, ac, period_clean) %>%
  summarise(
    n = n(),
    capital = sum(capital_investment, na.rm = TRUE),
    jobs = sum(jobs_created, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_wider(
    id_cols = c(state_no2011, ac),
    names_from = period_clean,
    values_from = c(n, capital, jobs),
    names_glue = "fdi_{period_clean}_total_{.value}",
    values_fill = 0
  )

fdi_ac_by_activity <- fdi_ac %>%
  filter(
    !is.na(period_clean),
    !is.na(activity_clean)
  ) %>%
  group_by(state_no2011, ac, period_clean, activity_clean) %>%
  summarise(
    n = n(),
    capital = sum(capital_investment, na.rm = TRUE),
    jobs = sum(jobs_created, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_wider(
    id_cols = c(state_no2011, ac),
    names_from = c(period_clean, activity_clean),
    values_from = c(n, capital, jobs),
    names_glue = "fdi_{period_clean}_{activity_clean}_{.value}",
    values_fill = 0
  )

fdi_ac_summary <- fdi_ac_totals %>%
  full_join(
    fdi_ac_by_activity,
    by = c("state_no2011", "ac")
  ) %>%
  mutate(
    across(
      starts_with("fdi_"),
      ~ replace_na(.x, 0)
    )
  )

```

```{r Join FDI to AC}
fdi_ac_map <- ac_map %>% 
  left_join(fdi_ac_summary, by = c("State_no2011" = "state_no2011", "ac")) %>% 
  mutate(
    across(
      starts_with("fdi_"),
      ~ tidyr::replace_na(.x, 0)
    ),
    fdi_diff = fdi_x2_total_n - fdi_x1_total_n
  )

elec_cand_nes_ec_m_fdi <- fdi_ac_map %>% 
  left_join(elec_cand_nes_ec_m, by = c("State_no2011" = "State_no2011", "ac" = "AC_no"))
```

```{r Regression: FDI * migration increases FR vote share}
library(dplyr)
library(tidyr)
library(purrr)
library(stringr)
library(broom)
library(sf)

# -----------------------------
# 1. Prepare regression data
# -----------------------------

reg_data <- elec_cand_nes_ec_m_fdi %>%
  { if (inherits(., "sf")) sf::st_drop_geometry(.) else . }

dv <- "fr_vote_share_change"

migration_vars <- c(
  "alloc_2011_Total_Persons_<1",
  "alloc_2011_Total_Persons_1-4",                     
  "alloc_2011_Total_Persons_5-9", 
  "log_alloc_2011_Total_Persons_<1", 
  "log_alloc_2011_Total_Persons_1-4", 
  "log_alloc_2011_Total_Persons_5-9",
  "log_agr_2009",
  "agr_2009",
  "log_agr_2014",
  "agr_2014"
)

fdi_vars <- c(
  "fdi_diff",
  names(reg_data) %>% keep(~ str_detect(.x, "^fdi"))
) %>%
  unique()

control_vars <- c(
  "ec13_emp_all_ac_alloc",
  "ec13_emp_f_ac_alloc",
  "ec13_emp_m_ac_alloc",
  "ec13_emp_gov_ac_alloc",
  "ec13_emp_priv_ac_alloc",
  "ec13_emp_own_m_ac_alloc",
  "ec13_emp_own_f_ac_alloc",
  "ec13_emp_st_ac_alloc",
  "ec13_emp_sc_ac_alloc",
  "ec13_emp_obc_ac_alloc"
)

# -----------------------------
# 2. Check that variables exist
# -----------------------------

all_model_vars <- unique(c(dv, migration_vars, fdi_vars, control_vars))

missing_vars <- setdiff(all_model_vars, names(reg_data))

if (length(missing_vars) > 0) {
  stop(
    "These variables are missing from reg_data:\n",
    paste(missing_vars, collapse = "\n")
  )
}

# -----------------------------
# 3. Define control sets
# -----------------------------
# Avoid putting ec13_emp_all_ac_alloc in the same preferred specification
# as all its subcomponents, since that may create collinearity.

control_sets <- list(
  no_controls = character(0),
  
  employment_total = c(
    "ec13_emp_all_ac_alloc"
  ),
  
  employment_disaggregated = c(
    "ec13_emp_f_ac_alloc",
    "ec13_emp_m_ac_alloc",
    "ec13_emp_gov_ac_alloc",
    "ec13_emp_priv_ac_alloc",
    "ec13_emp_own_m_ac_alloc",
    "ec13_emp_own_f_ac_alloc",
    "ec13_emp_st_ac_alloc",
    "ec13_emp_sc_ac_alloc",
    "ec13_emp_obc_ac_alloc"
  )
)

single_control_sets <- control_vars %>%
  set_names(paste0("single_", .)) %>%
  map(~ .x)

control_sets <- c(control_sets, single_control_sets)

# -----------------------------
# 4. Regression function
# -----------------------------
# This avoids formula problems from variables with names like:
# alloc_2011_Total_Persons_<1
# alloc_2011_Total_Persons_1-4
#
# Each model is estimated as:
# y ~ migration * fdi + controls
#
# But the output records the original variable names.

run_fdi_model <- function(data, migration_var, fdi_var, controls, control_set_name) {
  
  controls <- controls[!is.na(controls) & controls != ""]
  
  vars_needed <- unique(c(dv, migration_var, fdi_var, controls))
  
  missing_vars <- setdiff(vars_needed, names(data))
  
  if (length(missing_vars) > 0) {
    return(tibble(
      migration_var = migration_var,
      fdi_var = fdi_var,
      control_set = control_set_name,
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      n_obs = NA_integer_,
      r_squared = NA_real_,
      adj_r_squared = NA_real_,
      error = paste("Missing variables:", paste(missing_vars, collapse = ", "))
    ))
  }
  
  model_data <- tibble(
    y = data[[dv]],
    migration = data[[migration_var]],
    fdi = data[[fdi_var]]
  )
  
  if (length(controls) > 0) {
    controls_df <- data[controls]
    names(controls_df) <- paste0("control_", seq_along(controls))
    model_data <- bind_cols(model_data, controls_df)
  }
  
  model_data <- model_data %>%
    filter(
      if_all(everything(), ~ !is.na(.x)),
      if_all(where(is.numeric), ~ is.finite(.x))
    )
  
  min_obs_needed <- max(10, length(controls) + 4)
  
  if (nrow(model_data) < min_obs_needed) {
    return(tibble(
      migration_var = migration_var,
      fdi_var = fdi_var,
      control_set = control_set_name,
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      n_obs = nrow(model_data),
      r_squared = NA_real_,
      adj_r_squared = NA_real_,
      error = "Too few complete observations"
    ))
  }
  
  rhs_terms <- c(
    "migration * fdi",
    if (length(controls) > 0) paste0("control_", seq_along(controls)) else character(0)
  )
  
  fml <- reformulate(rhs_terms, response = "y")
  
  model <- tryCatch(
    lm(fml, data = model_data),
    error = function(e) e
  )
  
  if (inherits(model, "error")) {
    return(tibble(
      migration_var = migration_var,
      fdi_var = fdi_var,
      control_set = control_set_name,
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      n_obs = nrow(model_data),
      r_squared = NA_real_,
      adj_r_squared = NA_real_,
      error = model$message
    ))
  }
  
  base_lookup <- tibble(
    term = c("(Intercept)", "migration", "fdi", "migration:fdi"),
    term_original = c(
      "(Intercept)",
      migration_var,
      fdi_var,
      paste0(migration_var, ":", fdi_var)
    )
  )
  
  control_lookup <- if (length(controls) > 0) {
    tibble(
      term = paste0("control_", seq_along(controls)),
      term_original = controls
    )
  } else {
    tibble(
      term = character(0),
      term_original = character(0)
    )
  }
  
  term_lookup <- bind_rows(base_lookup, control_lookup)
  
  broom::tidy(model) %>%
    left_join(term_lookup, by = "term") %>%
    mutate(
      term_original = coalesce(term_original, term),
      migration_var = migration_var,
      fdi_var = fdi_var,
      control_set = control_set_name,
      n_obs = nobs(model),
      r_squared = summary(model)$r.squared,
      adj_r_squared = summary(model)$adj.r.squared,
      error = NA_character_
    )
}

# -----------------------------
# 5. Build model grid
# -----------------------------

model_grid <- expand_grid(
  migration_var = migration_vars,
  fdi_var = fdi_vars,
  control_set = names(control_sets)
) %>%
  mutate(
    controls = map(control_set, ~ control_sets[[.x]])
  )

# Optional check
model_grid %>%
  count(control_set)

# -----------------------------
# 6. Test first model before running all
# -----------------------------

test_result <- run_fdi_model(
  data = reg_data,
  migration_var = model_grid$migration_var[[1]],
  fdi_var = model_grid$fdi_var[[1]],
  controls = model_grid$controls[[1]],
  control_set_name = model_grid$control_set[[1]]
)

test_result

# -----------------------------
# 7. Run all regressions
# -----------------------------

reg_results <- model_grid %>%
  mutate(
    results = pmap(
      list(migration_var, fdi_var, controls, control_set),
      ~ run_fdi_model(
        data = reg_data,
        migration_var = ..1,
        fdi_var = ..2,
        controls = ..3,
        control_set_name = ..4
      )
    )
  ) %>%
  select(results) %>%
  unnest(results)

# -----------------------------
# 8. Extract interaction results
# -----------------------------

interaction_results <- reg_results %>%
  filter(term == "migration:fdi") %>%
  mutate(
    stars = case_when(
      p.value < 0.01 ~ "***",
      p.value < 0.05 ~ "**",
      p.value < 0.10 ~ "*",
      TRUE ~ ""
    )
  ) %>%
  arrange(p.value)

interaction_table <- interaction_results %>%
  transmute(
    migration_var,
    fdi_var,
    control_set,
    interaction_term = term_original,
    coefficient = estimate,
    se = std.error,
    t_stat = statistic,
    p_value = p.value,
    stars,
    n_obs,
    r_squared,
    adj_r_squared,
    error
  ) %>%
  arrange(migration_var, fdi_var, control_set)

View(interaction_table)

```
We can start off by confirming that exposure to the interaction of FDI and migration drives an increase in support for the far right. We do this using time series data for all assembly constituencies in 11 states.
Obs ≈ 2076


```{r Probability that a moderate voter will vote for the far right}

```
To understand (a), we can use a logit model to regress whether a moderate voter voted for the far right on their exposure to our two shocks of interest, an interaction, and controls. We can do the same for left voters and right voters to check that the effect is stronger for moderates than either left (not going to vote for the right) or right (already voting for the right). So:
Left Voter Voted for Far Right ~ FDI + Migration + FDI * Migration
Moderate Voter Voted for Far Right ~ FDI + Migration + FDI * Migration
Right Voter Voted for Far Right ~ FDI + Migration + FDI * Migration
Obs ≈ 550


```{r Share of moderate voters who do vote for the far right}
library(dplyr)
library(tidyr)
library(purrr)
library(stringr)
library(broom)
library(sf)

# -----------------------------
# 1. Prepare regression data
# -----------------------------

reg_data <- elec_cand_nes_ec_m_fdi %>%
  { if (inherits(., "sf")) sf::st_drop_geometry(.) else . }

# Optional: create migration-change variables
reg_data <- reg_data %>%
  mutate(
    agr_diff_09_14 = agr_2014 - agr_2009,
    log_agr_diff_09_14 = log_agr_2014 - log_agr_2009
  )

# -----------------------------
# 2. Outcome variables
# -----------------------------

dv_specs <- tibble::tribble(
  ~election_year, ~ideology_group, ~dv,
  2009, "moderate", "loc_bjp_mod_vote_share_2009",
  2009, "right",    "loc_bjp_right_vote_share_2009",
  2009, "left",     "loc_bjp_left_vote_share_2009",
  2014, "moderate", "loc_bjp_mod_vote_share_2014",
  2014, "right",    "loc_bjp_right_vote_share_2014",
  2014, "left",     "loc_bjp_left_vote_share_2014"
)

# Keep only outcome variables that exist
dv_specs <- dv_specs %>%
  filter(dv %in% names(reg_data))

# -----------------------------
# 3. FDI and migration variables
# -----------------------------

fdi_x1_vars <- names(reg_data) %>%
  keep(~ str_detect(.x, "^fdi_x1"))

fdi_x2_vars <- names(reg_data) %>%
  keep(~ str_detect(.x, "^fdi_x2"))

migration_2009_vars <- c(
  "agr_2009",
  "log_agr_2009",
  "log_alloc_2011_Total_Persons_1-4",
  "alloc_2011_Total_Persons_1-4"
)

migration_2014_vars <- c(
  "agr_2014",
  "log_agr_2014",
  "log_alloc_2011_Total_Persons_<1",
  "alloc_2011_Total_Persons_<1",
  "agr_diff_09_14",
  "log_agr_diff_09_14"
)

migration_2009_vars <- intersect(migration_2009_vars, names(reg_data))
migration_2014_vars <- intersect(migration_2014_vars, names(reg_data))

# -----------------------------
# 4. Controls
# -----------------------------

control_vars <- c(
  "ec13_emp_all_ac_alloc",
  "ec13_emp_f_ac_alloc",
  "ec13_emp_m_ac_alloc",
  "ec13_emp_gov_ac_alloc",
  "ec13_emp_priv_ac_alloc",
  "ec13_emp_own_m_ac_alloc",
  "ec13_emp_own_f_ac_alloc",
  "ec13_emp_st_ac_alloc",
  "ec13_emp_sc_ac_alloc",
  "ec13_emp_obc_ac_alloc"
)

control_vars <- intersect(control_vars, names(reg_data))

control_sets <- list(
  no_controls = character(0),
  
  employment_total = c(
    "ec13_emp_all_ac_alloc"
  ),
  
  employment_disaggregated = c(
    "ec13_emp_f_ac_alloc",
    "ec13_emp_m_ac_alloc",
    "ec13_emp_gov_ac_alloc",
    "ec13_emp_priv_ac_alloc",
    "ec13_emp_own_m_ac_alloc",
    "ec13_emp_own_f_ac_alloc",
    "ec13_emp_st_ac_alloc",
    "ec13_emp_sc_ac_alloc",
    "ec13_emp_obc_ac_alloc"
  )
)

# Drop controls from each set if they are not present
control_sets <- map(control_sets, ~ intersect(.x, names(reg_data)))

single_control_sets <- control_vars %>%
  set_names(paste0("single_", .)) %>%
  map(~ .x)

control_sets <- c(control_sets, single_control_sets)

# -----------------------------
# 5. Build model grid
# -----------------------------

model_grid_2009 <- expand_grid(
  dv_specs %>% filter(election_year == 2009),
  migration_var = migration_2009_vars,
  fdi_var = fdi_x1_vars,
  control_set = names(control_sets)
) %>%
  mutate(
    controls = map(control_set, ~ control_sets[[.x]])
  )

model_grid_2014 <- expand_grid(
  dv_specs %>% filter(election_year == 2014),
  migration_var = migration_2014_vars,
  fdi_var = fdi_x2_vars,
  control_set = names(control_sets)
) %>%
  mutate(
    controls = map(control_set, ~ control_sets[[.x]])
  )

model_grid <- bind_rows(model_grid_2009, model_grid_2014)

# -----------------------------
# 6. Regression function
# -----------------------------
# Uses temporary names:
# y ~ migration * fdi + control_1 + control_2 + ...
#
# This avoids errors from variables with names like:
# alloc_2011_Total_Persons_<1
# alloc_2011_Total_Persons_1-4

run_cross_section_model <- function(data, dv, migration_var, fdi_var,
                                    controls, election_year,
                                    ideology_group, control_set_name) {
  
  controls <- controls[!is.na(controls) & controls != ""]
  
  vars_needed <- unique(c(dv, migration_var, fdi_var, controls))
  missing_vars <- setdiff(vars_needed, names(data))
  
  if (length(missing_vars) > 0) {
    return(tibble(
      election_year = election_year,
      ideology_group = ideology_group,
      dv = dv,
      migration_var = migration_var,
      fdi_var = fdi_var,
      control_set = control_set_name,
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      n_obs = NA_integer_,
      r_squared = NA_real_,
      adj_r_squared = NA_real_,
      error = paste("Missing variables:", paste(missing_vars, collapse = ", "))
    ))
  }
  
  model_data <- tibble(
    y = data[[dv]],
    migration = data[[migration_var]],
    fdi = data[[fdi_var]]
  )
  
  if (length(controls) > 0) {
    controls_df <- as_tibble(data[controls])
    names(controls_df) <- paste0("control_", seq_along(controls))
    model_data <- bind_cols(model_data, controls_df)
  }
  
  model_data <- model_data %>%
    filter(
      if_all(everything(), ~ !is.na(.x)),
      if_all(where(is.numeric), ~ is.finite(.x))
    )
  
  min_obs_needed <- max(10, length(controls) + 4)
  
  if (nrow(model_data) < min_obs_needed) {
    return(tibble(
      election_year = election_year,
      ideology_group = ideology_group,
      dv = dv,
      migration_var = migration_var,
      fdi_var = fdi_var,
      control_set = control_set_name,
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      n_obs = nrow(model_data),
      r_squared = NA_real_,
      adj_r_squared = NA_real_,
      error = "Too few complete observations"
    ))
  }
  
  rhs_terms <- c(
    "migration * fdi",
    if (length(controls) > 0) paste0("control_", seq_along(controls)) else character(0)
  )
  
  fml <- reformulate(rhs_terms, response = "y")
  
  model <- tryCatch(
    lm(fml, data = model_data),
    error = function(e) e
  )
  
  if (inherits(model, "error")) {
    return(tibble(
      election_year = election_year,
      ideology_group = ideology_group,
      dv = dv,
      migration_var = migration_var,
      fdi_var = fdi_var,
      control_set = control_set_name,
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      n_obs = nrow(model_data),
      r_squared = NA_real_,
      adj_r_squared = NA_real_,
      error = model$message
    ))
  }
  
  base_lookup <- tibble(
    term = c("(Intercept)", "migration", "fdi", "migration:fdi"),
    term_original = c(
      "(Intercept)",
      migration_var,
      fdi_var,
      paste0(migration_var, ":", fdi_var)
    )
  )
  
  control_lookup <- if (length(controls) > 0) {
    tibble(
      term = paste0("control_", seq_along(controls)),
      term_original = controls
    )
  } else {
    tibble(
      term = character(0),
      term_original = character(0)
    )
  }
  
  term_lookup <- bind_rows(base_lookup, control_lookup)
  
  broom::tidy(model) %>%
    left_join(term_lookup, by = "term") %>%
    mutate(
      term_original = coalesce(term_original, term),
      election_year = election_year,
      ideology_group = ideology_group,
      dv = dv,
      migration_var = migration_var,
      fdi_var = fdi_var,
      control_set = control_set_name,
      n_obs = nobs(model),
      r_squared = summary(model)$r.squared,
      adj_r_squared = summary(model)$adj.r.squared,
      error = NA_character_
    )
}

# -----------------------------
# 7. Test one model
# -----------------------------

test_cross_section_result <- run_cross_section_model(
  data = reg_data,
  dv = model_grid$dv[[1]],
  migration_var = model_grid$migration_var[[1]],
  fdi_var = model_grid$fdi_var[[1]],
  controls = model_grid$controls[[1]],
  election_year = model_grid$election_year[[1]],
  ideology_group = model_grid$ideology_group[[1]],
  control_set_name = model_grid$control_set[[1]]
)

test_cross_section_result

# -----------------------------
# 8. Run all models
# -----------------------------

cross_section_results <- model_grid %>%
  mutate(
    results = pmap(
      list(
        dv,
        migration_var,
        fdi_var,
        controls,
        election_year,
        ideology_group,
        control_set
      ),
      ~ run_cross_section_model(
        data = reg_data,
        dv = ..1,
        migration_var = ..2,
        fdi_var = ..3,
        controls = ..4,
        election_year = ..5,
        ideology_group = ..6,
        control_set_name = ..7
      )
    )
  ) %>%
  select(results) %>%
  unnest(results)

# -----------------------------
# 9. Extract interaction terms
# -----------------------------

cross_section_interactions <- cross_section_results %>%
  filter(term == "migration:fdi") %>%
  mutate(
    stars = case_when(
      p.value < 0.01 ~ "***",
      p.value < 0.05 ~ "**",
      p.value < 0.10 ~ "*",
      TRUE ~ ""
    )
  ) %>%
  arrange(election_year, ideology_group, p.value)

cross_section_table <- cross_section_interactions %>%
  transmute(
    election_year,
    ideology_group,
    dv,
    migration_var,
    fdi_var,
    control_set,
    interaction_term = term_original,
    coefficient = estimate,
    se = std.error,
    t_stat = statistic,
    p_value = p.value,
    stars,
    n_obs,
    r_squared,
    adj_r_squared,
    error
  ) %>%
  arrange(election_year, ideology_group, migration_var, fdi_var, control_set)

View(cross_section_table)

```
To understand (b), we can regress the vote share of far right parties among moderate voters in an assembly constituency on an assembly constituency’s exposure to our two shocks of interest, an interaction, and controls. We can do the same for the vote share of far right parties among left and right voters to check that the effect is stronger for moderates than either left (not going to vote for the right) or right (already voting for the right). So:
Share of Left Voters Voting Far Right ~ FDI + Migration + FDI * Migration
Share of Moderate Voters Voting Far Right ~ FDI + Migration + FDI * Migration
Share of Right Voters Voting Far Right ~ FDI + Migration + FDI * Migration
Obs ≈ 550

