---
title: "Switchers India: Replacement Regression Analysis"
output:
  html_document:
    keep_md: true
date: "`r Sys.Date()`"
---

This script loads the replacement model-ready files created by
`Switchers-India-Data-Replacement.Rmd`. It estimates five distinct model
families: a first-difference AC panel, pooled AC-year levels regressions, a
pooled voter ideology-interaction logit, an aggregated ideology-cell grouped
binomial model, and a contextual moderate-share triple interaction.

Total FDI × logged five-year migration is the primary exposure specification.
Manufacturing FDI × logged five-year migration is secondary. The other four
FDI-migration combinations are appendix robustness specifications. Every
regression report page uses a landscape side-by-side layout, with the complete
table on the left and the relevant coefficient or marginal-effect plot on the
right.

```{r 1-load-packages-and-replacement-data, message = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)

library(tidyverse)
library(fixest)
library(marginaleffects)
library(gridExtra)
library(scales)

options(marginaleffects_lean = TRUE)

DERIVED_DIR <- "data/derived/switchers"
OUTPUT_DIR <- "outputs/switchers_replacement"
MAIN_TABLE_DIR <- file.path(OUTPUT_DIR, "main_text_reports")
APPENDIX_TABLE_DIR <- file.path(OUTPUT_DIR, "appendix_reports")
FIGURE_DIR <- file.path(OUTPUT_DIR, "figures")
MODEL_DIR <- file.path(OUTPUT_DIR, "models")
RESULT_DIR <- file.path(OUTPUT_DIR, "machine_readable_results")

walk(
  c(
    OUTPUT_DIR,
    MAIN_TABLE_DIR,
    APPENDIX_TABLE_DIR,
    FIGURE_DIR,
    MODEL_DIR,
    RESULT_DIR
  ),
  dir.create,
  recursive = TRUE,
  showWarnings = FALSE
)

required_files <- c(
  "ac_year_levels.rds",
  "ac_first_difference.rds",
  "voter_year_pooled.rds",
  "ac_year_ideology_counts.rds",
  "ideology_item_responses_long.rds",
  "centering_constants.csv"
)

missing_files <- required_files[
  !file.exists(file.path(DERIVED_DIR, required_files))
]

if (length(missing_files) > 0) {
  stop(
    "Run Switchers-India-Data-Replacement.Rmd first. Missing: ",
    paste(missing_files, collapse = ", ")
  )
}

ac_year_levels <- readRDS(
  file.path(DERIVED_DIR, "ac_year_levels.rds")
)
ac_first_difference <- readRDS(
  file.path(DERIVED_DIR, "ac_first_difference.rds")
)
voter_year_pooled <- readRDS(
  file.path(DERIVED_DIR, "voter_year_pooled.rds")
)
ac_year_ideology_counts <- readRDS(
  file.path(DERIVED_DIR, "ac_year_ideology_counts.rds")
)
ideology_item_responses_long <- readRDS(
  file.path(DERIVED_DIR, "ideology_item_responses_long.rds")
)
centering_constants <- read_csv(
  file.path(DERIVED_DIR, "centering_constants.csv"),
  show_col_types = FALSE
)
```

```{r 2-validate-model-ready-data}
assert_unique <- function(data, keys, label) {
  duplicates <- data %>%
    group_by(across(all_of(keys))) %>%
    summarise(n = n(), .groups = "drop") %>%
    filter(n > 1)

  if (nrow(duplicates) > 0) {
    print(duplicates, n = Inf)
    stop(label, " is not unique by ", paste(keys, collapse = ", "), ".")
  }

  invisible(data)
}

assert_unique(ac_year_levels, c("state_no", "ac", "year"), "AC-year levels data")
assert_unique(ac_first_difference, c("state_no", "ac"), "First-difference data")
assert_unique(
  ac_year_ideology_counts,
  c("state_no", "ac", "year", "voter_ideology"),
  "Ideology-cell data"
)

forbidden_variables <- c(
  "m_emp_rate",
  "pc_gdp_election",
  "pc_gdp_2009",
  "pc_gdp_2013",
  "delta_pc_gdp"
)

analysis_datasets <- list(
  ac_year_levels = ac_year_levels,
  ac_first_difference = ac_first_difference,
  voter_year_pooled = voter_year_pooled,
  ac_year_ideology_counts = ac_year_ideology_counts
)

for (dataset_name in names(analysis_datasets)) {
  leaked <- intersect(
    forbidden_variables,
    names(analysis_datasets[[dataset_name]])
  )

  if (length(leaked) > 0) {
    stop(
      "Obsolete variables in ", dataset_name, ": ",
      paste(leaked, collapse = ", ")
    )
  }
}

required_centered_variables <- c(
  "fdi_total_c",
  "fdi_mfg_c",
  "fdi_svc_c",
  "log_migration_c",
  "migration_share_c",
  "emp_rate_c",
  "sc_share_c",
  "st_share_c",
  "log_population_c",
  "log_land_area_c",
  "prior_migrant_share_c",
  "moderate_share_10pp_c"
)

missing_centered <- setdiff(
  required_centered_variables,
  names(ac_year_levels)
)

if (length(missing_centered) > 0) {
  stop(
    "Centered AC-year variables are missing: ",
    paste(missing_centered, collapse = ", ")
  )
}

required_fd_variables <- c(
  "delta_fr_vote_share",
  "delta_fdi_total",
  "delta_fdi_mfg",
  "delta_fdi_svc",
  "delta_log_migration",
  "delta_migration_share",
  "delta_product_total_log",
  "delta_product_mfg_log",
  "delta_product_svc_log",
  "delta_product_total_share",
  "delta_product_mfg_share",
  "delta_product_svc_share",
  "state_fe",
  "pc_cluster_id"
)

missing_fd <- setdiff(required_fd_variables, names(ac_first_difference))
if (length(missing_fd) > 0) {
  stop(
    "First-difference variables are missing: ",
    paste(missing_fd, collapse = ", ")
  )
}

required_voter_variables <- c(
  "fr_vote",
  "voter_ideology",
  required_centered_variables[1:11],
  "year_factor",
  "state_fe",
  "pc_cluster_id"
)

missing_voter <- setdiff(required_voter_variables, names(voter_year_pooled))
if (length(missing_voter) > 0) {
  stop(
    "Voter-level variables are missing: ",
    paste(missing_voter, collapse = ", ")
  )
}

required_binomial_variables <- c(
  "fr_vote_count",
  "non_fr_vote_count",
  "n_valid_vote",
  "fr_vote_prop",
  "voter_ideology",
  required_centered_variables[1:11],
  "year_factor",
  "state_fe",
  "pc_cluster_id"
)

missing_binomial <- setdiff(
  required_binomial_variables,
  names(ac_year_ideology_counts)
)
if (length(missing_binomial) > 0) {
  stop(
    "Grouped-binomial variables are missing: ",
    paste(missing_binomial, collapse = ", ")
  )
}

if (any(
  ac_year_ideology_counts$fr_vote_count +
    ac_year_ideology_counts$non_fr_vote_count !=
    ac_year_ideology_counts$n_valid_vote
)) {
  stop("Grouped-binomial successes and failures do not sum to the trial count.")
}

voter_year_pooled <- voter_year_pooled %>%
  mutate(
    voter_ideology = factor(
      as.character(voter_ideology),
      levels = c("C", "L", "R")
    )
  )

ac_year_ideology_counts <- ac_year_ideology_counts %>%
  mutate(
    voter_ideology = factor(
      as.character(voter_ideology),
      levels = c("C", "L", "R")
    )
  )

centering_validation <- centering_constants %>%
  filter(centered_variable %in% names(ac_year_levels)) %>%
  transmute(
    variable,
    centered_variable,
    center,
    scale,
    centered_mean = map_dbl(
      centered_variable,
      \(v) mean(ac_year_levels[[v]], na.rm = TRUE)
    )
  )

if (any(abs(centering_validation$centered_mean) > 1e-10, na.rm = TRUE)) {
  print(centering_validation, n = Inf)
  stop("Common centered variables do not have mean zero in the AC-year reference data.")
}

analysis_sample_summary <- tribble(
  ~dataset, ~rows, ~units, ~pc_clusters,
  "AC-year levels", nrow(ac_year_levels), n_distinct(ac_year_levels$ac_uid), n_distinct(ac_year_levels$pc_cluster_id),
  "First differences", nrow(ac_first_difference), n_distinct(ac_first_difference$ac_uid), n_distinct(ac_first_difference$pc_cluster_id),
  "Voter-level classified and unclassified", nrow(voter_year_pooled), n_distinct(voter_year_pooled$ac_uid, na.rm = TRUE), n_distinct(voter_year_pooled$pc_cluster_id, na.rm = TRUE),
  "AC-year ideology cells", nrow(ac_year_ideology_counts), n_distinct(ac_year_ideology_counts$ac_uid), n_distinct(ac_year_ideology_counts$pc_cluster_id)
)

write_csv(
  analysis_sample_summary,
  file.path(RESULT_DIR, "analysis_sample_summary.csv")
)
write_csv(
  centering_validation,
  file.path(RESULT_DIR, "centering_validation.csv")
)

analysis_sample_summary
centering_validation
```

```{r 3-define-exposure-order-model-columns-and-labels}
# Primary and secondary specifications go to the main-text reports. The other
# four are estimated identically and routed to appendix reports.
exposure_specs <- tribble(
  ~spec_id, ~spec_status, ~output_group, ~spec_label, ~fdi_name, ~fdi_var, ~migration_name, ~migration_var, ~fd_fdi_var, ~fd_migration_var, ~fd_product_var,
  "a", "Primary", "main", "Total FDI × logged five-year migration", "Total FDI", "fdi_total_c", "Centered logged five-year migrant total", "log_migration_c", "delta_fdi_total", "delta_log_migration", "delta_product_total_log",
  "b", "Secondary", "main", "Manufacturing FDI × logged five-year migration", "Manufacturing FDI", "fdi_mfg_c", "Centered logged five-year migrant total", "log_migration_c", "delta_fdi_mfg", "delta_log_migration", "delta_product_mfg_log",
  "c", "Robustness", "appendix", "Services FDI × logged five-year migration", "Services FDI", "fdi_svc_c", "Centered logged five-year migrant total", "log_migration_c", "delta_fdi_svc", "delta_log_migration", "delta_product_svc_log",
  "d", "Robustness", "appendix", "Total FDI × five-year migration share", "Total FDI", "fdi_total_c", "Centered five-year migrant share", "migration_share_c", "delta_fdi_total", "delta_migration_share", "delta_product_total_share",
  "e", "Robustness", "appendix", "Manufacturing FDI × five-year migration share", "Manufacturing FDI", "fdi_mfg_c", "Centered five-year migrant share", "migration_share_c", "delta_fdi_mfg", "delta_migration_share", "delta_product_mfg_share",
  "f", "Robustness", "appendix", "Services FDI × five-year migration share", "Services FDI", "fdi_svc_c", "Centered five-year migrant share", "migration_share_c", "delta_fdi_svc", "delta_migration_share", "delta_product_svc_share"
)

standard_controls <- c(
  "emp_rate_c",
  "sc_share_c",
  "st_share_c",
  "log_population_c",
  "log_land_area_c"
)

prior_migration_control <- "prior_migrant_share_c"

levels_variants <- tribble(
  ~variant, ~column_label, ~include_controls, ~include_year, ~include_prior_migration, ~include_state_fe,
  "base", "(1) Base", FALSE, FALSE, FALSE, FALSE,
  "controls", "(2) Controls", TRUE, FALSE, FALSE, FALSE,
  "year", "(3) Controls + Year", TRUE, TRUE, FALSE, FALSE,
  "prior_migration", "(4) + Prior Migrant Share", TRUE, TRUE, TRUE, FALSE,
  "state_fe", "(5) + State FE", TRUE, TRUE, TRUE, TRUE
)

fd_variants <- tribble(
  ~variant, ~column_label, ~include_state_fe,
  "first_difference", "(1) First Difference", FALSE,
  "first_difference_state_fe", "(2) + State FE", TRUE
)

variable_labels <- c(
  "(Intercept)" = "Intercept",
  "fdi_total_c" = "Total FDI per 100,000, centered",
  "fdi_mfg_c" = "Manufacturing FDI per 100,000, centered",
  "fdi_svc_c" = "Services FDI per 100,000, centered",
  "log_migration_c" = "Logged five-year migrant total, centered",
  "migration_share_c" = "Five-year migrant share, centered pp",
  "emp_rate_c" = "Employment rate, centered",
  "sc_share_c" = "Scheduled Caste population share, centered",
  "st_share_c" = "Scheduled Tribe population share, centered",
  "log_population_c" = "Log AC population, centered",
  "log_land_area_c" = "Log(1 + AC land area), centered",
  "prior_migrant_share_c" = "Pre-2004 migrant share, centered pp",
  "moderate_share_10pp_c" = "Moderate share, centered 10-pp units",
  "voter_ideologyL" = "Left voters vs. center",
  "voter_ideologyR" = "Right voters vs. center",
  "year_factor2014" = "2014 election",
  "delta_fdi_total" = "Change in total FDI per 100,000",
  "delta_fdi_mfg" = "Change in manufacturing FDI per 100,000",
  "delta_fdi_svc" = "Change in services FDI per 100,000",
  "delta_log_migration" = "Change in logged migration total",
  "delta_migration_share" = "Change in migration share",
  "delta_product_total_log" = "Change in centered Total FDI × logged migration product",
  "delta_product_mfg_log" = "Change in centered Manufacturing FDI × logged migration product",
  "delta_product_svc_log" = "Change in centered Services FDI × logged migration product",
  "delta_product_total_share" = "Change in centered Total FDI × migration-share product",
  "delta_product_mfg_share" = "Change in centered Manufacturing FDI × migration-share product",
  "delta_product_svc_share" = "Change in centered Services FDI × migration-share product"
)

family_labels <- c(
  "first_difference" = "First-difference AC panel",
  "levels" = "Pooled AC-year levels",
  "voter_ideology_logit" = "Pooled voter ideology-interaction logit",
  "ideology_binomial" = "Aggregated ideology-cell grouped binomial",
  "moderate_triple" = "Moderate-share contextual triple interaction"
)
```

```{r 4-formula-common-sample-and-estimation-helpers}
complete_case_sample <- function(data, variables) {
  missing_variables <- setdiff(variables, names(data))
  if (length(missing_variables) > 0) {
    stop("Variables missing from common-sample construction: ", paste(missing_variables, collapse = ", "))
  }

  keep <- complete.cases(data[, variables, drop = FALSE])
  numeric_variables <- variables[
    map_lgl(data[variables], is.numeric)
  ]

  if (length(numeric_variables) > 0) {
    finite_keep <- reduce(
      map(numeric_variables, \(v) is.finite(data[[v]])),
      `&`
    )
    keep <- keep & finite_keep
  }

  data[keep, , drop = FALSE]
}

make_levels_formula <- function(
  outcome,
  fdi_var,
  migration_var,
  include_controls,
  include_year,
  include_prior_migration,
  include_state_fe,
  ideology_interaction = FALSE,
  moderator_var = NULL
) {
  core <- if (ideology_interaction) {
    paste0(fdi_var, " * ", migration_var, " * voter_ideology")
  } else if (!is.null(moderator_var)) {
    paste0(fdi_var, " * ", migration_var, " * ", moderator_var)
  } else {
    paste0(fdi_var, " * ", migration_var)
  }

  rhs <- core

  if (include_controls) {
    rhs <- paste(rhs, paste(standard_controls, collapse = " + "), sep = " + ")
  }
  if (include_year) {
    rhs <- paste(rhs, "year_factor", sep = " + ")
  }
  if (include_prior_migration) {
    rhs <- paste(rhs, prior_migration_control, sep = " + ")
  }

  formula_text <- paste(outcome, "~", rhs)
  if (include_state_fe) {
    formula_text <- paste(formula_text, "| state_fe")
  }

  as.formula(formula_text)
}

make_fd_formula <- function(spec, include_state_fe) {
  rhs <- paste(
    spec$fd_fdi_var,
    spec$fd_migration_var,
    spec$fd_product_var,
    sep = " + "
  )

  formula_text <- paste("delta_fr_vote_share ~", rhs)
  if (include_state_fe) {
    formula_text <- paste(formula_text, "| state_fe")
  }

  as.formula(formula_text)
}

fit_fixest_model <- function(data, formula, estimator, trial_weights = FALSE) {
  if (estimator == "ols") {
    return(
      feols(
        formula,
        data = data,
        vcov = ~ pc_cluster_id,
        data.save = TRUE,
        warn = FALSE,
        notes = FALSE
      )
    )
  }

  if (estimator == "logit") {
    return(
      feglm(
        formula,
        data = data,
        family = binomial("logit"),
        vcov = ~ pc_cluster_id,
        data.save = TRUE,
        warn = FALSE,
        notes = FALSE
      )
    )
  }

  if (estimator == "grouped_binomial") {
    return(
      feglm(
        formula,
        data = data,
        family = binomial("logit"),
        weights = ~ n_valid_vote,
        vcov = ~ pc_cluster_id,
        data.save = TRUE,
        warn = FALSE,
        notes = FALSE
      )
    )
  }

  stop("Unknown estimator: ", estimator)
}

safe_fit <- function(data, formula, estimator) {
  tryCatch(
    list(
      model = fit_fixest_model(data, formula, estimator),
      error = NA_character_
    ),
    error = \(e) list(
      model = NULL,
      error = conditionMessage(e)
    )
  )
}

fit_levels_family <- function(
  data,
  family,
  outcome,
  estimator,
  ideology_interaction = FALSE,
  moderator_var = NULL
) {
  map_dfr(seq_len(nrow(exposure_specs)), \(i) {
    spec <- exposure_specs[i, ]

    full_sample_variables <- c(
      outcome,
      spec$fdi_var,
      spec$migration_var,
      standard_controls,
      prior_migration_control,
      "year_factor",
      "state_fe",
      "pc_cluster_id"
    )

    if (ideology_interaction) {
      full_sample_variables <- c(full_sample_variables, "voter_ideology")
    }
    if (!is.null(moderator_var)) {
      full_sample_variables <- c(full_sample_variables, moderator_var)
    }
    if (estimator == "grouped_binomial") {
      full_sample_variables <- c(full_sample_variables, "n_valid_vote")
    }

    sample_data <- complete_case_sample(
      data,
      unique(full_sample_variables)
    )

    if (ideology_interaction) {
      sample_data <- sample_data %>%
        filter(voter_ideology %in% c("C", "L", "R")) %>%
        mutate(
          voter_ideology = factor(
            as.character(voter_ideology),
            levels = c("C", "L", "R")
          )
        )
    }

    map_dfr(seq_len(nrow(levels_variants)), \(j) {
      variant_row <- levels_variants[j, ]
      formula <- make_levels_formula(
        outcome = outcome,
        fdi_var = spec$fdi_var,
        migration_var = spec$migration_var,
        include_controls = variant_row$include_controls,
        include_year = variant_row$include_year,
        include_prior_migration = variant_row$include_prior_migration,
        include_state_fe = variant_row$include_state_fe,
        ideology_interaction = ideology_interaction,
        moderator_var = moderator_var
      )
      result <- safe_fit(sample_data, formula, estimator)

      tibble(
        family = family,
        spec_id = spec$spec_id,
        spec_status = spec$spec_status,
        output_group = spec$output_group,
        spec_label = spec$spec_label,
        fdi_name = spec$fdi_name,
        fdi_var = spec$fdi_var,
        migration_name = spec$migration_name,
        migration_var = spec$migration_var,
        variant = variant_row$variant,
        column_label = variant_row$column_label,
        include_controls = variant_row$include_controls,
        include_year = variant_row$include_year,
        include_prior_migration = variant_row$include_prior_migration,
        include_state_fe = variant_row$include_state_fe,
        estimator = estimator,
        moderator_var = if (is.null(moderator_var)) NA_character_ else moderator_var,
        formula_text = paste(deparse(formula), collapse = " "),
        data_used = list(sample_data),
        model = list(result$model),
        model_fit = !is.null(result$model),
        model_error = result$error,
        table_id = paste(family, spec$spec_id, sep = "__"),
        model_id = paste(family, spec$spec_id, variant_row$variant, sep = "__")
      )
    })
  })
}

fit_first_difference_family <- function(data) {
  map_dfr(seq_len(nrow(exposure_specs)), \(i) {
    spec <- exposure_specs[i, ]
    sample_data <- complete_case_sample(
      data,
      c(
        "delta_fr_vote_share",
        spec$fd_fdi_var,
        spec$fd_migration_var,
        spec$fd_product_var,
        "state_fe",
        "pc_cluster_id"
      )
    )

    map_dfr(seq_len(nrow(fd_variants)), \(j) {
      variant_row <- fd_variants[j, ]
      formula <- make_fd_formula(spec, variant_row$include_state_fe)
      result <- safe_fit(sample_data, formula, "ols")

      tibble(
        family = "first_difference",
        spec_id = spec$spec_id,
        spec_status = spec$spec_status,
        output_group = spec$output_group,
        spec_label = spec$spec_label,
        fdi_name = spec$fdi_name,
        fdi_var = spec$fd_fdi_var,
        migration_name = spec$migration_name,
        migration_var = spec$fd_migration_var,
        fd_product_var = spec$fd_product_var,
        variant = variant_row$variant,
        column_label = variant_row$column_label,
        include_controls = FALSE,
        include_year = FALSE,
        include_prior_migration = FALSE,
        include_state_fe = variant_row$include_state_fe,
        estimator = "ols",
        moderator_var = NA_character_,
        formula_text = paste(deparse(formula), collapse = " "),
        data_used = list(sample_data),
        model = list(result$model),
        model_fit = !is.null(result$model),
        model_error = result$error,
        table_id = paste("first_difference", spec$spec_id, sep = "__"),
        model_id = paste("first_difference", spec$spec_id, variant_row$variant, sep = "__")
      )
    })
  })
}
```

```{r 5-fit-all-132-regressions}
first_difference_models <- fit_first_difference_family(
  ac_first_difference
)

levels_models <- fit_levels_family(
  data = ac_year_levels,
  family = "levels",
  outcome = "fr_party_vote_share",
  estimator = "ols"
)

voter_ideology_logit_models <- fit_levels_family(
  data = voter_year_pooled %>% filter(!is.na(fr_vote)),
  family = "voter_ideology_logit",
  outcome = "fr_vote",
  estimator = "logit",
  ideology_interaction = TRUE
)

ideology_binomial_models <- fit_levels_family(
  data = ac_year_ideology_counts %>%
    filter(n_valid_vote > 0, !is.na(fr_vote_prop)),
  family = "ideology_binomial",
  outcome = "fr_vote_prop",
  estimator = "grouped_binomial",
  ideology_interaction = TRUE
)

moderate_triple_models <- fit_levels_family(
  data = ac_year_levels %>% filter(!is.na(moderate_share_10pp_c)),
  family = "moderate_triple",
  outcome = "fr_party_vote_share",
  estimator = "ols",
  moderator_var = "moderate_share_10pp_c"
)

all_models <- bind_rows(
  first_difference_models,
  levels_models,
  voter_ideology_logit_models,
  ideology_binomial_models,
  moderate_triple_models
) %>%
  arrange(
    match(
      family,
      c(
        "first_difference",
        "levels",
        "voter_ideology_logit",
        "ideology_binomial",
        "moderate_triple"
      )
    ),
    match(spec_id, exposure_specs$spec_id),
    match(
      variant,
      c(
        fd_variants$variant,
        levels_variants$variant
      )
    )
  )

expected_model_count <-
  nrow(exposure_specs) * nrow(fd_variants) +
  4 * nrow(exposure_specs) * nrow(levels_variants)

if (nrow(all_models) != expected_model_count || expected_model_count != 132) {
  stop(
    "Unexpected regression-grid size. Expected 132 rows but created ",
    nrow(all_models), "."
  )
}

model_fit_summary <- all_models %>%
  summarise(
    requested_models = n(),
    fitted_models = sum(model_fit),
    failed_models = sum(!model_fit),
    .by = c(family, output_group)
  )

failed_models <- all_models %>%
  filter(!model_fit) %>%
  select(
    family,
    spec_id,
    variant,
    model_id,
    formula_text,
    model_error
  )

write_csv(
  model_fit_summary,
  file.path(RESULT_DIR, "model_fit_summary.csv")
)
write_csv(
  failed_models,
  file.path(RESULT_DIR, "model_failure_log.csv")
)

model_fit_summary
if (nrow(failed_models) > 0) print(failed_models, n = Inf)
```

```{r 6-model-statistics-and-coefficient-results}
tidy_fixest <- function(model) {
  if (is.null(model)) return(tibble())

  table <- fixest::coeftable(model)
  if (is.null(dim(table)) || nrow(table) == 0) return(tibble())

  tibble(
    term = rownames(table),
    estimate = as.numeric(table[, 1]),
    std.error = as.numeric(table[, 2]),
    statistic = as.numeric(table[, 3]),
    p.value = as.numeric(table[, 4])
  )
}

get_used_row_indices <- function(model, data) {
  if (is.null(model)) return(integer(0))

  removed <- unlist(
    model$obs_selection$obsRemoved,
    recursive = TRUE,
    use.names = FALSE
  )
  if (is.null(removed) || length(removed) == 0) {
    return(seq_len(nrow(data)))
  }

  setdiff(seq_len(nrow(data)), abs(as.integer(removed)))
}

get_cluster_count <- function(model, data) {
  used <- get_used_row_indices(model, data)
  if (length(used) == 0) return(NA_integer_)
  n_distinct(data$pc_cluster_id[used], na.rm = TRUE)
}

get_trial_count <- function(model, data, family) {
  if (family != "ideology_binomial" || is.null(model)) return(NA_real_)
  used <- get_used_row_indices(model, data)
  if (length(used) == 0) return(NA_real_)
  sum(data$n_valid_vote[used], na.rm = TRUE)
}

get_fit_stat <- function(model, family) {
  if (is.null(model)) return(NA_real_)
  statistic <- if (family %in% c("voter_ideology_logit", "ideology_binomial")) {
    "pr2"
  } else {
    "r2"
  }

  result <- tryCatch(
    fixest::fitstat(model, statistic),
    error = \(e) NULL
  )
  if (is.null(result)) return(NA_real_)

  numeric_result <- suppressWarnings(as.numeric(unlist(result)))
  numeric_result <- numeric_result[is.finite(numeric_result)]
  if (length(numeric_result) == 0) NA_real_ else numeric_result[1]
}

all_models <- all_models %>%
  mutate(
    nobs = map_int(model, \(m) if (is.null(m)) NA_integer_ else as.integer(nobs(m))),
    n_pc_clusters = map2_int(model, data_used, get_cluster_count),
    trial_count = pmap_dbl(
      list(model, data_used, family),
      get_trial_count
    ),
    fit_stat = map2_dbl(model, family, get_fit_stat),
    family_label = unname(family_labels[family])
  )

coefficient_results <- all_models %>%
  filter(model_fit) %>%
  mutate(tidied = map(model, tidy_fixest)) %>%
  select(
    family,
    family_label,
    output_group,
    spec_id,
    spec_status,
    spec_label,
    fdi_name,
    fdi_var,
    migration_name,
    migration_var,
    variant,
    column_label,
    model_id,
    tidied
  ) %>%
  unnest(tidied)

model_index <- all_models %>%
  select(
    family,
    family_label,
    output_group,
    spec_id,
    spec_status,
    spec_label,
    fdi_name,
    fdi_var,
    migration_name,
    migration_var,
    variant,
    column_label,
    model_id,
    model_fit,
    model_error,
    nobs,
    n_pc_clusters,
    trial_count,
    fit_stat,
    formula_text
  )

write_csv(
  coefficient_results,
  file.path(RESULT_DIR, "all_coefficient_results.csv")
)
write_csv(
  model_index,
  file.path(RESULT_DIR, "model_index.csv")
)

saveRDS(
  all_models %>% select(-data_used),
  file.path(MODEL_DIR, "all_model_objects.rds")
)
```

```{r 7-ideology-heterogeneity-tests}
# With center voters as the reference, the FDI × migration coefficient is the
# center-voter interaction. The left and right interactions are linear sums of
# that coefficient and their respective three-way difference terms.

find_interaction_term <- function(model, pieces) {
  terms <- names(coef(model))
  matches <- terms[
    map_lgl(
      terms,
      \(term) {
        term_pieces <- str_split(term, ":", simplify = FALSE)[[1]]
        all(pieces %in% term_pieces) && length(term_pieces) == length(pieces)
      }
    )
  ]

  if (length(matches) == 0) NA_character_ else matches[1]
}

linear_combination <- function(model, weights, label) {
  coefficients <- coef(model)
  covariance <- vcov(model)

  if (any(is.na(names(weights))) || any(names(weights) == "")) {
    present <- FALSE
  } else {
    present <- names(weights) %in% names(coefficients)
  }

  if (!all(present)) {
    return(
      tibble(
        contrast = label,
        estimate = NA_real_,
        std.error = NA_real_,
        conf.low = NA_real_,
        conf.high = NA_real_,
        p.value = NA_real_
      )
    )
  }

  weight_vector <- rep(0, length(coefficients))
  names(weight_vector) <- names(coefficients)
  weight_vector[names(weights)] <- weights

  estimate <- sum(weight_vector * coefficients)
  variance <- as.numeric(t(weight_vector) %*% covariance %*% weight_vector)
  standard_error <- sqrt(max(variance, 0))
  statistic <- estimate / standard_error
  p_value <- 2 * pnorm(abs(statistic), lower.tail = FALSE)

  tibble(
    contrast = label,
    estimate = estimate,
    std.error = standard_error,
    conf.low = estimate - 1.96 * standard_error,
    conf.high = estimate + 1.96 * standard_error,
    p.value = p_value
  )
}

make_ideology_heterogeneity_tests <- function(model_row) {
  model <- model_row$model[[1]]
  if (is.null(model)) return(tibble())

  fdi <- model_row$fdi_var
  migration <- model_row$migration_var
  center_term <- find_interaction_term(model, c(fdi, migration))
  left_difference <- find_interaction_term(
    model,
    c(fdi, migration, "voter_ideologyL")
  )
  right_difference <- find_interaction_term(
    model,
    c(fdi, migration, "voter_ideologyR")
  )

  bind_rows(
    linear_combination(
      model,
      set_names(1, center_term),
      "Center-voter FDI × migration interaction"
    ),
    linear_combination(
      model,
      c(set_names(1, center_term), set_names(1, left_difference)),
      "Left-voter FDI × migration interaction"
    ),
    linear_combination(
      model,
      c(set_names(1, center_term), set_names(1, right_difference)),
      "Right-voter FDI × migration interaction"
    ),
    linear_combination(
      model,
      set_names(1, left_difference),
      "Left minus center"
    ),
    linear_combination(
      model,
      set_names(1, right_difference),
      "Right minus center"
    )
  ) %>%
    mutate(
      family = model_row$family,
      spec_id = model_row$spec_id,
      spec_label = model_row$spec_label,
      variant = model_row$variant,
      .before = 1
    )
}

ideology_heterogeneity_rows <- all_models %>%
  filter(
    family %in% c("voter_ideology_logit", "ideology_binomial"),
    variant == "state_fe",
    model_fit
  )

ideology_heterogeneity_tests <- map_dfr(
  seq_len(nrow(ideology_heterogeneity_rows)),
  \(i) make_ideology_heterogeneity_tests(ideology_heterogeneity_rows[i, ])
)

write_csv(
  ideology_heterogeneity_tests,
  file.path(RESULT_DIR, "ideology_heterogeneity_tests.csv")
)
```

```{r 8-table-construction-helpers}
fmt_number <- function(x, digits = 3) {
  if (length(x) == 0 || is.na(x)) return("")
  formatC(x, format = "f", digits = digits)
}

fmt_integer <- function(x) {
  if (length(x) == 0 || is.na(x)) return("")
  format(x, big.mark = ",", scientific = FALSE, trim = TRUE)
}

significance_stars <- function(p) {
  case_when(
    is.na(p) ~ "",
    p < 0.001 ~ "***",
    p < 0.01 ~ "**",
    p < 0.05 ~ "*",
    p < 0.10 ~ "+",
    TRUE ~ ""
  )
}

label_term_piece <- function(piece) {
  if (piece %in% names(variable_labels)) {
    return(unname(variable_labels[piece]))
  }

  piece
}

label_term <- function(term) {
  pieces <- str_split(term, ":", simplify = FALSE)[[1]]
  paste(map_chr(pieces, label_term_piece), collapse = " × ")
}

make_coefficient_cell <- function(estimate, std.error, p.value) {
  paste0(
    fmt_number(estimate),
    significance_stars(p.value),
    "\n(",
    fmt_number(std.error),
    ")"
  )
}

display_variants_for_family <- function(family_name) {
  if (family_name == "first_difference") {
    fd_variants
  } else {
    levels_variants
  }
}

make_table_dataframe <- function(spec_models) {
  family_name <- first(spec_models$family)

  # State-FE models remain estimated and stored, but are omitted from the
  # publication table.
  display_variants <- display_variants_for_family(family_name)

  fitted <- spec_models %>%
    filter(
      model_fit,
      .data$variant %in% display_variants$variant
    )

  coefficient_long <- fitted %>%
    mutate(
      tidied = map(model, tidy_fixest)
    ) %>%
    select(
      variant,
      tidied
    ) %>%
    unnest(tidied) %>%
    mutate(
      cell = pmap_chr(
        list(
          estimate,
          std.error,
          p.value
        ),
        make_coefficient_cell
      )
    )

  term_order <- unique(coefficient_long$term)

  if ("(Intercept)" %in% term_order) {
    term_order <- c(
      "(Intercept)",
      setdiff(
        term_order,
        "(Intercept)"
      )
    )
  }

  coefficient_table <- coefficient_long %>%
    mutate(
      term = factor(
        term,
        levels = term_order
      ),
      Variable = map_chr(
        as.character(term),
        label_term
      )
    ) %>%
    select(
      Variable,
      variant,
      cell
    ) %>%
    pivot_wider(
      names_from = variant,
      values_from = cell,
      values_fill = ""
    ) %>%
    arrange(
      match(
        Variable,
        map_chr(
          term_order,
          label_term
        )
      )
    )

  # Create any missing display columns explicitly.
  for (
    variant_name in display_variants$variant
  ) {
    if (
      !variant_name %in%
        names(coefficient_table)
    ) {
      coefficient_table[[variant_name]] <- ""
    }
  }

  coefficient_table <- coefficient_table %>%
    select(
      Variable,
      all_of(
        display_variants$variant
      )
    ) %>%
    mutate(
      across(
        -Variable,
        ~ replace_na(.x, "")
      )
    )

  stat_rows <- map_dfr(
    seq_len(
      nrow(display_variants)
    ),
    \(i) {
      variant_row <-
        display_variants[i, ]

      model_row <- spec_models %>%
        filter(
          .data$variant ==
            variant_row$variant
        ) %>%
        slice_head(n = 1)

      tibble(
        variant =
          variant_row$variant,

        standard_controls =
          if_else(
            "include_controls" %in%
              names(variant_row) &&
              variant_row$include_controls,
            "Yes",
            "No"
          ),

        year_control =
          if_else(
            "include_year" %in%
              names(variant_row) &&
              variant_row$include_year,
            "Yes",
            "No"
          ),

        prior_migration =
          if_else(
            "include_prior_migration" %in%
              names(variant_row) &&
              variant_row$
                include_prior_migration,
            "Yes",
            "No"
          ),
        
        state_fixed_effects =
          if_else(
            "include_state_fe" %in%
              names(variant_row) &&
              variant_row$include_state_fe,
            "Yes",
            "No"
            ),

        pc_clustered = "Yes",

        regression_weights =
          case_when(
            family_name ==
              "ideology_binomial" ~
              "Valid-vote binomial trials",

            TRUE ~
              "Unweighted"
          ),

        observations =
          if_else(
            nrow(model_row) == 0,
            "",
            fmt_integer(
              model_row$nobs
            )
          ),

        trials =
          if_else(
            nrow(model_row) == 0 ||
              is.na(
                model_row$trial_count
              ),
            "",
            fmt_integer(
              model_row$trial_count
            )
          ),

        clusters =
          if_else(
            nrow(model_row) == 0,
            "",
            fmt_integer(
              model_row$n_pc_clusters
            )
          ),

        fit_stat =
          if_else(
            nrow(model_row) == 0,
            "",
            fmt_number(
              model_row$fit_stat
            )
          )
      )
    }
  )

  make_stat_row <- function(
    label,
    column_name
  ) {
    values <-
      stat_rows[[column_name]]

    names(values) <-
      stat_rows$variant

    tibble(
      Variable = label
    ) %>%
      bind_cols(
        as_tibble_row(
          values[
            display_variants$variant
          ]
        )
      )
  }

  statistics_table <- bind_rows(
    if (
      family_name !=
        "first_difference"
    ) {
      make_stat_row(
        "Standard controls",
        "standard_controls"
      )
    },

    if (
      family_name !=
        "first_difference"
    ) {
      make_stat_row(
        "Year control",
        "year_control"
      )
    },

    if (
      family_name !=
        "first_difference"
    ) {
      make_stat_row(
        "Prior migrant-share control",
        "prior_migration"
      )
    },
    
    make_stat_row(
  "State fixed effects",
  "state_fixed_effects"
),

    make_stat_row(
      "PC-clustered standard errors",
      "pc_clustered"
    ),

    make_stat_row(
      "Regression weights",
      "regression_weights"
    ),

    make_stat_row(
      "Observations",
      "observations"
    ),

    if (
      family_name ==
        "ideology_binomial"
    ) {
      make_stat_row(
        "Valid respondent trials",
        "trials"
      )
    },

    make_stat_row(
      "PC clusters",
      "clusters"
    ),

    make_stat_row(
      if_else(
        family_name %in%
          c(
            "voter_ideology_logit",
            "ideology_binomial"
          ),
        "Pseudo R²",
        "R²"
      ),
      "fit_stat"
    )
  )

  output <- bind_rows(
    coefficient_table,
    statistics_table
  )

  names(output) <- c(
    "Variable",
    display_variants$column_label
  )

  output
}
```

```{r 9-marginal-effect-and-coefficient-plot-helpers}
# =========================================================================
# Model selection and marginal-effect plots
#
# Plot models:
#   - First-difference coefficient plots: hidden state-FE robustness model
#   - Levels and moderate-share OLS plots: hidden state-FE robustness model
#   - Voter logit and grouped-binomial plots: Column 4, without state FE
#
# For nonlinear models, average marginal effects and their clustered
# delta-method standard errors are calculated directly. This avoids the
# marginaleffects/fixest fixed-effect uncertainty error.
# =========================================================================

select_plot_model_row <- function(spec_models) {
  family_name <- first(spec_models$family)

  candidate_variants <- switch(
    family_name,

    "first_difference" = c(
      "first_difference_state_fe",
      "first_difference"
    ),

    "voter_ideology_logit" = c(
      "prior_migration",
      "year",
      "controls",
      "base"
    ),

    "ideology_binomial" = c(
      "prior_migration",
      "year",
      "controls",
      "base"
    ),

    "levels" = c(
      "state_fe",
      "prior_migration",
      "year",
      "controls",
      "base"
    ),

    "moderate_triple" = c(
      "state_fe",
      "prior_migration",
      "year",
      "controls",
      "base"
    ),

    unique(spec_models$variant)
  )

  for (candidate_variant in candidate_variants) {
    candidate_row <- spec_models %>%
      filter(
        .data$variant == .env$candidate_variant,
        .data$model_fit
      ) %>%
      slice_head(n = 1)

    if (nrow(candidate_row) > 0) {
      if (
        family_name %in% c(
          "voter_ideology_logit",
          "ideology_binomial"
        ) &&
          isTRUE(candidate_row$include_state_fe[[1]])
      ) {
        stop(
          "A state-FE nonlinear model was incorrectly selected ",
          "for the marginal-effects plot."
        )
      }

      return(candidate_row)
    }
  }

  spec_models[0, ]
}


migration_grid_values <- function(data, variable) {
  values <- quantile(
    data[[variable]],
    probs = seq(
      0.10,
      0.90,
      length.out = 5
    ),
    na.rm = TRUE,
    names = FALSE
  )

  values <- as.numeric(values)
  values <- unique(values[is.finite(values)])

  if (length(values) < 2) {
    stop(
      "Insufficient variation in ",
      variable,
      " to create a marginal-effects plot."
    )
  }

  values
}


make_fd_coefficient_plot <- function(spec_models) {
  model_row <- select_plot_model_row(
    spec_models
  )

  if (
    nrow(model_row) == 0 ||
      is.null(model_row$model[[1]])
  ) {
    return(
      ggplot() +
        annotate(
          "text",
          x = 0,
          y = 0,
          label = "Coefficient plot unavailable"
        ) +
        theme_void()
    )
  }

  terms_to_plot <- c(
    model_row$fdi_var,
    model_row$migration_var,
    model_row$fd_product_var
  )

  coefficient_data <- tidy_fixest(
    model_row$model[[1]]
  ) %>%
    filter(
      term %in% terms_to_plot
    ) %>%
    mutate(
      label = factor(
        map_chr(term, label_term),
        levels = rev(
          map_chr(
            terms_to_plot,
            label_term
          )
        )
      ),
      conf.low = estimate - 1.96 * std.error,
      conf.high = estimate + 1.96 * std.error
    )

  if (nrow(coefficient_data) == 0) {
    return(
      ggplot() +
        annotate(
          "text",
          x = 0,
          y = 0,
          label = "No first-difference coefficients were available"
        ) +
        theme_void()
    )
  }

  ggplot(
    coefficient_data,
    aes(
      x = label,
      y = estimate
    )
  ) +
    geom_hline(
      yintercept = 0,
      linetype = "dashed",
      linewidth = 0.35
    ) +
    geom_errorbar(
      aes(
        ymin = conf.low,
        ymax = conf.high
      ),
      width = 0.15,
      linewidth = 0.4
    ) +
    geom_point(
      size = 1.5
    ) +
    coord_flip() +
    labs(
      title = "First-difference coefficients",
      subtitle = paste0(
        model_row$column_label,
        "; PC-clustered 95% confidence intervals"
      ),
      y = "Coefficient on 2009–2014 change",
      x = NULL
    ) +
    theme_minimal(
      base_size = 8.5
    ) +
    theme(
      plot.title = element_text(
        face = "bold",
        size = 9
      ),
      plot.subtitle = element_text(
        size = 6.8
      ),
      axis.text = element_text(
        size = 6.8
      ),
      axis.title = element_text(
        size = 7.2
      ),
      panel.grid.minor = element_blank()
    )
}


# -------------------------------------------------------------------------
# Construct a model matrix whose columns exactly match coef(model).
# -------------------------------------------------------------------------

make_aligned_rhs_matrix <- function(model, newdata) {
  coefficients <- coef(model)
  coefficient_names <- names(coefficients)

  candidate_matrix_functions <- list(
    function() {
      stats::model.matrix(
        model,
        data = newdata,
        type = "rhs"
      )
    },
    function() {
      stats::model.matrix(
        model,
        newdata = newdata,
        type = "rhs"
      )
    },
    function() {
      model_terms <- stats::delete.response(
        stats::terms(model)
      )

      stats::model.matrix(
        model_terms,
        data = newdata
      )
    }
  )

  raw_matrix <- NULL
  matrix_errors <- character()

  for (matrix_function in candidate_matrix_functions) {
    attempt <- tryCatch(
      matrix_function(),
      error = \(e) e
    )

    if (!inherits(attempt, "error")) {
      raw_matrix <- attempt
      break
    }

    matrix_errors <- c(
      matrix_errors,
      conditionMessage(attempt)
    )
  }

  if (is.null(raw_matrix)) {
    stop(
      "Could not construct the nonlinear model matrix. Attempts returned: ",
      paste(unique(matrix_errors), collapse = " | ")
    )
  }

  raw_matrix <- as.matrix(raw_matrix)

  missing_coefficient_columns <- setdiff(
    coefficient_names,
    colnames(raw_matrix)
  )

  if (length(missing_coefficient_columns) > 0) {
    stop(
      "The reconstructed model matrix is missing coefficient columns: ",
      paste(
        missing_coefficient_columns,
        collapse = ", "
      )
    )
  }

  aligned_matrix <- matrix(
    0,
    nrow = nrow(raw_matrix),
    ncol = length(coefficient_names),
    dimnames = list(
      NULL,
      coefficient_names
    )
  )

  aligned_matrix[, coefficient_names] <-
    raw_matrix[, coefficient_names, drop = FALSE]

  aligned_matrix
}


# -------------------------------------------------------------------------
# Average marginal effect for a grouped or individual logit model.
#
# For observation i:
#
#   ME_i = p_i(1-p_i) × d(eta_i)/d(FDI)
#
# The gradient with respect to beta is used with the model's PC-clustered
# covariance matrix to calculate a delta-method standard error.
# -------------------------------------------------------------------------

calculate_logit_ame <- function(
  model,
  data,
  fdi_var,
  migration_var,
  migration_value,
  ideology_value = NULL,
  weight_var = NULL
) {
  newdata <- data
  newdata[[migration_var]] <- migration_value

  if (!is.null(ideology_value)) {
    newdata$voter_ideology <- factor(
      ideology_value,
      levels = c(
        "C",
        "L",
        "R"
      )
    )
  }

  coefficients <- coef(model)
  coefficient_names <- names(coefficients)

  covariance_matrix <- tryCatch(
    as.matrix(vcov(model)),
    error = \(e) {
      stop(
        "Could not extract the model covariance matrix: ",
        conditionMessage(e)
      )
    }
  )

  if (
    is.null(rownames(covariance_matrix)) ||
      is.null(colnames(covariance_matrix))
  ) {
    if (
      nrow(covariance_matrix) !=
        length(coefficients)
    ) {
      stop(
        "The covariance matrix dimensions do not match ",
        "the number of coefficients."
      )
    }

    rownames(covariance_matrix) <- coefficient_names
    colnames(covariance_matrix) <- coefficient_names
  }

  missing_vcov_terms <- setdiff(
    coefficient_names,
    rownames(covariance_matrix)
  )

  if (length(missing_vcov_terms) > 0) {
    stop(
      "The covariance matrix is missing coefficient terms: ",
      paste(
        missing_vcov_terms,
        collapse = ", "
      )
    )
  }

  covariance_matrix <- covariance_matrix[
    coefficient_names,
    coefficient_names,
    drop = FALSE
  ]

  fdi_scale <- sd(
    newdata[[fdi_var]],
    na.rm = TRUE
  )

  if (
    !is.finite(fdi_scale) ||
      fdi_scale <= 0
  ) {
    fdi_scale <- 1
  }

  finite_difference_step <- max(
    1e-6,
    fdi_scale * 1e-6
  )

  newdata_plus <- newdata
  newdata_minus <- newdata

  newdata_plus[[fdi_var]] <-
    newdata_plus[[fdi_var]] +
    finite_difference_step

  newdata_minus[[fdi_var]] <-
    newdata_minus[[fdi_var]] -
    finite_difference_step

  model_matrix <- make_aligned_rhs_matrix(
    model,
    newdata
  )

  model_matrix_plus <- make_aligned_rhs_matrix(
    model,
    newdata_plus
  )

  model_matrix_minus <- make_aligned_rhs_matrix(
    model,
    newdata_minus
  )

  derivative_matrix <- (
    model_matrix_plus -
      model_matrix_minus
  ) / (
    2 * finite_difference_step
  )

  linear_predictor <- as.numeric(
    model_matrix %*% coefficients
  )

  probability <- plogis(
    linear_predictor
  )

  derivative_linear_predictor <- as.numeric(
    derivative_matrix %*% coefficients
  )

  observation_effect <- (
    probability *
      (1 - probability) *
      derivative_linear_predictor
  )

  if (is.null(weight_var)) {
    analysis_weights <- rep(
      1,
      nrow(newdata)
    )
  } else {
    if (!weight_var %in% names(newdata)) {
      stop(
        "The requested marginal-effect weight variable is missing: ",
        weight_var
      )
    }

    analysis_weights <- as.numeric(
      newdata[[weight_var]]
    )
  }

  valid_rows <- (
    is.finite(observation_effect) &
      is.finite(analysis_weights) &
      analysis_weights > 0
  )

  if (!any(valid_rows)) {
    stop(
      "No valid observations remained for the nonlinear ",
      "average marginal effect."
    )
  }

  analysis_weights <- analysis_weights[
    valid_rows
  ]

  normalized_weights <- analysis_weights /
    sum(analysis_weights)

  observation_effect <- observation_effect[
    valid_rows
  ]

  probability <- probability[
    valid_rows
  ]

  derivative_linear_predictor <-
    derivative_linear_predictor[
      valid_rows
    ]

  model_matrix <- model_matrix[
    valid_rows,
    ,
    drop = FALSE
  ]

  derivative_matrix <- derivative_matrix[
    valid_rows,
    ,
    drop = FALSE
  ]

  estimate <- sum(
    normalized_weights *
      observation_effect
  )

  probability_variance <- probability *
    (1 - probability)

  first_gradient_component <- sweep(
    derivative_matrix,
    MARGIN = 1,
    STATS = probability_variance,
    FUN = "*"
  )

  second_gradient_multiplier <- (
    derivative_linear_predictor *
      probability_variance *
      (1 - 2 * probability)
  )

  second_gradient_component <- sweep(
    model_matrix,
    MARGIN = 1,
    STATS = second_gradient_multiplier,
    FUN = "*"
  )

  observation_gradient <- (
    first_gradient_component +
      second_gradient_component
  )

  weighted_gradient <- colSums(
    sweep(
      observation_gradient,
      MARGIN = 1,
      STATS = normalized_weights,
      FUN = "*"
    )
  )

  variance <- as.numeric(
    t(weighted_gradient) %*%
      covariance_matrix %*%
      weighted_gradient
  )

  variance <- max(
    variance,
    0,
    na.rm = TRUE
  )

  standard_error <- sqrt(
    variance
  )

  if (
    is.finite(standard_error) &&
      standard_error > 0
  ) {
    statistic <- estimate /
      standard_error

    p_value <- 2 * pnorm(
      abs(statistic),
      lower.tail = FALSE
    )
  } else {
    p_value <- NA_real_
  }

  tibble(
    estimate = estimate,
    std.error = standard_error,
    conf.low = estimate - 1.96 * standard_error,
    conf.high = estimate + 1.96 * standard_error,
    p.value = p_value,
    uncertainty_status =
      "PC-clustered delta-method confidence interval",
    error = NA_character_
  )
}


make_marginal_effect_data <- function(spec_models) {
  model_row <- select_plot_model_row(
    spec_models
  )

  if (
    nrow(model_row) == 0 ||
      is.null(model_row$model[[1]])
  ) {
    return(
      tibble(
        error = paste(
          "No fitted model is available",
          "for the marginal-effects plot."
        )
      )
    )
  }

  family_name <- model_row$family[[1]]
  model <- model_row$model[[1]]
  data <- model_row$data_used[[1]]
  fdi_var <- model_row$fdi_var[[1]]
  migration_var <- model_row$migration_var[[1]]

  migration_values <- migration_grid_values(
    data,
    migration_var
  )

  ideology_family <- family_name %in% c(
    "voter_ideology_logit",
    "ideology_binomial"
  )

  moderator_family <- family_name ==
    "moderate_triple"

  if (ideology_family) {
    calculation_grid <- tidyr::crossing(
      migration_value = migration_values,
      ideology_value = c(
        "C",
        "L",
        "R"
      ),
      moderator_value = NA_real_
    )
  } else if (moderator_family) {
    moderator_values <- quantile(
      data$moderate_share_10pp_c,
      probs = c(
        0.25,
        0.50,
        0.75
      ),
      na.rm = TRUE,
      names = FALSE
    )

    moderator_values <- unique(
      as.numeric(
        moderator_values[
          is.finite(moderator_values)
        ]
      )
    )

    calculation_grid <- tidyr::crossing(
      migration_value = migration_values,
      ideology_value = NA_character_,
      moderator_value = moderator_values
    )
  } else {
    calculation_grid <- tidyr::crossing(
      migration_value = migration_values,
      ideology_value = NA_character_,
      moderator_value = NA_real_
    )
  }

  pmap_dfr(
    calculation_grid,
    \(migration_value,
      ideology_value,
      moderator_value) {

      # ---------------------------------------------------------------
      # Nonlinear voter and grouped-binomial models
      # ---------------------------------------------------------------

      if (ideology_family) {
        weight_variable <- if (
          family_name ==
            "ideology_binomial"
        ) {
          "n_valid_vote"
        } else {
          NULL
        }

        result <- tryCatch(
          calculate_logit_ame(
            model = model,
            data = data,
            fdi_var = fdi_var,
            migration_var = migration_var,
            migration_value = migration_value,
            ideology_value = ideology_value,
            weight_var = weight_variable
          ),
          error = \(e) {
            tibble(
              estimate = NA_real_,
              std.error = NA_real_,
              conf.low = NA_real_,
              conf.high = NA_real_,
              p.value = NA_real_,
              uncertainty_status = NA_character_,
              error = conditionMessage(e)
            )
          }
        )

        return(
          result %>%
            mutate(
              migration_value =
                migration_value,

              ideology_value =
                ideology_value,

              moderator_value =
                moderator_value,

              plot_variant =
                model_row$variant[[1]],

              plot_column_label =
                model_row$column_label[[1]],

              .before = 1
            )
        )
      }

      # ---------------------------------------------------------------
      # Linear levels and moderate-share models
      # ---------------------------------------------------------------

      newdata <- data
      newdata[[migration_var]] <-
        migration_value

      if (moderator_family) {
        newdata$moderate_share_10pp_c <-
          moderator_value
      }

      clustered_vcov <- tryCatch(
        as.matrix(vcov(model)),
        error = \(e) NULL
      )

      effect <- tryCatch(
        marginaleffects::avg_slopes(
          model,
          variables = fdi_var,
          newdata = newdata,
          type = "response",
          wts = FALSE,
          vcov = clustered_vcov
        ),
        error = \(e) e
      )

      if (inherits(effect, "error")) {
        return(
          tibble(
            migration_value =
              migration_value,

            ideology_value =
              ideology_value,

            moderator_value =
              moderator_value,

            estimate = NA_real_,
            std.error = NA_real_,
            conf.low = NA_real_,
            conf.high = NA_real_,
            p.value = NA_real_,

            uncertainty_status =
              NA_character_,

            plot_variant =
              model_row$variant[[1]],

            plot_column_label =
              model_row$column_label[[1]],

            error =
              conditionMessage(effect)
          )
        )
      }

      as_tibble(effect) %>%
        transmute(
          migration_value =
            migration_value,

          ideology_value =
            ideology_value,

          moderator_value =
            moderator_value,

          estimate,
          std.error,
          conf.low,
          conf.high,
          p.value,

          uncertainty_status =
            "PC-clustered confidence interval",

          plot_variant =
            model_row$variant[[1]],

          plot_column_label =
            model_row$column_label[[1]],

          error =
            NA_character_
        )
    }
  )
}


make_marginal_effect_plot <- function(spec_models) {
  family_name <- first(
    spec_models$family
  )

  if (
    family_name ==
      "first_difference"
  ) {
    return(
      make_fd_coefficient_plot(
        spec_models
      )
    )
  }

  effect_data <- make_marginal_effect_data(
    spec_models
  )

  successful_effect_data <- effect_data %>%
    filter(
      is.na(error),
      is.finite(estimate)
    )

  if (
    nrow(successful_effect_data) == 0
  ) {
    error_message <- effect_data$error[
      which(!is.na(effect_data$error))[1]
    ]

    if (
      length(error_message) == 0 ||
        is.na(error_message)
    ) {
      error_message <-
        "Marginal effect unavailable"
    }

    return(
      ggplot() +
        annotate(
          "text",
          x = 0,
          y = 0,
          label = str_wrap(
            error_message,
            width = 45
          ),
          size = 3
        ) +
        theme_void()
    )
  }

  effect_data <- successful_effect_data

  spec <- spec_models %>%
    slice_head(n = 1)

  plot_column <- first(
    effect_data$plot_column_label
  )

  has_confidence_intervals <- any(
    is.finite(
      effect_data$conf.low
    ) &
      is.finite(
        effect_data$conf.high
      )
  )

  subtitle_text <- if (
    has_confidence_intervals
  ) {
    paste0(
      plot_column,
      "; PC-clustered 95% confidence intervals"
    )
  } else {
    paste0(
      plot_column,
      "; point estimates only"
    )
  }

  base_plot <- ggplot(
    effect_data,
    aes(
      x = migration_value,
      y = estimate
    )
  ) +
    geom_hline(
      yintercept = 0,
      linetype = "dashed",
      linewidth = 0.35
    ) +
    labs(
      title = paste0(
        "Marginal effect of ",
        spec$fdi_name
      ),
      subtitle = str_wrap(
        subtitle_text,
        width = 48
      ),
      x = spec$migration_name,
      y = if_else(
        family_name %in% c(
          "voter_ideology_logit",
          "ideology_binomial"
        ),
        "Average marginal effect on Pr(far-right vote)",
        "Marginal effect on far-right vote percentage"
      )
    ) +
    theme_minimal(
      base_size = 8.5
    ) +
    theme(
      plot.title = element_text(
        face = "bold",
        size = 9
      ),
      plot.subtitle = element_text(
        size = 6.8
      ),
      axis.title = element_text(
        size = 7.5
      ),
      axis.text = element_text(
        size = 6.8
      ),
      panel.grid.minor = element_blank(),
      legend.position = "bottom",
      legend.text = element_text(
        size = 6.5
      ),
      legend.key.width = grid::unit(
        0.8,
        "lines"
      )
    )

  if (
    family_name %in% c(
      "voter_ideology_logit",
      "ideology_binomial"
    )
  ) {
    effect_data <- effect_data %>%
      mutate(
        ideology_label = recode(
          ideology_value,
          "C" = "Center voters",
          "L" = "Left voters",
          "R" = "Right voters"
        )
      )

    plot_output <- base_plot %+%
      effect_data

    if (has_confidence_intervals) {
      plot_output <- plot_output +
        geom_ribbon(
          aes(
            ymin = conf.low,
            ymax = conf.high,
            group = ideology_label,
            fill = ideology_label
          ),
          alpha = 0.10,
          colour = NA
        )
    }

    return(
      plot_output +
        geom_line(
          aes(
            group = ideology_label,
            linetype = ideology_label
          ),
          linewidth = 0.55
        ) +
        geom_point(
          aes(
            shape = ideology_label
          ),
          size = 1.4
        ) +
        labs(
          linetype = NULL,
          shape = NULL,
          fill = NULL
        )
    )
  }

  if (
    family_name ==
      "moderate_triple"
  ) {
    moderator_levels <- sort(
      unique(
        effect_data$moderator_value
      )
    )

    effect_data <- effect_data %>%
      mutate(
        moderate_level = factor(
          moderator_value,
          levels = moderator_levels,
          labels = c(
            "Low moderate share",
            "Median moderate share",
            "High moderate share"
          )[seq_along(moderator_levels)]
        )
      )

    plot_output <- base_plot %+%
      effect_data

    if (has_confidence_intervals) {
      plot_output <- plot_output +
        geom_ribbon(
          aes(
            ymin = conf.low,
            ymax = conf.high,
            group = moderate_level,
            fill = moderate_level
          ),
          alpha = 0.10,
          colour = NA
        )
    }

    return(
      plot_output +
        geom_line(
          aes(
            group = moderate_level,
            linetype = moderate_level
          ),
          linewidth = 0.55
        ) +
        geom_point(
          aes(
            shape = moderate_level
          ),
          size = 1.4
        ) +
        labs(
          linetype = NULL,
          shape = NULL,
          fill = NULL
        )
    )
  }

  plot_output <- base_plot

  if (has_confidence_intervals) {
    plot_output <- plot_output +
      geom_ribbon(
        aes(
          ymin = conf.low,
          ymax = conf.high
        ),
        alpha = 0.16
      )
  }

  plot_output +
    geom_line(
      linewidth = 0.55
    ) +
    geom_point(
      size = 1.4
    )
}


# =========================================================================
# Validate nonlinear plot-model selection.
# =========================================================================

nonlinear_plot_groups <- all_models %>%
  filter(
    family %in% c(
      "voter_ideology_logit",
      "ideology_binomial"
    )
  ) %>%
  group_split(
    family,
    table_id,
    .keep = TRUE
  )

nonlinear_plot_model_check <- map_dfr(
  nonlinear_plot_groups,
  \(model_group) {
    selected_model <- select_plot_model_row(
      model_group
    )

    tibble(
      family = first(
        model_group$family
      ),

      table_id = first(
        model_group$table_id
      ),

      spec_id = first(
        model_group$spec_id
      ),

      selected_variant = if (
        nrow(selected_model) == 0
      ) {
        NA_character_
      } else {
        selected_model$variant[[1]]
      },

      selected_column = if (
        nrow(selected_model) == 0
      ) {
        NA_character_
      } else {
        selected_model$column_label[[1]]
      },

      selected_state_fe = if (
        nrow(selected_model) == 0
      ) {
        NA
      } else {
        selected_model$include_state_fe[[1]]
      }
    )
  }
)

print(
  nonlinear_plot_model_check,
  n = Inf
)

if (
  any(
    nonlinear_plot_model_check$
      selected_state_fe %in% TRUE,
    na.rm = TRUE
  )
) {
  stop(
    paste(
      "At least one nonlinear marginal-effects plot",
      "selected an absorbed state-FE model."
    )
  )
}


# =========================================================================
# Calculate all marginal-effect results.
# =========================================================================

marginal_effect_table_index <- all_models %>%
  filter(
    family !=
      "first_difference"
  ) %>%
  distinct(
    table_id,
    family,
    spec_id,
    spec_label
  )

marginal_effect_results <- map_dfr(
  seq_len(
    nrow(
      marginal_effect_table_index
    )
  ),
  \(i) {
    one_table <-
      marginal_effect_table_index[i, ]

    table_models <- all_models %>%
      filter(
        table_id ==
          one_table$table_id
      )

    make_marginal_effect_data(
      table_models
    ) %>%
      mutate(
        family =
          one_table$family,

        spec_id =
          one_table$spec_id,

        spec_label =
          one_table$spec_label,

        .before = 1
      )
  }
)


marginal_effect_failures <- marginal_effect_results %>%
  filter(
    !is.na(error),
    error != ""
  ) %>%
  distinct(
    family,
    spec_id,
    spec_label,
    error
  )

if (
  nrow(
    marginal_effect_failures
  ) > 0
) {
  print(
    marginal_effect_failures,
    n = Inf
  )

  stop(
    paste(
      "One or more marginal-effects plots",
      "could not be calculated."
    )
  )
}


write_csv(
  marginal_effect_results,
  file.path(
    RESULT_DIR,
    "marginal_effect_results.csv"
  )
)

write_csv(
  nonlinear_plot_model_check,
  file.path(
    RESULT_DIR,
    "nonlinear_plot_model_check.csv"
  )
)
```

```{r 10-side-by-side-report-rendering}
wrap_regression_table <- function(
  table_df
) {
  display <- table_df

  # All variable labels remain in the first
  # column. Wrapping happens only within that
  # column.
  display$Variable <- str_wrap(
    display$Variable,
    width = 44
  )

  names(display)[-1] <-
    str_wrap(
      names(display)[-1],
      width = 13
    )

  display
}

left_align_first_table_column <-
  function(grob) {
    first_column <-
      min(grob$layout$l)

    text_cells <- which(
      grob$layout$l ==
        first_column &
        grob$layout$name %in%
        c(
          "core-fg",
          "colhead-fg"
        )
    )

    for (cell_index in text_cells) {
      grob$grobs[[cell_index]]$x <-
        grid::unit(
          0.02,
          "npc"
        )

      grob$grobs[[cell_index]]$hjust <- 0
    }

    grob
  }

add_journal_rules <- function(grob) {
  header_rows <- grob$layout$t[
    grob$layout$name == "colhead-fg"
  ]

  core_rows <- grob$layout$b[
    grob$layout$name == "core-fg"
  ]

  if (
    length(header_rows) == 0 ||
      length(core_rows) == 0
  ) {
    return(grob)
  }

  header_row <- min(header_rows)
  final_row <- max(core_rows)

  left_column <- min(grob$layout$l)
  right_column <- max(grob$layout$r)

  horizontal_rule <- function(
    y_position,
    line_width
  ) {
    grid::segmentsGrob(
      x0 = grid::unit(0, "npc"),
      x1 = grid::unit(1, "npc"),
      y0 = grid::unit(y_position, "npc"),
      y1 = grid::unit(y_position, "npc"),
      gp = grid::gpar(
        col = "black",
        lwd = line_width
      )
    )
  }

  # Top rule.
  grob <- gtable::gtable_add_grob(
    grob,
    grobs = horizontal_rule(
      y_position = 1,
      line_width = 0.9
    ),
    t = header_row,
    l = left_column,
    r = right_column,
    z = Inf,
    clip = "off"
  )

  # Rule below the column headings.
  grob <- gtable::gtable_add_grob(
    grob,
    grobs = horizontal_rule(
      y_position = 0,
      line_width = 0.65
    ),
    t = header_row,
    l = left_column,
    r = right_column,
    z = Inf,
    clip = "off"
  )

  # Bottom rule.
  grob <- gtable::gtable_add_grob(
    grob,
    grobs = horizontal_rule(
      y_position = 0,
      line_width = 0.9
    ),
    t = final_row,
    l = left_column,
    r = right_column,
    z = Inf,
    clip = "off"
  )

  grob
}

make_table_grob <- function(
  table_df
) {
  display <-
    wrap_regression_table(
      table_df
    )

  row_count <-
    nrow(display)

  column_count <-
    ncol(display)

  base_font <- case_when(
    row_count >= 30 ~ 5.4,
    row_count >= 25 ~ 5.8,
    row_count >= 20 ~ 6.2,
    column_count <= 2 ~ 7.2,
    TRUE ~ 6.6
  )

  journal_theme <-
    gridExtra::ttheme_minimal(
      base_size = base_font,
      base_family = "serif",

      padding =
        grid::unit(
          c(1.15, 1.7),
          "mm"
        ),

      core = list(
        fg_params = list(
          fontsize = base_font,
          fontfamily = "serif",
          hjust = 0.5,
          x = 0.5,
          lineheight = 0.92
        ),

        bg_params = list(
          fill = "white",
          col = NA
        )
      ),

      colhead = list(
        fg_params = list(
          fontsize =
            base_font + 0.25,
          fontfamily = "serif",
          fontface = "bold",
          hjust = 0.5,
          x = 0.5,
          lineheight = 0.92
        ),

        bg_params = list(
          fill = "white",
          col = NA
        )
      )
    )

  grob <-
    gridExtra::tableGrob(
      display,
      rows = NULL,
      theme = journal_theme
    )

  # Give the single variable-name column much
  # more space than each coefficient column.
  variable_width <- case_when(
    column_count == 2 ~ 4.8,
    column_count == 5 ~ 4.3,
    TRUE ~ 4.5
  )

  grob$widths <-
    grid::unit(
      c(
        variable_width,
        rep(
          1,
          column_count - 1
        )
      ),
      "null"
    )

  grob <-
    left_align_first_table_column(
      grob
    )

  grob <-
    add_journal_rules(
      grob
    )

  grob
}

make_page_title <- function(spec_models, page_number, total_pages) {
  spec <- spec_models %>% slice_head(n = 1)

  paste0(
    spec$family_label,
    " | ",
    spec$spec_label,
    "  (page ",
    page_number,
    " of ",
    total_pages,
    ")"
  )
}

make_page_note <- function(
  spec_models
) {
  family_name <-
    first(spec_models$family)

  plot_row <-
    select_plot_model_row(
      spec_models
    )

  plot_description <-
    if (
      nrow(plot_row) == 0
    ) {
      "No fitted model was available for the plot."
    } else if (
      family_name %in%
        c(
          "voter_ideology_logit",
          "ideology_binomial"
        )
    ) {
      paste0(
        "Probability-scale marginal effects use ",
        plot_row$column_label,
        " because uncertainty from the absorbed state fixed effects cannot be propagated reliably."
      )
    } else {
      paste0(
        "The plot uses ",
        plot_row$column_label,
        "."
      )
    }

  paste(
    "Notes:",
    "PC-clustered standard errors are in parentheses.",
    "State fixed effects are absorbed rather than reported individually.",
    "The intercept is blank in absorbed state-fixed-effect columns.",
    plot_description
  )
}

draw_report_page <- function(spec_models, page_number, total_pages) {
  table_df <- make_table_dataframe(spec_models)
  table_grob <- make_table_grob(table_df)

  effect_plot <- make_marginal_effect_plot(spec_models) +
    theme(
      plot.title = element_text(face = "bold", size = 8.3),
      plot.subtitle = element_text(size = 6.6),
      axis.title = element_text(size = 7.2),
      axis.text = element_text(size = 6.6),
      legend.title = element_blank(),
      legend.text = element_text(size = 6.2),
      legend.position = "bottom",
      plot.margin = margin(2, 2, 2, 2)
    )

  effect_grob <- ggplotGrob(effect_plot)

  title_grob <- grid::textGrob(
    make_page_title(spec_models, page_number, total_pages),
    x = 0,
    hjust = 0,
    just = "left",
    gp = grid::gpar(
      fontsize = 10.2,
      fontface = "bold",
      fontfamily = "serif"
    )
  )

  note_grob <- grid::textGrob(
    str_wrap(make_page_note(spec_models), width = 210),
    x = 0,
    hjust = 0,
    just = "left",
    gp = grid::gpar(
      fontsize = 6.4,
      lineheight = 0.92,
      fontfamily = "serif"
    )
  )

  content_grob <- gridExtra::arrangeGrob(
    table_grob,
    effect_grob,
    ncol = 2,
    widths = c(0.76, 0.24),
    padding = grid::unit(1.5, "mm")
  )

  page <- gridExtra::arrangeGrob(
    title_grob,
    content_grob,
    note_grob,
    ncol = 1,
    heights = c(0.07, 0.88, 0.05),
    padding = grid::unit(1.5, "mm")
  )

  grid::grid.newpage()
  grid::grid.draw(page)
}

render_family_report <- function(model_grid, output_file) {
  if (nrow(model_grid) == 0) return(invisible(NULL))

  table_index <- model_grid %>%
    distinct(table_id, spec_id) %>%
    arrange(match(spec_id, exposure_specs$spec_id))

  grDevices::pdf(
    output_file,
    width = 17,
    height = 10.5,
    onefile = TRUE
  )
  on.exit(grDevices::dev.off(), add = TRUE)

  for (i in seq_len(nrow(table_index))) {
    table_models <- model_grid %>%
      filter(table_id == table_index$table_id[i])
    draw_report_page(table_models, i, nrow(table_index))
  }

  invisible(output_file)
}

report_plan <- tribble(
  ~family, ~output_group, ~directory, ~filename,
  "first_difference", "main", MAIN_TABLE_DIR, "main_first_difference_panel.pdf",
  "levels", "main", MAIN_TABLE_DIR, "main_pooled_ac_levels.pdf",
  "voter_ideology_logit", "main", MAIN_TABLE_DIR, "main_voter_ideology_interaction_logit.pdf",
  "ideology_binomial", "main", MAIN_TABLE_DIR, "main_aggregated_binomial_ideology.pdf",
  "moderate_triple", "main", MAIN_TABLE_DIR, "main_moderate_share_triple_interaction.pdf",
  "first_difference", "appendix", APPENDIX_TABLE_DIR, "appendix_first_difference_panel.pdf",
  "levels", "appendix", APPENDIX_TABLE_DIR, "appendix_pooled_ac_levels.pdf",
  "voter_ideology_logit", "appendix", APPENDIX_TABLE_DIR, "appendix_voter_ideology_interaction_logit.pdf",
  "ideology_binomial", "appendix", APPENDIX_TABLE_DIR, "appendix_aggregated_binomial_ideology.pdf",
  "moderate_triple", "appendix", APPENDIX_TABLE_DIR, "appendix_moderate_share_triple_interaction.pdf"
)

graphics.off()

pwalk(
  report_plan,
  \(family_name, output_group_name, directory, filename) {
    selected_models <- all_models %>%
      filter(
        .data$family == .env$family_name,
        .data$output_group == .env$output_group_name
      )

    message(
      filename,
      ": ",
      n_distinct(selected_models$table_id),
      " table pages"
    )

    render_family_report(
      selected_models,
      file.path(directory, filename)
    )
  }
)
```

```{r 11-moderate-policy-response-distribution-figures}
# -------------------------------------------------------------------------
# Moderate-voter policy-response distributions
# -------------------------------------------------------------------------

required_response_columns <- c(
  "year",
  "axis",
  "item",
  "item_label",
  "voter_ideology",
  "raw_response",
  "score",
  "dont_know",
  "response_category"
)

missing_response_columns <- setdiff(
  required_response_columns,
  names(ideology_item_responses_long)
)

if (length(missing_response_columns) > 0) {
  stop(
    "The ideology-item response dataset is missing required columns: ",
    paste(missing_response_columns, collapse = ", ")
  )
}

item_response_data <- ideology_item_responses_long

if (!"original_response_label" %in% names(item_response_data)) {
  item_response_data <- item_response_data %>%
    mutate(original_response_label = NA_character_)
}

if (!"survey_weight" %in% names(item_response_data)) {
  item_response_data <- item_response_data %>%
    mutate(survey_weight = NA_real_)
}

if (!"survey_weight_validated" %in% names(item_response_data)) {
  item_response_data <- item_response_data %>%
    mutate(survey_weight_validated = FALSE)
}

# Short labels to avoid enormous whitespace.
short_item_labels <- c(
  "a6a" = "SC/ST reservation and social justice",
  "a5" = "Special concessions for Muslims",
  "a4c" = "Ban on religious conversions",
  "a4b" = "Community personal laws",
  "a4d" = "Ban inter-caste marriage",
  "a4g" = "Equal inheritance for sons and daughters",
  "q26a" = "Poverty: individual vs government responsibility",
  "a6b" = "Special schemes for poor and disadvantaged",
  "q27" = "Limit private land and property ownership",
  "q10b" = "Reservation and social justice",
  "q10e" = "Minority concessions",
  "q23c" = "Government versus individual responsibility"
)

item_order_lookup <- item_response_data %>%
  distinct(year, axis, item, item_label) %>%
  group_by(year) %>%
  mutate(item_order = row_number()) %>%
  ungroup() %>%
  mutate(
    item_label_short = dplyr::coalesce(
      short_item_labels[item],
      item_label
    ),
    item_label_short = str_wrap(item_label_short, width = 38)
  )

prepare_item_response_data <- function(data) {
  data %>%
    left_join(
      item_order_lookup,
      by = c("year", "axis", "item", "item_label"),
      relationship = "many-to-one"
    ) %>%
    mutate(
      response_display = case_when(
        dont_know %in% TRUE ~ "Don't know / no opinion",
        !is.na(response_category) & response_category != "" ~ as.character(response_category),
        !is.na(original_response_label) & original_response_label != "" ~ as.character(original_response_label),
        !is.na(score) ~ paste0("Score ", format(score, trim = TRUE)),
        TRUE ~ "Other / unmapped"
      )
    )
}

response_palette <- c(
  "Strongly negative-coded" = "#2166AC",
  "Negative-coded" = "#67A9CF",
  "Other / unmapped" = "#B2ABD2",
  "Positive-coded" = "#EF8A62",
  "Strongly positive-coded" = "#B2182B",
  "Don't know / no opinion" = "#8C8C8C"
)

response_plot_data <- item_response_data %>%
  filter(voter_ideology == "C") %>%
  prepare_item_response_data() %>%
  summarise(
    n = n(),
    .by = c(
      year,
      axis,
      item,
      item_order,
      item_label_short,
      response_display
    )
  ) %>%
  mutate(
    share = n / sum(n),
    .by = c(year, axis, item)
  )

moderate_response_plot <- ggplot(
  response_plot_data,
  aes(
    x = share,
    y = forcats::fct_reorder(
      item_label_short,
      item_order,
      .fun = min,
      .desc = TRUE
    ),
    fill = response_display
  )
) +
  geom_col(width = 0.78) +
  facet_grid(
    axis ~ year,
    scales = "free_y",
    space = "free_y"
  ) +
  scale_x_continuous(
    labels = scales::percent_format(accuracy = 1),
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0.01))
  ) +
  scale_fill_manual(
    values = response_palette,
    breaks = intersect(names(response_palette), unique(response_plot_data$response_display))
  ) +
  labs(
    title = "Policy-response distributions among classified center voters",
    subtitle = "Unweighted; don't-know responses are displayed but excluded from ideology scoring",
    x = "Share of responses",
    y = NULL,
    fill = "Response"
  ) +
  theme_minimal(base_size = 10) +
  theme(
    legend.position = "bottom",
    legend.box = "vertical",
    legend.title = element_text(face = "bold"),
    axis.text.y = element_text(size = 8, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold", size = 10),
    plot.title = element_text(face = "bold", size = 13),
    plot.subtitle = element_text(size = 10)
  ) +
  guides(
    fill = guide_legend(
      nrow = 2,
      byrow = TRUE
    )
  )

ggsave(
  filename = file.path(
    FIGURE_DIR,
    "moderate_policy_response_distribution_unweighted.png"
  ),
  plot = moderate_response_plot,
  width = 11.5,
  height = 8.5,
  dpi = 300
)

write_csv(
  response_plot_data,
  file.path(
    RESULT_DIR,
    "moderate_policy_response_distribution_unweighted.csv"
  )
)
```

```{r 12-first-difference-diagnostic-figure}
first_difference_plot_data <- ac_first_difference %>%
  select(
    delta_fr_vote_share,
    delta_fdi_total,
    delta_fdi_mfg,
    delta_fdi_svc,
    delta_log_migration,
    delta_migration_share
  ) %>%
  pivot_longer(
    everything(),
    names_to = "variable",
    values_to = "value"
  ) %>%
  mutate(
    variable = recode(
      variable,
      "delta_fr_vote_share" = "Change in far-right vote percentage",
      "delta_fdi_total" = "Change in total FDI per 100,000",
      "delta_fdi_mfg" = "Change in manufacturing FDI per 100,000",
      "delta_fdi_svc" = "Change in services FDI per 100,000",
      "delta_log_migration" = "Change in logged migrant total",
      "delta_migration_share" = "Change in migrant share"
    )
  )

first_difference_diagnostic_plot <- ggplot(
  first_difference_plot_data,
  aes(x = value)
) +
  geom_histogram(bins = 35) +
  facet_wrap(~ variable, scales = "free", ncol = 2) +
  labs(
    title = "First-difference variable distributions",
    x = NULL,
    y = "Assembly constituencies"
  ) +
  theme_minimal(base_size = 9)

ggsave(
  file.path(FIGURE_DIR, "first_difference_diagnostics.png"),
  first_difference_diagnostic_plot,
  width = 12,
  height = 10,
  dpi = 300
)
```

```{r 13-main-primary-secondary-summary-figure}
extract_summary_target <- function(row) {
  model <- row$model[[1]]
  if (is.null(model)) return(tibble())
  terms <- names(coef(model))

  target <- if (row$family == "first_difference") {
    row$fd_product_var
  } else if (row$family == "moderate_triple") {
    candidates <- terms[
      map_lgl(
        terms,
        \(term) all(
          c(row$fdi_var, row$migration_var, "moderate_share_10pp_c") %in%
            str_split(term, ":", simplify = FALSE)[[1]]
        )
      )
    ]
    if (length(candidates) == 0) NA_character_ else candidates[1]
  } else {
    candidates <- terms[
      map_lgl(
        terms,
        \(term) {
          pieces <- str_split(term, ":", simplify = FALSE)[[1]]
          all(c(row$fdi_var, row$migration_var) %in% pieces) &&
            length(pieces) == 2
        }
      )
    ]
    if (length(candidates) == 0) NA_character_ else candidates[1]
  }

  tidy_fixest(model) %>%
    filter(term == target) %>%
    transmute(
      family = row$family,
      family_label = row$family_label,
      spec_id = row$spec_id,
      spec_label = row$spec_label,
      estimate,
      std.error,
      conf.low = estimate - 1.96 * std.error,
      conf.high = estimate + 1.96 * std.error
    )
}

main_primary_secondary_rows <- all_models %>%
  filter(
    output_group == "main",
    model_fit,
    (
      family == "first_difference" &
        variant == "first_difference_state_fe"
    ) |
      (
        family != "first_difference" &
          variant == "state_fe"
      )
  )

main_primary_secondary_effects <- map_dfr(
  seq_len(nrow(main_primary_secondary_rows)),
  \(i) extract_summary_target(main_primary_secondary_rows[i, ])
)

main_effect_summary_plot <- ggplot(
  main_primary_secondary_effects,
  aes(x = spec_label, y = estimate)
) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    width = 0.15
  ) +
  geom_point() +
  coord_flip() +
  facet_wrap(~ family_label, scales = "free_x", ncol = 1) +
  labs(
    title = "Primary and secondary interaction estimates across model families",
    subtitle = "Scales differ across OLS, first-difference, logit, and grouped-binomial models; compare signs and uncertainty within panels",
    y = "Interaction coefficient with 95% confidence interval",
    x = NULL
  ) +
  theme_minimal(base_size = 9)

ggsave(
  file.path(FIGURE_DIR, "main_primary_secondary_effect_summary.png"),
  main_effect_summary_plot,
  width = 11,
  height = 12,
  dpi = 300
)

write_csv(
  main_primary_secondary_effects,
  file.path(RESULT_DIR, "main_primary_secondary_effect_summary.csv")
)
```

```{r 14-output-manifest-and-final-checks}
expected_report_files <- report_plan %>%
  transmute(path = file.path(directory, filename)) %>%
  pull(path)

fixed_outputs <- c(
  expected_report_files,
  file.path(FIGURE_DIR, "moderate_policy_response_distribution_unweighted.png"),
  file.path(FIGURE_DIR, "first_difference_diagnostics.png"),
  file.path(FIGURE_DIR, "main_primary_secondary_effect_summary.png"),
  file.path(RESULT_DIR, "analysis_sample_summary.csv"),
  file.path(RESULT_DIR, "centering_validation.csv"),
  file.path(RESULT_DIR, "model_fit_summary.csv"),
  file.path(RESULT_DIR, "model_failure_log.csv"),
  file.path(RESULT_DIR, "all_coefficient_results.csv"),
  file.path(RESULT_DIR, "model_index.csv"),
  file.path(RESULT_DIR, "ideology_heterogeneity_tests.csv"),
  file.path(RESULT_DIR, "marginal_effect_results.csv"),
  file.path(RESULT_DIR, "main_primary_secondary_effect_summary.csv"),
  file.path(MODEL_DIR, "all_model_objects.rds")
)

output_manifest <- tibble(
  path = fixed_outputs,
  exists = file.exists(path),
  bytes = if_else(exists, file.info(path)$size, NA_real_)
)

write_csv(
  output_manifest,
  file.path(OUTPUT_DIR, "output_manifest.csv")
)

regression_count_check <- all_models %>%
  summarise(
    total_requested = n(),
    main_text_requested = sum(output_group == "main"),
    appendix_requested = sum(output_group == "appendix"),
    fitted = sum(model_fit),
    failed = sum(!model_fit)
  )

if (
  regression_count_check$total_requested != 132 ||
    regression_count_check$main_text_requested != 44 ||
    regression_count_check$appendix_requested != 88
) {
  stop(
    "The final regression grid must contain 132 fits: 44 main-text and 88 appendix."
  )
}

regression_count_check
output_manifest
```
