---
title: "Switchers-India"
output: 
  html_document: 
    keep_md: true
date: "2026-03-24"
---
This is the replication code for "Switchers." In this paper, we test hypotheses regarding the rise of far-right parties that were developed from the case of the West in India. We are particularly interested in how the combination of economic insecurity and demographic change affects moderates' voting behavior, and we test this using data on globalization (Foreign Direct Investment) and (internal) migration. The first X chunks in this code go step-by-step through the process of loading and cleaning the data that we use in our regressions, including creating relevant variables.

```{r Load libraries, message = FALSE}
library(tidyverse)
library(sf)
library(foreign)
library(xtable)
library(haven)
library(janitor)
library(broom)
library(marginaleffects)
```

```{r Load data, message = FALSE}

# Assembly constituency election returns
ac_elections <- read_csv("data/lok_dhaba_ae.csv")

# Survey data for 2009/2014 elections

# Foreign direct investment data
fdi <- read_csv("data/IN_FDI_2004_2014.csv")

# District-wise migration data

# District-wise employment data

# District-wise SC/ST data

# District-wise household data

# Polling station data





```



```{r Create helper functions for loading data, message = FALSE}
# Build a helper function for cleaning PC names for use as labels
clean_constituency_name <- function(x) {
  x %>%
    as.character() %>%
    str_replace_all("\u00A0", " ") %>%          # replace non-breaking spaces
    str_to_upper() %>%                          # standardize case
    str_remove_all("\\s*\\((SC|ST)\\)\\s*") %>% # remove (SC) or (ST)
    str_replace_all("[^A-Z0-9]+", " ") %>%      # standardize punctuation/spaces
    str_squish()                                # collapse repeated spaces
}

# Build a helper function to avoid carrying over missing constituency names
first_nonmissing <- function(x) {
  x <- x[!is.na(x) & x != ""]
  if (length(x) == 0) NA_character_ else x[1]
}
```

```{r Load and clean 2009 AC voting data, message = FALSE}
# Load Jensenius et al.'s voting data for 2009
fileshere <- list.files("data/jensenius_et_al/PSdata_2009",
                        pattern = ".csv",
                        recursive = TRUE,
                        full.names = TRUE
                        )

# Merge state voting data into a single file 
for (h in 1:length(fileshere)) {
  onefile <- read.csv(fileshere[h])
  
  if (h == 1) {
    PSdata_2009 <- onefile
  } else {
    PSdata_2009 <- rbind(PSdata_2009, onefile)
  }
}

# Group voting data to the AC level
ACdata_2009 <- PSdata_2009 %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    PC_no = as.integer(PC_no),
    AC_no = as.integer(AC_no),
    PC_name = clean_constituency_name(PC_name),
    AC_name = clean_constituency_name(AC_name)
  ) %>% 
  group_by(State_no2011, AC_no) %>% 
  summarise(
    PC_no_09 = first_nonmissing(PC_no),
    PC_name_09 = first_nonmissing(PC_name),
    AC_name_09 = first_nonmissing(AC_name),
    across(starts_with("Votes_"), ~ sum(.x, na.rm = TRUE)),
    .groups = "drop"
  ) %>% 
  rename_with(
    ~ paste0(.x, "_09"),
    starts_with("Votes_")
  )
```

```{r Load and clean 2009 AC merge data, message = FALSE}
# Load 2009 merge files
fileshere <- list.files("data/jensenius_et_al/Mergefiles_2009", 
                        pattern = ".csv", 
                        recursive = TRUE, 
                        full.names = TRUE)

# Merge 2009 merge files into a single file
for (h in 1:length(fileshere)) {
  onefile <- read.csv(fileshere[h])
  
  if (h == 1) {
    merge_2009 <- onefile
    } else {
      merge_2009 <- rbind(merge_2009, onefile)	
    }
}

# Group voting data to the AC level and calculate the number of voters
ACmerge_2009 <- merge_2009 %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    AC_no = as.integer(AC_no),
    District_name2011 = clean_constituency_name(District_name2011),
    AC_name = clean_constituency_name(AC_name)
  ) %>% 
  group_by(State_no2011, AC_no) %>% 
  summarise(
    Electors_09 = sum(Electors, na.rm = TRUE),
    District_no2011_09 = first_nonmissing(District_no2011),
    District_name2011_09 = first_nonmissing(District_name2011),
    AC_name_09 = first_nonmissing(AC_name),
    .groups = "drop"
  )
```

```{r Merge 2009 voting and merge files}
elec_09 <- ACdata_2009 %>% 
  left_join(
    ACmerge_2009,
    by = c("State_no2011", "AC_no"),
    relationship = "one-to-one"
  )
```

```{r Load and clean 2014 AC voting data, message = FALSE}
# Load Jensenius et al.'s voting data for 2014
fileshere <- list.files("data/jensenius_et_al/PSdata_2014",
                        pattern = ".csv",
                        recursive = TRUE,
                        full.names = TRUE
                        )

# Merge state voting data into a single file 
for (h in 1:length(fileshere)) {
  onefile <- read.csv(fileshere[h])
  
  if (h == 1) {
    PSdata_2014 <- onefile
  } else {
    PSdata_2014 <- rbind(PSdata_2014, onefile)
  }
}

# Group voting data to the AC level
ACdata_2014 <- PSdata_2014 %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    PC_no = as.integer(PC_no),
    AC_no = as.integer(AC_no),
    PC_name = clean_constituency_name(PC_name),
    AC_name = clean_constituency_name(AC_name)
  ) %>% 
  group_by(State_no2011, AC_no) %>% 
  summarise(
    PC_no_14 = first_nonmissing(PC_no),
    PC_name_14 = first_nonmissing(PC_name),
    AC_name_14 = first_nonmissing(AC_name),
    across(starts_with("Votes_"), ~ sum(.x, na.rm = TRUE)),
    .groups = "drop"
  ) %>% 
  rename_with(
    ~ paste0(.x, "_14"),
    starts_with("Votes_")
  )
```

```{r Load and clean 2014 AC merge data, message = FALSE}
# Load 2014 merge files
fileshere <- list.files("data/jensenius_et_al/Mergefiles_2014", 
                        pattern = ".csv", 
                        recursive = TRUE, 
                        full.names = TRUE)

# Merge 2014 merge files into a single file
for (h in 1:length(fileshere)) {
  onefile <- read.csv(fileshere[h])
  
  if (h == 1) {
    merge_2014 <- onefile
    } else {
      merge_2014 <- rbind(merge_2014, onefile)	
    }
}

# Group voting data to the AC level and calculate the number of voters
ACmerge_2014 <- merge_2014 %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    AC_no = as.integer(AC_no),
    District_name2011 = clean_constituency_name(District_name2011),
    AC_name = clean_constituency_name(AC_name)
  ) %>% 
  group_by(State_no2011, AC_no) %>% 
  summarise(
    Electors_14 = sum(Electors, na.rm = TRUE),
    District_no2011_14 = first_nonmissing(District_no2011),
    District_name2011_14 = first_nonmissing(District_name2011),
    AC_name_14 = first_nonmissing(AC_name),
    .groups = "drop"
  )
```

```{r Merge 2014 voting and merge files}
elec_14 <- ACdata_2014 %>% 
  left_join(
    ACmerge_2014,
    by = c("State_no2011", "AC_no"),
    relationship = "one-to-one"
  )
```

```{r Merge 2009 and 2014 election files}
elec <- elec_09 %>% 
  left_join(elec_14, by = c("State_no2011", "AC_no"))
```

```{r Load candidate data and clean state IDs, message = FALSE}
# Load candidate information files
cand_noUP_09 <- read_csv("data/jensenius_et_al/Candidates_2009/candidate_order2009_noUP.csv")
cand_UP_09   <- read_csv("data/jensenius_et_al/Candidates_2009/candidate_order2009_UP.csv")
cand_14      <- read_csv("data/jensenius_et_al/Candidates_2014/candidate_order2014.csv")

# Assign state codes to states in the data
state_codes <- function(df) {
  df %>%
    mutate(
      State_no2011 = case_when(
        State_name == "Andhra Pradesh" ~ 28,
        State_name == "Bihar" ~ 10,
        State_name == "Gujarat" ~ 24,
        State_name == "Himachal Pradesh" ~ 2,
        State_name == "Jharkhand" ~ 20,
        State_name == "Madhya Pradesh" ~ 23,
        State_name == "Punjab" ~ 3,
        State_name == "Rajasthan" ~ 8,
        State_name == "Uttar Pradesh" ~ 9,
        State_name == "Uttarakhand" ~ 5,
        State_name == "West Bengal" ~ 19,
        TRUE ~ NA_integer_
      )
    )
}
```

```{r Create a far-right candidate lookup}
fr_parties <- c("BJP", "SHS")

fr_lookup <- function(cand_df, year, party_col = "Cand_party") {
  cand_df %>% 
    state_codes() %>% 
    mutate(
      Cand_no = as.integer(Cand_no)
    ) %>% 
    filter(.data[[party_col]] %in% fr_parties) %>% 
    group_by(State_no2011, PC_id) %>% 
    summarise(
      fr_cand = as.integer(n() > 0),
      fr_cand_nos = list(sort(unique(Cand_no[!is.na(Cand_no)]))),
      .groups = "drop"
    ) %>% 
    rename(
      !!paste0("fr_cand_", year) := fr_cand,
      !!paste0("fr_cand_nos_", year) := fr_cand_nos
    )
}
```

```{r Extract far-right candidate IDs}
fr_cands_09 <- bind_rows(cand_noUP_09, cand_UP_09) %>% 
  fr_lookup(year = "09", party_col = "Cand_party")

fr_cands_14 <- cand_14 %>% 
  fr_lookup(year = "14", party_col = "Cand_party")
```

```{r Define vote summation}
sum_candidate_votes <- function(df, cand_list_col, vote_suffix) {
  
  cand_lists <- df[[cand_list_col]]
  out <- rep(NA_real_, nrow(df))
  
  for (i in seq_len(nrow(df))) {
    
    cand_nos <- cand_lists[[i]]
    
    if (is.null(cand_nos) || length(cand_nos) == 0 || all(is.na(cand_nos))) {
      out[i] <- 0
      next
    }
    
    vote_cols <- paste0("Votes_cand", cand_nos, vote_suffix)
    vote_cols <- vote_cols[vote_cols %in% names(df)]
    
    if (length(vote_cols) == 0) {
      out[i] <- NA_real_
      next
    }
    
    vals <- unlist(df[i, vote_cols], use.names = FALSE)
    out[i] <- sum(vals, na.rm = TRUE)
  }
  
  out
}
```

```{r Join candidate files with election data}
elec_cand <- elec %>%
  left_join(
    fr_cands_09,
    by = c("State_no2011", "PC_no_09" = "PC_id"),
    relationship = "many-to-one"
  ) %>%
  left_join(
    fr_cands_14,
    by = c("State_no2011", "PC_no_14" = "PC_id"),
    relationship = "many-to-one"
  ) %>%
  mutate(
    fr_cands_09 = coalesce(fr_cand_09, 0L),
    fr_cands_14 = coalesce(fr_cand_14, 0L)
  )

elec_cand$fr_votes_09 <- sum_candidate_votes(
  elec_cand,
  cand_list_col = "fr_cand_nos_09",
  vote_suffix = "_09"
)

elec_cand$fr_votes_14 <- sum_candidate_votes(
  elec_cand,
  cand_list_col = "fr_cand_nos_14",
  vote_suffix = "_14"
)

elec_cand <- elec_cand %>%
  mutate(
    fr_vote_share_09 = if_else(
      !is.na(Votes_total_09) & Votes_total_09 > 0,
      fr_votes_09 / Votes_total_09,
      NA_real_
    ),
    
    fr_vote_share_14 = if_else(
      !is.na(Votes_total_14) & Votes_total_14 > 0,
      fr_votes_14 / Votes_total_14,
      NA_real_
    ),
    
    fr_vote_share_change = if_else(
      is.finite(fr_vote_share_09) & is.finite(fr_vote_share_14),
      fr_vote_share_14 - fr_vote_share_09,
      NA_real_
    )
  )
```

```{r Establish Lokniti state recoding}
nes_state_recode <- function(x) {
  case_when(
    x == 1 ~ 28,   # AP
    x == 4 ~ 10,   # BH
    x == 6 ~ 24,   # GJ
    x == 8 ~ 2,    # HP
    x == 33 ~ 20,  # JH
    x == 12 ~ 23,  # MP
    x == 19 ~ 3,   # PJ
    x == 20 ~ 8,   # RJ
    x == 24 ~ 9,   # UP
    x == 25 ~ 19,  # WB
    x == 35 ~ 5,   # UK
    TRUE ~ NA_integer_
  )
}
```

```{r Add a helper for safe Lokniti z-score computation}
safe_z <- function(x) {
  x <- as.numeric(x)
  m <- mean(x, na.rm = TRUE)
  s <- sd(x, na.rm = TRUE)
  
  if (is.na(s) || s == 0) {
    return(rep(NA_real_, length(x)))
  }
  
  (x - m) / s
}
```

```{r Clean 2009 Lokniti data, message = FALSE}
nes_2009 <- read_sav("data/lokniti/nes_2009.sav") %>% 
  mutate(State_no2011 = nes_state_recode(as.numeric(st_id))) %>% 
  filter(!is.na(State_no2011)) %>% 
  mutate(
    q26a = case_match(q26a, 1 ~ 2, 2 ~ 1, 8 ~ 0, 3 ~ -1, 4 ~ -2),
    q27 = case_match(q27, 2 ~ 1, c(7, 8) ~ 0, 1 ~ -1),
    a4b = case_match(a4b, 4 ~ 2, 3 ~ 1, 8 ~ 0, 2 ~ -1, 1 ~ -2),
    a4c = case_match(a4c, 1 ~ 2, 2 ~ 1, 8 ~ 0, 3 ~ -1, 4 ~ -2),
    a4d = case_match(a4d, 1 ~ 2, 2 ~ 1, 8 ~ 0, 3 ~ -1, 4 ~ -2),
    a4g = case_match(a4g, 4 ~ 2, 3 ~ 1, 8 ~ 0, 2 ~ -1, 1 ~ -2),
    a5 = case_match(a5, 2 ~ 1, 8 ~ 0, 1 ~ -1),
    a6a = case_match(a6a, 2 ~ 1, 8 ~ 0, 1 ~ -1),
    a6b = case_match(a6b, 2 ~ 1, 8 ~ 0, 1 ~ -1),
    
    z_q26a = safe_z(q26a),
    z_q27  = safe_z(q27),
    z_a4b  = safe_z(a4b),
    z_a4c  = safe_z(a4c),
    z_a4d  = safe_z(a4d),
    z_a4g  = safe_z(a4g),
    z_a5   = safe_z(a5),
    z_a6a  = safe_z(a6a),
    z_a6b  = safe_z(a6b)
  )

bjp_codes <- c(2, 46, 91)

vote_share <- function(vote, condition, codes = bjp_codes) {
  x <- vote[condition & !is.na(condition)]
  
  if (length(x) == 0) {
    return(NA_real_)
  }
  
  mean(if_else(is.na(x), NA, x %in% codes), na.rm = TRUE)
}

nes_2009_scored <- nes_2009 %>%
  mutate(
    recognition_score = rowMeans(
      pick(z_a6a, z_a5, z_a4c, z_a4b),
      na.rm = TRUE
    ),
    statism_score = rowMeans(
      pick(z_a4d, z_a4g, z_q26a, z_a6b, z_q27),
      na.rm = TRUE
    ),
    recognition_score = if_else(is.nan(recognition_score), NA_real_, recognition_score),
    statism_score = if_else(is.nan(statism_score), NA_real_, statism_score)
  )

group_nes_2009 <- nes_2009_scored %>% 
  group_by(State_no2011, ac_id) %>% 
  summarise(
    loc_bjp_vote_share_2009 = vote_share(q1a, TRUE),
    loc_bjp_close_to_2009 = vote_share(q11a, TRUE),
    loc_bjp_never_vote_2009 = vote_share(q12a, TRUE),
    
    recognition_score_2009 = mean(recognition_score, na.rm = TRUE),
    statism_score_2009 = mean(statism_score, na.rm = TRUE),
    
    mean_econ_trend_2009 = mean(e2, na.rm = TRUE),
    mean_educ_2009 = mean(z5, na.rm = TRUE),
    
    loc_up_caste_share_2009 = sum(z7a == 4 & z8 %in% c(1, 4, 6), na.rm = TRUE) / 
      sum(!is.na(z7a) & !is.na(z8)),
    
    loc_h_obc_share_2009 = sum(z7a == 3 & z8 == 1, na.rm = TRUE) / 
      sum(!is.na(z7a) & !is.na(z8)),
    
    mean_hhi_2009 = mean(z18, na.rm = TRUE),
    
    loc_bjp_mod_vote_share_2009 = vote_share(
      q1a,
      recognition_score > -0.25 & recognition_score < 0.25 &
        statism_score > -0.25 & statism_score < 0.25
    ),
    
    loc_bjp_right_vote_share_2009 = vote_share(
      q1a,
      recognition_score > 0.25 &
        statism_score > 0.25
    ),
    
    loc_bjp_left_vote_share_2009 = vote_share(
      q1a,
      recognition_score < -0.25 &
        statism_score < -0.25
    ),
    
    .groups = "drop"
  ) %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    ac_id = as.integer(ac_id)
  )
```

```{r Clean 2014 Lokniti data, message = FALSE}
nes_2014 <- read_sav("data/lokniti/nes_2014.sav") %>% 
  mutate(State_no2011 = nes_state_recode(as.numeric(state_id))) %>% 
  filter(!is.na(State_no2011)) %>% 
  mutate(
    q10b = case_match(q10b, 1 ~ 2, 2 ~ 1, 8 ~ 0, 3 ~ -1, 4 ~ -2),
    z_q10b = (q10b - mean(q10b)) / sd(q10b),
    
    q10e = case_match(q10e, 4 ~ 2, 3 ~ 1, 8 ~ 0, 2 ~ -1, 1 ~ -2),
    z_q10e = (q10e - mean(q10e)) / sd(q10e),
    
    q23c = case_match(q23c, 4 ~ 2, 3 ~ 1, 8 ~ 0, 2 ~ -1, 1 ~ -2), # this should have been 23d...
    z_q23c = (q23c - mean(q23c)) / sd(q23c)
  )

nes_2014_scored <- nes_2014 %>%
  mutate(
    recognition_score = rowMeans(
      pick(z_q10b, z_q10e),
      na.rm = TRUE
    ),
    statism_score = q23c,
    
    recognition_score = if_else(is.nan(recognition_score), NA_real_, recognition_score),
    statism_score = if_else(is.nan(statism_score), NA_real_, statism_score)
  )

group_nes_2014 <- nes_2014_scored %>% 
  group_by(State_no2011, ac_id) %>% 
  summarise(
    loc_bjp_vote_share_2014 = vote_share(q1a, TRUE),
    loc_bjp_close_to_2014 = vote_share(q11a, TRUE),
    
    recognition_score_2014 = mean(recognition_score, na.rm = TRUE),
    statism_score_2014 = mean(statism_score, na.rm = TRUE),
    
    mean_educ_2014 = mean(z3, na.rm = TRUE),
    
    loc_up_caste_share_2014 = sum(z5a == 4 & z6 %in% c(1, 4, 6), na.rm = TRUE) / 
      sum(!is.na(z5a) & !is.na(z6)),
    
    loc_h_obc_share_2014 = sum(z5a == 3 & z6 == 1, na.rm = TRUE) / 
      sum(!is.na(z5a) & !is.na(z6)),
    
    mean_hhi_2014 = mean(z13, na.rm = TRUE),
    
    loc_bjp_mod_vote_share_2014 = vote_share(
      q1a,
      recognition_score > -0.25 & recognition_score < 0.25 &
        statism_score > -0.25 & statism_score < 0.25
    ),
    
    loc_bjp_right_vote_share_2014 = vote_share(
      q1a,
      recognition_score > 0.25 &
        statism_score > 0.25
    ),
    
    loc_bjp_left_vote_share_2014 = vote_share(
      q1a,
      recognition_score < -0.25 &
        statism_score < -0.25
    ),
    
    .groups = "drop"
  ) %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    ac_id = as.integer(ac_id)
  )
```

```{r Join 2009 and 2014 Lokniti data to main data file}
nes_2009_vars <- group_nes_2009 %>%
  select(-State_no2011, -ac_id) %>%
  names()

nes_2014_vars <- group_nes_2014 %>%
  select(-State_no2011, -ac_id) %>%
  names()

# Remove unnecessary columns
elec_cand_nes <- elec_cand %>% 
  left_join(
    group_nes_2009,
    by = c("State_no2011", "AC_no" = "ac_id")
  ) %>% 
  left_join(
    group_nes_2014,
    by = c("State_no2011", "AC_no" = "ac_id")
  ) %>%
  select(
    any_of(c(
      "State_no2011",
      "AC_no",
      "PC_no_09",
      "PC_name_09",
      "AC_name_09.x",
      "Votes_total_09",
      "Electors_09",
      "District_no2011_09",
      "District_name2011_09",
      "PC_no_14",
      "PC_name_14",
      "AC_name_14.x",
      "Votes_total_14",
      "Electors_14",
      "District_no2011_14",
      "District_name2011_14",
      "fr_cands_09",
      "fr_cands_14",
      "fr_votes_09",
      "fr_votes_14",
      "fr_vote_share_09",
      "fr_vote_share_14",
      "fr_vote_share_change"
    )),
    all_of(nes_2009_vars),
    all_of(nes_2014_vars)
  ) %>%
  mutate(
    District_no2011_09 = as.integer(District_no2011_09),
    District_no2011_14 = as.integer(District_no2011_14),
    District_no2011 = coalesce(District_no2011_14, District_no2011_09)
  ) %>% 
  select(
    -any_of(c(
      "District_no2011_09",
      "District_no2011_14",
      "District_name2011_09"
    ))
  )
```

```{r Merge in EC 2013 and PC 2011 data}
# Create an object to save 
ec13_cols <- c(
  "ec13_emp_all", "ec13_emp_f", "ec13_emp_m", "ec13_emp_gov",
  "ec13_emp_priv", "ec13_emp_own_m", "ec13_emp_own_f",
  "ec13_emp_st", "ec13_emp_sc", "ec13_emp_obc"
)

# Create within-district weights based on each AC's share of the district's total electors
district_elector_weights <- elec_cand_nes %>%
  mutate(
    State_no2011 = as.integer(State_no2011),
    District_no2011 = as.integer(District_no2011),
    AC_no = as.integer(AC_no),
    Electors_14 = as.numeric(Electors_14)
  ) %>%
  distinct(State_no2011, District_no2011, AC_no, Electors_14) %>%
  filter(
    !is.na(State_no2011),
    !is.na(District_no2011),
    !is.na(AC_no)
  ) %>%
  group_by(State_no2011, District_no2011) %>%
  mutate(
    district_electors_14 = sum(Electors_14, na.rm = TRUE),
    elector_weight_14 = if_else(
      !is.na(Electors_14) & district_electors_14 > 0,
      Electors_14 / district_electors_14,
      NA_real_
    )
  ) %>%
  ungroup() %>%
  select(
    State_no2011,
    District_no2011,
    AC_no,
    Electors_14,
    district_electors_14,
    elector_weight_14
  )

shrug_ec13 <- read_csv(
  "data/shrug/ec13_pc11dist.csv",
  show_col_types = FALSE
) %>% 
  mutate(
    pc11_state_id = str_remove(pc11_state_id, "^0+") %>% as.integer(),
    pc11_district_id = str_remove(pc11_district_id, "^0+") %>% as.integer()
  ) %>% 
  select(
    pc11_state_id,
    pc11_district_id,
    all_of(ec13_cols)
  )

elec_cand_nes_ec <- elec_cand_nes %>% 
  mutate(
    State_no2011 = as.integer(State_no2011),
    District_no2011 = as.integer(District_no2011),
    AC_no = as.integer(AC_no),
    Electors_14 = as.numeric(Electors_14)
  ) %>%
  left_join(
    shrug_ec13,
    by = c(
      "State_no2011" = "pc11_state_id",
      "District_no2011" = "pc11_district_id"
    ),
    relationship = "many-to-one"
  ) %>%
  group_by(State_no2011, District_no2011) %>%
  mutate(
    n_acs_in_district = n_distinct(AC_no),
    district_electors_14 = sum(Electors_14, na.rm = TRUE),
    
    elector_weight_14 = case_when(
      !is.na(Electors_14) & district_electors_14 > 0 ~
        Electors_14 / district_electors_14,
      
      district_electors_14 == 0 & n_acs_in_district > 0 ~
        1 / n_acs_in_district,
      
      TRUE ~ NA_real_
    )
  ) %>%
  ungroup() %>%
  mutate(
    across(
      all_of(ec13_cols),
      ~ .x * elector_weight_14,
      .names = "{.col}_ac_alloc"
    )
  )
```

```{r Merge in migration data and impute missing values}
migra <- list.files(
  path = "data/migration",
  pattern = "_2001_2011_merged\\.csv$",
  full.names = TRUE
)

migra_cols <- c(
  "2011_Total_Persons_<1",
  "2011_Total_Persons_1-4",
  "2011_Total_Persons_5-9"
)

dist_migra <- migra %>% 
  set_names() %>% 
  map_dfr(\(f) {
    read_csv(f, show_col_types = FALSE) %>%
      select(
        State,
        `2011_District`,
        Last_Residence,
        all_of(migra_cols)
      ) %>%
      mutate(
        State = as.integer(State),
        `2011_District` = as.integer(`2011_District`)
      ) %>%
      filter(
        Last_Residence == "STATES IN INDIA BEYOND THE STATE OF ENUMERATION",
        !is.na(`2011_District`),
        `2011_District` != 0
      ) %>%
      group_by(State, `2011_District`) %>%
      summarise(
        across(all_of(migra_cols), ~ sum(.x, na.rm = TRUE)),
        .groups = "drop"
      )
  }) %>%
  group_by(State, `2011_District`) %>%  
  summarise(
    across(all_of(migra_cols), ~ sum(.x, na.rm = TRUE)),
    .groups = "drop"
  )

elec_cand_nes_ec_m <- elec_cand_nes_ec %>%
  mutate(
    State_no2011 = as.integer(State_no2011),
    District_no2011 = as.integer(District_no2011),
    AC_no = as.integer(AC_no),
    Electors_09 = as.numeric(Electors_09)
  ) %>%
  left_join(
    dist_migra,
    by = c(
      "State_no2011" = "State",
      "District_no2011" = "2011_District"
    ),
    relationship = "many-to-one"
  ) %>%
  replace_na(as.list(setNames(rep(0, length(migra_cols)), migra_cols))) %>%
  group_by(State_no2011, District_no2011) %>%
  mutate(
    n_acs_in_district = n_distinct(AC_no),
    district_electors_09 = sum(Electors_09, na.rm = TRUE),
    
    elector_weight_09 = case_when(
      !is.na(Electors_09) & district_electors_09 > 0 ~
        Electors_09 / district_electors_09,
      
      district_electors_09 == 0 & n_acs_in_district > 0 ~
        1 / n_acs_in_district,
      
      TRUE ~ NA_real_
    )
  ) %>%
  ungroup() %>%
  mutate(
    across(
      all_of(migra_cols),
      ~ .x * elector_weight_09,
      .names = "alloc_{.col}"
    ),
    
    across(
      starts_with("alloc_2011_Total_Persons"),
      ~ log1p(.x),
      .names = "log_{.col}"
    )
  )

# Calculate the change in average change in migration between 2009 and 2014
elec_cand_nes_ec_m <- elec_cand_nes_ec_m %>%
  mutate(
    agr_2009 = if_else(
      `alloc_2011_Total_Persons_5-9` > 0,
      (`alloc_2011_Total_Persons_1-4` / 4) /
        (`alloc_2011_Total_Persons_5-9` / 5),
      NA_real_
    ),
    
    agr_2014 = if_else(
      `alloc_2011_Total_Persons_1-4` > 0,
      `alloc_2011_Total_Persons_<1` /
        (`alloc_2011_Total_Persons_1-4` / 4),
      NA_real_
    ),
    
    log_agr_2009 = if_else(agr_2009 > 0, log(agr_2009), NA_real_),
    log_agr_2014 = if_else(agr_2014 > 0, log(agr_2014), NA_real_)
  )
```

```{r Read in assembly shape files and assign them to ACs}

# Data come from Susewind 2014
fileshere <- list.files("data/mapping-indias-elections",
                        pattern = ".assembly.shp",
                        recursive = TRUE,
                        full.names = TRUE
                        )

for (h in 1:length(fileshere)) {
  onefile <- read_sf(fileshere[h])
  
  if (h == 1) {
    ac_map <- onefile
  } else {
    ac_map <- rbind(ac_map, onefile)
  }
}

ac_map <- ac_map %>% 
  mutate(
      State_no2011 = case_when(
        state == "Andhra Pradesh" ~ 28,
        state == "Bihar" ~ 10,
        state == "Gujarat" ~ 24,
        state == "Himachal Pradesh" ~ 2,
        state == "Jharkhand" ~ 20,
        state == "Madhya Pradesh" ~ 23,
        state == "Punjab" ~ 3,
        state == "Rajasthan" ~ 8,
        state == "Uttar Pradesh" ~ 9,
        state == "Uttarakhand" ~ 5,
        state == "West Bengal" ~ 19,
        TRUE ~ NA_integer_
      )
  ) %>% 
  select(State_no2011, ac, ac_name, geometry)
```

```{r Read in FDI data and match sites to ACs}
fdi_raw <- read_csv("data/IN_FDI_2004_2014.csv")

fdi_coords <- fdi_raw %>%
  extract(
    col = Coordinates,
    into = c("lat", "lon"),
    regex = "^\\s*(-?\\d+(?:\\.\\d+)?)\\s*,\\s*(-?\\d+(?:\\.\\d+)?)\\s*$",
    remove = FALSE,
    convert = TRUE
  ) %>%
  mutate(
    has_coord = !is.na(lat) & !is.na(lon)
  )

fdi_points <- fdi_coords %>%
  filter(has_coord) %>%
  st_as_sf(
    coords = c("lon", "lat"),
    crs = 4326,
    remove = FALSE
  )

ac_clean <- ac_map %>%
  st_make_valid() %>%
  select(State_no2011, ac, geometry)

fdi_points <- st_transform(fdi_points, st_crs(ac_clean))

fdi_points_joined <- fdi_points %>%
  st_join(ac_clean, join = st_within, left = TRUE)

fdi_ac_lookup <- fdi_points_joined %>%
  st_drop_geometry() %>%
  select(`#`, State_no2011, ac)

fdi_final <- fdi_coords %>%
  left_join(fdi_ac_lookup, by = "#")
```

```{r Assign periods to FDI}
fdi_final <- fdi_final %>% 
  mutate(
    project_month = as.Date(parse_date_time(
      `Project date`,
      orders = c("b Y", "B Y")
    )),
    period = case_when(
      project_month >= as.Date("2004-04-01") &
        project_month <= as.Date("2009-04-01") ~ "1",
      
      project_month >= as.Date("2009-05-01") &
        project_month <= as.Date("2014-05-01") ~ "2",
      
      TRUE ~ NA_character_
    )
  )
```

```{r Pivot a dataframe with investment qualities included}
fdi_ac <- fdi_final %>%
  filter(!is.na(State_no2011), !is.na(ac)) %>%
  clean_names() %>%
  mutate(
    period_clean = make_clean_names(as.character(period), allow_dupes = TRUE),
    activity_clean = make_clean_names(activity, allow_dupes = TRUE)
  )

fdi_ac_totals <- fdi_ac %>%
  filter(!is.na(period_clean)) %>%
  group_by(state_no2011, ac, period_clean) %>%
  summarise(
    n = n(),
    capital = sum(capital_investment, na.rm = TRUE),
    jobs = sum(jobs_created, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_wider(
    id_cols = c(state_no2011, ac),
    names_from = period_clean,
    values_from = c(n, capital, jobs),
    names_glue = "fdi_{period_clean}_total_{.value}",
    values_fill = 0
  )

fdi_ac_by_activity <- fdi_ac %>%
  filter(
    !is.na(period_clean),
    !is.na(activity_clean)
  ) %>%
  group_by(state_no2011, ac, period_clean, activity_clean) %>%
  summarise(
    n = n(),
    capital = sum(capital_investment, na.rm = TRUE),
    jobs = sum(jobs_created, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_wider(
    id_cols = c(state_no2011, ac),
    names_from = c(period_clean, activity_clean),
    values_from = c(n, capital, jobs),
    names_glue = "fdi_{period_clean}_{activity_clean}_{.value}",
    values_fill = 0
  )

fdi_ac_summary <- fdi_ac_totals %>%
  full_join(
    fdi_ac_by_activity,
    by = c("state_no2011", "ac")
  ) %>%
  mutate(
    across(
      starts_with("fdi_"),
      ~ replace_na(.x, 0)
    )
  )

```

```{r Join FDI to AC}
fdi_ac_map <- ac_map %>% 
  left_join(fdi_ac_summary, by = c("State_no2011" = "state_no2011", "ac")) %>% 
  mutate(
    across(
      starts_with("fdi_"),
      ~ tidyr::replace_na(.x, 0)
    ),
    fdi_diff = fdi_x2_total_n - fdi_x1_total_n
  )

elec_cand_nes_ec_m_fdi <- fdi_ac_map %>% 
  left_join(elec_cand_nes_ec_m, by = c("State_no2011" = "State_no2011", "ac" = "AC_no"))
```

https://kclpure.kcl.ac.uk/portal/en/publications/gis-shapefiles-for-indias-parliamentary-and-assembly-constituenci/
https://pub.uni-bielefeld.de/download/2674065/2674106/README.txt
Begin restructured, still mostly AI section
```{r setup, message=FALSE, warning=FALSE}
# ============================================================
# SETUP
# ============================================================

library(dplyr)
library(tidyr)
library(purrr)
library(stringr)
library(broom)
library(sf)
library(readr)
library(ggplot2)
library(marginaleffects)

dir.create("outputs", recursive = TRUE, showWarnings = FALSE)
dir.create("outputs/tables", recursive = TRUE, showWarnings = FALSE)
dir.create("outputs/figures", recursive = TRUE, showWarnings = FALSE)

# Assumes this object already exists from your earlier data construction:
# elec_cand_nes_ec_m_fdi

reg_data <- elec_cand_nes_ec_m_fdi %>%
  { if (inherits(., "sf")) sf::st_drop_geometry(.) else . } %>%
  mutate(
    agr_diff_09_14 = agr_2014 - agr_2009,
    log_agr_diff_09_14 = log_agr_2014 - log_agr_2009,
    fdi_total_n_diff = fdi_x2_total_n - fdi_x1_total_n,
    fdi_manufacturing_n_diff = fdi_x2_manufacturing_n - fdi_x1_manufacturing_n
  )
```

```{r define-focused-fdi, message=FALSE, warning=FALSE}
# ============================================================
# DEFINE FOCUSED FDI, MIGRATION, CONTROLS, AND DVs
# ============================================================

# -----------------------------
# Focused FDI variables only
# -----------------------------

fdi_change_vars <- c(
  "fdi_total_n_diff",
  "fdi_manufacturing_n_diff"
) %>%
  intersect(names(reg_data))

fdi_x1_vars <- c(
  "fdi_x1_total_n",
  "fdi_x1_manufacturing_n"
) %>%
  intersect(names(reg_data))

fdi_x2_vars <- c(
  "fdi_x2_total_n",
  "fdi_x2_manufacturing_n"
) %>%
  intersect(names(reg_data))

# -----------------------------
# Migration variables
# -----------------------------

# migration_change_vars <- c(
#   "alloc_2011_Total_Persons_<1",
#   "alloc_2011_Total_Persons_1-4",                     
#   "alloc_2011_Total_Persons_5-9", 
#   "log_alloc_2011_Total_Persons_<1", 
#   "log_alloc_2011_Total_Persons_1-4", 
#   "log_alloc_2011_Total_Persons_5-9",
#   "log_agr_2009",
#   "agr_2009",
#   "log_agr_2014",
#   "agr_2014"
# ) %>%
#   intersect(names(reg_data))

migration_2009_vars <- c(
  "agr_2009",
  "log_agr_2009",
  "alloc_2011_Total_Persons_1-4",
  "log_alloc_2011_Total_Persons_1-4"
) %>%
  intersect(names(reg_data))

migration_2014_vars <- c(
  "agr_2014",
  "log_agr_2014",
  "alloc_2011_Total_Persons_<1",
  "log_alloc_2011_Total_Persons_<1",
  "agr_diff_09_14",
  "log_agr_diff_09_14"
) %>%
  intersect(names(reg_data))

# -----------------------------
# Controls
# -----------------------------

# control_vars <- c(
#   "ec13_emp_all_ac_alloc",
#   "ec13_emp_f_ac_alloc",
#   "ec13_emp_m_ac_alloc",
#   "ec13_emp_gov_ac_alloc",
#   "ec13_emp_priv_ac_alloc",
#   "ec13_emp_own_m_ac_alloc",
#   "ec13_emp_own_f_ac_alloc",
#   "ec13_emp_st_ac_alloc",
#   "ec13_emp_sc_ac_alloc",
#   "ec13_emp_obc_ac_alloc"
# ) %>%
#   intersect(names(reg_data))

control_sets <- list(
  no_controls = character(0),
  employment_total = c("ec13_emp_all_ac_alloc"),
  employment_disaggregated = c(
    "ec13_emp_f_ac_alloc",
    "ec13_emp_m_ac_alloc",
    "ec13_emp_gov_ac_alloc",
    "ec13_emp_priv_ac_alloc",
    "ec13_emp_own_m_ac_alloc",
    "ec13_emp_own_f_ac_alloc",
    "ec13_emp_st_ac_alloc",
    "ec13_emp_sc_ac_alloc",
    "ec13_emp_obc_ac_alloc"
  )
)

# control_sets <- map(control_sets, ~ intersect(.x, names(reg_data)))
# 
# single_control_sets <- control_vars %>%
#   set_names(paste0("single_", .)) %>%
#   map(~ .x)

control_sets <- c(control_sets, single_control_sets)

# -----------------------------
# AC-share dependent variables
# -----------------------------

dv_specs_raw <- tibble::tribble(
  ~election_year, ~ideology_group, ~dv,
  2009, "moderate", "loc_bjp_mod_vote_share_2009",
  2009, "right",    "loc_bjp_right_vote_share_2009",
  2009, "left",     "loc_bjp_left_vote_share_2009",
  2014, "moderate", "loc_bjp_mod_vote_share_2014",
  2014, "right",    "loc_bjp_right_vote_share_2014",
  2014, "left",     "loc_bjp_left_vote_share_2014"
)

missing_dvs <- dv_specs_raw %>%
  filter(!dv %in% names(reg_data))

if (nrow(missing_dvs) > 0) {
  print(missing_dvs)
  stop("Some AC-share dependent variables are missing from reg_data.")
}

dv_specs <- dv_specs_raw

# -----------------------------
# Sanity checks
# -----------------------------

focused_variable_check <- list(
  fdi_change_vars = fdi_change_vars,
  fdi_x1_vars = fdi_x1_vars,
  fdi_x2_vars = fdi_x2_vars,
#  migration_change_vars = migration_change_vars,
  migration_2009_vars = migration_2009_vars,
  migration_2014_vars = migration_2014_vars,
  control_sets = names(control_sets)
)

focused_variable_check
```

```{r helper-functions, message=FALSE, warning=FALSE}
# ============================================================
# HELPER FUNCTIONS
# ============================================================

safe_name <- function(x) {
  x %>%
    as.character() %>%
    str_replace_all("[^A-Za-z0-9]+", "_") %>%
    str_replace_all("_+", "_") %>%
    str_replace_all("^_|_$", "") %>%
    str_to_lower()
}

write_tables_by_group <- function(df, group_vars, out_dir, prefix) {
  
  dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)
  
  if (nrow(df) == 0) {
    empty_index <- tibble(
      file_name = character(0),
      file_path = character(0)
    )
    
    readr::write_csv(
      empty_index,
      file.path(out_dir, paste0(prefix, "__index.csv"))
    )
    
    return(list(index = empty_index, tables = list()))
  }
  
  nested <- df %>%
    group_by(across(all_of(group_vars))) %>%
    group_nest(.key = "table") %>%
    ungroup()
  
  make_file_name <- function(row_id) {
    row <- nested[row_id, ]
    
    group_label <- group_vars %>%
      map_chr(~ paste0(safe_name(.x), "-", safe_name(row[[.x]][[1]]))) %>%
      paste(collapse = "__")
    
    paste0(prefix, "__", group_label, ".csv")
  }
  
  nested <- nested %>%
    mutate(
      file_name = map_chr(row_number(), make_file_name),
      file_path = file.path(out_dir, file_name)
    )
  
  walk2(nested$table, nested$file_path, readr::write_csv)
  
  readr::write_csv(
    nested %>% select(-table),
    file.path(out_dir, paste0(prefix, "__index.csv"))
  )
  
  table_list <- nested$table
  names(table_list) <- str_remove(nested$file_name, "\\.csv$")
  
  list(
    index = nested %>% select(-table),
    tables = table_list
  )
}

tidy_lm_interaction <- function(data, dv, migration_var, fdi_var, controls,
                                min_obs_base = 10) {
  
  controls <- controls[!is.na(controls) & controls != ""]
  vars_needed <- unique(c(dv, migration_var, fdi_var, controls))
  missing_vars <- setdiff(vars_needed, names(data))
  
  if (length(missing_vars) > 0) {
    return(tibble(
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      n_obs = NA_integer_,
      r_squared = NA_real_,
      adj_r_squared = NA_real_,
      error = paste("Missing variables:", paste(missing_vars, collapse = ", "))
    ))
  }
  
  model_data <- tibble(
    y = data[[dv]],
    migration = data[[migration_var]],
    fdi = data[[fdi_var]]
  )
  
  if (length(controls) > 0) {
    controls_df <- as_tibble(data[controls])
    names(controls_df) <- paste0("control_", seq_along(controls))
    model_data <- bind_cols(model_data, controls_df)
  }
  
  model_data <- model_data %>%
    filter(
      if_all(everything(), ~ !is.na(.x)),
      if_all(where(is.numeric), ~ is.finite(.x))
    )
  
  min_obs_needed <- max(min_obs_base, length(controls) + 4)
  
  if (nrow(model_data) < min_obs_needed) {
    return(tibble(
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      n_obs = nrow(model_data),
      r_squared = NA_real_,
      adj_r_squared = NA_real_,
      error = "Too few complete observations"
    ))
  }
  
  rhs_terms <- c(
    "migration * fdi",
    if (length(controls) > 0) paste0("control_", seq_along(controls)) else character(0)
  )
  
  fml <- reformulate(rhs_terms, response = "y")
  
  model <- tryCatch(
    lm(fml, data = model_data),
    error = function(e) e
  )
  
  if (inherits(model, "error")) {
    return(tibble(
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      n_obs = nrow(model_data),
      r_squared = NA_real_,
      adj_r_squared = NA_real_,
      error = model$message
    ))
  }
  
  base_lookup <- tibble(
    term = c("(Intercept)", "migration", "fdi", "migration:fdi"),
    term_original = c(
      "(Intercept)",
      migration_var,
      fdi_var,
      paste0(migration_var, ":", fdi_var)
    )
  )
  
  control_lookup <- if (length(controls) > 0) {
    tibble(
      term = paste0("control_", seq_along(controls)),
      term_original = controls
    )
  } else {
    tibble(term = character(0), term_original = character(0))
  }
  
  term_lookup <- bind_rows(base_lookup, control_lookup)
  
  broom::tidy(model) %>%
    left_join(term_lookup, by = "term") %>%
    mutate(
      term_original = coalesce(term_original, term),
      n_obs = nobs(model),
      r_squared = summary(model)$r.squared,
      adj_r_squared = summary(model)$adj.r.squared,
      error = NA_character_
    )
}

tidy_lm_additive <- function(data, dv, migration_var, fdi_var, controls,
                             min_obs_base = 10) {
  
  controls <- controls[!is.na(controls) & controls != ""]
  vars_needed <- unique(c(dv, migration_var, fdi_var, controls))
  missing_vars <- setdiff(vars_needed, names(data))
  
  if (length(missing_vars) > 0) {
    return(tibble(
      model_type = "additive",
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      n_obs = NA_integer_,
      r_squared = NA_real_,
      adj_r_squared = NA_real_,
      error = paste("Missing variables:", paste(missing_vars, collapse = ", "))
    ))
  }
  
  model_data <- tibble(
    y = data[[dv]],
    migration = data[[migration_var]],
    fdi = data[[fdi_var]]
  )
  
  if (length(controls) > 0) {
    controls_df <- as_tibble(data[controls])
    names(controls_df) <- paste0("control_", seq_along(controls))
    model_data <- bind_cols(model_data, controls_df)
  }
  
  model_data <- model_data %>%
    filter(
      if_all(everything(), ~ !is.na(.x)),
      if_all(where(is.numeric), ~ is.finite(.x))
    )
  
  min_obs_needed <- max(min_obs_base, length(controls) + 3)
  
  if (nrow(model_data) < min_obs_needed) {
    return(tibble(
      model_type = "additive",
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      n_obs = nrow(model_data),
      r_squared = NA_real_,
      adj_r_squared = NA_real_,
      error = "Too few complete observations"
    ))
  }
  
  rhs_terms <- c(
    "migration",
    "fdi",
    if (length(controls) > 0) paste0("control_", seq_along(controls)) else character(0)
  )
  
  fml <- reformulate(rhs_terms, response = "y")
  
  model <- tryCatch(
    lm(fml, data = model_data),
    error = function(e) e
  )
  
  if (inherits(model, "error")) {
    return(tibble(
      model_type = "additive",
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      n_obs = nrow(model_data),
      r_squared = NA_real_,
      adj_r_squared = NA_real_,
      error = model$message
    ))
  }
  
  base_lookup <- tibble(
  term = c("(Intercept)", "migration", "fdi"),
  term_original = c("(Intercept)", migration_var, fdi_var)
)

control_lookup <- if (length(controls) > 0) {
  tibble(
    term = paste0("control_", seq_along(controls)),
    term_original = controls
  )
} else {
  tibble(
    term = character(0),
    term_original = character(0)
  )
}

term_lookup <- bind_rows(base_lookup, control_lookup)
  
  broom::tidy(model) %>%
    left_join(term_lookup, by = "term") %>%
    mutate(
      model_type = "additive",
      term_original = coalesce(term_original, term),
      n_obs = nobs(model),
      r_squared = summary(model)$r.squared,
      adj_r_squared = summary(model)$adj.r.squared,
      error = NA_character_
    )
}

make_terms_table <- function(results_df, include_model_type = FALSE) {
  
  out <- results_df %>%
    filter(term %in% c("migration", "fdi", "migration:fdi")) %>%
    mutate(
      component = case_when(
        term == "migration" ~ "migration_main_effect",
        term == "fdi" ~ "fdi_main_effect",
        term == "migration:fdi" ~ "interaction",
        TRUE ~ term
      ),
      stars = case_when(
        p.value < 0.01 ~ "***",
        p.value < 0.05 ~ "**",
        p.value < 0.10 ~ "*",
        TRUE ~ ""
      )
    )
  
  out
}
```

```{r time-series-models, message=FALSE, warning=FALSE}
# ============================================================
# TIME-SERIES / CHANGE MODELS
# Outcome: change in far-right vote share
# ============================================================

time_series_dv <- "fr_vote_share_change"

time_series_grid <- expand_grid(
  dv = time_series_dv,
  migration_var = migration_2014_vars,
  fdi_var = fdi_change_vars,
  control_set = names(control_sets)
) %>%
  mutate(
    controls = map(control_set, ~ control_sets[[.x]])
  )

time_series_grid %>% count(fdi_var)
time_series_grid %>% count(migration_var)
time_series_grid %>% count(control_set)

time_series_results <- time_series_grid %>%
  mutate(
    results = pmap(
      list(dv, migration_var, fdi_var, controls, control_set),
      ~ tidy_lm_interaction(
          data = reg_data,
          dv = ..1,
          migration_var = ..2,
          fdi_var = ..3,
          controls = ..4
        ) %>%
        mutate(
          model_family = "time_series_change",
          dv = ..1,
          migration_var = ..2,
          fdi_var = ..3,
          control_set = ..5
        )
    )
  ) %>%
  select(results) %>%
  unnest(results)

time_series_terms <- make_terms_table(time_series_results) %>%
  transmute(
    model_family,
    dv,
    migration_var,
    fdi_var,
    control_set,
    component,
    term_original,
    coefficient = estimate,
    se = std.error,
    t_stat = statistic,
    p_value = p.value,
    stars,
    n_obs,
    r_squared,
    adj_r_squared,
    error
  ) %>%
  arrange(dv, migration_var, fdi_var, control_set, component)

time_series_interactions <- time_series_terms %>%
  filter(component == "interaction") %>%
  arrange(p_value)

# Optional additive models without interaction
time_series_additive_results <- time_series_grid %>%
  mutate(
    results = pmap(
      list(dv, migration_var, fdi_var, controls, control_set),
      ~ tidy_lm_additive(
          data = reg_data,
          dv = ..1,
          migration_var = ..2,
          fdi_var = ..3,
          controls = ..4
        ) %>%
        mutate(
          model_family = "time_series_change",
          dv = ..1,
          migration_var = ..2,
          fdi_var = ..3,
          control_set = ..5
        )
    )
  ) %>%
  select(results) %>%
  unnest(results)

time_series_additive_terms <- time_series_additive_results %>%
  filter(term %in% c("migration", "fdi")) %>%
  mutate(
    component = case_when(
      term == "migration" ~ "migration_additive_effect",
      term == "fdi" ~ "fdi_additive_effect"
    ),
    stars = case_when(
      p.value < 0.01 ~ "***",
      p.value < 0.05 ~ "**",
      p.value < 0.10 ~ "*",
      TRUE ~ ""
    )
  ) %>%
  transmute(
    model_family,
    dv,
    migration_var,
    fdi_var,
    control_set,
    component,
    term_original,
    coefficient = estimate,
    se = std.error,
    t_stat = statistic,
    p_value = p.value,
    stars,
    n_obs,
    r_squared,
    adj_r_squared,
    error
  )
```

```{r voter-logit-models, message=FALSE, warning=FALSE}
# ============================================================
# VOTER-LEVEL LOGIT MODELS
# Outcome: individual voter voted far right
# ============================================================

# -----------------------------
# Assembly-level treatment data for voter-level merge
# -----------------------------

ac_treatments <- reg_data %>%
  mutate(
    State_no2011 = as.integer(State_no2011),
    ac = as.integer(ac)
  ) %>%
  select(
    State_no2011,
    ac,
    any_of(c(
      fdi_x1_vars,
      fdi_x2_vars,
      migration_2009_vars,
      migration_2014_vars,
      control_vars
    ))
  ) %>%
  distinct(State_no2011, ac, .keep_all = TRUE)

bjp_codes <- c(2, 46, 91)

nes_2009_voter <- nes_2009 %>%
  mutate(
    State_no2011 = as.integer(State_no2011),
    ac = as.integer(ac_id),
    election_year = 2009,
    voted_fr = case_when(
      is.na(q1a) ~ NA_real_,
      q1a %in% bjp_codes ~ 1,
      TRUE ~ 0
    ),
    recognition_score = rowMeans(
      pick(z_a6a, z_a5, z_a4c, z_a4b),
      na.rm = TRUE
    ),
    statism_score = rowMeans(
      pick(z_a4d, z_a4g, z_q26a, z_a6b, z_q27),
      na.rm = TRUE
    ),
    recognition_score = if_else(is.nan(recognition_score), NA_real_, recognition_score),
    statism_score = if_else(is.nan(statism_score), NA_real_, statism_score),
    ideology_group = case_when(
      recognition_score > -0.25 & recognition_score < 0.25 &
        statism_score > -0.25 & statism_score < 0.25 ~ "moderate",
      recognition_score > 0.25 &
        statism_score > 0.25 ~ "right",
      recognition_score < -0.25 &
        statism_score < -0.25 ~ "left",
      TRUE ~ NA_character_
    )
  ) %>%
  left_join(ac_treatments, by = c("State_no2011", "ac"))

nes_2014_voter <- nes_2014 %>%
  mutate(
    State_no2011 = as.integer(State_no2011),
    ac = as.integer(ac_id),
    election_year = 2014,
    voted_fr = case_when(
      is.na(q1a) ~ NA_real_,
      q1a %in% bjp_codes ~ 1,
      TRUE ~ 0
    ),
    recognition_score = rowMeans(
      pick(z_q10b, z_q10e),
      na.rm = TRUE
    ),
    statism_score = q23c,
    recognition_score = if_else(is.nan(recognition_score), NA_real_, recognition_score),
    statism_score = if_else(is.nan(statism_score), NA_real_, statism_score),
    ideology_group = case_when(
      recognition_score > -0.25 & recognition_score < 0.25 &
        statism_score > -0.25 & statism_score < 0.25 ~ "moderate",
      recognition_score > 0.25 &
        statism_score > 0.25 ~ "right",
      recognition_score < -0.25 &
        statism_score < -0.25 ~ "left",
      TRUE ~ NA_character_
    )
  ) %>%
  left_join(ac_treatments, by = c("State_no2011", "ac"))

voter_reg_data <- bind_rows(nes_2009_voter, nes_2014_voter) %>%
  filter(
    !is.na(voted_fr),
    !is.na(ideology_group),
    !is.na(State_no2011),
    !is.na(ac)
  ) %>%
  mutate(
    across(starts_with("fdi_"), ~ replace_na(.x, 0))
  )

voter_group_counts <- voter_reg_data %>%
  group_by(election_year, ideology_group) %>%
  summarise(
    n = n(),
    n_far_right = sum(voted_fr == 1, na.rm = TRUE),
    n_not_far_right = sum(voted_fr == 0, na.rm = TRUE),
    far_right_share = mean(voted_fr == 1, na.rm = TRUE),
    .groups = "drop"
  )

voter_merge_diagnostics <- voter_reg_data %>%
  summarise(
    n_voters = n(),
    n_missing_fdi_x1_total_n = sum(is.na(fdi_x1_total_n)),
    n_missing_fdi_x2_total_n = sum(is.na(fdi_x2_total_n)),
    n_missing_agr_2009 = sum(is.na(agr_2009)),
    n_missing_agr_2014 = sum(is.na(agr_2014))
  )

voter_fdi_x1_vars <- intersect(fdi_x1_vars, names(voter_reg_data))
voter_fdi_x2_vars <- intersect(fdi_x2_vars, names(voter_reg_data))
voter_migration_2009_vars <- intersect(migration_2009_vars, names(voter_reg_data))
voter_migration_2014_vars <- intersect(migration_2014_vars, names(voter_reg_data))
voter_control_sets <- map(control_sets, ~ intersect(.x, names(voter_reg_data)))

voter_model_grid_2009 <- expand_grid(
  election_year = 2009,
  ideology_group = c("left", "moderate", "right"),
  migration_var = voter_migration_2009_vars,
  fdi_var = voter_fdi_x1_vars,
  control_set = names(voter_control_sets)
) %>%
  mutate(
    controls = map(control_set, ~ voter_control_sets[[.x]])
  )

voter_model_grid_2014 <- expand_grid(
  election_year = 2014,
  ideology_group = c("left", "moderate", "right"),
  migration_var = voter_migration_2014_vars,
  fdi_var = voter_fdi_x2_vars,
  control_set = names(voter_control_sets)
) %>%
  mutate(
    controls = map(control_set, ~ voter_control_sets[[.x]])
  )

voter_model_grid <- bind_rows(
  voter_model_grid_2009,
  voter_model_grid_2014
)

voter_model_grid %>% count(election_year, fdi_var)

run_voter_logit <- function(data, election_year, ideology_group,
                            migration_var, fdi_var, controls, control_set_name) {
  
  controls <- controls[!is.na(controls) & controls != ""]
  
  vars_needed <- unique(c("voted_fr", migration_var, fdi_var, controls))
  missing_vars <- setdiff(vars_needed, names(data))
  
  if (length(missing_vars) > 0) {
    return(tibble(
      election_year = election_year,
      ideology_group = ideology_group,
      migration_var = migration_var,
      fdi_var = fdi_var,
      control_set = control_set_name,
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      odds_ratio = NA_real_,
      n_obs = NA_integer_,
      n_far_right = NA_integer_,
      n_not_far_right = NA_integer_,
      min_fitted = NA_real_,
      max_fitted = NA_real_,
      warning = NA_character_,
      error = paste("Missing variables:", paste(missing_vars, collapse = ", "))
    ))
  }
  
  filtered_data <- data %>%
    filter(
      election_year == !!election_year,
      ideology_group == !!ideology_group
    )
  
  model_data <- tibble(
    y = filtered_data[["voted_fr"]],
    migration = filtered_data[[migration_var]],
    fdi = filtered_data[[fdi_var]]
  )
  
  if (length(controls) > 0) {
    controls_df <- filtered_data[, controls, drop = FALSE] %>%
      as_tibble()
    names(controls_df) <- paste0("control_", seq_along(controls))
    model_data <- bind_cols(model_data, controls_df)
  }
  
  model_data <- model_data %>%
    filter(
      if_all(everything(), ~ !is.na(.x)),
      if_all(where(is.numeric), ~ is.finite(.x))
    )
  
  min_obs_needed <- max(30, length(controls) + 5)
  
  if (nrow(model_data) < min_obs_needed) {
    return(tibble(
      election_year = election_year,
      ideology_group = ideology_group,
      migration_var = migration_var,
      fdi_var = fdi_var,
      control_set = control_set_name,
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      odds_ratio = NA_real_,
      n_obs = nrow(model_data),
      n_far_right = sum(model_data$y == 1, na.rm = TRUE),
      n_not_far_right = sum(model_data$y == 0, na.rm = TRUE),
      min_fitted = NA_real_,
      max_fitted = NA_real_,
      warning = NA_character_,
      error = "Too few complete observations"
    ))
  }
  
  if (length(unique(model_data$y)) < 2) {
    return(tibble(
      election_year = election_year,
      ideology_group = ideology_group,
      migration_var = migration_var,
      fdi_var = fdi_var,
      control_set = control_set_name,
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      odds_ratio = NA_real_,
      n_obs = nrow(model_data),
      n_far_right = sum(model_data$y == 1, na.rm = TRUE),
      n_not_far_right = sum(model_data$y == 0, na.rm = TRUE),
      min_fitted = NA_real_,
      max_fitted = NA_real_,
      warning = NA_character_,
      error = "Outcome has no variation"
    ))
  }
  
  rhs_terms <- c(
    "migration * fdi",
    if (length(controls) > 0) paste0("control_", seq_along(controls)) else character(0)
  )
  
  fml <- reformulate(rhs_terms, response = "y")
  model_warnings <- character(0)
  
  model <- tryCatch(
    withCallingHandlers(
      glm(fml, data = model_data, family = binomial(link = "logit")),
      warning = function(w) {
        model_warnings <<- c(model_warnings, conditionMessage(w))
        invokeRestart("muffleWarning")
      }
    ),
    error = function(e) e
  )
  
  if (inherits(model, "error")) {
    return(tibble(
      election_year = election_year,
      ideology_group = ideology_group,
      migration_var = migration_var,
      fdi_var = fdi_var,
      control_set = control_set_name,
      term = NA_character_,
      term_original = NA_character_,
      estimate = NA_real_,
      std.error = NA_real_,
      statistic = NA_real_,
      p.value = NA_real_,
      odds_ratio = NA_real_,
      n_obs = nrow(model_data),
      n_far_right = sum(model_data$y == 1, na.rm = TRUE),
      n_not_far_right = sum(model_data$y == 0, na.rm = TRUE),
      min_fitted = NA_real_,
      max_fitted = NA_real_,
      warning = if_else(
        length(model_warnings) > 0,
        paste(unique(model_warnings), collapse = "; "),
        NA_character_
      ),
      error = model$message
    ))
  }
  
  base_lookup <- tibble(
    term = c("(Intercept)", "migration", "fdi", "migration:fdi"),
    term_original = c(
      "(Intercept)",
      migration_var,
      fdi_var,
      paste0(migration_var, ":", fdi_var)
    )
  )
  
  control_lookup <- if (length(controls) > 0) {
    tibble(
      term = paste0("control_", seq_along(controls)),
      term_original = controls
    )
  } else {
    tibble(term = character(0), term_original = character(0))
  }
  
  term_lookup <- bind_rows(base_lookup, control_lookup)
  
  broom::tidy(model) %>%
    left_join(term_lookup, by = "term") %>%
    mutate(
      term_original = coalesce(term_original, term),
      election_year = election_year,
      ideology_group = ideology_group,
      migration_var = migration_var,
      fdi_var = fdi_var,
      control_set = control_set_name,
      odds_ratio = exp(estimate),
      n_obs = nobs(model),
      n_far_right = sum(model_data$y == 1, na.rm = TRUE),
      n_not_far_right = sum(model_data$y == 0, na.rm = TRUE),
      min_fitted = min(fitted(model), na.rm = TRUE),
      max_fitted = max(fitted(model), na.rm = TRUE),
      warning = if_else(
        length(model_warnings) > 0,
        paste(unique(model_warnings), collapse = "; "),
        NA_character_
      ),
      error = NA_character_
    )
}

voter_logit_results <- voter_model_grid %>%
  mutate(
    results = pmap(
      list(
        election_year,
        ideology_group,
        migration_var,
        fdi_var,
        controls,
        control_set
      ),
      ~ run_voter_logit(
        data = voter_reg_data,
        election_year = ..1,
        ideology_group = ..2,
        migration_var = ..3,
        fdi_var = ..4,
        controls = ..5,
        control_set_name = ..6
      )
    )
  ) %>%
  select(results) %>%
  unnest(results)

voter_logit_terms <- voter_logit_results %>%
  filter(term %in% c("migration", "fdi", "migration:fdi")) %>%
  mutate(
    dv = "voted_fr",
    component = case_when(
      term == "migration" ~ "migration_main_effect",
      term == "fdi" ~ "fdi_main_effect",
      term == "migration:fdi" ~ "interaction"
    ),
    stars = case_when(
      p.value < 0.01 ~ "***",
      p.value < 0.05 ~ "**",
      p.value < 0.10 ~ "*",
      TRUE ~ ""
    ),
    likely_unstable = if_else(
      !is.na(warning) | abs(estimate) > 10 | std.error > 10,
      TRUE,
      FALSE
    )
  ) %>%
  transmute(
    election_year,
    ideology_group,
    dv,
    migration_var,
    fdi_var,
    control_set,
    component,
    term_original,
    logit_coefficient = estimate,
    odds_ratio,
    se = std.error,
    z_stat = statistic,
    p_value = p.value,
    stars,
    n_obs,
    n_far_right,
    n_not_far_right,
    min_fitted,
    max_fitted,
    likely_unstable,
    warning,
    error
  )

voter_logit_interactions <- voter_logit_terms %>%
  filter(component == "interaction") %>%
  arrange(election_year, migration_var, fdi_var, ideology_group, p_value)

voter_logit_compare <- voter_logit_interactions %>%
  select(
    election_year,
    migration_var,
    fdi_var,
    control_set,
    ideology_group,
    logit_coefficient,
    odds_ratio,
    se,
    p_value,
    n_obs,
    likely_unstable
  ) %>%
  pivot_wider(
    names_from = ideology_group,
    values_from = c(
      logit_coefficient,
      odds_ratio,
      se,
      p_value,
      n_obs,
      likely_unstable
    )
  )

problem_models <- voter_logit_results %>%
  filter(!is.na(warning) | !is.na(error)) %>%
  distinct(
    election_year,
    ideology_group,
    migration_var,
    fdi_var,
    control_set,
    n_obs,
    n_far_right,
    n_not_far_right,
    min_fitted,
    max_fitted,
    warning,
    error
  ) %>%
  arrange(election_year, ideology_group, control_set)
```

```{r ac-share-models, message=FALSE, warning=FALSE}
# ============================================================
# AC-LEVEL IDEOLOGY-SHARE MODELS
# Outcome: share of left/moderate/right voters voting far right
# ============================================================

ac_share_grid_2009 <- expand_grid(
  dv_specs %>% filter(election_year == 2009),
  migration_var = migration_2009_vars,
  fdi_var = fdi_x1_vars,
  control_set = names(control_sets)
) %>%
  mutate(
    controls = map(control_set, ~ control_sets[[.x]])
  )

ac_share_grid_2014 <- expand_grid(
  dv_specs %>% filter(election_year == 2014),
  migration_var = migration_2014_vars,
  fdi_var = fdi_x2_vars,
  control_set = names(control_sets)
) %>%
  mutate(
    controls = map(control_set, ~ control_sets[[.x]])
  )

ac_share_grid <- bind_rows(
  ac_share_grid_2009,
  ac_share_grid_2014
)

ac_share_grid %>% count(election_year, fdi_var)

cross_section_results <- ac_share_grid %>%
  mutate(
    results = pmap(
      list(
        dv,
        migration_var,
        fdi_var,
        controls,
        election_year,
        ideology_group,
        control_set
      ),
      ~ tidy_lm_interaction(
          data = reg_data,
          dv = ..1,
          migration_var = ..2,
          fdi_var = ..3,
          controls = ..4
        ) %>%
        mutate(
          model_family = "ac_share",
          dv = ..1,
          migration_var = ..2,
          fdi_var = ..3,
          election_year = ..5,
          ideology_group = ..6,
          control_set = ..7
        )
    )
  ) %>%
  select(results) %>%
  unnest(results)

cross_section_terms <- make_terms_table(cross_section_results) %>%
  transmute(
    model_family,
    election_year,
    ideology_group,
    dv,
    migration_var,
    fdi_var,
    control_set,
    component,
    term_original,
    coefficient = estimate,
    se = std.error,
    t_stat = statistic,
    p_value = p.value,
    stars,
    n_obs,
    r_squared,
    adj_r_squared,
    error
  ) %>%
  arrange(election_year, ideology_group, dv, migration_var, fdi_var, control_set, component)

cross_section_interactions <- cross_section_terms %>%
  filter(component == "interaction") %>%
  arrange(election_year, ideology_group, p_value)

# Optional additive AC-share models
cross_section_additive_results <- ac_share_grid %>%
  mutate(
    results = pmap(
      list(
        dv,
        migration_var,
        fdi_var,
        controls,
        election_year,
        ideology_group,
        control_set
      ),
      ~ tidy_lm_additive(
          data = reg_data,
          dv = ..1,
          migration_var = ..2,
          fdi_var = ..3,
          controls = ..4
        ) %>%
        mutate(
          model_family = "ac_share",
          dv = ..1,
          migration_var = ..2,
          fdi_var = ..3,
          election_year = ..5,
          ideology_group = ..6,
          control_set = ..7
        )
    )
  ) %>%
  select(results) %>%
  unnest(results)

cross_section_additive_terms <- cross_section_additive_results %>%
  filter(term %in% c("migration", "fdi")) %>%
  mutate(
    component = case_when(
      term == "migration" ~ "migration_additive_effect",
      term == "fdi" ~ "fdi_additive_effect"
    ),
    stars = case_when(
      p.value < 0.01 ~ "***",
      p.value < 0.05 ~ "**",
      p.value < 0.10 ~ "*",
      TRUE ~ ""
    )
  ) %>%
  transmute(
    model_family,
    election_year,
    ideology_group,
    dv,
    migration_var,
    fdi_var,
    control_set,
    component,
    term_original,
    coefficient = estimate,
    se = std.error,
    t_stat = statistic,
    p_value = p.value,
    stars,
    n_obs,
    r_squared,
    adj_r_squared,
    error
  )
```

```{r marginal-effects, message=FALSE, warning=FALSE}
# ============================================================
# MARGINAL EFFECTS FOR AC-SHARE MODELS
# ============================================================

fit_ac_share_model <- function(data, dv, migration_var, fdi_var,
                               controls = character(0)) {
  
  controls <- controls[!is.na(controls) & controls != ""]
  
  vars_needed <- unique(c(dv, migration_var, fdi_var, controls))
  missing_vars <- setdiff(vars_needed, names(data))
  
  if (length(missing_vars) > 0) {
    stop("Missing variables: ", paste(missing_vars, collapse = ", "))
  }
  
  model_data <- tibble(
    y = data[[dv]],
    migration = data[[migration_var]],
    fdi = data[[fdi_var]]
  )
  
  if (length(controls) > 0) {
    controls_df <- as_tibble(data[controls])
    names(controls_df) <- paste0("control_", seq_along(controls))
    model_data <- bind_cols(model_data, controls_df)
  }
  
  model_data <- model_data %>%
    filter(
      if_all(everything(), ~ !is.na(.x)),
      if_all(where(is.numeric), ~ is.finite(.x))
    )
  
  rhs_terms <- c(
    "migration * fdi",
    if (length(controls) > 0) paste0("control_", seq_along(controls)) else character(0)
  )
  
  fml <- reformulate(rhs_terms, response = "y")
  model <- lm(fml, data = model_data)
  
  list(
    model = model,
    model_data = model_data,
    dv = dv,
    migration_var = migration_var,
    fdi_var = fdi_var,
    controls = controls
  )
}

get_marginal_effect_summary <- function(dv, migration_var, fdi_var, control_set,
                                        n_grid = 50) {
  
  fit_obj <- fit_ac_share_model(
    data = reg_data,
    dv = dv,
    migration_var = migration_var,
    fdi_var = fdi_var,
    controls = control_sets[[control_set]]
  )
  
  fdi_grid <- seq(
    quantile(fit_obj$model_data$fdi, 0.05, na.rm = TRUE),
    quantile(fit_obj$model_data$fdi, 0.95, na.rm = TRUE),
    length.out = n_grid
  )
  
  me <- marginaleffects::slopes(
    fit_obj$model,
    variables = "migration",
    newdata = marginaleffects::datagrid(
      fdi = fdi_grid
    )
  ) %>%
    as_tibble() %>%
    mutate(
      fdi_value = fdi,
      me_significant_positive = conf.low > 0,
      me_significant_negative = conf.high < 0,
      me_significant = me_significant_positive | me_significant_negative
    )
  
  me_summary <- me %>%
    summarise(
      min_fdi = min(fdi_value, na.rm = TRUE),
      max_fdi = max(fdi_value, na.rm = TRUE),
      min_marginal_effect = min(estimate, na.rm = TRUE),
      max_marginal_effect = max(estimate, na.rm = TRUE),
      mean_marginal_effect = mean(estimate, na.rm = TRUE),
      n_grid = n(),
      n_sig_positive = sum(me_significant_positive, na.rm = TRUE),
      n_sig_negative = sum(me_significant_negative, na.rm = TRUE),
      n_sig_any = sum(me_significant, na.rm = TRUE),
      share_grid_sig_positive = mean(me_significant_positive, na.rm = TRUE),
      share_grid_sig_negative = mean(me_significant_negative, na.rm = TRUE),
      share_grid_sig_any = mean(me_significant, na.rm = TRUE),
      status = case_when(
        n_sig_positive > 0 & n_sig_negative == 0 ~ "Migration effect significantly positive somewhere",
        n_sig_negative > 0 & n_sig_positive == 0 ~ "Migration effect significantly negative somewhere",
        n_sig_positive > 0 & n_sig_negative > 0 ~ "Migration effect changes sign significantly",
        TRUE ~ "Interaction significant, but marginal migration effect not significant on grid"
      ),
      .groups = "drop"
    )
  
  list(
    marginal_effects = me,
    summary = me_summary
  )
}

# Screen significant interactions, but only within the focused FDI universe
models_for_me <- cross_section_interactions %>%
  filter(
    is.na(error),
    !is.na(p_value),
    p_value < 0.05
  ) %>%
  arrange(p_value)

if (nrow(models_for_me) > 0) {
  
  me_results <- models_for_me %>%
    mutate(
      me_object = pmap(
        list(dv, migration_var, fdi_var, control_set),
        ~ get_marginal_effect_summary(
          dv = ..1,
          migration_var = ..2,
          fdi_var = ..3,
          control_set = ..4
        )
      ),
      me_summary = map(me_object, "summary"),
      me_grid = map(me_object, "marginal_effects")
    )
  
  marginal_effect_status <- me_results %>%
    select(
      election_year,
      ideology_group,
      dv,
      migration_var,
      fdi_var,
      control_set,
      coefficient,
      se,
      p_value,
      stars,
      n_obs,
      r_squared,
      me_summary
    ) %>%
    unnest(me_summary) %>%
    mutate(
      likely_useful_plot = share_grid_sig_any > 0,
      weak_me_result = share_grid_sig_any == 0,
      strong_me_result = share_grid_sig_any >= 0.25
    ) %>%
    arrange(desc(share_grid_sig_any), p_value)
  
  marginal_effect_grid <- me_results %>%
    mutate(
      me_grid = map(
        me_grid,
        ~ .x %>%
          select(-any_of(c("dv", "migration_var", "fdi_var", "control_set")))
      )
    ) %>%
    select(
      election_year,
      ideology_group,
      dv,
      migration_var,
      fdi_var,
      control_set,
      p_value,
      me_grid
    ) %>%
    unnest(me_grid)
  
  models_to_plot_from_screen <- marginal_effect_status %>%
  arrange(election_year, ideology_group, p_value)
  
} else {
  
  me_results <- tibble()
  marginal_effect_status <- tibble()
  marginal_effect_grid <- tibble()
  models_to_plot_from_screen <- tibble()
}

plot_screened_marginal_effect <- function(dv, migration_var, fdi_var, control_set) {
  
  fit_obj <- fit_ac_share_model(
    data = reg_data,
    dv = dv,
    migration_var = migration_var,
    fdi_var = fdi_var,
    controls = control_sets[[control_set]]
  )
  
  fdi_grid <- seq(
    quantile(fit_obj$model_data$fdi, 0.05, na.rm = TRUE),
    quantile(fit_obj$model_data$fdi, 0.95, na.rm = TRUE),
    length.out = 50
  )
  
  marginaleffects::plot_slopes(
    fit_obj$model,
    variables = "migration",
    condition = list(fdi = fdi_grid)
  ) +
    labs(
      title = "Marginal effect of migration across FDI exposure",
      subtitle = paste0(
        "Outcome: ", dv,
        "\nMigration: ", migration_var,
        "\nFDI: ", fdi_var,
        "\nControls: ", control_set
      ),
      x = fdi_var,
      y = paste0("Marginal effect of ", migration_var)
    ) +
    theme_minimal()
}

if (nrow(models_to_plot_from_screen) > 0) {
  
  plot_specs <- models_to_plot_from_screen %>%
    select(dv, migration_var, fdi_var, control_set) %>%
    distinct() %>%
    mutate(
      plot_file = paste0(
  "outputs/figures/marginal_effects_migration_across_fdi/",
  "me_migration__dv-", safe_name(dv),
  "__migration-", safe_name(migration_var),
  "__fdi-", safe_name(fdi_var),
  "__controls-", safe_name(control_set),
  ".png"
)
    )
  
  screened_marginal_effect_plots <- pmap(
    plot_specs %>% select(dv, migration_var, fdi_var, control_set),
    ~ plot_screened_marginal_effect(
      dv = ..1,
      migration_var = ..2,
      fdi_var = ..3,
      control_set = ..4
    )
  )
  
} else {
  
  plot_specs <- tibble()
  screened_marginal_effect_plots <- list()
}
```

```{r write-outputs, message=FALSE, warning=FALSE}
# ============================================================
# WRITE OUTPUTS
# ============================================================

dir.create("outputs/tables/time_series_change", recursive = TRUE, showWarnings = FALSE)
dir.create("outputs/tables/voter_logit_models", recursive = TRUE, showWarnings = FALSE)
dir.create("outputs/tables/ac_share_models", recursive = TRUE, showWarnings = FALSE)
dir.create("outputs/tables/marginal_effect_status", recursive = TRUE, showWarnings = FALSE)
dir.create("outputs/tables/marginal_effect_grid", recursive = TRUE, showWarnings = FALSE)
dir.create("outputs/figures/fdi_exposure", recursive = TRUE, showWarnings = FALSE)
dir.create("outputs/figures/marginal_effects", recursive = TRUE, showWarnings = FALSE)
dir.create(
  "outputs/figures/marginal_effects_migration_across_fdi",
  recursive = TRUE,
  showWarnings = FALSE
)

# -----------------------------
# Master tables
# -----------------------------

write_csv(time_series_terms, "outputs/tables/time_series_terms_all.csv")
write_csv(time_series_interactions, "outputs/tables/time_series_interactions_all.csv")
write_csv(time_series_additive_terms, "outputs/tables/time_series_additive_terms_all.csv")

write_csv(voter_group_counts, "outputs/tables/voter_group_counts.csv")
write_csv(voter_merge_diagnostics, "outputs/tables/voter_merge_diagnostics.csv")
write_csv(voter_logit_terms, "outputs/tables/voter_logit_terms_all.csv")
write_csv(voter_logit_interactions, "outputs/tables/voter_logit_interactions_all.csv")
write_csv(voter_logit_compare, "outputs/tables/voter_logit_compare.csv")
write_csv(problem_models, "outputs/tables/voter_logit_problem_models.csv")

write_csv(cross_section_terms, "outputs/tables/ac_share_terms_all.csv")
write_csv(cross_section_interactions, "outputs/tables/ac_share_interactions_all.csv")
write_csv(cross_section_additive_terms, "outputs/tables/ac_share_additive_terms_all.csv")

if (nrow(marginal_effect_status) > 0) {
  write_csv(marginal_effect_status, "outputs/tables/marginal_effect_status_all.csv")
}

if (nrow(marginal_effect_grid) > 0) {
  write_csv(marginal_effect_grid, "outputs/tables/marginal_effect_grid_all.csv")
}

if (nrow(plot_specs) > 0) {
  write_csv(plot_specs, "outputs/figures/marginal_effects/plot_index.csv")
}

# -----------------------------
# Split tables by interpretable groups
# -----------------------------

time_series_outputs <- write_tables_by_group(
  df = time_series_terms,
  group_vars = c("dv", "migration_var"),
  out_dir = "outputs/tables/time_series_change",
  prefix = "time_series"
)

voter_logit_outputs <- write_tables_by_group(
  df = voter_logit_terms,
  group_vars = c("election_year", "ideology_group", "migration_var"),
  out_dir = "outputs/tables/voter_logit_models",
  prefix = "voter_logit"
)

cross_section_outputs <- write_tables_by_group(
  df = cross_section_terms,
  group_vars = c("dv", "migration_var"),
  out_dir = "outputs/tables/ac_share_models",
  prefix = "ac_share"
)

if (nrow(marginal_effect_status) > 0) {
  marginal_effect_status_outputs <- write_tables_by_group(
    df = marginal_effect_status,
    group_vars = c("dv", "migration_var"),
    out_dir = "outputs/tables/marginal_effect_status",
    prefix = "me_status"
  )
}

if (nrow(marginal_effect_grid) > 0) {
  marginal_effect_grid_outputs <- write_tables_by_group(
    df = marginal_effect_grid,
    group_vars = c("dv", "migration_var"),
    out_dir = "outputs/tables/marginal_effect_grid",
    prefix = "me_grid"
  )
}

# -----------------------------
# FDI exposure distribution plot
# -----------------------------

fdi_exposure_long <- reg_data %>%
  select(
    State_no2011,
    ac,
    fdi_x1_total_n,
    fdi_x2_total_n
  ) %>%
  pivot_longer(
    cols = c(fdi_x1_total_n, fdi_x2_total_n),
    names_to = "period",
    values_to = "total_fdi_n"
  ) %>%
  mutate(
    period = recode(
      period,
      fdi_x1_total_n = "2004-2009",
      fdi_x2_total_n = "2009-2014"
    ),
    total_fdi_n = replace_na(total_fdi_n, 0),
    total_fdi_bin = case_when(
      total_fdi_n == 0 ~ "0",
      total_fdi_n == 1 ~ "1",
      total_fdi_n == 2 ~ "2",
      total_fdi_n == 3 ~ "3",
      total_fdi_n == 4 ~ "4",
      total_fdi_n >= 5 ~ "5+",
      TRUE ~ NA_character_
    ),
    total_fdi_bin = factor(
      total_fdi_bin,
      levels = c("0", "1", "2", "3", "4", "5+")
    )
  )

write_csv(fdi_exposure_long, "outputs/tables/fdi_exposure_long.csv")

fdi_exposure_plot <- ggplot(fdi_exposure_long, aes(x = total_fdi_bin)) +
  geom_bar() +
  facet_wrap(~ period) +
  labs(
    title = "Total FDI exposure across constituency-periods",
    x = "Total FDI projects",
    y = "Number of constituency-periods"
  ) +
  theme_minimal()

ggsave(
  filename = "outputs/figures/fdi_exposure/total_fdi_exposure_binned.png",
  plot = fdi_exposure_plot,
  width = 8,
  height = 5,
  dpi = 300
)

# -----------------------------
# Save screened marginal-effect plots
# -----------------------------

if (length(screened_marginal_effect_plots) > 0) {
  walk2(
    screened_marginal_effect_plots,
    plot_specs$plot_file,
    ~ ggsave(
      filename = .y,
      plot = .x,
      width = 8,
      height = 6,
      dpi = 300
    )
  )
}

# -----------------------------
# Quick final checks
# -----------------------------

list(
  time_series_models = nrow(time_series_grid),
  voter_logit_models = nrow(voter_model_grid),
  ac_share_models = nrow(ac_share_grid),
  marginal_effect_models_screened = nrow(models_for_me),
  marginal_effect_plots_saved = length(screened_marginal_effect_plots)
)
```

```{r}
# ============================================================
# Focused AC-share regressions with employment control:
# ideology-specific BJP/far-right vote share ~ agr * manufacturing FDI + employment
# ============================================================

library(dplyr)
library(tidyr)
library(purrr)
library(stringr)
library(broom)
library(sf)
library(ggplot2)
library(marginaleffects)

# -----------------------------
# 1. Prepare regression data
# -----------------------------

reg_data <- elec_cand_nes_ec_m_fdi %>%
  { if (inherits(., "sf")) sf::st_drop_geometry(.) else . }

# -----------------------------
# 2. Define control
# -----------------------------
# Use the exact variable name in your data.
# In your previous code this is usually "ec13_emp_all_ac_alloc".

control_var <- "ec13_emp_all_ac_alloc"

if (!control_var %in% names(reg_data)) {
  stop(
    "Control variable not found in reg_data. Check exact spelling. Similar variables:\n",
    paste(names(reg_data) %>% stringr::str_subset("ec.*emp.*all"), collapse = "\n")
  )
}

# -----------------------------
# 3. Define the six models
# -----------------------------

ac_share_focused_specs <- tibble::tribble(
  ~election_year, ~ideology_group, ~dv,                              ~migration_var, ~fdi_var,
  2009,           "left",          "loc_bjp_left_vote_share_2009",    "agr_2009",     "fdi_x1_manufacturing_n",
  2009,           "moderate",      "loc_bjp_mod_vote_share_2009",     "agr_2009",     "fdi_x1_manufacturing_n",
  2009,           "right",         "loc_bjp_right_vote_share_2009",   "agr_2009",     "fdi_x1_manufacturing_n",
  2014,           "left",          "loc_bjp_left_vote_share_2014",    "agr_2014",     "fdi_x2_manufacturing_n",
  2014,           "moderate",      "loc_bjp_mod_vote_share_2014",     "agr_2014",     "fdi_x2_manufacturing_n",
  2014,           "right",         "loc_bjp_right_vote_share_2014",   "agr_2014",     "fdi_x2_manufacturing_n"
) %>%
  mutate(control_var = control_var)

# Check that all variables exist
vars_needed <- ac_share_focused_specs %>%
  select(dv, migration_var, fdi_var, control_var) %>%
  unlist(use.names = FALSE) %>%
  unique()

missing_vars <- setdiff(vars_needed, names(reg_data))

if (length(missing_vars) > 0) {
  stop(
    "These required variables are missing from reg_data:\n",
    paste(missing_vars, collapse = "\n")
  )
}

# -----------------------------
# 4. Fit one model with control
# -----------------------------
# Uses temporary names y, migration, fdi, control so formulas are clean.

fit_focused_ac_model <- function(data, election_year, ideology_group,
                                 dv, migration_var, fdi_var, control_var) {
  
  model_data <- tibble(
    y = data[[dv]],
    migration = data[[migration_var]],
    fdi = data[[fdi_var]],
    control = data[[control_var]]
  ) %>%
    filter(
      if_all(everything(), ~ !is.na(.x)),
      if_all(where(is.numeric), ~ is.finite(.x))
    )
  
  model <- lm(y ~ migration * fdi + control, data = model_data)
  
  list(
    model = model,
    model_data = model_data,
    election_year = election_year,
    ideology_group = ideology_group,
    dv = dv,
    migration_var = migration_var,
    fdi_var = fdi_var,
    control_var = control_var
  )
}

focused_models <- ac_share_focused_specs %>%
  mutate(
    fit = pmap(
      list(election_year, ideology_group, dv, migration_var, fdi_var, control_var),
      ~ fit_focused_ac_model(
        data = reg_data,
        election_year = ..1,
        ideology_group = ..2,
        dv = ..3,
        migration_var = ..4,
        fdi_var = ..5,
        control_var = ..6
      )
    )
  )
# -----------------------------
# 4. Regression table: coefficients, p-values, R-squared
# -----------------------------

extract_focused_regression_table <- function(fit_obj) {
  
  term_lookup <- tibble(
    term = c("(Intercept)", "migration", "fdi", "migration:fdi", "control"),
    term_label = c(
      "Intercept",
      fit_obj$migration_var,
      fit_obj$fdi_var,
      paste0(fit_obj$migration_var, " × ", fit_obj$fdi_var),
      fit_obj$control_var
    ),
    component = c(
      "intercept",
      "migration_main_effect",
      "fdi_main_effect",
      "interaction",
      "employment_control"
    )
  )
  
  broom::tidy(fit_obj$model) %>%
    left_join(term_lookup, by = "term") %>%
    mutate(
      election_year = fit_obj$election_year,
      ideology_group = fit_obj$ideology_group,
      dv = fit_obj$dv,
      migration_var = fit_obj$migration_var,
      fdi_var = fit_obj$fdi_var,
      control_var = fit_obj$control_var,
      n_obs = nobs(fit_obj$model),
      r_squared = summary(fit_obj$model)$r.squared,
      adj_r_squared = summary(fit_obj$model)$adj.r.squared,
      stars = case_when(
        p.value < 0.01 ~ "***",
        p.value < 0.05 ~ "**",
        p.value < 0.10 ~ "*",
        TRUE ~ ""
      )
    ) %>%
    transmute(
      election_year,
      ideology_group,
      dv,
      migration_var,
      fdi_var,
      control_var,
      component,
      term_label,
      coefficient = estimate,
      se = std.error,
      t_stat = statistic,
      p_value = p.value,
      stars,
      n_obs,
      r_squared,
      adj_r_squared
    )
}

focused_regression_table <- focused_models %>%
  mutate(table = map(fit, extract_focused_regression_table)) %>%
  select(table) %>%
  unnest(table) %>%
  arrange(election_year, ideology_group, component)

View(focused_regression_table)

# A compact wide version, one row per model
focused_regression_table_wide <- focused_regression_table %>%
  filter(component %in% c(
    "migration_main_effect",
    "fdi_main_effect",
    "interaction",
    "employment_control"
  )) %>%
  select(
    election_year,
    ideology_group,
    dv,
    migration_var,
    fdi_var,
    control_var,
    component,
    coefficient,
    p_value,
    stars,
    n_obs,
    r_squared,
    adj_r_squared
  ) %>%
  pivot_wider(
    names_from = component,
    values_from = c(coefficient, p_value, stars)
  ) %>%
  arrange(election_year, ideology_group)

View(focused_regression_table_wide)

# -----------------------------
# 5. Marginal effect of migration across FDI
# -----------------------------
# This estimates:
# d(vote share) / d(migration) = beta_migration + beta_interaction * FDI

get_fdi_grid <- function(model_data, n_grid = 50) {
  
  fdi_values <- sort(unique(model_data$fdi))
  
  # If FDI is discrete with not too many values, use observed values.
  # Otherwise use 5th-95th percentile grid.
  if (length(fdi_values) <= 10) {
    return(fdi_values)
  }
  
  seq(
    quantile(model_data$fdi, 0.05, na.rm = TRUE),
    quantile(model_data$fdi, 0.95, na.rm = TRUE),
    length.out = n_grid
  )
}

extract_marginal_effects <- function(fit_obj) {
  
  fdi_grid <- get_fdi_grid(fit_obj$model_data)
  
  marginaleffects::slopes(
    fit_obj$model,
    variables = "migration",
    newdata = marginaleffects::datagrid(
      fdi = fdi_grid
    )
  ) %>%
    as_tibble() %>%
    mutate(
      election_year = fit_obj$election_year,
      ideology_group = fit_obj$ideology_group,
      dv = fit_obj$dv,
      migration_var = fit_obj$migration_var,
      fdi_var = fit_obj$fdi_var,
      fdi_value = fdi,
      significant_positive = conf.low > 0,
      significant_negative = conf.high < 0,
      significant_any = significant_positive | significant_negative
    ) %>%
    select(
      election_year,
      ideology_group,
      dv,
      migration_var,
      fdi_var,
      fdi_value,
      estimate,
      std.error,
      statistic,
      p.value,
      conf.low,
      conf.high,
      significant_positive,
      significant_negative,
      significant_any
    )
}

focused_marginal_effect_grid <- focused_models %>%
  mutate(me = map(fit, extract_marginal_effects)) %>%
  select(me) %>%
  unnest(me) %>%
  arrange(election_year, ideology_group, fdi_value)

View(focused_marginal_effect_grid)

focused_marginal_effect_summary <- focused_marginal_effect_grid %>%
  group_by(election_year, ideology_group, dv, migration_var, fdi_var) %>%
  summarise(
    min_fdi = min(fdi_value, na.rm = TRUE),
    max_fdi = max(fdi_value, na.rm = TRUE),
    min_marginal_effect = min(estimate, na.rm = TRUE),
    max_marginal_effect = max(estimate, na.rm = TRUE),
    mean_marginal_effect = mean(estimate, na.rm = TRUE),
    n_grid = n(),
    n_sig_positive = sum(significant_positive, na.rm = TRUE),
    n_sig_negative = sum(significant_negative, na.rm = TRUE),
    n_sig_any = sum(significant_any, na.rm = TRUE),
    share_grid_sig_positive = mean(significant_positive, na.rm = TRUE),
    share_grid_sig_negative = mean(significant_negative, na.rm = TRUE),
    share_grid_sig_any = mean(significant_any, na.rm = TRUE),
    status = case_when(
      n_sig_positive > 0 & n_sig_negative == 0 ~ "Migration effect significantly positive somewhere",
      n_sig_negative > 0 & n_sig_positive == 0 ~ "Migration effect significantly negative somewhere",
      n_sig_positive > 0 & n_sig_negative > 0 ~ "Migration effect changes sign significantly",
      TRUE ~ "Marginal migration effect not significant on FDI grid"
    ),
    .groups = "drop"
  ) %>%
  arrange(election_year, ideology_group)

View(focused_marginal_effect_summary)

# -----------------------------
# 6. Marginal-effect plots
# -----------------------------

plot_migration_effect_across_fdi <- function(fit_obj) {
  
  fdi_grid <- get_fdi_grid(fit_obj$model_data)
  
  marginaleffects::plot_slopes(
    fit_obj$model,
    variables = "migration",
    condition = list(fdi = fdi_grid)
  ) +
    labs(
      title = "Marginal effect of migration across manufacturing FDI exposure",
      subtitle = paste0(
        "Outcome: ", fit_obj$dv,
        "\nMigration: ", fit_obj$migration_var,
        "\nFDI: ", fit_obj$fdi_var
      ),
      x = fit_obj$fdi_var,
      y = paste0("Marginal effect of ", fit_obj$migration_var)
    ) +
    theme_minimal()
}

focused_marginal_effect_plots <- focused_models %>%
  mutate(plot = map(fit, plot_migration_effect_across_fdi))

# Print all plots in RStudio
for (i in seq_len(nrow(focused_marginal_effect_plots))) {
  print(focused_marginal_effect_plots$plot[[i]])
}

# Individual plots if you want to inspect them one at a time:
plot_2009_left <- focused_marginal_effect_plots$plot[[1]]
plot_2009_moderate <- focused_marginal_effect_plots$plot[[2]]
plot_2009_right <- focused_marginal_effect_plots$plot[[3]]
plot_2014_left <- focused_marginal_effect_plots$plot[[4]]
plot_2014_moderate <- focused_marginal_effect_plots$plot[[5]]
plot_2014_right <- focused_marginal_effect_plots$plot[[6]]

plot_2009_moderate
```

```{r}
# ============================================================
# VISUALIZE FOCUSED AC-SHARE REGRESSION OUTPUTS WITH GGPLOT2
# ============================================================

library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(forcats)
library(scales)

# -----------------------------
# 1. Helper labels
# -----------------------------

pretty_component <- function(x) {
  dplyr::recode(
    x,
    "migration_main_effect" = "Migration",
    "fdi_main_effect" = "Manufacturing FDI",
    "interaction" = "Migration × Manufacturing FDI",
    "intercept" = "Intercept",
    .default = x
  )
}

pretty_ideology <- function(x) {
  stringr::str_to_title(x)
}

# -----------------------------
# 2. Clean regression table for plotting
# -----------------------------

reg_plot_df <- focused_regression_table %>%
  filter(component %in% c(
    "migration_main_effect",
    "fdi_main_effect",
    "interaction"
  )) %>%
  mutate(
    component_label = pretty_component(component),
    ideology_label = pretty_ideology(ideology_group),
    model_label = paste0(election_year, " | ", ideology_label),
    ci_low = coefficient - 1.96 * se,
    ci_high = coefficient + 1.96 * se,
    sig_05 = p_value < 0.05,
    sig_label = case_when(
      p_value < 0.01 ~ "p < .01",
      p_value < 0.05 ~ "p < .05",
      p_value < 0.10 ~ "p < .10",
      TRUE ~ "n.s."
    )
  )

# -----------------------------
# 3. Coefficient plot
# -----------------------------

coef_plot <- ggplot(
  reg_plot_df,
  aes(
    x = coefficient,
    y = fct_rev(model_label),
    xmin = ci_low,
    xmax = ci_high,
    shape = sig_05
  )
) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbarh(height = 0.2) +
  geom_point(size = 2.5) +
  facet_wrap(~ component_label, scales = "free_x") +
  labs(
    title = "AC ideology-share regressions",
    subtitle = "Outcome: share of ideological group voting BJP/far-right",
    x = "Coefficient estimate with 95% confidence interval",
    y = NULL,
    shape = "p < .05"
  ) +
  theme_minimal()

coef_plot
```

```{r}
library(modelsummary)
library(dplyr)
library(purrr)
library(tibble)

model_list <- focused_models %>%
  mutate(
    model_name = paste0(election_year, " ", stringr::str_to_title(ideology_group))
  ) %>%
  select(model_name, fit) %>%
  mutate(model = map(fit, "model")) %>%
  select(model_name, model) %>%
  deframe()

coef_map <- c(
  "migration" = "Migration Growth",
  "fdi" = "Manufacturing FDI projects",
  "migration:fdi" = "Migration Growth × Manufacturing FDI",
  "control" = "Employment, all workers"
)

gof_map <- tribble(
  ~raw,        ~clean,        ~fmt,
  "nobs",      "Observations", 0,
  "r.squared", "R-squared",    3
)

focused_modelsummary_table <- modelsummary(
  model_list,
  coef_map = coef_map,
  estimate = "{estimate}{stars}",
  statistic = c("SE = {std.error}", "p = {p.value}"),
  stars = c("*" = 0.10, "**" = 0.05, "***" = 0.01),
  gof_map = gof_map,
  output = "gt",
  title = "AC ideology-share regressions: migration growth × manufacturing FDI, controlling for employment"
)

focused_modelsummary_table
```

