---
title: "Switchers-Models"
output: html_document
date: "2026-08-06"
---

## R Markdown
Puzzle: Why is there a significant increase in the share of centrists casting votes for the far right, especially the BJP, from 2009 to 2014?
```{r, echo = FALSE}
library(tidyverse)
library(scales)

nes_voters <-
  nes$respondents |>
  filter(
    year %in% c(2009, 2014),
    vote_valid,
    !is.na(reported_vote_party_label)
  ) |>
  mutate(
    year = factor(year, levels = c(2009, 2014)),
    voter_ideology = factor(
      as.character(voter_ideology),
      levels = c("Left", "Center", "Right", "Mixed")
    ),
    party = case_when(
      voted_bjp == 1 ~ "BJP",
      voted_congress == 1 ~ "Congress",
      voted_shs == 1 ~ "Shiv Sena",
      voted_mns == 1 ~ "MNS",
      TRUE ~ str_squish(reported_vote_party_label)
    )
  )

# Identify the top 10 parties separately within each year.
make_party_shares <- function(data, top_n = 10) {

  party_counts <-
    data |>
    summarise(
      weighted_n = sum(
        survey_weight_norm_year,
        na.rm = TRUE
      ),
      .by = c(year, party)
    ) |>
    group_by(year) |>
    arrange(desc(weighted_n), party, .by_group = TRUE) |>
    mutate(
      party_rank = row_number(),
      party_plot = if_else(
        party_rank <= top_n,
        party,
        "Other"
      )
    ) |>
    ungroup()

  party_counts |>
    summarise(
      weighted_n = sum(weighted_n),
      .by = c(year, party_plot)
    ) |>
    group_by(year) |>
    mutate(
      share = weighted_n / sum(weighted_n)
    ) |>
    ungroup()
}


plot_party_shares <- function(data, title) {

  plot_data <-
    make_party_shares(data) |>
    mutate(
      # A year-specific identifier permits different party ordering
      # in the two facets.
      party_year = paste(
        party_plot,
        year,
        sep = "___"
      ),
      party_year = forcats::fct_reorder(
        party_year,
        share
      )
    )

  ggplot(
    plot_data,
    aes(
      x = share,
      y = party_year,
      fill = year
    )
  ) +
    geom_col(
      width = 0.7,
      show.legend = FALSE
    ) +
    geom_text(
      aes(
        label = percent(
          share,
          accuracy = 0.1
        )
      ),
      hjust = -0.1,
      size = 3
    ) +
    facet_wrap(
      ~ year,
      scales = "free_y"
    ) +
    scale_y_discrete(
      labels = function(x) {
        sub("___.*$", "", x)
      }
    ) +
    scale_x_continuous(
      labels = label_percent(),
      expand = expansion(mult = c(0, 0.18))
    ) +
    coord_cartesian(clip = "off") +
    labs(
      title = title,
      subtitle = paste(
        "Top 10 parties separately in each year;",
        "remaining parties grouped as Other"
      ),
      x = "Survey-weighted vote share",
      y = NULL
    ) +
    theme_minimal() +
    theme(
      panel.grid.major.y = element_blank(),
      panel.grid.minor = element_blank(),
      plot.title.position = "plot",
      plot.margin = margin(10, 35, 10, 10)
    )
}

# Vote share nationally of each party in 2009 versus 2014
plot_party_shares(
  nes_voters,
  "Reported party vote among NES respondents"
)

# Share of voters in each ideological bucket voting for the far right in 2009 versus 2014
fr_by_ideology <-
  nes$respondents |>
  filter(
    year %in% c(2009, 2014),
    !is.na(voter_ideology),
    !is.na(voted_fr)
  ) |>
  summarise(
    share = weighted.mean(
      voted_fr,
      survey_weight_norm_year,
      na.rm = TRUE
    ),
    .by = c(year, voter_ideology)
  ) |>
  mutate(
    year = factor(year),
    voter_ideology = factor(
      voter_ideology,
      levels = c("Left", "Center", "Right", "Mixed")
    )
  )

ggplot(
  fr_by_ideology,
  aes(voter_ideology, share, fill = year)
) +
  geom_col(position = "dodge") +
  geom_text(
    aes(label = percent(share, accuracy = 0.1)),
    position = position_dodge(width = 0.9),
    vjust = -0.3,
    size = 3
  ) +
  scale_y_continuous(
    labels = label_percent(),
    expand = expansion(mult = c(0, 0.12))
  ) +
  labs(
    title = "Far-right voting by ideological bucket",
    x = NULL,
    y = "Survey-weighted share voting far right",
    fill = NULL
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")

# Share of centrists who voted for the BJP and other parties in 2009 versus 2014
plot_party_shares(
  filter(nes_voters, voter_ideology == "Center"),
  "Party choices of centrist voters"
)

# What happened to the left? Share of leftists who voted for the BJP and other parties in 2009 versus 2014
plot_party_shares(
  filter(nes_voters, voter_ideology == "Left"),
  "Party choices of left-wing voters"
)

# What happened to the left? Share of the shift in leftists to the BJP that is accounted for by West Bengal
left_bjp_decomposition <-
  nes$respondents |>
  filter(
    year %in% c(2009, 2014),
    voter_ideology == "Left",
    !is.na(voted_bjp)
  ) |>
  mutate(
    region = if_else(
      state_no == 19L,
      "West Bengal",
      "All other states"
    )
  ) |>
  group_by(year) |>
  mutate(
    national_left_weight =
      sum(survey_weight_norm_year, na.rm = TRUE)
  ) |>
  ungroup() |>
  summarise(
    contribution_to_national_share =
      sum(
        survey_weight_norm_year * voted_bjp,
        na.rm = TRUE
      ) / first(national_left_weight),
    .by = c(year, region)
  ) |>
  complete(
    year = c(2009L, 2014L),
    region = c("West Bengal", "All other states"),
    fill = list(contribution_to_national_share = 0)
  ) |>
  pivot_wider(
    names_from = year,
    values_from = contribution_to_national_share,
    names_prefix = "share_"
  ) |>
  mutate(
    contribution_pp =
      100 * (share_2014 - share_2009),
    national_change_pp = sum(contribution_pp),
    share_of_net_change =
      contribution_pp / national_change_pp
  )

ggplot(
  left_bjp_decomposition,
  aes(contribution_pp, region)
) +
  geom_col() +
  geom_vline(xintercept = 0) +
  geom_text(
    aes(
      label = paste0(
        number(contribution_pp, accuracy = 0.1),
        " pp\n",
        percent(share_of_net_change, accuracy = 1),
        " of net change"
      ),
      hjust = if_else(contribution_pp >= 0, -0.1, 1.1)
    ),
    size = 3.4
  ) +
  scale_x_continuous(
    expand = expansion(mult = c(0.25, 0.25))
  ) +
  labs(
    title = "Who accounted for the left-to-BJP shift?",
    subtitle = paste0(
      "National change in BJP support among leftists: ",
      number(
        unique(left_bjp_decomposition$national_change_pp),
        accuracy = 0.1
      ),
      " percentage points"
    ),
    x = "Contribution to national change",
    y = NULL
  ) +
  theme_minimal() +
  theme(panel.grid.major.y = element_blank())

# What happened to the right? Share of rightists who voted for the BJP and other parties in 2009 versus 2014
plot_party_shares(
  filter(nes_voters, voter_ideology == "Right"),
  "Party choices of right-wing voters"
)
```

Diagnostic: How much FDI was there from 2004-2009 versus 2009-2014? Were the places that got more FDI in either period the places with more population growth, migration, or Muslims?
```{r}

```

H1: Contingent on an assembly constituency's pre-treatment Muslim population share/log Muslim population and the share of voters who are self-identified centrists, increasing per capita exposure to FDI/change in per capita exposure to FDI is associated with a larger share of the vote going to the far right.
```{r}
# Pooled cross-section
modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_local_all_pc100k * muslim_share_2001_dist_proxy + proxy_ac_pop + ed_sec_share + log_secc_cons_pc + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_own_all_pc100k * muslim_share_2001_dist_proxy + proxy_ac_pop + ed_sec_share + log_secc_cons_pc + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

# Triple interaction
modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_local_all_pc100k * muslim_share_2001_dist_proxy * nes_share_center_all_respondents + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_own_all_pc100k * muslim_share_2001_dist_proxy * nes_share_center_all_respondents + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

# Lagged-outcome

# Lagged-outcome triple interaction
```

C-H1A: Contingent on an assembly constituency's pre-treatment Bihari and Bengali migrant population share/log Bihari and Bengali migrant population and the share of voters who are self-identified centrists, increasing per capita exposure to FDI/change in per capita exposure to FDI is associated with a larger share of the vote going to the far right.
```{r}
# Pooled cross-section
modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_local_all_pc100k * target_bengali_bhojpuri_share_2001_dist_proxy + proxy_ac_pop + ed_sec_share + log_secc_cons_pc + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_own_all_pc100k * target_bengali_bhojpuri_share_2001_dist_proxy + proxy_ac_pop + ed_sec_share + log_secc_cons_pc + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

# Triple interaction
modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_local_all_pc100k * target_bengali_bhojpuri_share_2001_dist_proxy * nes_share_center_all_respondents + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_own_all_pc100k * target_bengali_bhojpuri_share_2001_dist_proxy * nes_share_center_all_respondents + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

# Lagged-outcome

# Lagged-outcome triple interaction
```

C-H1B: Contingent on an assembly constituency's pre-treatment SC population share/log SC population and the share of voters who are self-identified centrists, increasing per capita exposure to FDI/change in per capita exposure to FDI is associated with a larger share of the vote going to the far right.
```{r}
# Pooled cross-section
modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_local_all_pc100k * sc_higher_secondary_plus_share_age7plus_2001_dist_proxy + proxy_ac_pop + ed_sec_share + log_secc_cons_pc + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_own_all_pc100k * sc_higher_secondary_plus_share_age7plus_2001_dist_proxy + proxy_ac_pop + ed_sec_share + log_secc_cons_pc + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

# Triple interaction
modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_local_all_pc100k * sc_higher_secondary_plus_share_age7plus_2001_dist_proxy * nes_share_center_all_respondents + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_own_all_pc100k * sc_higher_secondary_plus_share_age7plus_2001_dist_proxy * nes_share_center_all_respondents + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

# Lagged-outcome

# Lagged-outcome triple interaction
```

C-H1C: Contingent on the (percentage point) change in an assembly constituency's Muslim population share/log Muslim population and the share of voters who are self-identified centrists, increasing per capita exposure to FDI/change in per capita exposure to FDI is associated with a larger share of the vote going to the far right.
```{r}
# Pooled cross-section
modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_local_all_pc100k * d_muslim_share_2001_2011_pp + proxy_ac_pop + ed_sec_share + log_secc_cons_pc + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_own_all_pc100k * d_muslim_share_2001_2011_pp + proxy_ac_pop + ed_sec_share + log_secc_cons_pc + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

# Triple interaction
modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_local_all_pc100k * d_muslim_share_2001_2011_pp * nes_share_center_all_respondents + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_own_all_pc100k * d_muslim_share_2001_2011_pp * nes_share_center_all_respondents + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

# Lagged-outcome

# Lagged-outcome triple interaction
```

C-H1D: Contingent on the (percentage point) change in an assembly constituency's Bihari and Bengali population share/log Bihari and Bengali population and the share of voters who are self-identified centrists, increasing per capita exposure to FDI/change in per capita exposure to FDI is associated with a larger share of the vote going to the far right.
```{r}
# Pooled cross-section
modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_local_all_pc100k * d_target_bengali_bhojpuri_share_2001_2011_pp + proxy_ac_pop + ed_sec_share + log_secc_cons_pc + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_own_all_pc100k * d_target_bengali_bhojpuri_share_2001_2011_pp + proxy_ac_pop + ed_sec_share + log_secc_cons_pc + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

# Triple interaction
modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_local_all_pc100k * d_target_bengali_bhojpuri_share_2001_2011_pp * nes_share_center_all_respondents + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_own_all_pc100k * d_target_bengali_bhojpuri_share_2001_2011_pp * nes_share_center_all_respondents + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

# Lagged-outcome

# Lagged-outcome triple interaction
```

C-H1E: Contingent on the (percentage point) change in an assembly constituency's SC population share/log SC population and the share of voters who are self-identified centrists, increasing per capita exposure to FDI/change in per capita exposure to FDI is associated with a larger share of the vote going to the far right.
```{r}
# Pooled cross-section
modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_local_all_pc100k * d_sc_higher_secondary_plus_share_age7plus_2001_2011_pp + proxy_ac_pop + ed_sec_share + log_secc_cons_pc + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_own_all_pc100k * d_sc_higher_secondary_plus_share_age7plus_2001_2011_pp + proxy_ac_pop + ed_sec_share + log_secc_cons_pc + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

# Triple interaction
modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_local_all_pc100k * d_sc_higher_secondary_plus_share_age7plus_2001_2011_pp * nes_share_center_all_respondents + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

modelsummary(feols(bjp_vote_share ~ log1p_fdi_total_own_all_pc100k * d_sc_higher_secondary_plus_share_age7plus_2001_2011_pp * nes_share_center_all_respondents + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no + year, data = ac_year), stars = TRUE)

# Lagged-outcome

# Lagged-outcome triple interaction
```

H2: Contingent on an assembly constituency's pre-treatment Muslim population share/log Muslim population and a voter's ideological affinity, increasing per capita exposure to FDI is associated with a greater propensity to vote for the far right.
```{r}
# Logit
modelsummary(feglm(voted_fr ~ log1p_fdi_total_local_all_pc100k * muslim_share_2001_dist_proxy * voter_ideology + education_harmonized + household_income_monthly + caste_group + religion_group | state_no + year, data = nes_respondent_analysis, family = binomial), stars = TRUE)

modelsummary(feglm(voted_fr ~ log1p_fdi_total_own_all_pc100k * muslim_share_2001_dist_proxy * voter_ideology + education_harmonized + household_income_monthly + caste_group + religion_group | state_no + year, data = nes_respondent_analysis, family = binomial), stars = TRUE)

# MLM triple interaction
```

C-H2A: Contingent on an assembly constituency's pre-treatment Bihari and Bengali migrant population share/log Bihari and Bengali migrant population and a voter's ideological affinity, increasing per capita exposure to FDI is associated with a greater propensity to vote for the far right.
```{r}
# Logit
modelsummary(feglm(voted_fr ~ log1p_fdi_total_local_all_pc100k * target_bengali_bhojpuri_share_2001_dist_proxy * voter_ideology + education_harmonized + household_income_monthly + caste_group + religion_group | state_no + year, data = nes_respondent_analysis, family = binomial), stars = TRUE)

modelsummary(feglm(voted_fr ~ log1p_fdi_total_own_all_pc100k * target_bengali_bhojpuri_share_2001_dist_proxy * voter_ideology + education_harmonized + household_income_monthly + caste_group + religion_group | state_no + year, data = nes_respondent_analysis, family = binomial), stars = TRUE)

# MLM triple interaction
```

C-H2B: Contingent on an assembly constituency's pre-treatment SC population share/log SC population and a voter's ideological affinity, increasing per capita exposure to FDI is associated with a greater propensity to vote for the far right.
```{r}
# Logit
modelsummary(feglm(voted_fr ~ log1p_fdi_total_local_all_pc100k * sc_higher_secondary_plus_share_age7plus_2001_dist_proxy * voter_ideology + education_harmonized + household_income_monthly + caste_group + religion_group | state_no + year, data = nes_respondent_analysis, family = binomial), stars = TRUE)

modelsummary(feglm(voted_fr ~ log1p_fdi_total_own_all_pc100k * sc_higher_secondary_plus_share_age7plus_2001_dist_proxy * voter_ideology + education_harmonized + household_income_monthly + caste_group + religion_group | state_no + year, data = nes_respondent_analysis, family = binomial), stars = TRUE)

# MLM triple interaction
```

C-H2C: Contingent on the (percentage point) change in an assembly constituency's Muslim population share/log Muslim population and a voter's ideological affinity, increasing per capita exposure to FDI is associated with a greater propensity to vote for the far right.
```{r}
modelsummary(feglm(voted_fr ~ log1p_fdi_total_local_all_pc100k * d_muslim_share_2001_2011_pp * voter_ideology + education_harmonized + household_income_monthly + caste_group + religion_group | state_no + year, data = nes_respondent_analysis, family = binomial), stars = TRUE)

modelsummary(feglm(voted_fr ~ log1p_fdi_total_own_all_pc100k * d_muslim_share_2001_2011_pp * voter_ideology + education_harmonized + household_income_monthly + caste_group + religion_group | state_no + year, data = nes_respondent_analysis, family = binomial), stars = TRUE)

# MLM triple interaction
```

C-H2D: Contingent on the (percentage point) change in an assembly constituency's Bihari and Bengali population share/log Bihari and Bengali population and a voter's ideological affinity, increasing per capita exposure to FDI is associated with a greater propensity to vote for the far right.
```{r}
# Logit
modelsummary(feglm(voted_fr ~ log1p_fdi_total_local_all_pc100k * d_target_bengali_bhojpuri_share_2001_2011_pp * voter_ideology + education_harmonized + household_income_monthly + caste_group + religion_group | state_no + year, data = nes_respondent_analysis, family = binomial), stars = TRUE)

modelsummary(feglm(voted_fr ~ log1p_fdi_total_own_all_pc100k * d_target_bengali_bhojpuri_share_2001_2011_pp * voter_ideology + education_harmonized + household_income_monthly + caste_group + religion_group | state_no + year, data = nes_respondent_analysis, family = binomial), stars = TRUE)

# MLM triple interaction
```

C-H2E: Contingent on the (percentage point) change in an assembly constituency's SC population share/log SC population and a voter's ideological affinity, increasing per capita exposure to FDI is associated with a greater propensity to vote for the far right.
```{r}
# Logit
modelsummary(feglm(voted_fr ~ log1p_fdi_total_local_all_pc100k * d_sc_higher_secondary_plus_share_age7plus_2001_2011_pp * voter_ideology + education_harmonized + household_income_monthly + caste_group + religion_group | state_no + year, data = nes_respondent_analysis, family = binomial), stars = TRUE)

modelsummary(feglm(voted_fr ~ log1p_fdi_total_own_all_pc100k * d_sc_higher_secondary_plus_share_age7plus_2001_2011_pp * voter_ideology + education_harmonized + household_income_monthly + caste_group + religion_group | state_no + year, data = nes_respondent_analysis, family = binomial), stars = TRUE)

# MLM triple interaction
```

H3: Contingent on an assembly constituency's pre-treatment Muslim population share/log Muslim population and the share of voters who are self-identified centrists, increasing per capita exposure to FDI is associated with a larger change in the share of the vote going to the far right.
```{r}
# 2014 cross-section
modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_local_all_pc100k_2014 * muslim_share_2001_dist_proxy + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * muslim_share_2001_dist_proxy + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

# 2014 triple interaction
modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * muslim_share_2001_dist_proxy * nes_share_center_all_respondents_2014 + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * muslim_share_2001_dist_proxy * nes_share_center_all_respondents_2014 + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

# Lagged-outcome

# Lagged-outcome triple interaction
```

C-H3A: Contingent on an assembly constituency's pre-treatment Bihari and Bengali migrant population share/log Bihari and Bengali migrant population and the share of voters who are self-identified centrists, increasing per capita exposure to FDI is associated with a larger change in the share of the vote going to the far right.
```{r}
# 2014 cross-section
modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_local_all_pc100k_2014 * target_bengali_bhojpuri_share_2001_dist_proxy + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * target_bengali_bhojpuri_share_2001_dist_proxy + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

# 2014 triple interaction
modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * target_bengali_bhojpuri_share_2001_dist_proxy * nes_share_center_all_respondents_2014 + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * target_bengali_bhojpuri_share_2001_dist_proxy * nes_share_center_all_respondents_2014 + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

# Lagged-outcome

# Lagged-outcome triple interaction
```

C-H3B: Contingent on an assembly constituency's pre-treatment SC population share/log SC population and the share of voters who are self-identified centrists, increasing per capita exposure to FDI/change in per capita exposure to FDI is associated with a larger change in the share of the vote going to the far right.
```{r}
# 2014 cross-section
modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_local_all_pc100k_2014 * sc_higher_secondary_plus_share_age7plus_2001_dist_proxy + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * sc_higher_secondary_plus_share_age7plus_2001_dist_proxy + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

# 2014 triple interaction
modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * sc_higher_secondary_plus_share_age7plus_2001_dist_proxy * nes_share_center_all_respondents_2014 + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * sc_higher_secondary_plus_share_age7plus_2001_dist_proxy * nes_share_center_all_respondents_2014 + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

# Lagged-outcome

# Lagged-outcome triple interaction
```

C-H3C: Contingent on the (percentage point) change in an assembly constituency's Muslim population share/log Muslim population and the share of voters who are self-identified centrists, increasing per capita exposure to FDI/change in per capita exposure to FDI is associated with a larger change in the share of the vote going to the far right.
```{r}
# 2014 cross-section
modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_local_all_pc100k_2014 * d_muslim_share_2001_2011_pp + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * d_muslim_share_2001_2011_pp + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

# 2014 triple interaction
modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * d_muslim_share_2001_2011_pp * nes_share_center_all_respondents_2014 + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * d_muslim_share_2001_2011_pp * nes_share_center_all_respondents_2014 + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

# Lagged-outcome

# Lagged-outcome triple interaction
```

C-H3D: Contingent on the (percentage point) change in an assembly constituency's Bihari and Bengali population share/log Bihari and Bengali population and the share of voters who are self-identified centrists, increasing per capita exposure to FDI/change in per capita exposure to FDI is associated with a larger change in the share of the vote going to the far right.
```{r}
# 2014 cross-section
modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_local_all_pc100k_2014 * d_target_bengali_bhojpuri_share_2001_2011_pp + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * d_target_bengali_bhojpuri_share_2001_2011_pp + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

# 2014 triple interaction
modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * d_target_bengali_bhojpuri_share_2001_2011_pp * nes_share_center_all_respondents_2014 + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * d_target_bengali_bhojpuri_share_2001_2011_pp * nes_share_center_all_respondents_2014 + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

# Lagged-outcome

# Lagged-outcome triple interaction
```

C-H3E: Contingent on the (percentage point) change in an assembly constituency's SC population share/log SC population and the share of voters who are self-identified centrists, increasing per capita exposure to FDI/change in per capita exposure to FDI is associated with a larger change in the share of the vote going to the far right.
```{r}
# 2014 cross-section
modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_local_all_pc100k_2014 * d_sc_higher_secondary_plus_share_age7plus_2001_2011_pp + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * d_sc_higher_secondary_plus_share_age7plus_2001_2011_pp + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

# 2014 triple interaction
modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * d_sc_higher_secondary_plus_share_age7plus_2001_2011_pp * nes_share_center_all_respondents_2014 + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

modelsummary(feols(d_fr_party_vote_share_2009_2014_pp ~ log1p_fdi_total_own_all_pc100k_2014 * d_sc_higher_secondary_plus_share_age7plus_2001_2011_pp * nes_share_center_all_respondents_2014 + ed_sec_share + log_secc_cons_pc + proxy_ac_pop + sc_pop_share + st_pop_share | state_no, data = ac_change), stars = TRUE)

# Lagged-outcome

# Lagged-outcome triple interaction
```